### 2023-02-13 article.Rmd
new version of article

---
title: Repairing cooperation through a cognitive intervention in the repeated Trust Game
subtitle: 
titlerunning: 
authorrunning: 
# thanks: The authors have no conflicts of interest to declare that are relevant to the content of this article. This work was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1.

authors: 
- name: Ismail Guennouni
  address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
  email: i.guennouni.17@ucl.ac.uk

- name: Maarten Speekenbrink
  address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
  email: m.speekenbrink@ucl.ac.uk

- name: Quentin Huys
  address: Max Planck Institute of Computational Psychiatry 
  email: q.huys@ucl.ac.uk

- name: Samuel Dupret 
  address: HLI 
  email: sam.dupret@ucl.ac.uk

keywords:
- Economic Games 
- Hidden Markov Models
- Repair of Cooperation
- Cognitive Intervention

abstract: | 
  abstract to be added.

bibliography: "bib/cogIntervention.bib"
biblio-style: spphys
output:
  bookdown::pdf_document2:
   toc: false
---

```{r setupCoax, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE) 
knitr::opts_chunk$set(out.width = "\\textwidth")
```

```{r load-packages05, include = FALSE}
library(papaja)
library(kableExtra)
require(knitr)
require(citr)
require(bookdown)

# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
library(tidyverse)
library(afex)
library(PairedData)
library(multcompView)
library(lsmeans)
library(depmixS4)
library(flextable)
library(gridExtra)
library(forcats)
library(ggsignif)

```

```{r analysis-preferences, include = FALSE}
# Seed for random number generation
set.seed(42)
options(tinytex.verbose = TRUE)
```

# Introduction

At the core of social interaction is figuring out the goals, intentions, and decision-making process of the interaction partner. This inference is however fraught with uncertainty, as we cannot reasonably observe these features without prior knowledge of the person. Absent a history of interaction, one needs to decide whether to take the risk of trusting others. @rousseau_introduction_1998 define trust as a "psychological state comprising the intention to accept vulnerability based upon positive expectations of the intentions or behavior of another". As such, whilst trusting and being able to signal trustworthiness are necessary conditions for building and maintaining important social bonds,  the challenge of trust is that it is by construction a risky endeavour. For example, if we deem a person trustworthy, we might decide to take the risk of investing in the relationship hoping for a collaborative outcome. If we misplace our trust, this can come at a high cost to us. Not trusting others is also risky since opportunities may be foregone, and any substitution for trust, such as excessive suspicion, over-reliance on self and other maladaptive strategies are likely to add burden and costs to a person.

Evidence from the literature emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016 ; @meng_multilevel_2014]. It affects the health status of individuals through reinforcing social support networks, maintaining community norms and facilitating collective action. Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders. @fonagy_role_2014 identified epistemic trust as an important function of early attachment relationships. Epistemic trust can be defined as the trust in the authenticity and personal relevance of interpersonally transmitted knowledge. It enables individuals to learn from their social environment in dynamic social and cultural contexts. Importantly, it allows the individual receiving social information to let go of their natural self-protective vigilance, dubbed hyper-vigilance. @fonagy_mentalizing_2017 identified hyper-vigilance, or lack of "epistemic trust" which may partially be rooted in adverse childhood experiences, as a key risk factor for the emergence of multiple mental health disorders such as Borderline Personality Disorder and Anti-Social Personality Disorder.

A popular paradigm in the study of the emergence and maintenance of trust is the repeated trust game [@joyce_trust_1995]. In this game, one player takes the role of the "investor" and is provided with a fixed endowment at the start of each trial. They get to decide how much of their endowment to invest with the other player taking the role of the "trustee". The amount that is sent is tripled and the trustee gets to decide, in return, how much of the tripled amount to send back to the investor. If the investor sends a non-zero amount, they express trust in the other player for that round, as the amount they will receive back is uncertain. Assuming the trustee sends back more than the initial investment, they signal trustworthiness to the investor and both players make gains. This scenario would constitute a cooperative exchange and would be mutually beneficial. However, cooperation in this setting is prone to be broken through intentional or simply misinterpreted actions on behalf of either player [@bendor_when_1991]. In order to repair a damaged cooperative equilibrium, players need to infer that their behaviour has violated social norms and offer amends through generous actions at potentially a high cost to them. @king-casas_rupture_2008 links the breakdown of cooperation in trustees with Borderline Personality Disorder to the absence or reduction of activation in brain regions associated with the perception of norm violations.

Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions to foster and strengthen trust-based cooperation would be highly beneficial to society. Such an intervention would allow people to more easily repair broken relationships, and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations. In the context of social dilemmas, there have been many attempts at fostering cooperative outcomes through either mechanism design, environment modifications or other.

Mechanism design, pioneered by @vickrey_counterspeculation_1961, is a field that studies incentive alignment and looks for ways to promote social welfare or revenue maximization, despite self-interest of the individual actors. In the context of social dilemmas, key mechanisms were explored with good effect to foster and maintain the cooperative outcome. @axelrod_evolutionary_1986 studied the emergence and stability of behavioral norms to regulate non-cooperative actions in social settings. He identifies a behavioral norm as a dominant behavioural strategy which is often punished by others when not adhered to. A meta-norm is the propensity to incur a cost in order to enforce a norm. @axelrod_evolutionary_1986 showed that when playing a social dilemma game, individuals have a strong incentive to enforce punishment of defectors lest they are in turn punished by others. This led to a decline of defection. Thus, meta-norms can be seen as a mechanism to promote and sustain cooperation in a population. In the context of the trust game, @charness_investment_2008 explored the effect a third party monitor can have on the amounts sent and received. This third-party's payoff is unaffected by the decisions made by the investor and trustee. However, the study allowed the third party to punish overly selfish trustees or reward Investors making a loss on the interaction. They found that the actions of both players were materially more cooperative in the presence of this third party. @fiedler_effect_2017 found that the introduction of a third party that monitors the investments and returns of the players led to more cooperative behavior, even when the third party had no ability to reward or punish the players.

Rather than try to modify the mechanism of the game, other approaches focused on intervening directly on the participants. @drazkowski_gratitude_2017 investigated the effect of expressing gratitude on later behaviour in the trust game. The gratitude intervention consisted of thinking about and writing down 5 things that the participants were grateful for in their life. The exercise was repeated over three sessions. Those completing the gratitude intervention reported more positive emotions and this mediated an increase in their investment in one-shot trust games. @burnham_friend-or-foe_2000 primed participants by introducing the investor as either a "friend" or "foe". They found that this priming produces significant differences in both trust (measured by the proportion of endowment sent) and trustworthiness  (measured by the proportion returned) with participants in the "friend" treatment exhibiting over twice as much trustworthiness than those in the "foe" condition.

Whilst these interventions show that it is possible to improve cooperative outcomes at the start of the game, they did not address how to repair a breakdown of trust that might occur due to intentional or accidental non-cooperative actions by the players. Indeed, cooperative play in the repeated trust game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor after cooperation has been established, or a return of the trustee below the investment sent. Such ruptures of cooperation appear frequently when the trustee suffers from mental health disorders affecting the social domain such as Borderline Personality Disorder [@lieb_borderline_2004]. In theses situations, BPD trustees fail to engage in trust repairing behavior such as coaxing the investor through sending high return to signal trustworthiness, and this failure may be linked to a failure to perceive their low returns in the game as a violation of social norms [@king-casas_rupture_2008].

<!-- why this particular intervention? Why use this intervention for repair of trust? One motivation which you don't mention is the motivation to use cognitive probes to understand mechanisms of psychotherapy itself - this may be worth introducing.  -->

In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of interpersonal dysfunction in BPD patients. Whilst there is no proven pharmacological therapy for BPD, some forms of psychotherapy such as Mentalisation Based Therapy (MBT) and Dialectical Behavior Therapy (DBT), have been clinically validated as efficacious approaches to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018]. However, these therapies suffer from a high variability in treatment responses. Determining which interventions are effective for particular patients has been very challenging  [@rudge_mechanisms_2020; @arch_longitudinal_2012]. One promising approach is the study of how specific psychotherapeutic treatment components affect quantitative markers of behavior such as those inferred through computational modelling techniques [@huys_computational_2016]. As such, using specific cognitive probes inspired by therapeutic interventions complemented by computational modelling of behavior in tasks, may allow us to uncover cognitive mechanisms targeted by common forms of psychotherapy, as well as evaluate whether knowledge about these different mechanisms can improve the targeting of existing psychotherapies to different individuals.

In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a pre-programmed, one-off low investment sent by the investor. The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation. It explicitly articulates the advantages of adopting a coaxing behavior in this setting, and as such, is directly relevant to the task at hand and is very clear about the desired behavior without being overly directive. The idea being that if participants show no response to this type of direct intervention in this setting, then other forms of intervention that may target general processes such as better emotional regulation or better mentalising are then even less likely to show a benefit. As such this intervention can be seen as a litmus test for the success of more "general" forms of cognitive interventions. Moreover, in the event of the intervention's failure, analysis of the resistance to an explicit intervention itself might be worthy of further investigation to understand the mechanism behind the lack of success.

In this experiment, participants are given the role of the trustee and are randomly assigned to either a control group or an intervention group. They play two instances of the repeated Trust Game facing what they believe are two different players. In between games, they either receive a cognitive intervention (intervention condition) or not (control condition, where participants are asked to solve anagrams). In reality, participants face the same computerised agent in both instances, which is programmed to play according to an HMM fitted to rela players data. We explore whether the intervention has an effect on the behaviour of the trustee and whether the learning is transferred to a new repeated Prisoner's Dilemma game when facing a seemingly new player.

<!-- DATA WRANGLING  -->
```{r dataLoad, include=FALSE }
d_finished <- readRDS("data/d_finished.RDS")
```

<!-- Before you introduce the tasks, you need to introduce the overall design of the experiment, i.e. the before/after randomized controlled experimental setup. A figure to illustrate this is a good idea. You could then have a section called 'measures' which includes details about each of the tasks (probably including the HMM), questionnaires and also emotion grid, and a section called 'interventions', which contains both the low return and the actual intervention. -->

# Method

## Participants and Design
A total of 318  participants were recruited on the Prolific Academic platform. The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years. Participants were paid a fixed fee of £5 plus a bonus dependent on their performance. The experiment had a 2 (Condition: Intervention or Control) by 2 (Game : Pre or Post Intervention) design, with repeated measures on the first factor. Participants were randomly assigned to one of the two levels of the second factor.

## Procedure

```{r timeline,fig.cap = "Overview of the timeline of the experiment detailing the various phases participants go through.", fig.align='center', out.width="80%"}

knitr::include_graphics("figures/timeline.png")

```

Figure \ref{fig:timeline} shows the timeline of the experiment. After reviewing an information sheet about the experiment, participants were informed that there would be three phases to go through, with them facing a different opponent in each phase. They would face the same player throughout the first phase, consisting of the "Investment Game" with several rounds. This was the moniker used for the repeated trust game, and a total of 15 rounds were played.

After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.  A comprehension quiz on the trust game followed the instructions. The first trust game then ensued:  Each round started with an investment stage where the investor decided how much to send to the trustee and that choice was revealed. Immediately afterwards, participants were presented with a two-dimensional field to indicate their emotional state on two dimensions: valence, from unpleasant to pleasant (on the horizontal axis) and arousal, from low arousal to high arousal (on the vertical axis). After selecting a point on the field, participants were asked to decide how much to send back to the investor using a slider ranging from sending back nothing to sending back the whole (tripled) investment. Following that choice, an outcome page summarised both players decisions and showed the total pay-off for each player and the round then concluded. At the end of the game, participants were asked to rate the player they were facing on 4 attributes using a scale from 1 to 10: Trustworthiness, friendliness, cooperativeness and selfishness.

After being randomly assigned to either a control or intervention condition, participants were informed they would be paired with a different player in a second phase of the experiment. This second phase was similar to the first phase in terms of the game played (RTG) and the number of rounds. Finally, players were told they would be paired with a new player in the third phase of the experiment. This third phase consisted of 7 rounds of the prisoner's dilemma game, facing the new player. Throughout all games, players were explicitly told to aim to maximise the number of points as their bonus would depend on the score they accumulated throughout the experiment. The total number of rounds was not communicated to the participants in any of the games played.

After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment. These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016]. Finally, participants were asked a series of questions around how they played each phase. First, participants were asked whether they thought they played differently in the second compared to the first phase of the RTG. Second, participants had to select whether they thought the opponents they faced were human or computer agents. Finally, we revealed to the participants that they faced the same computer agent throughout the RTG. We explained that any change in their perception of the opponent or any change in how the opponent played is due to their own change in behavior as the agent was simply reacting to their actions. Finally, we asked participants to reveal whether this experiment has taught them anything about how they should behave in social situations.

```{r interventionSlide,fig.cap = "Screenshot of the main  slide in the intervention condition", fig.align='center', out.width="80%"}

knitr::include_graphics("figures/intervention_text.png")

```

## Interventions

After a total of 15 rounds of the trust game, players were given either an "intervention" or a "control" manipulation. The intervention consisted of presenting a hypothetical scenario in which they were playing the repeated trust game and the investor would send a low investment in a new round after having previously sent higher amounts. Participants were then asked how they would react in this situation and what sort of return (low or high) they were thinking of sending back. The players then were presented with an educational slide about the benefits of not resorting to impulsive decisions such as punishment when they feel they have been wronged. In this text, players were told that punishment can create a negative feedback loop where the other player might trust them even less. An alternative action was suggested, whereby players would respond kindly to such a transgression in the hope of gaining trust from the investor. The full text of the intervention slide is presented in Figure \ref{fig:interventionSlide}. Afterwards, participants were asked whether they would send a low or high return in the same hypothetical scenario now that they have read the information on the slide. Players were asked to justify their answer. For each question during this intervention, participants had to wait for a fixed duration of 20 seconds before being able to write their answers, and they were prevented from proceeding before that time was up.  This choice was made to allow participants to engage with the questions, think about their answers and provide meaningful feedback.

In the control condition, participants were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care"). They provided their answers in a free-form text box. The time given to solve the anagrams was the same as that given to respond to questions in the intervention manipulation.

## Measures

### Repeated Trust Game 
Participants played two iterations of the standard version of the repeated trust game [@joyce_trust_1995]. The game is played in dyads, with one player assigned the role of the "investor" and the other player that of the "trustee". In the variant of the game we chose, the investor is endowed with 20 units at the start of each round. They need to decide how much of that endowment they want to invest with the trustee. The investment is then multiplied by a factor of 3 and sent to the trustee. As shown in Figure \ref{fig:trustGame}, the trustee in turn needs to decide how much of the (multiplied) investment they want to send back to the investor. If they send back more than a third of what they received, then both the investor and the trustee make a gain. Otherwise, the trustee would benefit but the investor would lose on their investment. If the interaction lasts for only one round, the Nash equilibrium of this game is for the investor to send nothing, as there is no incentive for the trustee to send back any return. In the repeated version, to maximise their rewards over time, both players need to build trust so that they can share the benefits of the bigger pie (the investment multiplied by three). If during the course of the interaction, the investor has been rewarded for taking the risk of sending an investment, then they would be more likely to invest more, and the multiplied investment would give both a bigger pie to share. If however the investor felt that they were not getting a return on their investment, then they would refrain from investing and neither would gain from the interaction.

```{r trustGame,fig.cap = "Screenshot of the repeated Trust Game. The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee. The investor is endowed with 20 units at the start of each round. They need to decide how much of that endowment they want to invest with the trustee. The investment is then multiplied by a factor of 3 and sent to the trustee. The trustee in turn needs to decide how much of the multiplied investment they want to send back to the investor. Shown here is the stage at which the trustee makes a decision of how much to send back the investor", fig.align='center'}

knitr::include_graphics("figures/trust_game.png")

```

### Repeated Prisoner's Dilemma 
The other game the participants played is the repeated Prisoner's Dilemma (RPD). Over multiple rounds, participants could choose one of two actions: A cooperative action that would yield a high pay-off if the other person also cooperated, and the lowest possible pay-off if they did not cooperate. Or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect. Figure \ref{fig:payoffsRPD} shows the payoff of each combination of actions as presented to the participants.

```{r payoffsRPD,fig.cap = "Screenshot of the Repeated Prisoner's Dilemma game. Over multiple rounds, participants could choose one of two actions: A cooperative action that would yield a high pay-off if the other person also cooperated, and the lowest possible pay-off if they did not cooperate. Or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect. Shown here is the table explaining the payoffs of each combination of actions the participant and their opponent choose", fig.align='center'}

knitr::include_graphics("figures/screenshot_RPD_payoffs.png")

```

### Feedback post investment in the repeated Trust Game

```{r grid,fig.cap = "Screenshot of the two axis grid in the Coaxing condition where participants were asked to report the valence and arousal of their emotional response ", fig.align='center'}

knitr::include_graphics("figures/emotion_grid.png")

```

Whilst playing the RTG, participants were asked to provide some feedback, in each round of the game, after seeing the amount sent by the investor. This feedback took the form of the answer to a question using a two dimensional field. What the axes of the field represented differed by condition. In the intervention condition, participants were asked to rate their emotional state with regard to the other player's choice of investment, with the x-axis representing the valence of the emotion they felt (positive or negative) and the Y-axis representing the emotional "arousal" they experienced (low or high). In the control condition, players were asked to rate attributes of the investment that were not related to their emotion, with the X-axis rating of how fast the investor is (slow or fast) and the Y-axis the magnitude of the investment (low or high). Figure \ref{fig:grid} shows a screenshot of the field in the intervention condition where participants were asked about their own emotional response to the investment. At the beginning of each game, participants were provided with detailed explanations of the meaning of the two axes as well as the opportunity to provide a baseline emotional state through using the field prior to the start of the game.

### Design of the AI agents in the RTG and RPD

```{r}
Anti_social <-  c(0.1025436430408, 0.1221931236853, 0.1345215238995,
0.1368182252617, 0.1285592471751, 0.1116014322677, 0.0895041220882,
0.0663166721334, 0.0453950277118, 0.0287077419587, 0.0167723588011,
0.0090530028158, 0.0045143317507, 0.0020796744990, 0.0008851094702,
0.0003480141146, 0.0001264134789, 0.0000424213859, 0.0000131513231,
0.0000037665630, 0.0000009965755)

Neutral <- c(0.003393529, 0.006930874, 0.013053553, 0.022671228,
0.036310144, 0.053627606, 0.073039389, 0.091734929, 0.106248217,
0.113479701, 0.111769796, 0.101517390, 0.085028780, 0.065675083,
0.046778251, 0.030725245, 0.018610323, 0.010394861, 0.005354126,
0.002543094, 0.001113881)

Pro_social <- c(0.003162697, 0.001057162, 0.001410197, 0.001881016,
0.002508877, 0.003346113, 0.004462480, 0.005950950, 0.007935434,
0.010581067, 0.014107909, 0.018809194, 0.025075644, 0.033427845,
0.044559370, 0.059394206, 0.079163228, 0.105506029, 0.140606514,
0.187373417, 0.249680651)

investment <- seq(0:20) -1

response_probs <- as.data.frame(cbind(investment,Anti_social,Neutral,Pro_social)) %>% 
  rename("low-trust" = "Anti_social", "medium-trust"="Neutral", "high-trust" = "Pro_social") %>%
  pivot_longer(cols=c("low-trust","medium-trust","high-trust"),
                    names_to='Investor_state',
                    values_to='probability') %>% 
   mutate(across(Investor_state, factor, levels=c("low-trust","medium-trust","high-trust")))
```

```{r invHMMPlot, fig.cap="Distribution of investments by the artificial investor agent conditional on its latent state as estimated by a three state hidden Markov model with a discretised truncated Gaussian as a response function",fig.align="center", fig.width=6, fig.height = 4}

ggplot(response_probs,                            
       aes(x = investment,
           y = probability,
           fill = Investor_state)) +
  geom_bar(stat = "identity",
           position = "dodge") + 
  labs(fill='Latent investor state') + 
  theme_bw() + 
  theme(legend.position = "bottom")

```

```{r, include=FALSE}

unhappy_pars <- rbind(c(3.5435248 , 0.0592584), c(0.1611541, 0.4675468), c(0,0)) 
neutral_pars <- rbind(c(0.8846036, - 0.4394031), c(2.4214322, - 0.0710711), c(0,0))
happy_pars <- rbind(c(-2.004988 ,- 0.151186), c(-1.2976976 , - 0.1357088), c(0,0))

pars_inv <- list(unhappy_pars, neutral_pars, happy_pars)

plot_HMM_transitions <- function(ns, pars_mat) {

  trans_prob <- data.frame(
    from = rep(1:ns, each=100*ns),
    to = rep(1:ns, each=100),
    ret = seq(-20,60,length=100),
    probs = 0
  )

  y <- matrix(0.0,ncol=ns, nrow=100)

  for(from in 1:ns) {
  pars <- matrix(pars_mat[[from]], ncol=2)
  # print(pars)

    for(to in 1:ns) {
        x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"ret"]
        y[,to] <- exp(pars[to,1] + pars[to,2]*x)
    }
    y <- y/rowSums(y)

    for(to in 1:ns) {
      trans_prob$probs[trans_prob$from == from & trans_prob$to == to] <- y[,to]
    }
  }

  df <- as.data.frame(trans_prob) %>% 
    mutate(from = recode(from, "1" = "low-trust", "2" = "medium-trust", "3" = "high-trust"),
           to = recode(to, "1" = "low-trust", "2" = "medium-trust", "3" = "high-trust") ) %>% 
    mutate(across(from, factor, levels=c("low-trust","medium-trust","high-trust"))) %>% 
    mutate(across(to, factor, levels=c("low-trust","medium-trust","high-trust")))

  ggplot(df,aes(x=ret,y=probs, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) +  labs(x = "Investor's Net Return", y = "Transition probability", color='State Transitioned to') + 
    theme_bw() + theme(legend.position = "bottom")

}

```

```{r invHmmTrans, fig.cap="Transition function for investor conditional on current state",fig.align="center", fig.width=6, fig.height = 4}

plot_HMM_transitions(3, pars_inv)

```

The role of the investor was in reality played by an adaptive artificial agent whose strategy was modelled on the behaviour of human participants taking the role of the investor in the RTG. Using data from human dyadic interaction in the 10 round trust game, we estimate a Hidden Markov Model (HMM) to characterise the investor's behavior as emanating from a small number of latent states [@rabiner_hmm_1989]. In this instance, for both iterations of the repeated trust game, the HMM used was identical: it had three states that can be described as "low-trust", "medium-trust" and "high-trust". Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust, as presented in Figure \ref{fig:invHMMPlot}.

<!-- The advantages of this approach is that it does not require any a priori assumptions about the model features. The number of states, the policy conditional on the state, and the transition function between states can all determined in a purely data driven way. These HMMs can in turn be used to simulate a human-like agent playing the trust game. This agent may transition to a new state depending on the other player's actions and adopt a policy reflecting its state, thus simulating changes in emotional dispositions of human players during a repeated game. When the investor gains from the interaction, they become more likely to transition to a state where their policy is to be more trusting and invest more. However, faced with losses, the investor is more likely to transition to a more cautious policy where its investment belies lower trust in the trustee. The policies and the transitions between states are sufficient to build an agent that reflects this type of adaptive behavior and reacts to the trustee's action choices in a way that mimics a human player.  -->

The HMM assumes that the probability of each investment $I_t=0,…,20$, at each trial t, conditional on the current state of the investor $S_t$, is dependent on an underlying normal distribution with mean $\mu_s$ and standard deviation $\sigma_s$. The probability of each discrete investment was determined by the cumulative normal distribution $\Phi$. For instance, the probability of an investment $I_t=2$ is defined as:

$$P(I_t=2 | S_t=s)= \frac{\Phi(2.5 | \mu_s,\sigma_s ) - \Phi(1.5 | \mu_s,\sigma_s )} {\Phi(20.5 | \mu_s,\sigma_s ) - \Phi(-0.5 | \mu_s,\sigma_s )}$$

Note that the denominator truncates the distribution between 0 and 20. To estimate the transition probability between states for the investor, a multinomial logistic regression model was fitted to the investor's data such as:

$$P(S_{t+1} = s' | S_t=s , X_t = x)= \frac{\exp(\beta_{0,s,s'} + \beta_{1,s,s'} x)}{\sum_{s''} \exp(\beta_{0,s,s''} + \beta_{1,s,s''} x)}$$

where $X_t=R_t-I_t$ is the net return to the investor with  $R_t$ the amount returned by the trustee and $I_t$ is the Investment sent. Figure \ref{fig:invHmmTrans} shows these transition probabilities as a function of the net return conditional on the investor's state.

For the repeated prisoner's dilemma, we used an artificial agent that was playing according to Tit-For-Tat [@axelrod_evolution_1981]. It started by choosing the cooperative action and then it mirrored whatever the other player played in the previous round.

### AI agents pre-programmed defection

In order to probe efforts to repair trust, we introduced rounds where the investor deviated from the policy provided by the HMM, and chose to send a low investment in the Trust Game, or chose the non-cooperative action in the Prisoner's Dilemma. In the trust games, we programmed the HMM agent to send a very low investment (2 out of 20) to the trustee on specific rounds (round 12 pre-intervention and 13 post-intervention). For the repeated Prisoner's Dilemma game, we programmed the agent to choose the non-cooperative action on round 4. After each "defection" round, the agents were programmed to proceed their policy from before that round, effectively ignoring the participants' response to their defection. For instance, the HMM investor would send an investment in the post defection round that was consistent with the outcome of the round immediately prior to that round. For the RPD, the agent would continue to play tit-for-tat, but also ignoring what happened in the defection round, and basing its action on mirroring what the other player did in the round immediately prior to the defection round. This ignorance of reactions to the defection rounds was chosen to reflect an accidental defection, with the Investor being open to repair subsequent interaction.

<!-- ## Statistical analysis of Behavior -->

<!-- Since we aim to compare pre and post intervention measures between groups, we have to analyse repeated measures. To do that we will use linear mixed effects models as implemented in the R package "afex" [@singmann_afex_2022]. When models contain interactions between variables that involve continuous covariates such as the "Investment", we standardise the continuous covariate by transforming it into a z-score. This allows us to correctly interpret the coefficient of the interaction variable.  For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".  -->

<!-- ## Computational analysis of trustee returns -->

<!-- In order to characterise the effect of the intervention on the trustees strategy, we fit a Hidden Markov Model to the percentage returns of the trustees for the RTG data. The model allows for switching between latent trustee states over time. Hidden Markov models assume that an observable trustee return at time $t$ depends on a latent trustee state at time $t$. It is assumed that the latent state at time $t$ depends on the latent state at the previous time $t-1$. The model is specified by the state-conditional action distributions (these are provided by the likelihood of the fitted models), an initial state distribution (the distribution over the strategies at the initial round), and the state-transition probabilities (probability of switching from one state/strategy to another). Initial state probabilities and the transition probabilities were estimated with the depmixS4 package [@visser_depmixs4_2021]. -->

### HMM analysis of participants returns in the RTG

To model participants returns in the RTG across games and conditions, we used an HMM response function based on a discretised Gaussian distribution that takes into account what proportion the trustee would ideally like to return, and what returns are possible given the investment. For instance, if the investor sends an amount of $2$, the trustee would receive $6$ and they can send back any amount between $0$ and $6$. As such, we assume that the response is a distribution over proportions that can be calculated from these possible returns, i.e. $\{0,1/6, 2/6,...,1 \}$. The model assumes an underlying Normal distribution for each possible proportional return, predicting the probability of each via the cumulative Normal distribution with cut-off points set halfway between the proportions (e.g. the probability of returning 1/6 is determined as the probability of returning anything between 1/12 and 3/12).  The transition between states is assumed to depend on the investment through a multinomial logistic function such as:

$$P(S_{t+1} = s' | S_t=s , X_t = x)= \frac{\exp(\beta_{0,s,s'} + \beta_{1,s,s'} \ \text{inv} + \beta_{2,s,s'} \ x)}{\sum_{s''}\exp(\beta_{0,s,s''} + beta_{1,s,s'} \ \text{inv} + \beta_{2,s,s'} \ x)}$$

where $\text{inv}$ is a variable representing the investment received, $x$ is a dummy variable to characterise the group that the participant belongs to. We define four contrast codes for these dummy variables: pre-post (comparing pre and post games), post-coax (compares the post-intervention group to all others), post-control (compares the post-control group to all others) and full-contrast (a three level dummy variable: post-intervention compared to post-control and  all pre games).

Having defined these contrast codes, we then fit HMM models where the transition function between latent states depends both on the investment received and depending on the model, one of the aforementioned contrast codes. To select the number of hidden states governing participants' policies, we fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978] to select the best model.

# Behavioral results

<!-- Our investment levels are clearly comparable. Our random matching condition is the most directly comparable to Berg et al., (1995) and Charness et al., (2008), both of whom used random matching. Our investment averages 4.97 out of 10 in the individual feedback condition, which falls right in between the investment level of 5.16 documented by Berg et al., (1995) and the 3.73 documented by Charness et al., (2008). The amount returned in the individual feedback condition with random matching is 5.61, which is slightly higher than the amounts returned in Berg et al., (1995) of 3.73 and Charness et al., (2008) of 4.65. The 19% return rate is comparable to results in similar designs. In an almost identical design, Fiedler et al., (2011) report a 17% return rate by responders. This is similar to our finding.  -->

```{r dataClean, include=FALSE}
# Filter only trust rounds and create % returns and investments

avg_ret_df <- d_finished %>%
  dplyr::select(id, condition.f,roundType,investment,returns,roundNum,gameNum.f,BPD_trait,PBOR_score,DERS_score,RFQ_c,RFQ_u) %>% 
  mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing"))%>%
  filter(roundType=="trust",!is.na(roundNum)) %>% 
  mutate(roundNum = as.numeric(as.character(roundNum))) %>%
  mutate(inv_scaled = scale(investment)) %>% 
  mutate(inv_pct = investment/20, ret_pct = returns/(3*investment), ret_pct_0 = ifelse(investment==0,0,returns/(3*investment)))  %>% 
  # Creating Quartiles of % returns by participant over BOTH TRUST GAMES
  group_by(id) %>% 
  mutate(mean_pct_ret = mean(ret_pct), mean_abs_ret = mean(returns), mean_inv = mean(investment)) %>%
  ungroup() %>% 
  mutate(Quart_pct_ret = ntile(mean_pct_ret,4),
         Quart_abs_ret = ntile(mean_abs_ret,4),
         Quart_inv     = ntile(mean_inv, 4))

# %>%
#   filter(complete.cases(.))   # <- one player had NA in one round as a return, so we exclude him from analysis.

# Number of people left for analysis. 
nrow(avg_ret_df %>% filter(condition.f == "intervention"))/30
nrow(avg_ret_df %>% filter(condition.f == "control"))/30

# average investment for first 10 rounds pre intervention
avg_pct <- avg_ret_df %>% filter(roundNum < 11 , gameNum.f == "pre") %>% summarise(avg_inv = mean(inv_pct), avg_ret = mean(ret_pct, na.rm=TRUE))
```

For the outcomes of the RTG, we first check the benchmark results for the average investment and return to see if they are comparable to results in the literature. We focus on the first 10 rounds pre-manipulation (the first RTG) and pre-defection trial to exclude the effects of the investor's transgression and those of the intervention and to have a comparable number of rounds to the standard version of the RTG. The average investments and returns were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature, and hence comparable to other implementations of this task reported in the literature [@charness_investment_2008; @fiedler_social_2011].

<!-- Investments averaged `r round(avg_pct$avg_inv,3)*100` $\%$ of endowment which is less than the $63.2\%$ documented by @fiedler_social_2011 and higher than the $37.3%$ documented by @charness_investment_2008, although the latter used repeated one shot games with random matching. Returns averaged `r round(avg_pct$avg_ret,3)*100` $\%$  of the total yield (3x investment sent), which is higher than the $35\%$ found in the same setting in @fiedler_social_2011.  -->

```{r gamesPlot, echo=FALSE, fig.cap="Average and standard errors of the trustee's return as a percentage of the multiplied investment received for each round and for both conditions. The red line shows the returns pre-manipulation and the blue line post-manipulation. ",fig.align="center", fig.width=6, fig.height = 4}

# colors <- c("investment" = "blue", "returns" = "red")
# 
# ggplot(avg_ret_df,aes(x=as.factor(roundNum),group = 1)) +
#   stat_summary(fun = "mean", geom = "line", aes(y=returns, color ="returns")) +
#   stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=returns) ) +
#   stat_summary(fun = "mean", geom = "line", alpha =0.4,aes(y=investment, color = "investment")) +
#   stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=investment) ) +
#   facet_wrap(~condition.f*gameNum.f) +
#   labs(x = "Round",
#        y = "Investment / Return",
#        color = "Legend") +
#   scale_color_manual(values = colors) +
#   theme_bw() +
#   theme(legend.position = "bottom")

# Alternative chart with pre vs post percentage returns in one panel as suggested by QH.

ggplot(avg_ret_df ,aes(x=as.factor(roundNum),group=gameNum.f, color = gameNum.f)) +
  stat_summary(fun = "mean", geom = "line", aes(y=ret_pct)) +
  stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=ret_pct) )+
  labs(x = "Round",
       y = "Percentage Return",
       color = "Game") +
  # ylab("Percentage Return") +
  # xlab("Round") +
  theme_bw() +
  theme(legend.position = "bottom") +
  facet_wrap(~condition.f)

```
Figure \ref{fig:gamesPlot} shows the average and standard error of trustee returns as a percentage of the total yield (3 x investment) over the full 15 rounds for both conditions and both RTG games. We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.

To explore whether participants behaved differently after the intervention compared to the control group over all rounds, we estimate a linear-mixed effects model, with fixed effects for Condition (intervention or control), Game-number (pre- or post-intervention) and Investment, as well as interactions between Condition and both Investment and Game-number, and participant-wise random intercepts and random slopes for Game-number. We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions. More complex models with additional random effects provided could not be estimated reliably.

```{r, include=FALSE, cache=TRUE}

mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), avg_ret_df, REML= TRUE)
anova(mod_returns_pct)
summary(mod_returns_pct)

prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))

```

```{r afexPLotPctRet, fig.cap="Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition",fig.align="center", fig.width=6, fig.height = 4}
afex::afex_plot(mod_returns_pct, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
            mapping = c("linetype", "shape", "fill"),
            data_geom = geom_violin, 
            data_arg = list(width = 0.5),
            factor_levels = list(gameNum.f = c("Pre", "Post")), legend_title = "Condition") + 
  theme_bw() + 
  labs(y = "Percentage Return", x = "Game") + 
  theme(legend.position = "bottom") +

```

Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:afexPLotPctRet}. If the intervention has an effect, then we should expect a higher increase in returns after the intervention compared to the control condition, which should be evident from an interaction between Condition (intervention vs control) and Game-number (pre- vs post-manipulation). Therefore, the variable of interest here is the interaction between Condition and Game-number. We do find an interaction effect due to an increase in the percentage returned in the intervention but not in the control group ($F(1,314.2) =  26.9, p < 0.001$). We also find a significant main effect for Condition ( $F(1,315.31) = 9.52, p = 0.002)$), which is due to participants returning higher percentage returns, in the post game, in the intervention group ($p < 0.001$), and lower returns in the control group ($p = 0.02$). We also find a main effect of Investment due to higher percentage returns being sent back for higher investments ( $F(1,9208) = 373.6, p < 0.001$), and an interaction effect of Investment by Condition ($F(1,9207) =45.38, p < 0.001$), with investments having less of a positive effect on the percentage returns in the intervention group compared to the control group. The latter effect indicates that the higher returns we see in the intervention group are unlikely to be purely driven by higher investments. Finally, we find a three way interaction between Game-number, Condition and Investment ($F(1,8988)= 24.6, p < 0.001$), showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game-number.

```{r, include=FALSE, cache=TRUE}
mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| id), avg_ret_df )
summary(mod_invs)
anova(mod_invs)

# pairs(emmeans::emmeans(mod_invs, c("condition.f"), by = "gameNum.f" ))
# 
# pairs(emmeans::emmeans(mod_invs,c("gameNum.f") , by = c("condition.f")))
# 
# pairs(emmeans::emmeans(mod_invs, c("gameNum.f")))
# pairs(emmeans::emmeans(mod_invs, c("condition.f")))

```

```{r afexPlotInv, fig.cap="Marginal means and distributions of investments over all rounds for HMM agents playing the role of the investor, by Game number and Condition.",fig.align="center", fig.width=6, fig.height = 4}

afex_plot(mod_invs, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
            mapping = c("linetype", "shape", "fill"),
            data_geom = geom_violin,
            data_arg = list(width = 0.5),
            factor_levels = list(gameNum.f = c("Pre", "Post")), 
            legend_title = "Condition") + 
  theme_bw() + 
  labs(y = "HMM Investment", x = "Game") + 
  theme(legend.position = "bottom")

```

Since the artificial agent taking the role of the investor adapts its behavior to the actions of the participants, we can analyse whether the HMM agent exhibits a differentiated behavior between games and conditions.  We use a linear-mixed effects model, with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number. We find a main effect for both Condition ($F(1,317) = 8.7, p = 0.003$) and Game-number($F(1,317) = 8.3, p = 0.004$). As can be seen in Figure \ref{fig:afexPlotInv}, investment was higher in the intervention compared to the control condition across games ($p=0.003$). Across conditions, investment was also higher in the second game compared to the first ($p=0.003$).

In summary, participants in the control group sent back **lower** returns in the second game (`r apa_print(prepost_bycond)$full_result$control`) despite the HMM investor sending, on average higher absolute investments. Those in the intervention group returned **higher** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$intervention`), with the investor also sending higher investments. We can rule out that these higher returns in the intervention group compared to the control group were purely driven by higher investments. If that was the case, then we would expect the presence of the Investment variable in our model of returns to lead to a non-significant interaction between Game-number and Condition. Since we find the interaction effect whilst controlling for Investment, this suggests this effect is not purely explained by the change in investments.

## Pre-defection trials

```{r, include=FALSE, cache=TRUE}
# ALL ROUNDS BEFORE DEFECTION TRIAL
pre_int_data <- avg_ret_df %>% filter(roundType=="trust",!is.na(gameNum.f),(roundNum < 12 & gameNum.f =="pre")| (roundNum < 13 & gameNum.f =="post"))

mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), pre_int_data, REML= TRUE)
anova(mod_returns_pre)
summary(mod_returns_pre)

pairs_pre_int <- pairs(emmeans::emmeans(mod_returns_pre, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400, reverse=TRUE))

```
Since we observed higher returns pre-defection trials, we can also explore whether there was differentiated behavior if we restrict our analysis to the rounds prior to the pre-programmed one-off investment (rounds 1 to 11 pre-manipulation and 1 to 12 post-manipulation). We fit the same linear mixed effects model to percentage returns as the one for the full data. Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:preCoaxPlot}. We do find an interaction effect between Condition and Game number ($F(1,317.99) =  17.1, p < 0.001$). This was due to an increase in the percentage returned pre low-investment trial in the intervention condition (`r apa_print(pairs_pre_int)$full_result$intervention`) but not in the control group (`r apa_print(pairs_pre_int)$full_result$control`). This indicates that the differentiated behavior we saw, where participants were sending back higher returns in the intervention condition but not in the control condition, was not simply due to their reaction post the low-investment trial. The higher returns were consistent with the message of the intervention, but have also happened, on average across participants, before the participants experienced the event similar to the one described in the intervention.

```{r preCoaxPlot, fig.cap="Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.",fig.align="center", fig.width=6, fig.height = 4}
afex_plot(mod_returns_pre, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
            mapping = c("linetype", "shape", "fill"),
            data_geom = geom_violin,
            data_arg = list(width = 0.5),
            factor_levels = list(gameNum.f = c("Pre", "Post")), 
            legend_title = "Condition") + 
  theme_bw() + 
  labs(y = "Percentage Return", x = "Game") + 
  theme(legend.position = "bottom")
```

## Defection and post defection trials

The interventions focused on repairing cooperation in the wake of a transgressive action by the investor. To assess the effect of the intervention, we can therefore consider the percentage return after the "transgression" trials. We fit the same linear mixed effects model to percentage returns as the one for the full data. We now restrict the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game. These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).

```{r, include =FALSE}

# Defection trial only 
coax_data <- avg_ret_df %>%  filter(roundType=="trust",!is.na(gameNum.f),(roundNum == "12" & gameNum.f =="pre")| (roundNum == "13" & gameNum.f =="post"))

coax_data %>% group_by(gameNum.f, condition.f) %>% summarise(avg_inv = mean(investment),avg_return = mean(returns))

# ALL ROUNDS AFTER DEFECTION TRIAL (INCLUSIVE)
post_coax_data <- avg_ret_df %>% filter(roundType=="trust",!is.na(gameNum.f),(roundNum >= 12 & gameNum.f =="pre")| (roundNum >= 13 & gameNum.f =="post"))

post_coax_data %>% group_by(gameNum.f, condition.f) %>% summarise(avg_inv = mean(investment),avg_return = mean(returns))

```

```{r, include=FALSE, cache=TRUE}

mod_postcoax_trust <- mixed(ret_pct ~ gameNum.f*condition.f*inv_scaled  + ( 1 + gameNum.f|id), post_coax_data)
anova(mod_postcoax_trust)

postcoax_bygame <- emmeans::emmeans(mod_postcoax_trust, ~gameNum.f, pbkrtest.limit = 9400)
postcoax_bycond <- emmeans::emmeans(mod_postcoax_trust, ~condition.f, pbkrtest.limit = 9400)

postcoax_interaction <- emmeans::emmeans(mod_postcoax_trust, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400)
postcoax_interaction

pairs(emmeans::emmeans(mod_postcoax_trust, c("gameNum.f"), by = "condition.f"))
```

```{r postCoaxPlot, fig.cap="Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.",fig.align="center", fig.width=6, fig.height = 4}
afex_plot(mod_postcoax_trust, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
            mapping = c("linetype", "shape", "fill"),
            data_geom = geom_violin,
            data_arg = list(width = 0.5),
            factor_levels = list(gameNum.f = c("Pre", "Post")), 
            legend_title = "Condition") + 
  theme_bw() + 
  labs(y = "Percentage Return", x = "Game") + 
  theme(legend.position = "bottom")
```

Figure \ref{fig:postCoaxPlot} shows the marginal means of trustee returns and their distribution by Game-number and Condition. We found a main effect of Condition with returns on the intervention group higher than returns in the control group (`r apa_print(pairs(postcoax_bycond))$full_result$intervention_control`). We also found a main effect of Game-number, with returns higher for the pre-manipulation game compared to the post-manipulation game  (`r apa_print(pairs(postcoax_bygame))$full_result$pre_post`).
In addition, there was a significant interaction between Game-number and Condition. We found a significant decrease in returns between games in the control condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$control_pre_post`), but no such difference in the intervention condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$intervention_pre_post`).

## Emotion self-reports

```{r, include=TRUE}

# Get Emotions on x axis per round (valence)
emo.x <- d_finished %>% 
  mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>% 
  dplyr::select(id,roundType,condition.f,contains("emotionGrid")) %>% 
  dplyr::filter(roundType=="trust") %>% dplyr::select (-contains(".y") ) %>% pivot_longer(cols=contains(".x"), names_to = c("gameNumber","roundNum"), names_pattern ="return_trust_emotionGrid_(.*)_(.*)[.]x", values_to = "emo_coord_x") %>%
  distinct()

#Get emotions on y axis (arousal)
emo.y <- d_finished %>%
  mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>%
  dplyr::select(id,roundType,condition.f,contains("emotionGrid")) %>% 
  dplyr::filter(roundType=="trust") %>% dplyr::select(-contains(".x") ) %>% pivot_longer(cols=contains(".y"), names_to = c("gameNumber","roundNum"), names_pattern ="return_trust_emotionGrid_(.*)_(.*)[.]y", values_to = "emo_coord_y") %>%
  distinct()

# put emotions in one dataframe
full_emo <- full_join(emo.x,emo.y, by=c("id", "gameNumber","roundNum","roundType", "condition.f"))  %>% 
  mutate(roundNum=as.numeric(as.character(roundNum))) %>% 
  mutate(gameNum.f = factor(gameNumber,labels = c("pre","post"),levels=c("1","2"))) %>% 
  dplyr::select(-c("roundType","gameNumber")) %>% 
  group_by(condition.f) %>% 
  mutate(emo_scaled_x = scale(emo_coord_x), emo_scaled_y= -scale(emo_coord_y))  %>%    # <--- SCALING and reversing Y coordinates (0,0 is top left)
  ungroup()

#merge with returns dataframe
full_dat <- full_join(avg_ret_df, full_emo, by = c("id","condition.f","gameNum.f","roundNum" )) %>% filter(complete.cases(.))
#nrow(full_dat)

datCoax <- full_dat %>% filter(condition.f=="intervention")
datCtrl <- full_dat %>% filter(condition.f=="control")

```

```{r emoPlotCoax, fig.cap="Self-reported emotion valence and arousal as well as investment z-scores for each round of the repeated Trust Game averaged across participants in the intervention condition only.",fig.align="center", fig.width=6, fig.height = 4}

colors <- c("Investment" = "blue", "Valence" = "red", "Arousal" = "green")
ggplot(datCoax,aes(x=roundNum)) + 
  stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_x, color = "Valence")) + 
  stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_y, color = "Arousal") ) + 
  stat_summary(fun = "mean", geom = "line",group =1, aes(y=scale(investment), color = "Investment") ) + 
  # 
  # stat_summary(fun = "mean", geom = "point",shape=15, size=2.5,group=1,  alpha =0.3,aes(y=investment/10,color = "Investment")) +
  # scale_y_continuous(name="Valence/Arousal z-score", sec.axis=sec_axis(~./0.1, name="investment")) +
  scale_color_manual(name = " ",values = colors,labels = c("Investment", "Emotion valence", "Emotion arousal")) +
  labs(x = "Round", y="Series Z-score") +
  geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
  facet_grid(cols = vars(gameNum.f) ) +
  theme_bw() + 
  theme(legend.position = "bottom")

```

The results of the mixed-effects model of returns suggest that returns of participants in the intervention condition were less associated with the magnitude of the investment compared to those in the control condition. We can explore whether the emotional reaction to the investment was also lessened in the intervention condition through analysing the self-reported emotions on the two-axes feedback field.  Figure \ref{fig:emoPlotCoax} shows the average, across participants *in the intervention condition*, of emotion valence, the degree of arousal as well as the HMM's investment z-scores. We find a significant positive correlation between the two emotion axis ($r=0.52, p < 0.001$) as well as between valence and Investment ($r=0.47, p < 0.001$), and arousal and Investment ($r=0.50, p < 0.001$). Unsurprisingly, the low investment in the pre-determined defection round leads to negatively valenced emotions. Perhaps less expected is that they also lead to low arousal. We fit a linear mixed effects model to both emotion dimensions (valence and arousal) for the intervention group to explore whether the intervention changed the emotional appraisal of the investment, with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number. 
```{r, include=FALSE}

mod_emo_x <- mixed( emo_scaled_x ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
summary(mod_emo_x)
anova(mod_emo_x)

modVal <- emmeans::emmeans(mod_emo_x, ~gameNum.f)
pairs(modVal)

mod_emo_y <- mixed( emo_scaled_y ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
summary(mod_emo_y)
anova(mod_emo_y)

modArousal <- emmeans::emmeans(mod_emo_y, ~gameNum.f)
pairs(modArousal)

# afex_plot(mod_emo_x, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
#             data_geom = geom_violin, 
#             data_arg = list(width = 0.5))
#

# library(GGally)
# ggpairs(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,inv_scaled))

cor(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,investment))
cor.test(datCoax$emo_scaled_x, datCoax$emo_scaled_y)
```

For emotional valence, we find a main effect of Investment ($F(1,4664) = 2902, p < 0.001$), with higher investment leading to more positive emotions. We also find a main effect for Game-number, due tothe reported emotional valence of investments decreasing significantly after the intervention ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$). For emotional arousal, fitting a similar mixed effects model we find only a main effect of Investment  ($F(1,4668.4) = 1919, p < 0.001$) with higher investment leading to higher arousal. These effects are still present if we exclude the defection trial. We did not find any interaction between emotional valence or arousal and the investment, which would indicate a moderating effect of the intervention on the reaction to investments.

## Player rating

One possible reason of the differentiated returns post manipulation between conditions is that participants had a different perception of the investor, post-manipulation, in the control condition compared to the control condition. To explore this possibility, we can determine whether participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention) using the players ratings they had to submit at the end of each game. To analyse the participants rating of their opponents, we used a linear mixed-effects model for each of the four players ratings (cooperativeness, selfishness, trustworthiness, friendliness) with fixed effects for Game-number (pre or post manipulation) and Condition (intervention or control), as well as interaction between condition and Game-number, and participant-wise random intercepts.

```{r, include=FALSE}

# Pivot longer ratings on each attribute 
df_coop <- d_finished %>% dplyr::select(id,condition.f,contains("cooperative")) %>%  
  pivot_longer(cols=contains("cooperative"), names_to = c("gameNumber"), names_pattern ="rating_cooperative_(.*)", values_to = "rating_coop") %>% distinct()

df_selfish <- d_finished %>% dplyr::select(id,condition.f,contains("selfish")) %>% 
  pivot_longer(cols=contains("selfish"), names_to = c("gameNumber"), names_pattern ="rating_selfish_(.*)", values_to = "rating_selfish") %>% distinct

df_trustworthy <- d_finished %>% dplyr::select(id,condition.f,contains("trustworthy")) %>% 
  pivot_longer(cols=contains("trustworthy"), names_to = c("gameNumber"), names_pattern ="rating_trustworthy_(.*)", values_to = "rating_trustworthy") %>% distinct()

df_friendly  <-  d_finished %>% dplyr::select(id,condition.f,contains("friendly")) %>% 
  pivot_longer(cols=contains("friendly"), names_to = c("gameNumber"), names_pattern ="rating_friendly_(.*)", values_to = "rating_friendly") %>%  distinct()

#merge all data frames together
datRatings <- list(df_coop, df_selfish,df_trustworthy, df_friendly) %>% 
              reduce(full_join, by=c('id','gameNumber','condition.f') ) %>% 
              mutate(gameNum.f = factor(gameNumber,labels = c("pre","post"),levels=c("1","2")))

# Group means for each rating 
mu <- datRatings %>% group_by(gameNum.f, condition.f) %>% summarise(mean_coop = mean(rating_coop),
                                                  mean_selfish = mean(rating_selfish),
                                                  mean_trustworthy = mean(rating_trustworthy),
                                                  mean_friendly = mean(rating_friendly)
                                                  )
```

```{r, include=FALSE}

# Cooperative
coop_mod <- mixed(rating_coop ~ gameNum.f*condition.f + (1 | id), datRatings)
summary(coop_mod)

pairs(emmeans::emmeans(coop_mod, c("gameNum.f"), by = "condition.f"))

#Selfish
self_mod <- mixed(rating_selfish ~ gameNum.f*condition.f + (1 | id), datRatings)
summary(self_mod)
pairs(emmeans::emmeans(self_mod, c("gameNum.f"), by = "condition.f"))

#Trustworthy 
trust_mod <- mixed(rating_trustworthy ~ gameNum.f*condition.f + (1 | id), datRatings)
summary(trust_mod)
pairs(emmeans::emmeans(trust_mod, c("gameNum.f"), by = "condition.f"))

#Friendly
friend_mod <- mixed(rating_friendly ~ gameNum.f*condition.f + (1 | id), datRatings)
summary(friend_mod)
pairs(emmeans::emmeans(friend_mod, c("gameNum.f"), by = "condition.f"))

# Conduction t-tests 
# t.test(rating_coop ~ gameNumber, data = datRatingsCoax, paired = TRUE)
# t.test(rating_selfish ~ gameNumber, data = datRatingsCoax, paired = TRUE)
# t.test(rating_trustworthy ~ gameNumber, data = datRatingsCoax, paired = TRUE)
# t.test(rating_friendly ~ gameNumber, data = datRatingsCoax, paired = TRUE)

```

We find a main effect of Game-number on all attributes, with participants rating the second player as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result$pre_post`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result$pre_post`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result$pre_post`) and more selfish(`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result$pre_post`). We also find a main effect of Condition as participants in the intervention condition rated players higher than those in the control condition on cooperativeness (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("condition.f"))))$full_result$coaxing_control`) and lower on selfishness  (`r apa_print(pairs(emmeans::emmeans(self_mod, c("condition.f"))))$full_result$coaxing_control`). There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.

<!-- However, breaking down the interaction term by Condition, we find that participants rated the post-intervention player significantly lower on all positive attributes and higher on the negative one (selfish). There was no such difference in player ratings the control condition. -->

## Transfer to the Prisoner's Dilemma Game

```{r, include=FALSE}

PD_data <- d_finished %>%
  mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>%
  dplyr::select(id, condition.f,roundType,roundNum, PDoption,PDchoice, AiChoicePD,gameNum.f, PBOR_score) %>% 
                          filter(roundType == "PD",!is.na(roundNum)) %>% 
                          dplyr::mutate(coop = ifelse(PDchoice=="cooperate",1,0),phase = ifelse(roundNum <= 4, 0,1))

# Average cooperation rates per round
#PD_data %>% group_by(roundNum, condition.f) %>% summarise(coopRate = mean(coop))
```

```{r PDCoop, fig.cap="Mean and standard error of the rate at which the cooperative action was chosen by the participants for each round of the repeated Prisoner's Dilemma game. The decrease of cooperation seen from round 5 onwards is likely due to a pre-determined defection of the agent in round 4",fig.align="center", fig.width=6, fig.height =3}
# plot of cooperation rates per round
ggplot(PD_data,aes(x=roundNum,group = 1)) + 
  stat_summary(fun = "mean", geom = "line", aes(y=coop), color ="red") + 
  stat_summary(fun.data = "mean_se", geom = "errorbar",alpha =0.3, width = 0.2, aes(y=coop) ) + 
  facet_grid(~ condition.f) +
  xlab("Round") + 
  ylab("Cooperation rate (%)") +
  scale_x_continuous(breaks = round(seq(1,10, by = 1),1)) + 
  theme_bw()

```

```{r, include=FALSE}

ipd_mod <- mixed(coop ~ condition.f * phase + (1 |id), data= PD_data, method = "LRT", family= "binomial") 
summary(ipd_mod)

ipd_mod_r5 <- glm(coop ~ condition.f, data= PD_data%>% filter(roundNum >= 5)) 
summary(ipd_mod_r5)

```

If the intervention successfully increased coaxing behaviour in participants, we would hope they generalized this to other games beyond the Trust Game. Across participants, we first look at the rate at which the cooperative action was chosen in each round. Figure \ref{fig:PDCoop} shows the mean and standard error of the cooperation rate by round. Round 4 is where we programmed the Tit-for-Tat agent to defect, which explains the lower cooperation rate we see in round 5 onwards. Using a logistic mixed-effects model with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, we found no evidence for a different cooperation rate in the intervention condition compared to the control condition. We also found no difference in cooperation rates post defection trial between conditions.

## Self report questionnaires

```{r, include=FALSE}
########### HOW DO PBOR SCORES affect returns and intervention effect ?########

avg_ret_df <- avg_ret_df %>% mutate(PBOR_scaled = scale(PBOR_score), DERS_scaled = scale(DERS_score), RFQc_scaled = scale(RFQ_c))

# these are repeated measures here, so not independent. need to used mixed effects model.
mixed_PBOR_pct <- afex::mixed(ret_pct ~ PBOR_scaled*gameNum.f*condition.f + investment + (1 | id ), data= avg_ret_df)
summary(mixed_PBOR_pct)

# At average value of PBOR score  
emmeans(mixed_PBOR_pct, pairwise ~ PBOR_scaled * condition.f )

## Looking at difference between average returns across rounds
#scoreDAT <- avg_ret_df %>% dplyr::select(id,diff_pctRet, PBOR_scaled, DERS_scaled, RFQ_c, condition.f) %>% unique()

```

Failure to repair a breakdown in trust in the repeated trust game has been associated with trustees with BPD traits [@king-casas_rupture_2008]. Theories of social dysfunction in BPD have focused on dysfunction in the patients' mentalising ability [@allen_handbook_2006] as well as difficulties in emotional regulation [@rudge_mechanisms_2020]. The questionnaires we included in the experiment tried to assess borderline traits (PAI-BOR), emotional regulation capabilities (DERS) and mentalising ability (RFQ8). As such, we wanted to test whether there was an association between scores in these questionnaires and the effect of the intervention. We fit a linear mixed effect model to the percentage return of trustees with fixed effects for Condition (intervention or control), Game-number (pre or post manipulation), Investment, and questionnaire score as well as all interactions between the fixed effects. We assume participant-wise random intercepts. We Z-transform the questionnaire scores and Investment as centering would be beneficial to interpreting the main effects more easily. We find no interaction effect of the questionnaire scores with Condition variable, nor a main effect of the questionnaire scores.

## Debrief Questions

In post experimental debrief questions, when asked whether they thought they were facing humans or machines, participants were divided in their answers. Although these were open questions, not easily amenable to quantitative analysis, we noted some important trends. Reading through participants answers, we note that most of those who correctly deduced that their opponents were artificial agents mentioned cues such as the speed of response of the agent or the duration it took to match up with a game partner to justify their answers. This means that this deduction was not associated with the way the agent was perceived to play the game. In terms of the agent's behavior, participants expressed they felt it was either human or possessed human-like characteristics such as "spitefulness" or "greed". In summary, participants did not systematically detect that their opponents were AI agents reacting to their returns, and were sometimes projecting human traits onto the observed behavior of their artificial opponents.

# HMM analysis of participant returns

```{r, include=FALSE}

# Removing player whose return was not properly recorded by data (NA in one of the rounds) so as to run depmixS4
id_with_na <-  as.character(avg_ret_df[is.na(avg_ret_df$returns),"id"])

# Create return percentage bins Bins
avg_ret_df <- avg_ret_df %>%
  filter(id != id_with_na) %>% 
  mutate(game_id = rep(1:636, each=15)) %>%
  group_by(game_id) %>%
  mutate(next_investment = lead(investment, default=0),
         investment_bin = cut(investment, breaks = c(-1,2.5,7.5,12.5,17.5,21)),  
         return_pct_bin = cut(ret_pct_0, breaks = c(-.1,.16,.33,.50,.66,0.84,1.1)),  # 0, 1/6, 2/6, 3/6,...
         intervention_ctrst = factor(ifelse(gameNum.f=="pre", 0,ifelse(condition.f=="control",1,2))),
         ctrl_only_ctrst = factor(ifelse(gameNum.f=="post" && condition.f=="control", 1,0)),
         coax_only_ctrst = factor(ifelse(gameNum.f=="post" && condition.f=="intervention", 1,0)),
         pre_post_ctrst = factor(ifelse(gameNum.f=="post", 1,0)))  %>% 
  ungroup()
# We put factor as otherwise R thinks that it's a linear variable. We want the first level to be reference group, 0. Default uses that.

priordat <- avg_ret_df %>% filter(roundNum==1)

############### HMM support functions   #########################

# order the states of the HMM to allow it to order them as low ret/mid/ret/high ret. 
label_switch <- function(mod,labels) {
  # labels is vector, first element is new label for original state 1, second is new label for original state 2, etc.
  if(!is(mod,"depmix") || !is(mod,"depmix.fitted")) stop("this function is for depmix models")
  n_states <- mod@nstates
  if(length(labels) != n_states || length(unique(labels)) != n_states || !(all(labels) %in% 1:n_states)) {
    stop("labels needs to be a vector of unique integers between 1 and", n_states)
  }
  inv_labels <- sapply(1:n_states,function(x) which(labels == x))
  tmp <- mod
  # relabel prior
  ppars <- getpars(mod@prior)
  fpars <- getpars(mod@prior,which="fixed")
  out_pars <- as.numeric(t(matrix(ppars,nrow=length(ppars)/n_states,byrow = TRUE)[,inv_labels]))
  out_fixed <- as.logical(t(matrix(fpars,nrow=length(fpars)/n_states,byrow = TRUE)[,inv_labels]))
  if(!tmp@prior@family$link=="identity") tmp@prior@family$base <- labels[tmp@prior@family$base]
  # relabel transition
  for(i in 1:n_states) {
    ppars <- getpars(mod@transition[[inv_labels[i]]])
    fpars <- getpars(mod@transition[[inv_labels[i]]],which="fixed")
    out_pars <- c(out_pars,as.numeric(t(matrix(ppars,nrow=length(ppars)/n_states,byrow = TRUE)[,inv_labels])))
    out_fixed <- c(out_fixed,as.logical(t(matrix(fpars,nrow=length(fpars)/n_states,byrow = TRUE)[,inv_labels])))
    tmp@transition[[i]] <- mod@transition[[inv_labels[i]]]
    if(!tmp@transition[[i]]@family$link=="identity") tmp@transition[[i]]@family$base <- labels[tmp@transition[[i]]@family$base]
    #out_pars <- c(out_pars,getpars(mod@transition[[inv_labels[i]]]))
  }
  # relabel response
  for(i in 1:n_states) {
    out_pars <- c(out_pars,unlist(lapply(mod@response[[inv_labels[i]]],getpars)))
    out_fixed <- c(out_fixed,unlist(lapply(mod@response[[inv_labels[i]]],getpars,which="fixed")))
  }
  tmp <- setpars(tmp,out_fixed,which="fixed")
  tmp <- setpars(tmp,out_pars)
  if(is(tmp,"depmix.fitted")) tmp@posterior <- viterbi(tmp)
  return(tmp)
}

# ORDERING STATES
order_mod_gauss <- function(mod) {
  ns <- nstates(mod)
  sum <- rep(0.0,ns)
  for(i in 1:ns) {
    # Expected return in each state calculation 
    sum[i] = mod@response[[i]][[1]]@parameters$mu
  }
  # reordering the states
  mod <- label_switch(mod, rank(sum))
  return(mod)
}

```

```{r, include=F}
# define a response class which only contains the standard slots, no additional slots
setClass("discgaus", contains="response", slots=c(breaks="numeric"))

# define a generic for the method defining the response class

setGeneric("discgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("discgaus"))

# define the method that creates the response class

setMethod("discgaus", 
          signature(y="ANY"), 
          function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), ...) {
            y <- matrix(y,length(y))
            x <- matrix(1)
            parameters <- list()
            npar <- 2
            if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
            if(!is.null(pstart)) {
              if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
              parameters$mu <- pstart[1]
              parameters$sigma <- pstart[2]
            }
            mod <- new("discgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, breaks=breaks)
            mod
          }
)

setMethod("show","discgaus",
          function(object) {
            cat("Gaussian with discrete support\n")
            cat("Parameters: \n")
            cat("mu: ", object@parameters$mu, "\n")
            cat("sigma: ", object@parameters$sigma, "\n")
          }
)

setMethod("dens","discgaus",
          function(object,log=FALSE) {
            p <- pnorm(object@breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@breaks[-length(object@breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
            if(log) return(log(p[as.numeric(cut(object@y, breaks=object@breaks))])) else return(p[as.numeric(cut(object@y, breaks=object@breaks))])
          }
)

setMethod("setpars","discgaus",
          function(object, values, which="pars", ...) {
            npar <- npar(object)
            if(length(values)!=npar) stop("length of 'values' must be",npar)
            # determine whether parameters or fixed constraints are being set
            nms <- names(object@parameters)
            switch(which,
                   "pars"= {
                     object@parameters$mu <- values[1]
                     object@parameters$sigma <- values[2]
                   },
                   "fixed" = {
                     object@fixed <- as.logical(values)
                   }
            )
            names(object@parameters) <- nms
            return(object)
          }
)

setMethod("getpars","discgaus",
          function(object,which="pars",...) {
            switch(which,
                   "pars" = {
                     parameters <- numeric()
                     parameters <- unlist(object@parameters)
                     pars <- parameters
                   },
                   "fixed" = {
                     pars <- object@fixed
                   }
            )
            return(pars)
          }
)

setMethod("fit","discgaus",
          function(object,w) {
            if(missing(w)) w <- NULL
            if(!is.null(w)) {
              negLL <- function(pars) {
                object <- setpars(object, c(pars[1], exp(pars[2])))
                -sum(w*log(dens(object)))
              }
            } else {
              negLL <- function(pars) {
                object <- setpars(object, c(pars[1], exp(pars[2])))
                -sum(log(dens(object)))
              }
            }
            pars <- optim(c(object@parameters$mu, log(object@parameters$sigma)), fn=negLL)$par
            object <- setpars(object,c(pars[1], exp(pars[2])))
            object
          }
)

setClass("truncdiscgaus", contains="discgaus", slots=c(min="numeric", max="numeric"))

setMethod("dens","truncdiscgaus",
          function(object,log=FALSE) {
            breaks <- c(object@min, object@breaks[object@breaks > object@min & object@breaks < object@max], object@max)
            p <- pnorm(breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(breaks[-length(breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
            p <- p/sum(p)
            if(log) return(log(p[as.numeric(cut(object@y, breaks=object@breaks))])) else return(p[as.numeric(cut(object@y, breaks=object@breaks))])
          }
)

setGeneric("truncdiscgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("truncdiscgaus"))

setMethod("truncdiscgaus", 
          signature(y="ANY"), 
          function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), min=0, max=20, ...) {
            y <- matrix(y,length(y))
            x <- matrix(1)
            parameters <- list()
            npar <- 2
            if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
            if(!is.null(pstart)) {
              if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
              parameters$mu <- pstart[1]
              parameters$sigma <- pstart[2]
            }
            mod <- new("truncdiscgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, breaks=breaks, min=min, max=max)
            mod
          }
)

order_mod_gauss <- function(mod) {
  ns <- nstates(mod)
  sum <- rep(0.0,ns)
  for(i in 1:ns) {
    # Expected return in each state calculation 
    sum[i] = mod@response[[i]][[1]]@parameters$mu
  }
  # reordering the states
  mod <- label_switch(mod, rank(sum))
  return(mod)
}

# define a response class which only contains the standard slots, no additional slots
setClass("vtdgaus", contains="response", slots=c(yield="numeric"))

# define a generic for the method defining the response class

setGeneric("vtdgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("vtdgaus"))

# define the method that creates the response class

setMethod("vtdgaus", 
          signature(y="ANY"), 
          function(y, yield, pstart=NULL,fixed=NULL, ...) {
            y <- matrix(y,length(y))
            x <- matrix(1)
            parameters <- list()
            npar <- 2
            if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
            if(!is.null(pstart)) {
              if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
              parameters$mu <- pstart[1]
              parameters$sigma <- pstart[2]
            } else {
              parameters <- list(mu=.5,sigma=1)
            }
            mod <- new("vtdgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, yield=yield)
            mod
          }
)

setMethod("show","vtdgaus",
  function(object) {
    cat("Gaussian with variable discrete support for percentage responses\n")
    cat("Parameters: \n")
    cat("mu: ", object@parameters$mu, "\n")
    cat("sigma: ", object@parameters$sigma, "\n")
  }
)

setMethod("dens","vtdgaus",
  function(object,log=FALSE) {
      # determine cuts for pnorm based on 
      p <- pnorm(sapply(object@y + .5*(1/object@yield),function(x) min(x,1.001)), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(sapply(object@y - .5*(1/object@yield),function(x) max(x,-0.001)), mean = object@parameters$mu, sd = object@parameters$sigma)
      norm <- (pnorm(1 + .001, mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(-0.001, mean = object@parameters$mu, sd = object@parameters$sigma))
      p <- p/norm
      # alternatively, normalize factor based on size of cuts
      #p <- pnorm(object@y + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@y - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma)
      #p <- p/(pnorm(1 + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(0 - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma))
    # probability when yield == 0 is always 1 
      p[object@yield == 0] <- 1
      if(log) return(log(p)) else return(p)
    }
)

setMethod("setpars","vtdgaus",
          function(object, values, which="pars", ...) {
            npar <- npar(object)
            if(length(values)!=npar) stop("length of 'values' must be",npar)
            # determine whether parameters or fixed constraints are being set
            nms <- names(object@parameters)
            switch(which,
                   "pars"= {
                     object@parameters$mu <- values[1]
                     object@parameters$sigma <- values[2]
                   },
                   "fixed" = {
                     object@fixed <- as.logical(values)
                   }
            )
            names(object@parameters) <- nms
            return(object)
          }
)

setMethod("getpars","vtdgaus",
          function(object,which="pars",...) {
            switch(which,
                   "pars" = {
                     parameters <- numeric()
                     parameters <- unlist(object@parameters)
                     pars <- parameters
                   },
                   "fixed" = {
                     pars <- object@fixed
                   }
            )
            return(pars)
          }
)

setMethod("fit","vtdgaus",
          function(object,w) {
            if(missing(w)) w <- NULL
            if(!is.null(w)) {
              negLL <- function(pars) {
                object <- setpars(object, c(pars[1], exp(pars[2])))
                -sum(w*log(dens(object)))
              }
            } else {
              negLL <- function(pars) {
                object <- setpars(object, c(pars[1], exp(pars[2])))
                -sum(log(dens(object)))
              }
            }
            pars <- optim(c(object@parameters$mu, log(object@parameters$sigma)), fn=negLL)$par
            object <- setpars(object,c(pars[1], exp(pars[2])))
            object
          }
)
```

```{r, include=F}
priordat <- avg_ret_df %>% filter(roundNum==1)
n_state_min <- 2
n_state_max <- 7

trust_simple <- trust_ctrl <- trust_coax <- trust_fullCtrst <- trust_prePost <- list()

# HMMs based on bins
for(i in n_state_min:n_state_max) {

  trust_simple[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))

  trust_ctrl[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*ctrl_only_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))

  trust_coax[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*coax_only_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))

  trust_fullCtrst[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*intervention_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))

  trust_prePost[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*pre_post_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))

}

# vtdgaus no contrasts
simple_HMMs <- ctrl_HMMs <- coax_HMMs <- fullCtrst_HMMs <- prePost_HMMs <- list()

for(i in n_state_min:n_state_max) {

  rModels <- rep(list(list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment))),each=i)

  simple_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_simple[[i]]@transition,prior=trust_simple[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)

  ctrl_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_ctrl[[i]]@transition,prior=trust_ctrl[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)

  coax_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_coax[[i]]@transition,prior=trust_coax[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)

  fullCtrst_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_fullCtrst[[i]]@transition,prior=trust_fullCtrst[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)

  prePost_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_prePost[[i]]@transition,prior=trust_prePost[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)

}
```

```{r, include=FALSE}

# fittedSimple <- fittedCoax  <- fittedCtrl  <- fittedFullCtrst  <- fittedPrePost  <- list()
# # increase default in multistart from 10 to 20. or set the same seed for every model
# 
# set.seed(20221028)
# for(i in n_state_min:n_state_max) {
# 
#   fittedSimple[[i]] <- multistart(simple_HMMs[[i]],nstart=20)
# }
# save(fittedSimple, file="fittedSimple.RData")
# ##############################
# 
# set.seed(20221028)
# for(i in n_state_min:n_state_max) {
#   fittedCtrl[[i]] <- multistart(ctrl_HMMs[[i]],nstart=20)
# }
# save(fittedCtrl, file="fittedCtrl.RData")
# ##############################
# 
# set.seed(20221028)
# for(i in n_state_min:n_state_max) {
#   fittedCoax[[i]] <- multistart(coax_HMMs[[i]],nstart=20)
# }
# save(fittedCoax, file="fittedCoax.RData")
# ##############################
# 
# set.seed(20221028)
# for(i in n_state_min:n_state_max) {
#   fittedPrePost[[i]] <- multistart(prePost_HMMs[[i]],nstart=20)
# }
# save(fittedPrePost, file="fittedPrePost.RData")
# #############################
# 
# 
# 
# for(i in n_state_min:n_state_max) {
#   fittedFullCtrst[[i]] <- multistart(fullCtrst_HMMs[[i]],nstart=20)
# }
# save(fittedFullCtrst, file="fittedFullCtrst.RData")
# ###############################

```

```{r, include=FALSE}
# # The full contrast model convergence was not attained. Here we use parameters of fitted PrePost model as initial values of the FullContrast model to speed up fitting and aim for faster convergence.

# newFull <- fittedFullCtrst
# for (ns in n_state_min :n_state_max){
# 
#   fmod <- fittedPrePost[[ns]]
#   origin_pars <- getpars(fmod)
#   numCovTr <- 4
#   numCovIn <- 2
#   
#   # create a new vector which has the right number of pars for the full contrast model. 
#   new_pars <- c(origin_pars[1:(ns*2)])
#   # from is state we are transitioning from 
#   for(from in 1:ns) {
#   mat <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
#   new_mat <- mat[,c(1:2,3,3,4,4)]
#   new_pars <- c(new_pars,as.numeric(new_mat))
#   }
#   
#   new_pars <- c(new_pars,origin_pars[(ns*numCovIn + 1 + (ns - 1)*numCovTr*ns + numCovTr*ns):length(origin_pars)])
#   
#   newFull[[ns]] <- setpars(newFull[[ns]],new_pars)
#   newFull[[ns]] <- fit(newFull[[ns]], emcontrol= em.control(maxit = 1000,random.start = FALSE))
# }
# 
# save(newFull, file="newFull.RData")

```

```{r, include=FALSE}

load("data/fittedSimple.RData")
load("data/fittedCtrl.RData")
load("data/fittedCoax.RData")
load("data/fittedFullCtrst.RData")
load("data/fittedPrePost.RData")
load("data/newFull.RData")

BICs_simple <- BICs_Ctrl <- BICs_Coax <- BICs_FullCtrst <- BICs_PrePost <-  BICs_newFull <- list()
for(i in n_state_min:n_state_max) {
  BICs_simple[[i]] <- BIC(fittedSimple[[i]]) 
  BICs_Ctrl[[i]] <- BIC(fittedCtrl[[i]])
  BICs_Coax[[i]] <- BIC(fittedCoax[[i]]) 
  BICs_FullCtrst[[i]] <- BIC(fittedFullCtrst[[i]]) 
  BICs_PrePost[[i]] <- BIC(fittedPrePost[[i]]) 
  BICs_newFull[[i]] <- BIC(newFull[[i]])

}

print("SIMPLE HMM models")
BICs_simple

print("HMM with contrast on post Control vs others")
BICs_Ctrl

print("HMM with contrast on post Coax vs others")
BICs_Coax

print("HMM with Pre vs Post Contrast")
BICs_PrePost

print("HMM with contrast levels Pre, Post Control and Post Coaxing")
BICs_FullCtrst

print("HMM with contrast levels Pre, Post Control and Post Coaxing, new fitting")
BICs_newFull

df_bics <- cbind(2:7,as.numeric(BICs_simple[2:7]), as.numeric(BICs_Ctrl[2:7]),as.numeric(BICs_Coax[2:7]), as.numeric(BICs_PrePost[2:7]), as.numeric(BICs_newFull[2:7]))
df_bics

```

```{r table-BICs-coax, warning = FALSE, echo=FALSE, ft.align="center", tab.id='table-BICs-coax', label='table-BICs-coax'}

data.frame(df_bics) %>% 
  `colnames<-` (c("Number of states","HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost","HMM-full")) %>%
  mutate_if(is.numeric, format, digits=4,nsmall = 0, big.mark = ",") %>% 
  knitr::kable(.,booktabs = TRUE,
  caption = 'Table of BICs for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>% kable_styling(latex_options="scale_down")
```

To characterise differences between participants' behavior in the intervention compared to the control condition following the manipulation, we analyse their observed returns using hidden Markov models.  Here we present the results from fitting the HMM models to trustee data using various contrasts that distinguish between pre and post-maipulation and/or between conditions.

We distinguish between five types of models: First, we fit a simple model where we assume that the transition function between states depends only on the investment (HMM-inv). This specification does not distinguish between pre- and post-manipulation games, nor does it distinguish between control and intervention conditions. It simply assumes that the way the investment affects the transition function of the trustee is the same regardless of which Game number and condition the data is from. Second, we specify a model for the transition function where we contrast two groups: Pre and Post Intervention, irrespective of the condition (HMM-prepost). Alternatively, we also specify three other models with contrasts distinguishing between pre and post intervention and the condition.  A model that contrasts the post-intervention condition to the pre-intervention and both control conditions (HMM-coax). Another model that contrasts the post-control condition to the pre-control and both intervention conditions (HMM-ctrl). Finally, in a full contrast model, both pre-control and pre-intervention groups are coded as one group, another group consists of post-control and a third group of post-intervention condition (HMM-full). For all five specifications, we fit various HMMs with a number of states varying between 2 and 7 and select the model with the lowest BIC.

Table \ref{tab:table-BICs-coax} shows the BICs of the various fitted models for an assumed number of states between 2 and 7.  For a simple model without any contrasts (HMM-inv) and a model with post-control only contrast (HMM-ctrl) we find a 6-state model to be best fitting. If the contrast is between the post-intervention group and all the other groups (HMM-coax), then a 7 state model is best fitting. When the contrast is comparing only pre and post Intervention groups (HMM-prepost), a 5 state model fits best. Finally, when we distinguish between pre-manipulation, post-control and post-intervention (HMM-full), we find that a 5 state model fits best. Since we only fit models between 2 and 7 states, it is possible that for those where we find the 7 state model to be best fitting, models with a higher number of states could fit the data better. We decided to stop at 7 states for computational cost reasons and because the interpretation of models with a higher number of states becomes complex.

```{r, include=FALSE}
summary(fittedSimple[[5]])

logLik(fittedSimple[[5]])
logLik(fittedCtrl[[5]])
logLik(fittedCoax[[5]])
logLik(fittedPrePost[[5]])
# logLik(fittedFullCtrst[[5]])
logLik(newFull[[5]])

# Nested model comparison for 5 states, with and without intervention contrast. llratio test shows no effect, meaning interaction term addition does not change goodness of fit of model. 
llratio(newFull[[5]], fittedSimple[[5]])

llratio(fittedCtrl[[5]],fittedSimple[[5]])
llratio(fittedCoax[[5]],fittedSimple[[5]])
llratio(fittedPrePost[[5]],fittedSimple[[5]])

llratio(newFull[[5]],fittedCtrl[[5]])
llratio(newFull[[5]],fittedCoax[[5]])
llratio(newFull[[5]],fittedPrePost[[5]])

```

In order to compare the goodness of fit of the various models, we test the relative likelihood of models using a likelihood ratio test. This procedure is useful to compare the most complex model (HMM-full, which allows for differences between pre-intervention and the two conditions post-intervention) to nested models which equate behaviour in some if the stages and conditions.

<!-- We start by comparing HMM-full with HMM-inv. We find that HMM-full fits the data better than HMM-inv ($\chi^2(84) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$). Likewise HMM-ctrl fits better than HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedCtrl[[5]]))) , 2)`$, $p < .001$). The same is true for HMM-coax compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedCoax[[5]]))) , 2)`$, $p < .001$) and HMM-prepost compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedPrePost[[5]]))) , 2)`$, $p < .001$). HMM-inv being the worst fitting model compared to the others indicates the existence of differentiated behavior pre vs post manipulation and/or between the control and intervention groups.  -->

Using likelihood ratio tests, we find that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCtrl[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCoax[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedPrePost[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$). This is consistent with a differentiated behavior of the trustees between all three groups: the post-intervention group, the post-control group and the pre-manipulation group.

<!--    ORDER THE STATES    -->
```{r, include=FALSE}
tr_fdmod_5 <- order_mod_gauss(newFull[[5]])
```

```{r, include=FALSE}

state1 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[1]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))

state2 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[2]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))

state3 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[3]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))

state4 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[4]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))

state5 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[5]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))

returns <- seq(0.025,0.975,length=20)

response_best_mod <- as.data.frame(cbind(returns,state1,state2,state3,state4,state5)) %>% 
  pivot_longer(cols=c("state1","state2","state3","state4","state5"),
                    names_to='Trustee_state',
                    values_to='probability')

```

```{r trusteeHMMPlot, fig.cap="Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model",fig.align="center", fig.width=6, fig.height = 4}

ggplot(response_best_mod,                            
       aes(x = returns,
           y = probability,
           fill = Trustee_state)) +
  geom_bar(stat = "identity",
           position = "dodge") + 
  labs(fill='Latent trustee State') +
  theme_bw() + 
  theme(legend.position = "bottom")

```

Using the best fitting model (HMM-full), Figure \ref{fig:trusteeHMMPlot} shows the distribution of the participants' returns conditional on the latent state they are in. The states are ordered based on the mean of the Gaussian distribution fitted to the response (percentage return). State 1 represents the state in which the returns have have the lowest underlying mean, and state 5 is the state in which the returns have the highest underlying mean. The higher the state number the more pro-social the policy adopted. More specifically, state 1 can be thought of as a non-cooperative state in which returns are low and close to 0, meaning that the trustee is keeping most of the tripled investment. State 2 is a state where the average return is around the investment sent and can be interpreted as a cautious state in which the return on trust is small. States 3, 4 and 5 are increasingly cooperative states. For instance, in state 5, the average return is close to two thirds of the tripled investment, meaning the trustee is keeping an amount similar to the investment that was sent and returning to the investor double the investment.

Figure \ref{fig:plotTransitionsDiscGaus} shows the transition between states as a function of the investment received for each group (pre-manipulation, post-control and post-intervention) using results from the best fitting model: HMM-full. The best fitting HMM model has multiple states and a high number of parameters. We can nonetheless focus on particular states linked to the breakdown and repair of cooperation. For instance, focusing on the transition functions to state 1 (the lowest return state with returns close to 0) from higher return states, we can compare the  post-control group to the post-intervention group. The red line representing the probability of transitioning to the low-return state 1 when the investment is close to 0 is lower in the intervention group compared to the control group when the trustee is in a relatively pro-social state (states 3 to 5). This is pointing towards more "forgiving" behavior where participants in the intervention group were less likely to transition to this anti-social state compared to the control group.

```{r, include=FALSE}

plot_state_transitions <- function(fmod, numCovIn, numCovTr) {

  #print(getpars(fmod))
  ns <- nstates(fmod)

  trans_prob <- data.frame(
    from = rep(1:ns, each=100*ns),
    to = rep(1:ns, each=100),
    investment = seq(0,20,length=100),
    prob_pre = 0,
    prob_ctrl = 0,
    prob_coax =0
  )

  y0 <- matrix(0.0,ncol=ns, nrow=100)
  y1 <- matrix(0.0,ncol=ns, nrow=100)
  y2 <- matrix(0.0,ncol=ns, nrow=100)

  for(from in 1:ns) {
  pars <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
  #print(pars)

    for(to in 1:ns) {
        x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"investment"]
        y0[,to] <- exp(pars[to,1] + pars[to,2]*x)
        y2[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,3]*1 + pars[to,5]*x )
        y1[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,4]*1 + pars[to,6]*x )
    }
    y0 <- y0/rowSums(y0)
    y1 <- y1/rowSums(y1)
    y2 <- y2/rowSums(y2)

    for(to in 1:ns) {
      trans_prob$prob_pre[trans_prob$from == from & trans_prob$to == to] <- y0[,to]
      trans_prob$prob_ctrl[trans_prob$from == from & trans_prob$to == to] <- y1[,to]
      trans_prob$prob_coax[trans_prob$from == from & trans_prob$to == to] <- y2[,to]
    }
  }

  saveRDS(trans_prob, "data/trans_prob.RDS")

  return(trans_prob)

  #  p_pre <- ggplot(trans_prob,aes(x=investment,y=prob_pre, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function pre manipulation") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
  # 
  # p_ctrl <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post control") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
  # 
  # p_coax <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post intervention") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
  # 
  # grid.arrange(p_pre, p_ctrl,p_coax, nrow=3, ncol=1)

}

# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)

```

```{r,include=F}

trans_prob <- readRDS("data/trans_prob.RDS")

ctrl_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + 
  geom_line() + 
  geom_line(aes(y=prob_pre),linetype="dotted") +
  facet_wrap(~from) + 
  ylim(c(0,1)) + 
  ggtitle("Transition function pre- and post-control manipulation") + 
  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
  theme_bw()

coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
  geom_line() + 
  geom_line(aes(y=prob_pre),linetype="dotted") +
  facet_wrap(~from) + 
  ylim(c(0,1)) + 
  ggtitle("Transition function pre- and post-intervention manipulation") + 
  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
  theme_bw()

```

```{r plotTransitionsDiscGaus, fig.cap="Transition function for the HMM-full trustee model. Each panel represents the state transitioned from, and each color the state transitioned to. Solid lines show estimated transition probabillities post-manipulation. Dotted lines show the same probabilities prior to the manipulation",fig.align="center", fig.width=6, fig.height = 7 }

grid.arrange(ctrl_pre_plot , coax_pre_plot , nrow=2, ncol=1)

# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)

```

<!-- To explore the differences in transition probabilities between the control and coaxing conditions, we can choose an investment and compare the probabilities of transitioning between States. For instance, in case the trustee is low in trustworthiness (State 1), and the investor sends an average amount, we can compare the likelihood of the trustee transitioning away from the low trustworthiness state. Assuming an investment of 10 (half the endowment), The trustee remains in State 1 with around $85\%$ probability in the control condition, but only $67\%$ probability after the coaxing intervention. Likewise, assuming the trustee is in State 4, and receiving a low investment of 2, there is a much lower probability ($0.2\%$) of transitioning to low trustworthiness state in the coaxing condition compared to the control condition ($21\%$). -->

```{r, include = FALSE}
set.seed(20221010)
# Get investor posterior states from model and add to data table

# mention we are using local decoding (refer to the book). 
predTrStates <- posterior(tr_fdmod_5, type="local")
avg_ret_df$TrState <-  factor(predTrStates, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))

# avg_ret_df$TrState <-  factor(predTrStates, levels= c(5,4,3,2,1),labels=c("5","4","3","2","1"))

# predTrStates <- posterior(tr_fdmod_5)
# avg_ret_df$TrState <-  factor(predTrStates$state, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))

library(dplyr)
temp_df <- avg_ret_df %>% dplyr::select(roundNum,investment,returns, next_investment, TrState)
```

```{r postStatesBestMod,  echo=FALSE, fig.cap = "Distribution of posterior trustee states post manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.", fig.align="center", fig.width=8, fig.height = 4}
# investor real state distribution (posterior)
ggplot(avg_ret_df %>% dplyr::filter(gameNum.f=="post")) +
  geom_bar(aes(x = roundNum, group = TrState, fill = TrState),  position = position_stack(reverse = TRUE)) + 
  facet_wrap(~condition.f) +  
  labs(x = "Round", fill='Posterior trustee state') +
  theme_bw() +
  theme(legend.position = "bottom")

```

```{r, include= F}

props_df_5 <- avg_ret_df %>% 
  filter(gameNum.f=="post", roundNum== 5) %>% 
  group_by(condition.f,TrState) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

prop.test(c(11,29), c(159,159))

props_df_14 <- avg_ret_df %>% 
  filter(gameNum.f=="post", roundNum== 14) %>% 
  group_by(condition.f,TrState) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

prop.test(c(35,68), c(159,159))

props_df_13 <- avg_ret_df %>% 
  filter(gameNum.f=="post", roundNum== 13) %>% 
  group_by(condition.f,TrState) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

# compare proportions in state 1 in round 13 between conditions
prop.test(c(48,72), c(159,159))

# compare proportions in states 4 and 5  in round 13 between conditions
prop.test(c(48,18), c(159,159))

# props_df_12 <- avg_ret_df %>% 
#   filter(gameNum.f=="post", roundNum== 12) %>% 
#   group_by(condition.f,TrState) %>% 
#   summarise(n = n()) %>%
#   mutate(freq = n / sum(n))

```

To quantitatively explore the differences in transition probabilities between the control and intervention conditions, we can estimate from the model, using local decoding methods, the most likely posterior state of the trustee participants by round given the actions they have taken. Figure \ref{fig:postStatesBestMod} shows the distribution of these states by round for both the intervention and control groups post manipulation. We can see that participants were more likely to be in a lower return state in the control condition compared to the intervention condition. For instance, in round 5, state 1 was the most likely posterior state for $7$% of participants in the intervention condition compared to $24$% in the control condition, indicating a higher proportion of participants were in the lowest trustworthiness state without the intervention, and the differences between proportions were significant ($\chi^2(1) = 8.26, p < 0.01$). For the post defection trial after the intervention (round 14), state 1 was the most likely state for 22% of participants in the intervention condition compared to 43% in the control condition, and the differences between proportions were significant ($\chi^2(1) = 14.70, p < 0.001$).

It is also noteworthy that there is an important heterogeneity in participants' most likely posterior state when faced with a situation like the one described during the intervention manipulation. Focusing on round 13 (the round where the low investment was sent post manipulation), we can see that a high proportion of participants ($30.2$%) in the intervention condition were in a low-return state. This group does not exhibit a behaviour consistent with the goal of the intervention. By contrast, another group exhibited behavior that is likely to be driven by assimilating the message from the coaxing manipulation, through transitioning to a high-return state even in the face of a low investment, which would be consistent with a coaxing behavior. Whilst only 11.3% in the control condition were in states 4 and 5 following the pre-programmed low investment, 30.3% of participants in the intervention condition were estimated to be in those states. The difference between the proportions is  statistically significant ($\chi^2(1) = 16.08, p < 0.001$). These differences can be seen as an indication of important heterogeneity in the effectiveness of the intervention.

# Discussion

<!-- QH : I'd suggest introducing issues around trust in borderline a bit more early on, aslo discussing variability in treatment response, and the quest for mechanisms. This then forms an interesting platform for the discussion. The other aspect that probably needs discussing a bit more is the relationship between behaviour and emotion. -->

In this experiment, we made human participants face artificial computer agents endowed with the ability to transition between latent states and react to the participants' returns. The number of states, the policy in each state as well as the way these agents transitioned between states was based on estimating a hidden Markov model to behaviour from real human participants. On average, we saw the emergence of cooperative behavior with investment and returns in line with what is reported in human dyadic interaction in the repeated trust game [@charness_investment_2008; @fiedler_social_2011]. The emergence of cooperative behavior and comments projecting human attributes on the opponent from the answers to the debrief questions, point to the potential of these agents to mimic human behavior in economic games whilst offering a higher degree of experimental control.

The intervention's aim was to articulate the effect of acting on impulse in case of a transgressive action from the investor in the form of a one-off low investment. It explained that reciprocating this non-cooperative action might signal untrustworthiness and lead to a more permanent breakdown of cooperation. It also suggested an alternative strategy of coaxing the investor back into cooperation. When the agent defected as programmed, yielding a situation similar to the one presented in the intervention, we saw that the intervention led to higher percentage returns post defection compared to the control intervention, as intended. What was also notable, is that the intervention led to generally higher returns in post intervention, indicative of more cooperative behavior even before the defection trial. The question therefore is: what are the reasons for participants to engage in higher cooperative actions even in the absence of a sudden low investment? One possibility is that they have simply learned that by returning more, the investment on the next trial would be higher. If that was the case, we would expect a similar increase in percentage returns in the control condition, which we didn't find. Another possibility is that on average, the second player they faced invested more which prompted positive reciprocity in the human trustees. As all players were programmed in the same way, any difference would be due to participant's actions. Likewise, participants rated both players similarly on relevant attributes of cooperativeness and trust. The higher returns are thus unlikely to be driven by different beliefs about the investor. A likely explanation for overall higher trustworthiness as measured by higher percentage return post investment is that participants, on average, interpreted the intervention message as an argument for more pro-social behavior, irrespective of the investor's actions.

It is noteworthy that there were important individual differences in the percentage return changes post vs. pre intervention, which can be seen as a proxy for the intervention effectiveness. Some participants might not have been convinced by the intervention's message and decided to reduce their returns both pre and post defection in the second trust game, while others increased their returns in both phases. This raises important questions for the measurement of intervention effectiveness. Recent work has shed the light on the important heterogeneity inherent in how disorders are categorised: This heterogeneity arises from the view that mental health problems should be viewed as complex systems, or interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017]. This view was used to justify computational psychiatry's difficulty in establishing differential and reliable predictors of likely treatment responses [@hitchcock_computational_2022]. But if a healthy group's reaction to a relatively explicit intervention is itself heterogeneous as we have shown in this experiment, then the issue of variable treatment responses might the result of the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself.

As such, a rigorous exploration of the determinants of inter-individual differences to an intervention in the general patient population is required. In our case, judging by the inter-individual heterogeneity in responses, some people may not have been convinced that a coaxing behavior was a good way to establish long term cooperative outcomes, and their need to "punish" the other player for their low investment may have been more pertinent than what we suggested. This was also evident from the participants' replies to a question about whether they would change their behavior, just after seeing the intervention manipulation. An important avenue is to explore the role of emotion in decision making in such situations. We could aim to measure emotional reactions more accurately and explore whether specific emotions mediate the relationship between the investment received and the decision of what proportion to return. Measuring the emotions using the twos axes of valence and arousal could be improved: Results indicate that these concepts may not have been well understood by participants since we would not expect to see low arousal after the pre-programmed defection of the investor.

The effect of this short intervention was not transferred to the Repeated Prisoner's Dilemma game. In this game, the rate at which the cooperative option was chosen was not significantly different between the control and intervention groups, both pre and post defection. Since the prisoner's dilemma is a very popular economic game, it is possible that participants had strong prior preferences towards which strategy they would adopt, irrespective of whether or not they received the intervention. As such, this paradigm might not be the best test case for knowledge transfer. For those that took on the intervention message and showed coaxing behavior in the second trust game, the fact that the investor still defected in the final rounds might have reinforced the idea that not reciprocating negative behavior is a losing strategy after all.

Overall, it is remarkable that such a short intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments can lead to such differentiated behavior. In future studies, we aim to explore the effects of different cognitive interventions and improve the experimental design in multiple ways. First, the intervention could benefit from being more interactive, with visual inputs such as cartoons or short videos, rather than only text, which can be more cumbersome to read and lead to lower engagement. Second, we selected trustees from the general population, which might not suffer from the inability or unwillingness to repair relationships due to accidental breakdown of trust that characterises some mental health disorders such as BPD. As such, it would be interesting to contrast these results with findings from experiments involving trustees that are selected from patient populations known to suffer from difficulties in maintaining or repairing cooperative interactions. Third, as we explained above, the choice of the task to measure transfer of intervention learning could be made better by involving less popular paradigms. The high popularity of the Prisoner's Dilemma and the strategy of playing tit-for-tat may have resulted in a strong prior on which strategy to adopt in this game irrespective of the intervention. We opined that asking people about how they felt in the control condition might have affected how they behaved and might constitute an intervention in itself. However, being able to compare the differential impact of the intervention on the emotional interpretation of the opponent action between an intervention and control conditions could lead to insights on the mechanism through which the intervention affects the emotional reaction to the opponent's actions.

# Conclusion

We explored the effect of a short cognitive intervention on the behavior of human trustees facing adaptive artificial agents endowed with multiple latent behavioral states. Each state defines different levels of a cooperative response with the agent able to transition between these states based on the behavior of the human opponent. Feedback from participants indicated that these agents were sometimes perceived as humans. Their strategy led to emergent cooperative behavior when playing the repeated trust game with human players. The intervention, promoting a less impulsive reaction to transgressive actions, led to coaxing behavior and less negative reciprocity when the investor sent a very low investment. It also led to more trustworthy behavior prior to the pre-programmed defection trial  and to coaxing behavior after defection. Whilst this intervention effect varied between participants and generally was not transferred to a new game, an HMM analysis of participant's play post intervention showed differentiated patterns of transitions between latent states, indicating a change in the effect of the opponent action on the probability of transitioning between latent mental states.

# References

### 2023-02-15 article.Rmd
figures pooled

@@
 abstract: | 
-  abstract to be added.
+  Social trust is an important building block of strong social bonds, and its absence is a risk factor for social     dysfunction.
+As such, interventions to foster and strengthen trust-based cooperation are highly desirable.
+Using the repeated Trust Game paradigm, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a pre-programmed, one-off defection by the opponent.
+Over two games, participants are given the role of the trustee and face what they believe are two different players.
+In between games, they either receive a cognitive intervention  or not.
+In reality, participants face the same computerised agent in both instances, which is programmed to play according to an HMM fitted to real players data.
+We saw the emergence of cooperative behavior in these games, consistent with what is expected when humans interact.
+This substanstiates the use of these AI agents as credible human opponents whilst affording a high degree of experimental control.
+The intervention led to more cooperative behavior both pre and post defection by the opponent.
+HMM modelling of participants actions shows participants in the intervention group had a lower probability of transitioning to non cooperative states.
+Posterior latent state analysis also showed a  higher proportion of players best described by more cooperative latent states in the intervention condition compared to the control condition.
 
@@
 In between games, they either receive a cognitive intervention (intervention condition) or not (control condition, where participants are asked to solve anagrams).
-In reality, participants face the same computerised agent in both instances, which is programmed to play according to an HMM fitted to rela players data.
+In reality, participants face the same computerised agent in both instances, which is programmed to play according to an HMM fitted to real players data.
 We explore whether the intervention has an effect on the behaviour of the trustee and whether the learning is transferred to a new repeated Prisoner's Dilemma game when facing a seemingly new player.
@@
 
-```{r interventionSlide,fig.cap = "Screenshot of the main  slide in the intervention condition", fig.align='center', out.width="80%"}
+```{r interventionSlide,fig.cap = "Screenshot of the main  slide in the intervention condition", fig.align='center', out.width="80%"du}
 
@@
 
-```{r afexPLotPctRet, fig.cap="Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition",fig.align="center", fig.width=6, fig.height = 4}
-afex::afex_plot(mod_returns_pct, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
+```{r, include=FALSE}
+pctRet_all <- afex::afex_plot(mod_returns_pct, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
             mapping = c("linetype", "shape", "fill"),
@@
   labs(y = "Percentage Return", x = "Game") + 
-  theme(legend.position = "bottom") +
-
-```
-
-Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:afexPLotPctRet}.
+  ggtitle("All rounds percentage returns") + 
+  theme(plot.title = element_text(size = 10)) +
+  theme(legend.position = "bottom")
+
+```
+
+Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in panel A of Figure \ref{fig:violinPanels}.
 If the intervention has an effect, then we should expect a higher increase in returns after the intervention compared to the control condition, which should be evident from an interaction between Condition (intervention vs control) and Game-number (pre- vs post-manipulation).
@@
 
-```{r afexPlotInv, fig.cap="Marginal means and distributions of investments over all rounds for HMM agents playing the role of the investor, by Game number and Condition.",fig.align="center", fig.width=6, fig.height = 4}
-
-afex_plot(mod_invs, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
+```{r, include=FALSE}
+
+inv_all <- afex_plot(mod_invs, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
             mapping = c("linetype", "shape", "fill"),
@@
   theme_bw() + 
+  ggtitle("All rounds investments") +
   labs(y = "HMM Investment", x = "Game") + 
+  theme(plot.title = element_text(size = 10)) +
   theme(legend.position = "bottom")
@@
 We find a main effect for both Condition ($F(1,317) = 8.7, p = 0.003$) and Game-number($F(1,317) = 8.3, p = 0.004$).
-As can be seen in Figure \ref{fig:afexPlotInv}, investment was higher in the intervention compared to the control condition across games ($p=0.003$).
+As can be seen in panel D of Figure \ref{fig:violinPanels}, investment was higher in the intervention compared to the control condition across games ($p=0.003$).
 Across conditions, investment was also higher in the second game compared to the first ($p=0.003$).
@@
 We fit the same linear mixed effects model to percentage returns as the one for the full data.
-Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:preCoaxPlot}.
+Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in panel B of Figure \ref{fig:violinPanels}.
 We do find an interaction effect between Condition and Game number ($F(1,317.99) =  17.1, p < 0.001$).
@@
 
-```{r preCoaxPlot, fig.cap="Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.",fig.align="center", fig.width=6, fig.height = 4}
-afex_plot(mod_returns_pre, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
+```{r, include=F}
+pctRet_pre <- afex_plot(mod_returns_pre, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
             mapping = c("linetype", "shape", "fill"),
@@
   labs(y = "Percentage Return", x = "Game") + 
+  ggtitle("Pre defection trials percentage returns")+
+  theme(plot.title = element_text(size = 10)) +
   theme(legend.position = "bottom")
@@
 
-```{r postCoaxPlot, fig.cap="Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.",fig.align="center", fig.width=6, fig.height = 4}
-afex_plot(mod_postcoax_trust, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
+```{r, include=FALSE}
+pctRet_post <- afex_plot(mod_postcoax_trust, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
             mapping = c("linetype", "shape", "fill"),
@@
   labs(y = "Percentage Return", x = "Game") + 
+  ggtitle("Post defection trials percentage returns")+
+  theme(plot.title = element_text(size = 10)) +
   theme(legend.position = "bottom")
@@
 
-Figure \ref{fig:postCoaxPlot} shows the marginal means of trustee returns and their distribution by Game-number and Condition.
+```{r violinPanels, fig.cap="Panel A: Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition.
+Panel B: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
+Panel C: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.
+Panel D:Marginal means and distributions of investments over all rounds for HMM agents playing the role of the investor, by Game number and Condition", fig.align="center", fig.width=6, fig.height = 6}
+
+ggpubr::ggarrange(pctRet_all, pctRet_pre, pctRet_post, inv_all, nrow=2, ncol=2, labels = c("A", "B", "C", "D"), common.legend = TRUE, legend = "bottom")
+```
+
+Panel C of Figure \ref{fig:violinPanels} shows the marginal means of trustee returns and their distribution by Game-number and Condition.
 We found a main effect of Condition with returns on the intervention group higher than returns in the control group (`r apa_print(pairs(postcoax_bycond))$full_result$intervention_control`).

### 2023-05-12 article.Rmd
revision QH comments by ismail

@@
 Over two games, participants are given the role of the trustee and face what they believe are two different players.
-In between games, they either receive a cognitive intervention  or not.
-In reality, participants face the same computerised agent in both instances, which is programmed to play according to an HMM fitted to real players data.
-We saw the emergence of cooperative behavior in these games, consistent with what is expected when humans interact.
-This substanstiates the use of these AI agents as credible human opponents whilst affording a high degree of experimental control.
+In between games, they either receive a brief cognitive intervention or not.
 The intervention led to more cooperative behavior both pre and post defection by the opponent.
@@
 Absent a history of interaction, one needs to decide whether to take the risk of trusting others.
-@rousseau_introduction_1998 define trust as a "psychological state comprising the intention to accept vulnerability based upon positive expectations of the intentions or behavior of another".
-As such, whilst trusting and being able to signal trustworthiness are necessary conditions for building and maintaining important social bonds,  the challenge of trust is that it is by construction a risky endeavour.
+The challenge of trust is that it is by construction a risky endeavour.
 For example, if we deem a person trustworthy, we might decide to take the risk of investing in the relationship hoping for a collaborative outcome.
 If we misplace our trust, this can come at a high cost to us.
-Not trusting others is also risky since opportunities may be foregone, and any substitution for trust, such as excessive suspicion, over-reliance on self and other maladaptive strategies are likely to add burden and costs to a person.
+Not trusting others is also risky since opportunities for cooperation may be foregone.
+
+<!-- and any substitution for trust, such as excessive suspicion, over-reliance on self and other maladaptive strategies are likely to add burden and costs to a person. -->
 
@@
 Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders.
-@fonagy_role_2014 identified epistemic trust as an important function of early attachment relationships.
-Epistemic trust can be defined as the trust in the authenticity and personal relevance of interpersonally transmitted knowledge.
-It enables individuals to learn from their social environment in dynamic social and cultural contexts.
-Importantly, it allows the individual receiving social information to let go of their natural self-protective vigilance, dubbed hyper-vigilance.
-@fonagy_mentalizing_2017 identified hyper-vigilance, or lack of "epistemic trust" which may partially be rooted in adverse childhood experiences, as a key risk factor for the emergence of multiple mental health disorders such as Borderline Personality Disorder and Anti-Social Personality Disorder.
-
-A popular paradigm in the study of the emergence and maintenance of trust is the repeated trust game [@joyce_trust_1995].
+@fonagy_role_2014 identified epistemic trust, or the belief in the authenticity and personal relevance of interpersonally transmitted knowledge, as an important function of early attachment relationships.
+It allows the individual receiving social information to let go of their natural self-protective vigilance, which can become a pathological hypervigilance frequently observed after traumatic experiences and a key factor for the emergence of multiple mental health disorders [@fonagy_mentalizing_2017].
+
+<!-- A well-established paradigm in the study of the emergence and maintenance of trust is the repeated trust game [@joyce_trust_1995].
 In this game, one player takes the role of the "investor" and is provided with a fixed endowment at the start of each trial.
@@
 This scenario would constitute a cooperative exchange and would be mutually beneficial.
-However, cooperation in this setting is prone to be broken through intentional or simply misinterpreted actions on behalf of either player [@bendor_when_1991].
+However, cooperation in this setting is prone to be broken through intentional or simply misinterpreted actions that can convey lack of trust or trustworthiness such as low investments and returns [@bendor_when_1991].
 In order to repair a damaged cooperative equilibrium, players need to infer that their behaviour has violated social norms and offer amends through generous actions at potentially a high cost to them.
 @king-casas_rupture_2008 links the breakdown of cooperation in trustees with Borderline Personality Disorder to the absence or reduction of activation in brain regions associated with the perception of norm violations.
+-->
 
 Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions to foster and strengthen trust-based cooperation would be highly beneficial to society.
-Such an intervention would allow people to more easily repair broken relationships, and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
-In the context of social dilemmas, there have been many attempts at fostering cooperative outcomes through either mechanism design, environment modifications or other.
-
-Mechanism design, pioneered by @vickrey_counterspeculation_1961, is a field that studies incentive alignment and looks for ways to promote social welfare or revenue maximization, despite self-interest of the individual actors.
+Such interventions would allow people to more easily repair broken relationships, and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
+
+<!-- Mechanism design, pioneered by @vickrey_counterspeculation_1961, is a field that studies incentive alignment and looks for ways to promote social welfare or revenue maximization, despite self-interest of the individual actors.
 In the context of social dilemmas, key mechanisms were explored with good effect to foster and maintain the cooperative outcome.
@@
 @fiedler_effect_2017 found that the introduction of a third party that monitors the investments and returns of the players led to more cooperative behavior, even when the third party had no ability to reward or punish the players.
-
-Rather than try to modify the mechanism of the game, other approaches focused on intervening directly on the participants.
-@drazkowski_gratitude_2017 investigated the effect of expressing gratitude on later behaviour in the trust game.
-The gratitude intervention consisted of thinking about and writing down 5 things that the participants were grateful for in their life.
-The exercise was repeated over three sessions.
-Those completing the gratitude intervention reported more positive emotions and this mediated an increase in their investment in one-shot trust games.
-@burnham_friend-or-foe_2000 primed participants by introducing the investor as either a "friend" or "foe".
-They found that this priming produces significant differences in both trust (measured by the proportion of endowment sent) and trustworthiness  (measured by the proportion returned) with participants in the "friend" treatment exhibiting over twice as much trustworthiness than those in the "foe" condition.
+-->
+
+A well-established paradigm in the study of trust is the repeated trust game [@joyce_trust_1995].
+To encourage the emergence and maintenance of trust in this setting, some studies focused on modifying the game mechanism [@charness_investment_2008; @fiedler_effect_2017].
+Others chose to intervene directly on the participants.
+For example, @drazkowski_gratitude_2017 found that trust was increased when participants were asked to think about and write down five things that they were grateful for.
+@burnham_friend-or-foe_2000 found that trust was also increased when participants were primed with the concepts of friend and foe.
 
@@
 
-<!-- why this particular intervention?
-Why use this intervention for repair of trust?
-One motivation which you don't mention is the motivation to use cognitive probes to understand mechanisms of psychotherapy itself - this may be worth introducing.
--->
-
 In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of interpersonal dysfunction in BPD patients.
-Whilst there is no proven pharmacological therapy for BPD, some forms of psychotherapy such as Mentalisation Based Therapy (MBT) and Dialectical Behavior Therapy (DBT), have been clinically validated as efficacious approaches to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
+Whilst there is no proven pharmacological therapy for BPD, some forms of psychotherapy such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993], have been clinically validated as efficacious approaches to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
 However, these therapies suffer from a high variability in treatment responses.
 Determining which interventions are effective for particular patients has been very challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
-One promising approach is the study of how specific psychotherapeutic treatment components affect quantitative markers of behavior such as those inferred through computational modelling techniques [@huys_computational_2016].
-As such, using specific cognitive probes inspired by therapeutic interventions complemented by computational modelling of behavior in tasks, may allow us to uncover cognitive mechanisms targeted by common forms of psychotherapy, as well as evaluate whether knowledge about these different mechanisms can improve the targeting of existing psychotherapies to different individuals.
-
-In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a pre-programmed, one-off low investment sent by the investor.
+One promising approach is the study of how specific psychotherapeutic treatment components affect quantitative markers of behavior such as those inferred through computational modelling techniques [@huys_computational_2016; @reiter_neuro-cognitive_2021].
+As such, using specific cognitive probes inspired by therapeutic interventions complemented by computational modelling of behavior in tasks, may allow us to uncover cognitive mechanisms targeted by common forms of psychotherapy.
+This may in turn form the basis for targeting of existing psychotherapies to different individuals.
+
+In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a pre-programmed, one-off low investment sent by an computer investor.
 The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation.
-It explicitly articulates the advantages of adopting a coaxing behavior in this setting, and as such, is directly relevant to the task at hand and is very clear about the desired behavior without being overly directive.
-The idea being that if participants show no response to this type of direct intervention in this setting, then other forms of intervention that may target general processes such as better emotional regulation or better mentalising are then even less likely to show a benefit.
-As such this intervention can be seen as a litmus test for the success of more "general" forms of cognitive interventions.
-Moreover, in the event of the intervention's failure, analysis of the resistance to an explicit intervention itself might be worthy of further investigation to understand the mechanism behind the lack of success.
-
-In this experiment, participants are given the role of the trustee and are randomly assigned to either a control group or an intervention group.
+Participants are given the role of the trustee and are randomly assigned to either a control group or an intervention group.
 They play two instances of the repeated Trust Game facing what they believe are two different players.
@@
 
-<!-- DATA WRANGLING  -->
 ```{r dataLoad, include=FALSE }
@@
 
-<!-- Before you introduce the tasks, you need to introduce the overall design of the experiment, i.e.
-the before/after randomized controlled experimental setup.
-A figure to illustrate this is a good idea.
-You could then have a section called 'measures' which includes details about each of the tasks (probably including the HMM), questionnaires and also emotion grid, and a section called 'interventions', which contains both the low return and the actual intervention.
--->
-
 # Method
@@
 ## Participants and Design
-A total of 318  participants were recruited on the Prolific Academic platform.
+
+A total of 318 participants were recruited on the Prolific Academic platform (prolific.co).
 The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years.
@@
 
-```{r timeline,fig.cap = "Overview of the timeline of the experiment detailing the various phases participants go through.", fig.align='center', out.width="80%"}
+```{r timeline, fig.cap = "A) Experiment overview.
+After playing 15 rounds of a repeated trust game (RTG) as trustee, participants were randomized to either receive the control or active intervention.
+They then played the second set of 15 rounds of RTG (again as trustee) to examine intervention effects, and 7 rounds of a repeated prisoner’s dilemma to examine generalization of intervention effects.
+Finally, participants answered questionnaires and were debriefed.", fig.align='center', out.width="80%"}
 
@@
 
-Figure \ref{fig:timeline} shows the timeline of the experiment.
+<!-- Figure \ref{fig:timeline} shows the timeline of the experiment.
 After reviewing an information sheet about the experiment, participants were informed that there would be three phases to go through, with them facing a different opponent in each phase.
@@
 This was the moniker used for the repeated trust game, and a total of 15 rounds were played.
-
-After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.
+Participants were then randomly assigned to either a control or intervention condition.
+-->
+
+<!-- <!-- After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.
 A comprehension quiz on the trust game followed the instructions.
@@
 At the end of the game, participants were asked to rate the player they were facing on 4 attributes using a scale from 1 to 10: Trustworthiness, friendliness, cooperativeness and selfishness.
-
-After being randomly assigned to either a control or intervention condition, participants were informed they would be paired with a different player in a second phase of the experiment.
-This second phase was similar to the first phase in terms of the game played (RTG) and the number of rounds.
-Finally, players were told they would be paired with a new player in the third phase of the experiment.
+-->
+
+<!-- In the second phase of the experiment, participants were informed they would be paired with a different player.
+This phase was similar to the first phase in terms of the game played (RTG) and the number of rounds.
+In all rounds of the RTG, participants gave feedback after seeing the investment received.
+This feedback was given though a two dimensional grid that was either related to their emotional state (degree of valence of arousal) in the Intervention group, or unrelated to the emotional state in the control group (speed of investor's response and magnitude of investment).
+At the end of each RTG, participants were asked to rate how cooperative, selfish, trustworthy and friendly they thought their interaction partner was.
+Details of the two dimensional grid and player ratings are given in the supplement.
+-->
+
+<!-- After both trust games,  players were told they would be paired with a new player in the third phase of the experiment.
 This third phase consisted of 7 rounds of the prisoner's dilemma game, facing the new player.
@@
 The total number of rounds was not communicated to the participants in any of the games played.
-
-After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment.
-These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016].
-Finally, participants were asked a series of questions around how they played each phase.
-First, participants were asked whether they thought they played differently in the second compared to the first phase of the RTG.
+-->
+
+<!-- After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment.  -->
+
+<!-- <!-- These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016].
+-->
+
+<!-- Finally, participants were asked a series of questions around how they played each phase.
+First, they were asked whether they thought they played differently in the second compared to the first phase of the RTG.
 Second, participants had to select whether they thought the opponents they faced were human or computer agents.
@@
 Finally, we asked participants to reveal whether this experiment has taught them anything about how they should behave in social situations.
-
-```{r interventionSlide,fig.cap = "Screenshot of the main  slide in the intervention condition", fig.align='center', out.width="80%"du}
-
-knitr::include_graphics("figures/intervention_text.png")
-
-```
+-->
+
+The experiment as shown in Figure \ref{fig:timeline} began with participants briefed there will be three phases, and that they would face a new opponent in each phase.
+Phase one was a 15 round Trust Game (RTG) in which participants had the role of the trustee, facing the same investor opponent.
+Participants were then assigned to either the control or intervention conditions.
+Phase two was similar to Phase one, with participants being told they faced a new player.
+In both phases, participants were asked for feedback in each round after seeing the investment.
+The nature of the feedback solicited varied by condition, either emotion-related (intervention) or unrelated (control).
+Participants rated their interaction partner on various attributes after each phase.
+More details on these attributes, nature of feedback and exact instructions are found in the supplement.
+Phase three involved 7 rounds of the repeated prisoner's dilemma game (RPD) with a third player.
+Participants were explicitly told to aim to maximise the number of points in all phases.
+The total number of rounds was not communicated to the participants in any of the games played.
+
+Post-experiment, participants completed questionnaires related to mentalising abilities, emotion regulation and BPD traits (see details in supplement).
+They were then quizzed on their game-play, including whether they detected that all opponents were computer agents.
+The reveal explained that they were facing identical AI agents and that any perceived opponent changes were due to participants' own behavior.
 
@@
 
-After a total of 15 rounds of the trust game, players were given either an "intervention" or a "control" manipulation.
-The intervention consisted of presenting a hypothetical scenario in which they were playing the repeated trust game and the investor would send a low investment in a new round after having previously sent higher amounts.
-Participants were then asked how they would react in this situation and what sort of return (low or high) they were thinking of sending back.
-The players then were presented with an educational slide about the benefits of not resorting to impulsive decisions such as punishment when they feel they have been wronged.
-In this text, players were told that punishment can create a negative feedback loop where the other player might trust them even less.
-An alternative action was suggested, whereby players would respond kindly to such a transgression in the hope of gaining trust from the investor.
-The full text of the intervention slide is presented in Figure \ref{fig:interventionSlide}.
-Afterwards, participants were asked whether they would send a low or high return in the same hypothetical scenario now that they have read the information on the slide.
-Players were asked to justify their answer.
-For each question during this intervention, participants had to wait for a fixed duration of 20 seconds before being able to write their answers, and they were prevented from proceeding before that time was up.
-This choice was made to allow participants to engage with the questions, think about their answers and provide meaningful feedback.
+The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taking in emotional states [@linehan_dbt_2015].
+Specifically, participants were presented with a low investment and asked to indicate their response.
+They were then invited to consider what their ultimate aim in the game was and whether this response was most likely to achieve their aim.
+The intervention is detailed in the supplementary information.
 
@@
 
-## Measures
-
-### Repeated Trust Game 
-Participants played two iterations of the standard version of the repeated trust game [@joyce_trust_1995].
-The game is played in dyads, with one player assigned the role of the "investor" and the other player that of the "trustee".
-In the variant of the game we chose, the investor is endowed with 20 units at the start of each round.
-They need to decide how much of that endowment they want to invest with the trustee.
-The investment is then multiplied by a factor of 3 and sent to the trustee.
-As shown in Figure \ref{fig:trustGame}, the trustee in turn needs to decide how much of the (multiplied) investment they want to send back to the investor.
-If they send back more than a third of what they received, then both the investor and the trustee make a gain.
-Otherwise, the trustee would benefit but the investor would lose on their investment.
-If the interaction lasts for only one round, the Nash equilibrium of this game is for the investor to send nothing, as there is no incentive for the trustee to send back any return.
-In the repeated version, to maximise their rewards over time, both players need to build trust so that they can share the benefits of the bigger pie (the investment multiplied by three).
-If during the course of the interaction, the investor has been rewarded for taking the risk of sending an investment, then they would be more likely to invest more, and the multiplied investment would give both a bigger pie to share.
-If however the investor felt that they were not getting a return on their investment, then they would refrain from investing and neither would gain from the interaction.
-
-```{r trustGame,fig.cap = "Screenshot of the repeated Trust Game.
-The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee.
-The investor is endowed with 20 units at the start of each round.
-They need to decide how much of that endowment they want to invest with the trustee.
-The investment is then multiplied by a factor of 3 and sent to the trustee.
-The trustee in turn needs to decide how much of the multiplied investment they want to send back to the investor.
-Shown here is the stage at which the trustee makes a decision of how much to send back the investor", fig.align='center'}
-
-knitr::include_graphics("figures/trust_game.png")
-
-```
-
-### Repeated Prisoner's Dilemma 
-The other game the participants played is the repeated Prisoner's Dilemma (RPD).
-Over multiple rounds, participants could choose one of two actions: A cooperative action that would yield a high pay-off if the other person also cooperated, and the lowest possible pay-off if they did not cooperate.
-Or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect.
-Figure \ref{fig:payoffsRPD} shows the payoff of each combination of actions as presented to the participants.
-
-```{r payoffsRPD,fig.cap = "Screenshot of the Repeated Prisoner's Dilemma game.
-Over multiple rounds, participants could choose one of two actions: A cooperative action that would yield a high pay-off if the other person also cooperated, and the lowest possible pay-off if they did not cooperate.
-Or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect.
-Shown here is the table explaining the payoffs of each combination of actions the participant and their opponent choose", fig.align='center'}
-
-knitr::include_graphics("figures/screenshot_RPD_payoffs.png")
-
-```
-
-### Feedback post investment in the repeated Trust Game
-
-```{r grid,fig.cap = "Screenshot of the two axis grid in the Coaxing condition where participants were asked to report the valence and arousal of their emotional response ", fig.align='center'}
-
-knitr::include_graphics("figures/emotion_grid.png")
-
-```
-
-Whilst playing the RTG, participants were asked to provide some feedback, in each round of the game, after seeing the amount sent by the investor.
-This feedback took the form of the answer to a question using a two dimensional field.
-What the axes of the field represented differed by condition.
-In the intervention condition, participants were asked to rate their emotional state with regard to the other player's choice of investment, with the x-axis representing the valence of the emotion they felt (positive or negative) and the Y-axis representing the emotional "arousal" they experienced (low or high).
-In the control condition, players were asked to rate attributes of the investment that were not related to their emotion, with the X-axis rating of how fast the investor is (slow or fast) and the Y-axis the magnitude of the investment (low or high).
-Figure \ref{fig:grid} shows a screenshot of the field in the intervention condition where participants were asked about their own emotional response to the investment.
-At the beginning of each game, participants were provided with detailed explanations of the meaning of the two axes as well as the opportunity to provide a baseline emotional state through using the field prior to the start of the game.
-
-### Design of the AI agents in the RTG and RPD
-
-```{r}
+## Design of the AI agents in the RTG and RPD
+
+```{r, include=FALSE}
 Anti_social <-  c(0.1025436430408, 0.1221931236853, 0.1345215238995,
@@
 
-```{r invHMMPlot, fig.cap="Distribution of investments by the artificial investor agent conditional on its latent state as estimated by a three state hidden Markov model with a discretised truncated Gaussian as a response function",fig.align="center", fig.width=6, fig.height = 4}
-
-ggplot(response_probs,                            
+```{r, include=FALSE}
+
+plotinvHMM <- ggplot(response_probs,                            
        aes(x = investment,
@@
 
-```{r invHmmTrans, fig.cap="Transition function for investor conditional on current state",fig.align="center", fig.width=6, fig.height = 4}
-
-plot_HMM_transitions(3, pars_inv)
-
-```
-
+```{r, include=FALSE}
+
+plotInvTran <- plot_HMM_transitions(3, pars_inv)
+
+```
+
+```{r HMMPanels, fig.cap="A: Distribution of investments by the artificial investor agent conditional on its latent state as estimated by a three state hidden Markov model fitted to human dyadic play dataset.
+B: Transition function for the HMM investor conditional on its current state and the net return from the previous round of play.", fig.align="center"}
+
+ggpubr::ggarrange(plotinvHMM , plotInvTran, nrow=2, ncol=1, labels = c("A", "B"), common.legend = TRUE, legend = "bottom")
+
+```
 The role of the investor was in reality played by an adaptive artificial agent whose strategy was modelled on the behaviour of human participants taking the role of the investor in the RTG.
@@
 In this instance, for both iterations of the repeated trust game, the HMM used was identical: it had three states that can be described as "low-trust", "medium-trust" and "high-trust".
-Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust, as presented in Figure \ref{fig:invHMMPlot}.
-
-<!-- The advantages of this approach is that it does not require any a priori assumptions about the model features.
-The number of states, the policy conditional on the state, and the transition function between states can all determined in a purely data driven way.
-These HMMs can in turn be used to simulate a human-like agent playing the trust game.
-This agent may transition to a new state depending on the other player's actions and adopt a policy reflecting its state, thus simulating changes in emotional dispositions of human players during a repeated game.
-When the investor gains from the interaction, they become more likely to transition to a state where their policy is to be more trusting and invest more.
-However, faced with losses, the investor is more likely to transition to a more cautious policy where its investment belies lower trust in the trustee.
-The policies and the transitions between states are sufficient to build an agent that reflects this type of adaptive behavior and reacts to the trustee's action choices in a way that mimics a human player.
--->
-
-The HMM assumes that the probability of each investment $I_t=0,…,20$, at each trial t, conditional on the current state of the investor $S_t$, is dependent on an underlying normal distribution with mean $\mu_s$ and standard deviation $\sigma_s$.
-The probability of each discrete investment was determined by the cumulative normal distribution $\Phi$.
-For instance, the probability of an investment $I_t=2$ is defined as:
-
-$$P(I_t=2 | S_t=s)= \frac{\Phi(2.5 | \mu_s,\sigma_s ) - \Phi(1.5 | \mu_s,\sigma_s )} {\Phi(20.5 | \mu_s,\sigma_s ) - \Phi(-0.5 | \mu_s,\sigma_s )}$$
-
-Note that the denominator truncates the distribution between 0 and 20.
-To estimate the transition probability between states for the investor, a multinomial logistic regression model was fitted to the investor's data such as:
-
-$$P(S_{t+1} = s' | S_t=s , X_t = x)= \frac{\exp(\beta_{0,s,s'} + \beta_{1,s,s'} x)}{\sum_{s''} \exp(\beta_{0,s,s''} + \beta_{1,s,s''} x)}$$
-
-where $X_t=R_t-I_t$ is the net return to the investor with  $R_t$ the amount returned by the trustee and $I_t$ is the Investment sent.
-Figure \ref{fig:invHmmTrans} shows these transition probabilities as a function of the net return conditional on the investor's state.
-
-For the repeated prisoner's dilemma, we used an artificial agent that was playing according to Tit-For-Tat [@axelrod_evolution_1981].
-It started by choosing the cooperative action and then it mirrored whatever the other player played in the previous round.
-
-### AI agents pre-programmed defection
-
-In order to probe efforts to repair trust, we introduced rounds where the investor deviated from the policy provided by the HMM, and chose to send a low investment in the Trust Game, or chose the non-cooperative action in the Prisoner's Dilemma.
+Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust, as presented in Figure \ref{fig:HMMPanels}.A.
+Transition probabilities between these latent states were modelled as a function of the net return in the previous round conditional on the investor's state as shown in Figure \ref{fig:HMMPanels}.B.
+
+<!-- In order to probe efforts to repair trust, we introduced rounds where the investor deviated from the policy provided by the HMM, and chose to send a low investment in the Trust Game, or chose the non-cooperative action in the Prisoner's Dilemma.
 In the trust games, we programmed the HMM agent to send a very low investment (2 out of 20) to the trustee on specific rounds (round 12 pre-intervention and 13 post-intervention).
@@
 This ignorance of reactions to the defection rounds was chosen to reflect an accidental defection, with the Investor being open to repair subsequent interaction.
-
-<!-- ## Statistical analysis of Behavior -->
-
-<!-- Since we aim to compare pre and post intervention measures between groups, we have to analyse repeated measures.
-To do that we will use linear mixed effects models as implemented in the R package "afex" [@singmann_afex_2022].
-When models contain interactions between variables that involve continuous covariates such as the "Investment", we standardise the continuous covariate by transforming it into a z-score.
-This allows us to correctly interpret the coefficient of the interaction variable.
-For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
--->
+-->
+
+In order to probe efforts to repair trust, we simulated trust breaches in both Trust Games and the Prisoner's Dilemma.
+The AI was programmed to break trust on specific rounds (12 pre-intervention, 13 post-intervention in the Trust Game; round 4 in Prisoner's Dilemma).
+After these "defection" rounds, the AI returned to its previous strategy, disregarding the participant's response to the breach.
+This simulated an accidental defection and a readiness to repair the interaction, providing insights into trust repair dynamics.
 
@@
 
-### HMM analysis of participants returns in the RTG
-
-To model participants returns in the RTG across games and conditions, we used an HMM response function based on a discretised Gaussian distribution that takes into account what proportion the trustee would ideally like to return, and what returns are possible given the investment.
-For instance, if the investor sends an amount of $2$, the trustee would receive $6$ and they can send back any amount between $0$ and $6$.
-As such, we assume that the response is a distribution over proportions that can be calculated from these possible returns, i.e.
-$\{0,1/6, 2/6,...,1 \}$.
-The model assumes an underlying Normal distribution for each possible proportional return, predicting the probability of each via the cumulative Normal distribution with cut-off points set halfway between the proportions (e.g.
-the probability of returning 1/6 is determined as the probability of returning anything between 1/12 and 3/12).
-The transition between states is assumed to depend on the investment through a multinomial logistic function such as:
-
-$$P(S_{t+1} = s' | S_t=s , X_t = x)= \frac{\exp(\beta_{0,s,s'} + \beta_{1,s,s'} \ \text{inv} + \beta_{2,s,s'} \ x)}{\sum_{s''}\exp(\beta_{0,s,s''} + beta_{1,s,s'} \ \text{inv} + \beta_{2,s,s'} \ x)}$$
-
-where $\text{inv}$ is a variable representing the investment received, $x$ is a dummy variable to characterise the group that the participant belongs to.
-We define four contrast codes for these dummy variables: pre-post (comparing pre and post games), post-coax (compares the post-intervention group to all others), post-control (compares the post-control group to all others) and full-contrast (a three level dummy variable: post-intervention compared to post-control and  all pre games).
-
-Having defined these contrast codes, we then fit HMM models where the transition function between latent states depends both on the investment received and depending on the model, one of the aforementioned contrast codes.
-To select the number of hidden states governing participants' policies, we fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978] to select the best model.
+## Analysis of participants returns in the RTG
+
+To explore whether participants behaved differently after the intervention compared to the control group over all rounds, we estimate a linear-mixed effects model as implemented in the R package "afex" [@singmann_afex_2022], with fixed effects for Condition (intervention or control), Game-number (pre- or post-intervention) and Investment, as well as interactions between Condition and both Investment and Game-number, and participant-wise random intercepts and random slopes for Game-number.
+More complex models with additional random effects provided could not be estimated reliably.
+For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
+We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
+
+To model participants returns in the RTG across games and conditions, we fit various hidden Markov models to participants returns using the depmixS4 package [@visser_depmixs4_2021].
+The transition between latent states is assumed to depend on the investment received and a dummy variable to characterise the group that the participant belongs to.
+Details on how the models are constructed as well as the various contrast codes used for the dummy variables are found in the supplement.
+We fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978-1] to select the best model.
 
@@
 
-For the outcomes of the RTG, we first check the benchmark results for the average investment and return to see if they are comparable to results in the literature.
-We focus on the first 10 rounds pre-manipulation (the first RTG) and pre-defection trial to exclude the effects of the investor's transgression and those of the intervention and to have a comparable number of rounds to the standard version of the RTG.
-The average investments and returns were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature, and hence comparable to other implementations of this task reported in the literature [@charness_investment_2008; @fiedler_social_2011].
+Average investments and returns prior to the defection round (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
+Estimated marginal means of percentage returns from fitting the mixed effects model specified in the methods section, as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.A.
 
@@
 ```{r gamesPlot, echo=FALSE, fig.cap="Average and standard errors of the trustee's return as a percentage of the multiplied investment received for each round and for both conditions.
-The red line shows the returns pre-manipulation and the blue line post-manipulation.
-",fig.align="center", fig.width=6, fig.height = 4}
+The red line shows the returns pre-manipulation and the blue line post-manipulation.We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel",fig.align="center", fig.width=6, fig.height = 4}
 
@@
 ```
-Figure \ref{fig:gamesPlot} shows the average and standard error of trustee returns as a percentage of the total yield (3 x investment) over the full 15 rounds for both conditions and both RTG games.
-We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
-
-To explore whether participants behaved differently after the intervention compared to the control group over all rounds, we estimate a linear-mixed effects model, with fixed effects for Condition (intervention or control), Game-number (pre- or post-intervention) and Investment, as well as interactions between Condition and both Investment and Game-number, and participant-wise random intercepts and random slopes for Game-number.
-We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
-More complex models with additional random effects provided could not be estimated reliably.
 
@@
 
+cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
 ```
@@
 
-Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in panel A of Figure \ref{fig:violinPanels}.
-If the intervention has an effect, then we should expect a higher increase in returns after the intervention compared to the control condition, which should be evident from an interaction between Condition (intervention vs control) and Game-number (pre- vs post-manipulation).
+<!-- If the intervention has an effect, then we should expect a higher increase in returns after the intervention compared to the control condition, which should be evident from an interaction between Condition (intervention vs control) and Game-number (pre- vs post-manipulation).
 Therefore, the variable of interest here is the interaction between Condition and Game-number.
-We do find an interaction effect due to an increase in the percentage returned in the intervention but not in the control group ($F(1,314.2) =  26.9, p < 0.001$).
-We also find a significant main effect for Condition ( $F(1,315.31) = 9.52, p = 0.002)$), which is due to participants returning higher percentage returns, in the post game, in the intervention group ($p < 0.001$), and lower returns in the control group ($p = 0.02$).
-We also find a main effect of Investment due to higher percentage returns being sent back for higher investments ( $F(1,9208) = 373.6, p < 0.001$), and an interaction effect of Investment by Condition ($F(1,9207) =45.38, p < 0.001$), with investments having less of a positive effect on the percentage returns in the intervention group compared to the control group.
-The latter effect indicates that the higher returns we see in the intervention group are unlikely to be purely driven by higher investments.
+-->
+
+We find an interaction effect between Condition (intervention vs.
+control) and Game-number (pre- vs.
+post-manipulation) ($F(1,314.2) = 26.9, p < 0.001$).
+Post-hoc tests show that there was an increase in the percentage returned in the intervention group (`r papaja::apa_print(prepost_bycond)$statistic$Intervention_Pre_post`) but not in the control group (`r papaja::apa_print(prepost_bycond)$statistic$Control_Pre_post`).
+We also found a significant main effect for Condition ( $F(1,315.31) = 9.52, p = 0.002)$), such that the intervention group had higher percentage returns than the control group.
+There was also a significant main effect of Investment( $F(1,9208) = 373.6, p < 0.001$) such that higher investments were associated with higher percentage returns.
+
+There was an interaction effect of Investment by Condition ($F(1,9207) =45.38, p < 0.001$), such that the positive effect of investment on percentage returns was greater in the control group than in the intervention group.
+This suggests that the higher returns we see in the intervention group are not simply due to higher investments.
 Finally, we find a three way interaction between Game-number, Condition and Investment ($F(1,8988)= 24.6, p < 0.001$), showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game-number.
@@
 
-Since the artificial agent taking the role of the investor adapts its behavior to the actions of the participants, we can analyse whether the HMM agent exhibits a differentiated behavior between games and conditions.
-We use a linear-mixed effects model, with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number.
+The HMM agent exhibited a differentiated behavior between games and conditions.
+When examining the HMM agent investments, we fit a linear-mixed effects model, with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number.
 We find a main effect for both Condition ($F(1,317) = 8.7, p = 0.003$) and Game-number($F(1,317) = 8.3, p = 0.004$).
-As can be seen in panel D of Figure \ref{fig:violinPanels}, investment was higher in the intervention compared to the control condition across games ($p=0.003$).
+As can be seen in Figure \ref{fig:violinPanels}.D, investment was higher in the intervention compared to the control condition across games ($p=0.003$).
 Across conditions, investment was also higher in the second game compared to the first ($p=0.003$).
 
-In summary, participants in the control group sent back **lower** returns in the second game (`r apa_print(prepost_bycond)$full_result$control`) despite the HMM investor sending, on average higher absolute investments.
-Those in the intervention group returned **higher** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$intervention`), with the investor also sending higher investments.
-We can rule out that these higher returns in the intervention group compared to the control group were purely driven by higher investments.
-If that was the case, then we would expect the presence of the Investment variable in our model of returns to lead to a non-significant interaction between Game-number and Condition.
-Since we find the interaction effect whilst controlling for Investment, this suggests this effect is not purely explained by the change in investments.
-
-## Pre-defection trials
+In summary, participants in the control group sent back **lower** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$Control_Pre_post`) despite the HMM investor sending, on average higher investments.
+Those in the intervention group returned **higher** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$Intervention_Pre_post`), with the investor also sending higher investments.
+These higher returns in the intervention group compared to the control group were not purely driven by reciprocity towards higher investments since we find this interaction effect whilst controlling for investments in our model of participants returns.
+
+## Looking at pre- and post-defection trials only
 
@@
 ```
-Since we observed higher returns pre-defection trials, we can also explore whether there was differentiated behavior if we restrict our analysis to the rounds prior to the pre-programmed one-off investment (rounds 1 to 11 pre-manipulation and 1 to 12 post-manipulation).
-We fit the same linear mixed effects model to percentage returns as the one for the full data.
-Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in panel B of Figure \ref{fig:violinPanels}.
+
+We restrict our analysis to the rounds prior to the pre-programmed defection (rounds 1 to 11 pre-manipulation and 1 to 12 post-manipulation) and fit the same linear mixed effects model to percentage returns as the one for the full data.
+Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.B.
 We do find an interaction effect between Condition and Game number ($F(1,317.99) = 17.1, p < 0.001$).
-This was due to an increase in the percentage returned pre low-investment trial in the intervention condition (`r apa_print(pairs_pre_int)$full_result$intervention`) but not in the control group (`r apa_print(pairs_pre_int)$full_result$control`).
-This indicates that the differentiated behavior we saw, where participants were sending back higher returns in the intervention condition but not in the control condition, was not simply due to their reaction post the low-investment trial.
-The higher returns were consistent with the message of the intervention, but have also happened, on average across participants, before the participants experienced the event similar to the one described in the intervention.
+This was due to an increase in the percentage returned pre low-investment trial in the intervention condition (`r apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`) but not in the control group (`r apa_print(pairs_pre_int)$full_result$Control_Pre_post`).
+This indicates that participants were sending back higher returns in the intervention condition but not in the control condition even before the defection trial.
 
@@
 
-## Defection and post defection trials
-
 The interventions focused on repairing cooperation in the wake of a transgressive action by the investor.
 To assess the effect of the intervention, we can therefore consider the percentage return after the "transgression" trials.
-We fit the same linear mixed effects model to percentage returns as the one for the full data.
-We now restrict the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
+We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
 These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).
@@
 
-```{r violinPanels, fig.cap="Panel A: Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition.
-Panel B: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
-Panel C: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.
-Panel D:Marginal means and distributions of investments over all rounds for HMM agents playing the role of the investor, by Game number and Condition", fig.align="center", fig.width=6, fig.height = 6}
+```{r violinPanels, fig.cap="A: Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition.
+B: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
+C: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.
+D: Marginal means and distributions of investments over all rounds for HMM agents playing the role of the investor, by Game number and Condition", fig.align="center", fig.width=6, fig.height = 6}
 
@@
 
-Panel C of Figure \ref{fig:violinPanels} shows the marginal means of trustee returns and their distribution by Game-number and Condition.
-We found a main effect of Condition with returns on the intervention group higher than returns in the control group (`r apa_print(pairs(postcoax_bycond))$full_result$intervention_control`).
-We also found a main effect of Game-number, with returns higher for the pre-manipulation game compared to the post-manipulation game  (`r apa_print(pairs(postcoax_bygame))$full_result$pre_post`).
-In addition, there was a significant interaction between Game-number and Condition.
-We found a significant decrease in returns between games in the control condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$control_pre_post`), but no such difference in the intervention condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$intervention_pre_post`).
+Figure \ref{fig:violinPanels}.C shows the marginal means of trustee returns and their distribution by Game-number and Condition.
+There was a significant interaction between Game-number and Condition.
+Participants sent back lower returns between games in the control condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`), but no such difference in the intervention condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`).
+
+<!-- We found a main effect of Condition with returns on the intervention group higher than returns in the control group (`r apa_print(pairs(postcoax_bycond))$full_result`).
+We also found a main effect of Game-number, with returns higher for the pre-manipulation game compared to the post-manipulation game  (`r apa_print(pairs(postcoax_bygame))$full_result`).
+-->
 
@@
   dplyr::select(-c("roundType","gameNumber")) %>% 
-  group_by(condition.f) %>% 
-  mutate(emo_scaled_x = scale(emo_coord_x), emo_scaled_y= -scale(emo_coord_y))  %>%    # <--- SCALING and reversing Y coordinates (0,0 is top left)
-  ungroup()
+  # group_by(condition.f) %>% 
+  mutate(emo_scaled_x = scale(emo_coord_x), emo_scaled_y= -scale(emo_coord_y))    # <--- SCALING and reversing Y coordinates (0,0 is top left)
 
@@
 
-colors <- c("Investment" = "blue", "Valence" = "red", "Arousal" = "green")
-ggplot(datCoax,aes(x=roundNum)) + 
-  stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_x, color = "Valence")) + 
-  stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_y, color = "Arousal") ) + 
-  stat_summary(fun = "mean", geom = "line",group =1, aes(y=scale(investment), color = "Investment") ) + 
-  # 
-  # stat_summary(fun = "mean", geom = "point",shape=15, size=2.5,group=1,  alpha =0.3,aes(y=investment/10,color = "Investment")) +
-  # scale_y_continuous(name="Valence/Arousal z-score", sec.axis=sec_axis(~./0.1, name="investment")) +
-  scale_color_manual(name = " ",values = colors,labels = c("Investment", "Emotion valence", "Emotion arousal")) +
+# colors <- c("Investment" = "blue", "Valence" = "red", "Arousal" = "green")
+# 
+# ggplot(datCoax,aes(x=roundNum)) + 
+#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_x), color = "red") + 
+#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_y), color = "green") + 
+#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=scale(investment)), color = "blue") + 
+#   scale_color_manual(name = " ",values = colors, labels = c("Investment", "Emotion valence", "Emotion arousal")) +
+#   labs(x = "Round", y="Series Z-score") +
+#   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
+#   facet_grid(cols = vars(gameNum.f)) +
+#   theme_bw() + 
+#   theme(legend.position = "bottom")
+#
+
+# # BOTH IN ONE GRAPH 
+# library(ggplot2)
+# 
+# # Define the colors in alphabetical order
+# colors <- c("Arousal" = "green", "Investment" = "blue", "Valence" = "red")
+# 
+# # Plot 'pre'
+# p <- ggplot(datCoax[datCoax$gameNum.f == 'pre', ], aes(x=roundNum)) + 
+#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_x, color = "Valence", linetype = "pre")) + 
+#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_y, color = "Arousal", linetype = "pre")) + 
+#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=inv_scaled, color = "Investment", linetype = "pre")) +
+# # Plot 'post'
+#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_x, color = "Valence", linetype = "post")) + 
+#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_y, color = "Arousal", linetype = "post")) + 
+#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=inv_scaled, color = "Investment", linetype = "post")) +
+#   labs(x = "Round", y="Series Z-score") +
+#   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
+#   scale_color_manual(name = " ", values = colors, labels = c("Emotion arousal", "Investment", "Emotion valence")) +
+#   scale_linetype_manual(values = c("pre" = "dotted", "post" = "solid"), labels = c("Pre", "Post")) +
+#   theme_bw() + 
+#   theme(legend.position = "bottom")
+# 
+# # Print the plot
+# print(p)
+
+#################### two panels for before and after defection 
+library(ggplot2)
+
+# Define the colors in alphabetical order
+colors <- c("Arousal" = "green", "Investment" = "blue", "Valence" = "red")
+
+# Create a new variable to categorize the rounds
+datCoax$roundGroup <- ifelse(datCoax$roundNum <= 10, "Rounds 1-10", "Rounds 11-15")
+
+# Plot 'pre'
+p <- ggplot(datCoax[datCoax$gameNum.f == 'pre', ], aes(x=roundNum)) + 
+  stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_x, color = "Valence", linetype = "a_Pre")) + 
+  stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_y, color = "Arousal", linetype = "a_Pre")) + 
+  stat_summary(fun = "mean", geom = "line", group =1, aes(y=inv_scaled, color = "Investment", linetype = "a_Pre")) +
+# Plot 'post'
+  stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_x, color = "Valence", linetype = "b_Post")) + 
+  stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_y, color = "Arousal", linetype = "b_Post")) + 
+  stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=inv_scaled, color = "Investment", linetype = "b_Post")) +
   labs(x = "Round", y="Series Z-score") +
   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
-  facet_grid(cols = vars(gameNum.f) ) +
+  scale_color_manual(name = " ", values = colors, labels = c("Emotion arousal", "Investment", "Emotion valence")) +
+  scale_linetype_manual(values = c("a_Pre" = "dotted", "b_Post" = "solid"), labels = c("Pre", "Post")) +
+  scale_x_continuous(breaks = 1:max(datCoax$roundNum)) +
+  facet_wrap(~roundGroup, scales = "free_x") +
   theme_bw() + 
@@
 
-```
-
-The results of the mixed-effects model of returns suggest that returns of participants in the intervention condition were less associated with the magnitude of the investment compared to those in the control condition.
-We can explore whether the emotional reaction to the investment was also lessened in the intervention condition through analysing the self-reported emotions on the two-axes feedback field.
-Figure \ref{fig:emoPlotCoax} shows the average, across participants *in the intervention condition*, of emotion valence, the degree of arousal as well as the HMM's investment z-scores.
+# Print the plot
+print(p)
+
+```
+
+A key aspect of effective interventions is the emotional change.
+We examined emotion self-reports through fitting a linear mixed effects model to both emotion dimensions (valence and arousal) for the intervention group to explore whether the intervention changed the emotional appraisal of the investment, with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
+
+Higher investments were associated with more positive emotions ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$), while positive emotions declined between the two games ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
+However, there was no evidence that emotional reaction to the investment was lessened after the intervention.
+This means that participants in the intervention condition returned higher amounts post-intervention despite the emotional reaction to the lower investment being largely unchanged.
+
+<!-- Figure \ref{fig:emoPlotCoax} shows the average, across participants *in the intervention condition*, of emotion valence, the degree of arousal as well as the HMM's investment z-scores.
 We find a significant positive correlation between the two emotion axis ($r=0.52, p < 0.001$) as well as between valence and Investment ($r=0.47, p < 0.001$), and arousal and Investment ($r=0.50, p < 0.001$).
-Unsurprisingly, the low investment in the pre-determined defection round leads to negatively valenced emotions.
-Perhaps less expected is that they also lead to low arousal.
-We fit a linear mixed effects model to both emotion dimensions (valence and arousal) for the intervention group to explore whether the intervention changed the emotional appraisal of the investment, with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
+-->
+
 ```{r, include=FALSE}
@@
 
-For emotional valence, we find a main effect of Investment ($F(1,4664) = 2902, p < 0.001$), with higher investment leading to more positive emotions.
-We also find a main effect for Game-number, due tothe reported emotional valence of investments decreasing significantly after the intervention ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
+<!-- For emotional valence, we find a main effect of Investment ($F(1,4664) = 2902, p < 0.001$), with higher investment leading to more positive emotions.
+We also find a main effect for Game-number, due to the reported emotional valence of investments decreasing significantly after the intervention ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
 For emotional arousal, fitting a similar mixed effects model we find only a main effect of Investment  ($F(1,4668.4) = 1919, p < 0.001$) with higher investment leading to higher arousal.
@@
 We did not find any interaction between emotional valence or arousal and the investment, which would indicate a moderating effect of the intervention on the reaction to investments.
+-->
 
@@
 
-One possible reason of the differentiated returns post manipulation between conditions is that participants had a different perception of the investor, post-manipulation, in the control condition compared to the control condition.
+<!-- One possible reason of the differentiated returns post manipulation between conditions is that participants had a different perception of the investor, post-manipulation, in the control condition compared to the control condition.
 To explore this possibility, we can determine whether participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention) using the players ratings they had to submit at the end of each game.
 To analyse the participants rating of their opponents, we used a linear mixed-effects model for each of the four players ratings (cooperativeness, selfishness, trustworthiness, friendliness) with fixed effects for Game-number (pre or post manipulation) and Condition (intervention or control), as well as interaction between condition and Game-number, and participant-wise random intercepts.
+-->
 
@@
 
-We find a main effect of Game-number on all attributes, with participants rating the second player as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result$pre_post`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result$pre_post`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result$pre_post`) and more selfish(`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result$pre_post`).
-We also find a main effect of Condition as participants in the intervention condition rated players higher than those in the control condition on cooperativeness (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("condition.f"))))$full_result$coaxing_control`) and lower on selfishness  (`r apa_print(pairs(emmeans::emmeans(self_mod, c("condition.f"))))$full_result$coaxing_control`).
+<!-- showed a main effect of Game-number on all attributes, with participants rating the second player as less cooperative (∆M = 0.42, 95% CI [0.15, 0.69], t(317.00) = 3.10, p = .002), less trustworthy (∆M = 0.43, 95% CI [0.16, 0.70], t(317.00) = 3.19, p = .002), less friendly (∆M = 0.40, 95% CI [0.17, 0.64], t(317.00) = 3.36, p = .001) and more selfish(∆M = −0.36, 95% CI [−0.61, −0.10], t(317.00) = −2.76, p = .006).
+Importantly, there was a main effect of Condition , with participants in the intervention condition rated players higher than those in the control condition on cooperativeness (∆M = 0.40, 95% CI [0.00, 0.80], t(317.00) = 1.95, p = .052) and lower on selfishness (∆M = −0.41, 95% CI [−0.80, −0.02], t(317.00) = −2.04, p = .042).
+There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
+-->
+
+Participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention).
+The players ratings submitted at the end of each game showed a main effect of Game-number on all attributes, with participants rating the second player as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result`) and more selfish(`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result`).
+We also find a main effect of Condition as participants in the intervention condition rated players higher than those in the control condition on cooperativeness (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("condition.f"))))$full_result`) and lower on selfishness (`r apa_print(pairs(emmeans::emmeans(self_mod, c("condition.f"))))$full_result`).
 There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
@@
 
-```{r PDCoop, fig.cap="Mean and standard error of the rate at which the cooperative action was chosen by the participants for each round of the repeated Prisoner's Dilemma game.
-The decrease of cooperation seen from round 5 onwards is likely due to a pre-determined defection of the agent in round 4",fig.align="center", fig.width=6, fig.height =3}
+```{r PDCoop, include=FALSE, fig.cap="Mean and standard error of the rate at which the cooperative action was chosen by the participants for each round of the repeated Prisoner's Dilemma game.
+Round 4 is where we programmed the Tit-for-Tat agent to defect, which explains the lower cooperation rate we see in round 5 onwards",fig.align="center", fig.width=6, fig.height =3}
 # plot of cooperation rates per round
@@
 
-If the intervention successfully increased coaxing behaviour in participants, we would hope they generalized this to other games beyond the Trust Game.
-Across participants, we first look at the rate at which the cooperative action was chosen in each round.
-Figure \ref{fig:PDCoop} shows the mean and standard error of the cooperation rate by round.
-Round 4 is where we programmed the Tit-for-Tat agent to defect, which explains the lower cooperation rate we see in round 5 onwards.
+We next asked whether the coaxing behavior induced by the intervention generalized to the RPD.
+Across participants, we look at the rate at which the cooperative action was chosen in each round.
 Using a logistic mixed-effects model with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, we found no evidence for a different cooperation rate in the intervention condition compared to the control condition.
@@
 
-## Self report questionnaires
+## Self report and debrief questionnaires
 
@@
 
-Failure to repair a breakdown in trust in the repeated trust game has been associated with trustees with BPD traits [@king-casas_rupture_2008].
-Theories of social dysfunction in BPD have focused on dysfunction in the patients' mentalising ability [@allen_handbook_2006] as well as difficulties in emotional regulation [@rudge_mechanisms_2020].
-The questionnaires we included in the experiment tried to assess borderline traits (PAI-BOR), emotional regulation capabilities (DERS) and mentalising ability (RFQ8).
-As such, we wanted to test whether there was an association between scores in these questionnaires and the effect of the intervention.
-We fit a linear mixed effect model to the percentage return of trustees with fixed effects for Condition (intervention or control), Game-number (pre or post manipulation), Investment, and questionnaire score as well as all interactions between the fixed effects.
-We assume participant-wise random intercepts.
-We Z-transform the questionnaire scores and Investment as centering would be beneficial to interpreting the main effects more easily.
-We find no interaction effect of the questionnaire scores with Condition variable, nor a main effect of the questionnaire scores.
-
-## Debrief Questions
-
-In post experimental debrief questions, when asked whether they thought they were facing humans or machines, participants were divided in their answers.
-Although these were open questions, not easily amenable to quantitative analysis, we noted some important trends.
-Reading through participants answers, we note that most of those who correctly deduced that their opponents were artificial agents mentioned cues such as the speed of response of the agent or the duration it took to match up with a game partner to justify their answers.
-This means that this deduction was not associated with the way the agent was perceived to play the game.
-In terms of the agent's behavior, participants expressed they felt it was either human or possessed human-like characteristics such as "spitefulness" or "greed".
-In summary, participants did not systematically detect that their opponents were AI agents reacting to their returns, and were sometimes projecting human traits onto the observed behavior of their artificial opponents.
+```{r, include=FALSE}
+# Install the 'psych' package if you haven't already
+if (!requireNamespace("psych", quietly = TRUE)) {
+  install.packages("psych")
+}
+
+# Load the 'psych' package
+library(psych)
+
+questionnaires <- avg_ret_df %>% group_by(id) %>% dplyr::select(PBOR_score,DERS_score,RFQ_c) %>% unique() %>% ungroup()
+# Perform EFA
+efa_result <- fa(questionnaires %>% dplyr::select(PBOR_score,DERS_score,RFQ_c), nfactors = 2, fm = "minres", rotate = "varimax")
+# Print the EFA result
+print(efa_result)
+
+```
+
+We find no interaction effect of the questionnaire scores with the Condition variable, nor a main effect of the questionnaire scores on participants returns in the RTG.
+
+```{r, include=FALSE}
+turing <- read_csv("data/turing.csv")
+colnames(turing) <- c("responses", "category")
+
+turing  %>%
+    group_by(category) %>%
+    summarize(count = n()) %>%
+    mutate(percentage = count / sum(count) * 100) %>%
+    dplyr::select(category, percentage)
+
+```
+
+When asked whether they thought their opponent was Human or not, $40$% of participants thought they were either facing a human or were not sure of the nature of the opponent.
+Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behavior.
 
@@
 ```{r, include=FALSE}
+
+# THE CODE BELOW WAS NOT USED; ALL CONVERGED. PUT IT HERE IN CASE IT IS NEEDED LATER ON.
+# library(depmixS4)
+# 
+# load("data/fittedSimple.RData")
+# load("data/fittedCtrl.RData")
+# load("data/fittedCoax.RData")
+# load("data/fittedFullCtrst.RData")
+# load("data/fittedPrePost.RData")
+# load("data/newFull.RData")
+# 
+# has_converged <- function(object, numeric = TRUE){
+#   msg <- object@message
+#   if(numeric) as.integer(grepl("converged", msg)) else 0
+# }
+# 
+# 
+# fit_until_convergence <- function(fitted_model, max_iterations=2) {
+#   cat(fitted_model@nstates)
+#   iterations <- 0
+#   converged <- has_converged(fitted_model)
+#   
+#   while (!converged && iterations < max_iterations) {
+#     # Use parameters from the fitted model as initial parameters
+#     initial_params <- getpars(fitted_model)
+#     new_model <- setpars(fitted_model, initial_params)
+#     
+#     # Refit the model
+#     fitted_model <- fit(new_model)
+#     converged <- has_converged(fitted_model)
+#     iterations <- iterations + 1
+#   }
+#   
+#   if (converged) {
+#     cat("NS = ", fitted_model@nstates,"Convergence has been reached.\n")
+#     flush.console()
+#     return(fitted_model)
+#   } else {
+#     cat("Maximum iterations reached. Convergence has not been reached.\n")
+#     flush.console()
+#     return(fitted_model)
+#   }
+# }
+# 
+# 
+# run_parallel_fitting <- function(mods_vec,num_cores = 5) {
+#   # Set up the parallel backend
+#   my.cluster <- parallel::makeCluster(num_cores, type = "PSOCK")
+#   doParallel::registerDoParallel(cl = my.cluster)
+#   
+#   # Export the fit_until_convergence function to the workers
+#   parallel::clusterExport(my.cluster, "fit_until_convergence")
+#   parallel::clusterExport(my.cluster, "has_converged")
+# 
+#   # Run the loop in parallel using foreach
+#   converged_mods_vec <- foreach(mod = mods_vec, .packages = c("depmixS4"), .combine = "c") %dopar% {
+#     cat(mod@nstates)
+#     fit_until_convergence(mod)
+#   }
+# 
+#   # Stop the parallel backend
+#   parallel::stopCluster(my.cluster)
+#   return(converged_mods_vec)
+# }
+# 
+# 
+# sapply(fittedSimple[2:7],has_converged)
+# sapply(fittedCtrl[2:7],has_converged)
+# sapply(fittedCoax[2:7],has_converged)
+# sapply(fittedFullCtrst[2:7],has_converged)
+# sapply(fittedPrePost[2:7],has_converged)
+# sapply(newFull[2:7],has_converged)
+
+```
+
+```{r, include=FALSE}
 # # The full contrast model convergence was not attained. Here we use parameters of fitted PrePost model as initial values of the FullContrast model to speed up fitting and aim for faster convergence.
@@
 
-```{r table-BICs-coax, warning = FALSE, echo=FALSE, ft.align="center", tab.id='table-BICs-coax', label='table-BICs-coax'}
+```{r, include=FALSE}
+library(knitr)
+library(kableExtra)
+
+# Create a data frame for the models
+models <- data.frame(
+  Model = c("HMM-inv", "HMM-prepost", "HMM-coax", "HMM-ctrl", "HMM-full"),
+  Pre_Intervention =  c(0, -1, -1, -1, -1),
+  Post_Intervention = c(0, 1, 1, -1, 2),
+  Pre_Control =       c(0, -1, -1, -1, -1),
+  Post_Control =      c(0, 1, -1, 1, 1)
+)
+
+# Create a table
+models %>%
+  kable("pipe", caption = "Models and their Contrasts") %>%
+  kable_styling()
+
+```
+
+```{r table-BICs-coax, include =FALSE, warning = FALSE, echo=FALSE, ft.align="center", tab.id='table-BICs-coax', label='table-BICs-coax'}
 
@@
 
-To characterise differences between participants' behavior in the intervention compared to the control condition following the manipulation, we analyse their observed returns using hidden Markov models.
-Here we present the results from fitting the HMM models to trustee data using various contrasts that distinguish between pre and post-maipulation and/or between conditions.
-
-We distinguish between five types of models: First, we fit a simple model where we assume that the transition function between states depends only on the investment (HMM-inv).
-This specification does not distinguish between pre- and post-manipulation games, nor does it distinguish between control and intervention conditions.
-It simply assumes that the way the investment affects the transition function of the trustee is the same regardless of which Game number and condition the data is from.
-Second, we specify a model for the transition function where we contrast two groups: Pre and Post Intervention, irrespective of the condition (HMM-prepost).
-Alternatively, we also specify three other models with contrasts distinguishing between pre and post intervention and the condition.
-A model that contrasts the post-intervention condition to the pre-intervention and both control conditions (HMM-coax).
-Another model that contrasts the post-control condition to the pre-control and both intervention conditions (HMM-ctrl).
-Finally, in a full contrast model, both pre-control and pre-intervention groups are coded as one group, another group consists of post-control and a third group of post-intervention condition (HMM-full).
-For all five specifications, we fit various HMMs with a number of states varying between 2 and 7 and select the model with the lowest BIC.
-
-Table \ref{tab:table-BICs-coax} shows the BICs of the various fitted models for an assumed number of states between 2 and 7.
+We analyzed participants' behavior differences in the intervention versus control conditions using hidden Markov models (HMM).
+Five models were used: "HMM-inv" assumed transition states depended solely on investment, ignoring game number and condition.
+"HMM-prepost" contrasted Pre and Post Intervention.
+"HMM-coax" contrasted post-intervention with pre-intervention and both control conditions.
+"HMM-ctrl" contrasted post-control with pre-control and both intervention conditions.
+"HMM-full" grouped pre-control and pre-intervention as one, with separate groups for post-control and post-intervention.
+Models were fitted using 2 to 7 states, selecting the lowest BIC.
+Generally, 5-7 state models best explained the data.
+A likelihood ratio test compared the models' goodness of fit, contrasting the complex HMM-full model with nested models equating behavior in certain stages and conditions.
+
+<!-- Table \ref{tab:table-BICs-coax} shows the BICs of the various fitted models for an assumed number of states between 2 and 7.
 For a simple model without any contrasts (HMM-inv) and a model with post-control only contrast (HMM-ctrl) we find a 6-state model to be best fitting.
@@
 We decided to stop at 7 states for computational cost reasons and because the interpretation of models with a higher number of states becomes complex.
+-->
 
@@
 <!--    ORDER THE STATES    -->
+
 ```{r, include=FALSE}
@@
 
-```{r trusteeHMMPlot, fig.cap="Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model",fig.align="center", fig.width=6, fig.height = 4}
-
-ggplot(response_best_mod,                            
+<!-- Using the best fitting model according to likelihood ratio tests (HMM-full), Figure \ref{fig:trusteeHMMPlot} shows the distribution of the participants' returns conditional on the latent state they are in.
+The states are ordered based on the mean of the Gaussian distribution fitted to the response (percentage return).
+State 1 represents the state in which the returns have have the lowest underlying mean, and state 5 is the state in which the returns have the highest underlying mean.
+The higher the state number the more pro-social the policy adopted.
+More specifically, state 1 can be thought of as a non-cooperative state in which returns are low and close to 0, meaning that the trustee is keeping most of the tripled investment.
+State 2 is a state where the average return is around the investment sent and can be interpreted as a cautious state in which the return on trust is small.
+States 3, 4 and 5 are increasingly cooperative states.
+For instance, in state 5, the average return is close to two thirds of the tripled investment, meaning the trustee is keeping an amount similar to the investment that was sent and returning to the investor double the investment.
+-->
+
+<!-- Figure \ref{fig:plotTransitionsDiscGaus} shows the transition between states as a function of the investment received for each group (pre-manipulation, post-control and post-intervention) using results from the best fitting model: HMM-full.
+The best fitting HMM model has multiple states and a high number of parameters.
+We can nonetheless focus on particular states linked to the breakdown and repair of cooperation.
+For instance, focusing on the transition functions to state 1 (the lowest return state with returns close to 0) from higher return states, we can compare the  post-control group to the post-intervention group.
+The red line representing the probability of transitioning to the low-return state 1 when the investment is close to 0 is lower in the intervention group compared to the control group when the trustee is in a relatively pro-social state (states 3 to 5).
+This is pointing towards more "forgiving" behavior where participants in the intervention group were less likely to transition to this anti-social state compared to the control group.
+-->
+
+Using the HMM-full model, we can retrieve participants' return distributions based on their latent states (Figures \ref{fig:postStatesBestMod}.A) and transition probabilities between these states (Figure \ref{fig:plotTransitionsDiscGaus}).
+The states are ranked by mean return, with State 1 having the lowest mean return and State 5 the highest.
+A higher state number indicates a more pro-social policy.
+We focused on states related to cooperation's breakdown and repair.
+We compared the transition probabilities between states when the investment is low for post-control and post-intervention groups.
+Figure \ref{fig:plotTransitionsDiscGaus} suggests that the intervention group is more forgiving of low investments, as they are less likely to shift to an anti-social state when faced with defection compared to the control group.
+
+```{r, include=FALSE}
+
+plot_state_transitions <- function(fmod, numCovIn, numCovTr) {
+
+  #print(getpars(fmod))
+  ns <- nstates(fmod)
+
+  trans_prob <- data.frame(
+    from = rep(1:ns, each=100*ns),
+    to = rep(1:ns, each=100),
+    investment = seq(0,20,length=100),
+    prob_pre = 0,
+    prob_ctrl = 0,
+    prob_coax =0
+  )
+
+  y0 <- matrix(0.0,ncol=ns, nrow=100)
+  y1 <- matrix(0.0,ncol=ns, nrow=100)
+  y2 <- matrix(0.0,ncol=ns, nrow=100)
+
+  for(from in 1:ns) {
+  pars <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
+  #print(pars)
+
+    for(to in 1:ns) {
+        x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"investment"]
+        y0[,to] <- exp(pars[to,1] + pars[to,2]*x)
+        #ctrst 2 = 1, post intervention vs pre
+        y2[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,3]*1 + pars[to,5]*x )
+        #ctrst 1 = 1, post control vs pre
+        y1[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,4]*1 + pars[to,6]*x )
+    }
+    y0 <- y0/rowSums(y0)
+    y1 <- y1/rowSums(y1)
+    y2 <- y2/rowSums(y2)
+
+    for(to in 1:ns) {
+      trans_prob$prob_pre[trans_prob$from == from & trans_prob$to == to] <- y0[,to]
+      trans_prob$prob_ctrl[trans_prob$from == from & trans_prob$to == to] <- y1[,to]
+      trans_prob$prob_coax[trans_prob$from == from & trans_prob$to == to] <- y2[,to]
+    }
+  }
+
+  saveRDS(trans_prob, "data/trans_prob.RDS")
+
+  return(trans_prob)
+
+  #  p_pre <- ggplot(trans_prob,aes(x=investment,y=prob_pre, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function pre manipulation") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
+  # 
+  # p_ctrl <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post control") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
+  # 
+  # p_coax <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post intervention") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
+  # 
+  # grid.arrange(p_pre, p_ctrl,p_coax, nrow=3, ncol=1)
+
+}
+
+# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
+
+```
+
+```{r,include=F}
+
+trans_prob <- readRDS("data/trans_prob.RDS")
+
+ctrl_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + 
+  geom_line() + 
+  geom_line(aes(y=prob_pre),linetype="dotted") +
+  facet_wrap(~from) + 
+  ylim(c(0,1)) + 
+  ggtitle("Transition function pre- and post-control manipulation") + 
+  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
+  theme_bw()
+
+coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
+  geom_line() + 
+  geom_line(aes(y=prob_pre),linetype="dotted") +
+  facet_wrap(~from) + 
+  ylim(c(0,1)) + 
+  ggtitle("Transition function pre- and post-intervention manipulation") + 
+  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
+  theme_bw()
+
+```
+
+```{r plotTransitionsDiscGaus, fig.cap="Transition function for the HMM-full trustee model.
+Each panel represents the state transitioned from, and each color the state transitioned to.
+Solid lines show estimated transition probabillities post-manipulation.
+Dotted lines show the same probabilities prior to the manipulation",fig.align="center", fig.width=6, fig.height = 7 }
+
+grid.arrange(ctrl_pre_plot , coax_pre_plot , nrow=2, ncol=1)
+
+# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
+
+```
+
+<!-- To explore the differences in transition probabilities between the control and coaxing conditions, we can choose an investment and compare the probabilities of transitioning between States.
+For instance, in case the trustee is low in trustworthiness (State 1), and the investor sends an average amount, we can compare the likelihood of the trustee transitioning away from the low trustworthiness state.
+Assuming an investment of 10 (half the endowment), The trustee remains in State 1 with around $85\%$ probability in the control condition, but only $67\%$ probability after the coaxing intervention.
+Likewise, assuming the trustee is in State 4, and receiving a low investment of 2, there is a much lower probability ($0.2\%$) of transitioning to low trustworthiness state in the coaxing condition compared to the control condition ($21\%$).
+-->
+
+```{r, include = FALSE}
+set.seed(20221010)
+# Get investor posterior states from model and add to data table
+
+# mention we are using local decoding (refer to the book). 
+predTrStates <- posterior(tr_fdmod_5, type="local")
+avg_ret_df$TrState <-  factor(predTrStates, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))
+
+# avg_ret_df$TrState <-  factor(predTrStates, levels= c(5,4,3,2,1),labels=c("5","4","3","2","1"))
+
+# predTrStates <- posterior(tr_fdmod_5)
+# avg_ret_df$TrState <-  factor(predTrStates$state, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))
+
+library(dplyr)
+temp_df <- avg_ret_df %>% dplyr::select(roundNum,investment,returns, next_investment, TrState)
+```
+
+```{r, include=FALSE}
+
+trusteeHMMPlot <- ggplot(response_best_mod,                            
        aes(x = returns,
@@
 
-```
-
-Using the best fitting model (HMM-full), Figure \ref{fig:trusteeHMMPlot} shows the distribution of the participants' returns conditional on the latent state they are in.
-The states are ordered based on the mean of the Gaussian distribution fitted to the response (percentage return).
-State 1 represents the state in which the returns have have the lowest underlying mean, and state 5 is the state in which the returns have the highest underlying mean.
-The higher the state number the more pro-social the policy adopted.
-More specifically, state 1 can be thought of as a non-cooperative state in which returns are low and close to 0, meaning that the trustee is keeping most of the tripled investment.
-State 2 is a state where the average return is around the investment sent and can be interpreted as a cautious state in which the return on trust is small.
-States 3, 4 and 5 are increasingly cooperative states.
-For instance, in state 5, the average return is close to two thirds of the tripled investment, meaning the trustee is keeping an amount similar to the investment that was sent and returning to the investor double the investment.
-
-Figure \ref{fig:plotTransitionsDiscGaus} shows the transition between states as a function of the investment received for each group (pre-manipulation, post-control and post-intervention) using results from the best fitting model: HMM-full.
-The best fitting HMM model has multiple states and a high number of parameters.
-We can nonetheless focus on particular states linked to the breakdown and repair of cooperation.
-For instance, focusing on the transition functions to state 1 (the lowest return state with returns close to 0) from higher return states, we can compare the  post-control group to the post-intervention group.
-The red line representing the probability of transitioning to the low-return state 1 when the investment is close to 0 is lower in the intervention group compared to the control group when the trustee is in a relatively pro-social state (states 3 to 5).
-This is pointing towards more "forgiving" behavior where participants in the intervention group were less likely to transition to this anti-social state compared to the control group.
-
-```{r, include=FALSE}
-
-plot_state_transitions <- function(fmod, numCovIn, numCovTr) {
-
-  #print(getpars(fmod))
-  ns <- nstates(fmod)
-
-  trans_prob <- data.frame(
-    from = rep(1:ns, each=100*ns),
-    to = rep(1:ns, each=100),
-    investment = seq(0,20,length=100),
-    prob_pre = 0,
-    prob_ctrl = 0,
-    prob_coax =0
-  )
-
-  y0 <- matrix(0.0,ncol=ns, nrow=100)
-  y1 <- matrix(0.0,ncol=ns, nrow=100)
-  y2 <- matrix(0.0,ncol=ns, nrow=100)
-
-  for(from in 1:ns) {
-  pars <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
-  #print(pars)
-
-    for(to in 1:ns) {
-        x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"investment"]
-        y0[,to] <- exp(pars[to,1] + pars[to,2]*x)
-        y2[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,3]*1 + pars[to,5]*x )
-        y1[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,4]*1 + pars[to,6]*x )
-    }
-    y0 <- y0/rowSums(y0)
-    y1 <- y1/rowSums(y1)
-    y2 <- y2/rowSums(y2)
-
-    for(to in 1:ns) {
-      trans_prob$prob_pre[trans_prob$from == from & trans_prob$to == to] <- y0[,to]
-      trans_prob$prob_ctrl[trans_prob$from == from & trans_prob$to == to] <- y1[,to]
-      trans_prob$prob_coax[trans_prob$from == from & trans_prob$to == to] <- y2[,to]
-    }
-  }
-
-  saveRDS(trans_prob, "data/trans_prob.RDS")
-
-  return(trans_prob)
-
-  #  p_pre <- ggplot(trans_prob,aes(x=investment,y=prob_pre, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function pre manipulation") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # p_ctrl <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post control") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # p_coax <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post intervention") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # grid.arrange(p_pre, p_ctrl,p_coax, nrow=3, ncol=1)
-
-}
-
-# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
-
-```
-
-```{r,include=F}
-
-trans_prob <- readRDS("data/trans_prob.RDS")
-
-ctrl_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + 
-  geom_line() + 
-  geom_line(aes(y=prob_pre),linetype="dotted") +
-  facet_wrap(~from) + 
-  ylim(c(0,1)) + 
-  ggtitle("Transition function pre- and post-control manipulation") + 
-  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
-  theme_bw()
-
-coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
-  geom_line() + 
-  geom_line(aes(y=prob_pre),linetype="dotted") +
-  facet_wrap(~from) + 
-  ylim(c(0,1)) + 
-  ggtitle("Transition function pre- and post-intervention manipulation") + 
-  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
-  theme_bw()
-
-```
-
-```{r plotTransitionsDiscGaus, fig.cap="Transition function for the HMM-full trustee model.
-Each panel represents the state transitioned from, and each color the state transitioned to.
-Solid lines show estimated transition probabillities post-manipulation.
-Dotted lines show the same probabilities prior to the manipulation",fig.align="center", fig.width=6, fig.height = 7 }
-
-grid.arrange(ctrl_pre_plot , coax_pre_plot , nrow=2, ncol=1)
-
-# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
-
-```
-
-<!-- To explore the differences in transition probabilities between the control and coaxing conditions, we can choose an investment and compare the probabilities of transitioning between States.
-For instance, in case the trustee is low in trustworthiness (State 1), and the investor sends an average amount, we can compare the likelihood of the trustee transitioning away from the low trustworthiness state.
-Assuming an investment of 10 (half the endowment), The trustee remains in State 1 with around $85\%$ probability in the control condition, but only $67\%$ probability after the coaxing intervention.
-Likewise, assuming the trustee is in State 4, and receiving a low investment of 2, there is a much lower probability ($0.2\%$) of transitioning to low trustworthiness state in the coaxing condition compared to the control condition ($21\%$).
--->
-
-```{r, include = FALSE}
-set.seed(20221010)
-# Get investor posterior states from model and add to data table
-
-# mention we are using local decoding (refer to the book). 
-predTrStates <- posterior(tr_fdmod_5, type="local")
-avg_ret_df$TrState <-  factor(predTrStates, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))
-
-# avg_ret_df$TrState <-  factor(predTrStates, levels= c(5,4,3,2,1),labels=c("5","4","3","2","1"))
-
-# predTrStates <- posterior(tr_fdmod_5)
-# avg_ret_df$TrState <-  factor(predTrStates$state, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))
-
-library(dplyr)
-temp_df <- avg_ret_df %>% dplyr::select(roundNum,investment,returns, next_investment, TrState)
-```
-
-```{r postStatesBestMod,  echo=FALSE, fig.cap = "Distribution of posterior trustee states post manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.", fig.align="center", fig.width=8, fig.height = 4}
 # investor real state distribution (posterior)
-ggplot(avg_ret_df %>% dplyr::filter(gameNum.f=="post")) +
+postHMM <- ggplot(avg_ret_df %>% dplyr::filter(gameNum.f=="post")) +
   geom_bar(aes(x = roundNum, group = TrState, fill = TrState),  position = position_stack(reverse = TRUE)) + 
@@
 
+```{r postStatesBestMod,  echo=FALSE, fig.cap = "A: Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model.
+The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social.
+B: Distribution of posterior trustee states post manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.", fig.align="center", fig.height = 8}
+
+ggpubr::ggarrange(trusteeHMMPlot , postHMM , nrow=2, ncol=1,labels = c("A", "B"),common.legend = FALSE)
+
+```
+
 ```{r, include= F}
@@
 
-To quantitatively explore the differences in transition probabilities between the control and intervention conditions, we can estimate from the model, using local decoding methods, the most likely posterior state of the trustee participants by round given the actions they have taken.
-Figure \ref{fig:postStatesBestMod} shows the distribution of these states by round for both the intervention and control groups post manipulation.
-We can see that participants were more likely to be in a lower return state in the control condition compared to the intervention condition.
-For instance, in round 5, state 1 was the most likely posterior state for $7$% of participants in the intervention condition compared to $24$% in the control condition, indicating a higher proportion of participants were in the lowest trustworthiness state without the intervention, and the differences between proportions were significant ($\chi^2(1) = 8.26, p < 0.01$).
-For the post defection trial after the intervention (round 14), state 1 was the most likely state for 22% of participants in the intervention condition compared to 43% in the control condition, and the differences between proportions were significant ($\chi^2(1) = 14.70, p < 0.001$).
-
-It is also noteworthy that there is an important heterogeneity in participants' most likely posterior state when faced with a situation like the one described during the intervention manipulation.
-Focusing on round 13 (the round where the low investment was sent post manipulation), we can see that a high proportion of participants ($30.2$%) in the intervention condition were in a low-return state.
-This group does not exhibit a behaviour consistent with the goal of the intervention.
-By contrast, another group exhibited behavior that is likely to be driven by assimilating the message from the coaxing manipulation, through transitioning to a high-return state even in the face of a low investment, which would be consistent with a coaxing behavior.
-Whilst only 11.3% in the control condition were in states 4 and 5 following the pre-programmed low investment, 30.3% of participants in the intervention condition were estimated to be in those states.
-The difference between the proportions is  statistically significant ($\chi^2(1) = 16.08, p < 0.001$).
+To quantitatively explore the differences in transition probabilities between the control and intervention conditions, we can estimate from the model, using local decoding methods from the depmixS4 package [@visser_depmixs4_2021], the most likely posterior state of the trustee participants by round given the actions they have taken.
+Figure \ref{fig:postStatesBestMod}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
+For instance, in round 5, state 1 was the most likely posterior state for only $7$% of participants in the intervention condition compared to $24$% in the control condition ($\chi^2(1) = 8.26, p < 0.01$).
+For the post-defection trial after the intervention (round 14), state 1 was the most likely state for only $22$% of participants in the intervention condition compared to $43$% in the control condition ($\chi^2(1) = 14.70, p < 0.001$).
+
+The posteriors also suggest that a non-negligible proportion of participants in the intervention condition did not exhibit a behaviour consistent with the goal of the intervention as they were still best fit by low-return states post intervention.
+For instance, focusing on round 13 post defection $30.2$% of those in the intervention condition were most likely to be in the least pro-social state 1.
 These differences can be seen as an indication of important heterogeneity in the effectiveness of the intervention.
 
+```{r, include=FALSE}
+# library(depmixS4)
+# 
+# n_bootstraps <- 1  # number of bootstrap resamples
+# bootstrap_estimates <- matrix(NA, nrow=n_bootstraps, ncol=1)  # to store bootstrap estimates
+# 
+# ns <- 3
+# numCovIn <- 2
+# numCovTr <- 6
+# from <- 3
+# to <- 1
+# 
+# for (i in 1:n_bootstraps) {
+#   # create a bootstrap resample of the data
+#   #bootstrap_data <- data[sample(nrow(data), replace=TRUE), ]
+#   bootstrap_data <- avg_ret_df %>% filter(id %in% sample(id,replace=TRUE))
+#   
+#   rModels <- rep(list(list(vtdgaus(y=bootstrap_data$ret_pct_0,yield=3*bootstrap_data$investment))),each=ns)
+#   
+#   simple_mod <- depmix(ret_pct ~ 1, data = bootstrap_data, nstates = ns, transition = ~ next_investment*intervention_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
+#   
+#   
+#   # fit the model to the bootstrap resample
+# 
+#   model <- makeDepmix(response=rModels, transition = simple_mod@transition , prior = simple_mod@prior, initdata=priordat, ntimes = rep(15,636), homogeneous=FALSE)
+#   
+#   cat("two")
+#   # trust_fullCtrst[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*intervention_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
+#   
+#   
+# 
+#   fit <- fit(model)
+#   cat("post-fit")
+# 
+#   # store the estimates
+#   #bootstrap_estimates[i, ] <- getpars(fit)
+#   
+#   pars <- matrix(getpars(fit)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
+#   
+#    bootstrap_estimates[i, ] <- pars[to,3]
+#   
+# }
+# 
+# # calculate 95% confidence intervals
+# ci_lower <- apply(bootstrap_estimates, 2, function(x) quantile(x, 0.025))
+# ci_upper <- apply(bootstrap_estimates, 2, function(x) quantile(x, 0.975))
+# 
+# # print the confidence intervals
+# print(ci_lower)
+# print(ci_upper)
+
+```
+
 # Discussion
-
-<!-- QH : I'd suggest introducing issues around trust in borderline a bit more early on, aslo discussing variability in treatment response, and the quest for mechanisms.
-This then forms an interesting platform for the discussion.
-The other aspect that probably needs discussing a bit more is the relationship between behaviour and emotion.
--->
 
@@
 On average, we saw the emergence of cooperative behavior with investment and returns in line with what is reported in human dyadic interaction in the repeated trust game [@charness_investment_2008; @fiedler_social_2011].
-The emergence of cooperative behavior and comments projecting human attributes on the opponent from the answers to the debrief questions, point to the potential of these agents to mimic human behavior in economic games whilst offering a higher degree of experimental control.
+The emergence of cooperative behavior and participant's uncertainty about whether they were facing human or artificial opponents, point to the potential of these agents to mimic human behavior in economic games whilst offering a higher degree of experimental control.
 
 The intervention's aim was to articulate the effect of acting on impulse in case of a transgressive action from the investor in the form of a one-off low investment.
-It explained that reciprocating this non-cooperative action might signal untrustworthiness and lead to a more permanent breakdown of cooperation.
-It also suggested an alternative strategy of coaxing the investor back into cooperation.
-When the agent defected as programmed, yielding a situation similar to the one presented in the intervention, we saw that the intervention led to higher percentage returns post defection compared to the control intervention, as intended.
-What was also notable, is that the intervention led to generally higher returns in post intervention, indicative of more cooperative behavior even before the defection trial.
-The question therefore is: what are the reasons for participants to engage in higher cooperative actions even in the absence of a sudden low investment?
-One possibility is that they have simply learned that by returning more, the investment on the next trial would be higher.
-If that was the case, we would expect a similar increase in percentage returns in the control condition, which we didn't find.
-Another possibility is that on average, the second player they faced invested more which prompted positive reciprocity in the human trustees.
+When the agent defected as programmed, yielding a situation similar to the one presented in the intervention, the intervention led to higher percentage returns post defection compared to the control group, as intended.
+Participants emotional reactions to the received investment, we similar pre and post-intervention, so the higher returns were produced despite participants having the same emotional reaction.
+This might indicate that the intervention achieved its goal of encouraging participants to respond in a non-impulsive, considered way, overriding the emotional urge to retaliate.
+
+What was also notable was that the intervention led to generally higher returns post-intervention, even before the defection trial.
+This could be for a number of reasons.
+One possibility is that participants simply learned that by returning more, the investment on the next trial would be higher.
+However, this explanation is unlikely, as we did not see a similar increase in percentage returns in the control condition.
+Another possibility is that, on average, the second player they faced invested more, which prompted positive reciprocity in the human trustees.
 As all players were programmed in the same way, any difference would be due to participant's actions.
-Likewise, participants rated both players similarly on relevant attributes of cooperativeness and trust.
+Further, participants rated both players similarly on relevant attributes of cooperativeness and trust.
 The higher returns are thus unlikely to be driven by different beliefs about the investor.
-A likely explanation for overall higher trustworthiness as measured by higher percentage return post investment is that participants, on average, interpreted the intervention message as an argument for more pro-social behavior, irrespective of the investor's actions.
-
-It is noteworthy that there were important individual differences in the percentage return changes post vs.
+A likely explanation for overall higher trustworthiness, as measured by higher percentage return post investment, is that participants, on average, interpreted the intervention message as an argument for more pro-social behavior, irrespective of the investor's actions.
+
+It is also noteworthy that there were important individual differences in the percentage return changes post vs.
 pre intervention, which can be seen as a proxy for the intervention effectiveness.
@@
 This raises important questions for the measurement of intervention effectiveness.
-Recent work has shed the light on the important heterogeneity inherent in how disorders are categorised: This heterogeneity arises from the view that mental health problems should be viewed as complex systems, or interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017].
+Recent work has shed light on the important heterogeneity inherent in how disorders are categorised: This heterogeneity arises from the view that mental health problems should be viewed as complex systems, or interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017].
 This view was used to justify computational psychiatry's difficulty in establishing differential and reliable predictors of likely treatment responses [@hitchcock_computational_2022].
 But if a healthy group's reaction to a relatively explicit intervention is itself heterogeneous as we have shown in this experiment, then the issue of variable treatment responses might the result of the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself.
-
 As such, a rigorous exploration of the determinants of inter-individual differences to an intervention in the general patient population is required.
-In our case, judging by the inter-individual heterogeneity in responses, some people may not have been convinced that a coaxing behavior was a good way to establish long term cooperative outcomes, and their need to "punish" the other player for their low investment may have been more pertinent than what we suggested.
+
+In our case, judging by the inter-individual heterogeneity in responses, some people may not have been convinced that a coaxing behavior was a good way to establish long term cooperative outcomes, and their need to “punish” the other player for their low investment may have been more pertinent than what we suggested.
 This was also evident from the participants' replies to a question about whether they would change their behavior, just after seeing the intervention manipulation.
@@
 We could aim to measure emotional reactions more accurately and explore whether specific emotions mediate the relationship between the investment received and the decision of what proportion to return.
-Measuring the emotions using the twos axes of valence and arousal could be improved: Results indicate that these concepts may not have been well understood by participants since we would not expect to see low arousal after the pre-programmed defection of the investor.
+Measuring the emotions using the two axes of valence and arousal could be improved: Results indicate that these concepts may not have been well understood by participants since we would not expect to see low arousal after the pre-programmed defection of the investor.
 
@@
 In future studies, we aim to explore the effects of different cognitive interventions and improve the experimental design in multiple ways.
-First, the intervention could benefit from being more interactive, with visual inputs such as cartoons or short videos, rather than only text, which can be more cumbersome to read and lead to lower engagement.
+First, the intervention could benefit from being more interactive medium, with visual inputs such as cartoons and videos, rather than pure text which can be cumbersome to read and lead to lower engagement.
 Second, we selected trustees from the general population, which might not suffer from the inability or unwillingness to repair relationships due to accidental breakdown of trust that characterises some mental health disorders such as BPD.
@@
 The high popularity of the Prisoner's Dilemma and the strategy of playing tit-for-tat may have resulted in a strong prior on which strategy to adopt in this game irrespective of the intervention.
-We opined that asking people about how they felt in the control condition might have affected how they behaved and might constitute an intervention in itself.
+We believed that asking people about how they felt in the control condition might have affected how they behaved and might constitute an intervention in itself.
 However, being able to compare the differential impact of the intervention on the emotional interpretation of the opponent action between an intervention and control conditions could lead to insights on the mechanism through which the intervention affects the emotional reaction to the opponent's actions.

### 2023-05-12 supplement.Rmd
revision QH comments by ismail

---
title: "Supplement"
# author: "Ismail Guennouni"
date: "2023-04-28"
output: pdf_document

bibliography: "bib/cogIntervention.bib"
biblio-style: spphys
---

```{r setupCoax, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE) 
knitr::opts_chunk$set(out.width = "\\textwidth")
```

# Repeated Trust Game 
<!-- Participants played two iterations of the standard version of the repeated trust game [@joyce_trust_1995]. The game is played in dyads, with one player assigned the role of the "investor" and the other player that of the "trustee". In the variant of the game we chose, the investor is endowed with 20 units at the start of each round. They need to decide how much of that endowment they want to invest with the trustee. The investment is then multiplied by a factor of 3 and sent to the trustee. As shown in Figure \ref{fig:trustGame}, the trustee in turn needs to decide how much of the (multiplied) investment they want to send back to the investor. If they send back more than a third of what they received, then both the investor and the trustee make a gain. Otherwise, the trustee would benefit but the investor would lose on their investment. If the interaction lasts for only one round, the Nash equilibrium of this game is for the investor to send nothing, as there is no incentive for the trustee to send back any return. In the repeated version, to maximise their rewards over time, both players need to build trust so that they can share the benefits of the bigger pie (the investment multiplied by three). If during the course of the interaction, the investor has been rewarded for taking the risk of sending an investment, then they would be more likely to invest more, and the multiplied investment would give both a bigger pie to share. If however the investor felt that they were not getting a return on their investment, then they would refrain from investing and neither would gain from the interaction. -->

Participants played a 15-round repeated trust game [@joyce_trust_1995] in the trustee role against a computer-programmed investor. On each round the investor was endowed with 20 units and decided how much of that endowment to invest. This investment is multiplied by a factor of 3 and sent to the trustee, who then decides how to split this between them and the investor. If the trustee returns more than a third, then the investor makes a gain. The Nash equilibrium for a single-round version is for the investor to send nothing. In the repeated version, rewards for both players are maximised if they build trust and share the benefits of the the investment multiplied by three. An investor who has been rewarded for taking the risk of sending an investment is more likely to invest more on future rounds. An investor obtaining a low return on their investment may choose to reduce future investment and thereby reduce both players’ gains.

```{r trustGame,fig.cap = "Screenshot of the repeated Trust Game. The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee. The investor is endowed with 20 units at the start of each round. They need to decide how much of that endowment they want to invest with the trustee. The investment is then multiplied by a factor of 3 and sent to the trustee. The trustee in turn needs to decide how much of the multiplied investment they want to send back to the investor. Shown here is the stage at which the trustee makes a decision of how much to send back the investor", fig.align='center'}

knitr::include_graphics("figures/trust_game.png")

```

## Feedback post investment in the repeated Trust Game

```{r grid,fig.cap = "Screenshot of the two axis grid in the Coaxing condition where participants were asked to report the valence and arousal of their emotional response ", fig.align='center'}

knitr::include_graphics("figures/emotion_grid.png")

```

Whilst playing the RTG, participants were asked to provide some feedback, in each round of the game, after seeing the amount sent by the investor. This feedback took the form of the answer to a question using a two dimensional field. What the axes of the field represented differed by condition. In the intervention condition, participants were asked to rate their emotional state with regard to the other player's choice of investment, with the x-axis representing the valence of the emotion they felt (positive or negative) and the Y-axis representing the emotional "arousal" they experienced (low or high). In the control condition, players were asked to rate attributes of the investment that were not related to their emotion, with the X-axis rating of how fast the investor is (slow or fast) and the Y-axis the magnitude of the investment (low or high). Figure \ref{fig:grid} shows a screenshot of the field in the intervention condition where participants were asked about their own emotional response to the investment. At the beginning of each game, participants were provided with detailed explanations of the meaning of the two axes as well as the opportunity to provide a baseline emotional state through using the field prior to the start of the game.

# Repeated Prisoner's Dilemma

The other game the participants played is the repeated Prisoner's Dilemma (RPD). Over multiple rounds, participants could choose one of two actions: A cooperative action that would yield a high pay-off if the other person also cooperated, and the lowest possible pay-off if they did not cooperate. Or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect. Figure \ref{fig:payoffsRPD} shows the payoff of each combination of actions as presented to the participants. As an opponent in this game, we used an artificial agent that was playing according to Tit-For-Tat [@axelrod_evolution_1981]. It started by choosing the cooperative action and then it mirrored whatever the other player played in the previous round.

```{r payoffsRPD,fig.cap = "Screenshot of the Repeated Prisoner's Dilemma game. Over multiple rounds, participants could choose one of two actions: A cooperative action that would yield a high pay-off if the other person also cooperated, and the lowest possible pay-off if they did not cooperate. Or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect. Shown here is the table explaining the payoffs of each combination of actions the participant and their opponent choose", fig.align='center'}

knitr::include_graphics("figures/screenshot_RPD_payoffs.png")

```

# Intervention Detail

The intervention consisted of presenting a hypothetical scenario in which they were playing the repeated trust game and the investor would send a low investment in a new round after having previously sent higher amounts. Participants were then asked how they would react in this situation and what sort of return (low or high) they were thinking of sending back. The players then were presented with an educational slide about the benefits of not resorting to impulsive decisions such as punishment when they feel they have been wronged. In this text, players were told that punishment can create a negative feedback loop where the other player might trust them even less. An alternative action was suggested, whereby players would respond kindly to such a transgression in the hope of gaining trust from the investor. The full text of the intervention slide is presented in Figure \ref{fig:interventionSlide}. Afterwards, participants were asked whether they would send a low or high return in the same hypothetical scenario now that they have read the information on the slide. Players were asked to justify their answer. For each question during this intervention, participants had to wait for a fixed duration of 20 seconds before being able to write their answers, and they were prevented from proceeding before that time was up.  This choice was made to allow participants to engage with the questions, think about their answers and provide meaningful feedback.

```{r interventionSlide,fig.cap = "Screenshot of the main  slide in the intervention condition", fig.align='center', out.width="80%"}

knitr::include_graphics("figures/intervention_text.png")

```

# Self report questionnaires

Failure to repair a breakdown in trust in the repeated trust game has been associated with trustees with BPD traits [@king-casas_rupture_2008]. Theories of social dysfunction in BPD have focused on dysfunction in the patients' mentalising ability [@allen_handbook_2006-1] as well as difficulties in emotional regulation [@rudge_mechanisms_2020]. The questionnaires we included in the experiment tried to assess borderline traits (PAI-BOR), emotional regulation capabilities (DERS) and mentalising ability (RFQ8). As such, we test for any association between scores in these questionnaires and the effect of the intervention.To analyse responses,  we fit a linear mixed effect model to the percentage return of trustees with fixed effects for Condition (intervention or control), Game-number (pre or post manipulation), Investment, and questionnaire score as well as all interactions between the fixed effects. We assume participant-wise random intercepts. We Z-transform the questionnaire scores and Investment as centering would be beneficial to interpreting the main effects more easily.
<!-- ## Statistical analysis of Behavior -->

# Hidden markov Model used to simulate the Investor's actions

The HMM assumes that the probability of each investment $I_t=0,…,20$, at each trial t, conditional on the current state of the investor $S_t$, is dependent on an underlying normal distribution with mean $\mu_s$ and standard deviation $\sigma_s$. The probability of each discrete investment was determined by the cumulative normal distribution $\Phi$. For instance, the probability of an investment $I_t=2$ is defined as:

$$P(I_t=2 | S_t=s)= \frac{\Phi(2.5 | \mu_s,\sigma_s ) - \Phi(1.5 | \mu_s,\sigma_s )} {\Phi(20.5 | \mu_s,\sigma_s ) - \Phi(-0.5 | \mu_s,\sigma_s )}$$

Note that the denominator truncates the distribution between 0 and 20. To estimate the transition probability between states for the investor, a multinomial logistic regression model was fitted to the investor's data such as:

$$P(S_{t+1} = s' | S_t=s , X_t = x)= \frac{\exp(\beta_{0,s,s'} + \beta_{1,s,s'} x)}{\sum_{s''} \exp(\beta_{0,s,s''} + \beta_{1,s,s''} x)}$$

where $X_t=R_t-I_t$ is the net return to the investor with  $R_t$ the amount returned by the trustee and $I_t$ is the Investment sent.

The advantages of this approach is that it does not require any a priori assumptions about the model features. The number of states, the policy conditional on the state, and the transition function between states can all determined in a purely data driven way. These HMMs can in turn be used to simulate a human-like agent playing the trust game. This agent may transition to a new state depending on the other player's actions and adopt a policy reflecting its state, thus simulating changes in emotional dispositions of human players during a repeated game. When the investor gains from the interaction, they become more likely to transition to a state where their policy is to be more trusting and invest more. However, faced with losses, the investor is more likely to transition to a more cautious policy where its investment belies lower trust in the trustee. The policies and the transitions between states are sufficient to build an agent that reflects this type of adaptive behavior and reacts to the trustee's action choices in a way that mimics a human player.

# Hidden Markov models to analyse participants returns

To model participants returns in the RTG across games and conditions,  we fit various hidden Markov models to participants returns. The response function is modelled as a discretised Gaussian distribution that takes into account what proportion the trustee would ideally like to return, and what returns are possible given the investment. For instance, if the investor sends an amount of $2$, the trustee would receive $6$ and they can send back any amount between $0$ and $6$. As such, we assume that the response is a distribution over proportions that can be calculated from these possible returns, i.e. $\{0,1/6, 2/6,...,1 \}$. The model assumes an underlying Normal distribution for each possible proportional return, predicting the probability of each via the cumulative Normal distribution with cut-off points set halfway between the proportions (e.g. the probability of returning 1/6 is determined as the probability of returning anything between 1/12 and 3/12).  The transition between states is assumed to depend on the investment through a multinomial logistic function such as:

$$P(S_{t+1} = s' | S_t=s , X_t = x)= \frac{\exp(\beta_{0,s,s'} + \beta_{1,s,s'} \ \text{inv} + \beta_{2,s,s'} \ x)}{\sum_{s''}\exp(\beta_{0,s,s''} + beta_{1,s,s'} \ \text{inv} + \beta_{2,s,s'} \ x)}$$

where $\text{inv}$ is a variable representing the investment received, $x$ is a dummy variable to characterise the group that the participant belongs to. We define four contrast codes for these dummy variables: pre-post (comparing pre and post games), post-coax (compares the post-intervention group to all others), post-control (compares the post-control group to all others) and full-contrast (a three level dummy variable: post-intervention compared to post-control and  all pre games).

# References

### 2023-05-12 example.R

@@ -1,0 +1,50 @@
+# Create a synthetic dataset
+set.seed(42)
+n <- 300
+states <- c(rep(1, n/3), rep(2, n/3), rep(3, n/3))
+y <- numeric(n)
+x <- numeric(n)
+
+y[states == 1] <- rnorm(sum(states == 1), mean = 0, sd = 1)
+y[states == 2] <- rnorm(sum(states == 2), mean = 5, sd = 1)
+y[states == 3] <- rnorm(sum(states == 3), mean = 10, sd = 1)
+
+x[states == 1] <- sample(0:1, size = sum(states == 1), prob = c(0.7, 0.3), replace = TRUE)
+x[states == 2] <- sample(0:1, size = sum(states == 2), prob = c(0.3, 0.7), replace = TRUE)
+x[states == 3] <- sample(0:1, size = sum(states == 3), prob = c(0.5, 0.5), replace = TRUE)
+
+data <- data.frame(y = y, x = x)
+
+# Fit an HMM model with a binary covariate in the transition function
+hmm <- depmix(y ~ 1, data = data, nstates = 3, family = gaussian(),
+              transition = ~ x)
+fitted_model <- fit(hmm)
+
+# Get the estimates of the transition function
+transition_pars <- getpars(fitted_model, which = "transition")
+
+# Get the covariance matrix of the transition function parameters
+cov_matrix <- vcov(fitted_model, which = "transition")
+
+
+# Find the indices of the binary covariate coefficients in the transition function
+binary_covariate_indices <- c(4, 8)
+
+# Wald tests
+for (i in binary_covariate_indices) {
+  estimate <- transition_pars[i]
+  standard_error <- sqrt(cov_matrix$vcov[i, i])
+  wald_statistic <- (estimate / standard_error)^2
+  p_value <- pchisq(wald_statistic, df = 1, lower.tail = FALSE)
+  
+  cat("Wald statistic (", i, "):", wald_statistic, "\n")
+  cat("p-value (", i, "):", p_value, "\n")
+  
+  # Interpret the result
+  alpha <- 0.05
+  if (p_value < alpha) {
+    cat("The binary covariate coefficient (", i, ") is significantly different from 0.\n")
+  } else {
+    cat("The binary covariate coefficient (", i, ") is not significantly different from 0.\n")
+  }
+}

### 2023-05-23 article.Rmd
fixed title Latex

@@
 ---
-title: Repairing cooperation through a cognitive intervention in the repeated Trust Game
-subtitle: 
-titlerunning: 
-authorrunning: 
-# thanks: The authors have no conflicts of interest to declare that are relevant to the content of this article.
-This work was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1.
-
-authors:
-- name: Ismail Guennouni
-  address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
-  email: i.guennouni.17@ucl.ac.uk
-
-- name: Maarten Speekenbrink
-  address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
-  email: m.speekenbrink@ucl.ac.uk
-
-- name: Quentin Huys
-  address: Max Planck Institute of Computational Psychiatry
-  email: q.huys@ucl.ac.uk
-
-- name: Samuel Dupret
-  address: HLI
-  email: sam.dupret@ucl.ac.uk
-
+title: "Repairing cooperation through a cognitive intervention in the repeated Trust Game"
+author:
+  - Ismail Guennouni
+  - Maarten Speekenbrink
+  - Quentin Huys
+  - Samuel Dupret
+
+# - name: Ismail Guennouni
+#   address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
+#   email: i.guennouni.17@ucl.ac.uk
+# 
+# - name: Maarten Speekenbrink
+#   address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
+#   email: m.speekenbrink@ucl.ac.uk
+# 
+# - name: Quentin Huys
+#   address: Max Planck Institute of Computational Psychiatry
+#   email: q.huys@ucl.ac.uk
+# 
+# - name: Samuel Dupret
+#   address: HLI
+#   email: sam.dupret@ucl.ac.uk
 keywords:

### 2023-05-23 test.Rmd
fixed title Latex

--- 2023-05-23 article.Rmd
@@
 ---
-
-```{r setupCoax, include=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE) 
-knitr::opts_chunk$set(out.width = "\\textwidth")
-```
-
-```{r load-packages05, include = FALSE}
-library(papaja)
-library(kableExtra)
-require(knitr)
-require(citr)
-require(bookdown)
-
-# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
-library(tidyverse)
-library(afex)
-library(PairedData)
-library(multcompView)
-library(lsmeans)
-library(depmixS4)
-library(flextable)
-library(gridExtra)
-library(forcats)
-library(ggsignif)
-
-```
-
-```{r analysis-preferences, include = FALSE}
-# Seed for random number generation
-set.seed(42)
-options(tinytex.verbose = TRUE)
-```
-
-# Introduction
-
-At the core of social interaction is figuring out the goals, intentions, and decision-making process of the interaction partner.
-This inference is however fraught with uncertainty, as we cannot reasonably observe these features without prior knowledge of the person.
-Absent a history of interaction, one needs to decide whether to take the risk of trusting others.
-The challenge of trust is that it is by construction a risky endeavour.
-For example, if we deem a person trustworthy, we might decide to take the risk of investing in the relationship hoping for a collaborative outcome.
-If we misplace our trust, this can come at a high cost to us.
-Not trusting others is also risky since opportunities for cooperation may be foregone.
-
-<!-- and any substitution for trust, such as excessive suspicion, over-reliance on self and other maladaptive strategies are likely to add burden and costs to a person. -->
-
-Evidence from the literature emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016 ; @meng_multilevel_2014].
-It affects the health status of individuals through reinforcing social support networks, maintaining community norms and facilitating collective action.
-Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders.
-@fonagy_role_2014 identified epistemic trust, or the belief in the authenticity and personal relevance of interpersonally transmitted knowledge, as an important function of early attachment relationships.
-It allows the individual receiving social information to let go of their natural self-protective vigilance, which can become a pathological hypervigilance frequently observed after traumatic experiences and a key factor for the emergence of multiple mental health disorders [@fonagy_mentalizing_2017].
-
-<!-- A well-established paradigm in the study of the emergence and maintenance of trust is the repeated trust game [@joyce_trust_1995].
-In this game, one player takes the role of the "investor" and is provided with a fixed endowment at the start of each trial.
-They get to decide how much of their endowment to invest with the other player taking the role of the "trustee".
-The amount that is sent is tripled and the trustee gets to decide, in return, how much of the tripled amount to send back to the investor.
-If the investor sends a non-zero amount, they express trust in the other player for that round, as the amount they will receive back is uncertain.
-Assuming the trustee sends back more than the initial investment, they signal trustworthiness to the investor and both players make gains.
-This scenario would constitute a cooperative exchange and would be mutually beneficial.
-However, cooperation in this setting is prone to be broken through intentional or simply misinterpreted actions that can convey lack of trust or trustworthiness such as low investments and returns [@bendor_when_1991].
-In order to repair a damaged cooperative equilibrium, players need to infer that their behaviour has violated social norms and offer amends through generous actions at potentially a high cost to them.
-@king-casas_rupture_2008 links the breakdown of cooperation in trustees with Borderline Personality Disorder to the absence or reduction of activation in brain regions associated with the perception of norm violations.
--->
-
-Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions to foster and strengthen trust-based cooperation would be highly beneficial to society.
-Such interventions would allow people to more easily repair broken relationships, and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
-
-<!-- Mechanism design, pioneered by @vickrey_counterspeculation_1961, is a field that studies incentive alignment and looks for ways to promote social welfare or revenue maximization, despite self-interest of the individual actors.
-In the context of social dilemmas, key mechanisms were explored with good effect to foster and maintain the cooperative outcome.
-@axelrod_evolutionary_1986 studied the emergence and stability of behavioral norms to regulate non-cooperative actions in social settings.
-He identifies a behavioral norm as a dominant behavioural strategy which is often punished by others when not adhered to.
-A meta-norm is the propensity to incur a cost in order to enforce a norm.
-@axelrod_evolutionary_1986 showed that when playing a social dilemma game, individuals have a strong incentive to enforce punishment of defectors lest they are in turn punished by others.
-This led to a decline of defection.
-Thus, meta-norms can be seen as a mechanism to promote and sustain cooperation in a population.
-In the context of the trust game, @charness_investment_2008 explored the effect a third party monitor can have on the amounts sent and received.
-This third-party's payoff is unaffected by the decisions made by the investor and trustee.
-However, the study allowed the third party to punish overly selfish trustees or reward Investors making a loss on the interaction.
-They found that the actions of both players were materially more cooperative in the presence of this third party.
-@fiedler_effect_2017 found that the introduction of a third party that monitors the investments and returns of the players led to more cooperative behavior, even when the third party had no ability to reward or punish the players.
--->
-
-A well-established paradigm in the study of trust is the repeated trust game [@joyce_trust_1995].
-To encourage the emergence and maintenance of trust in this setting, some studies focused on modifying the game mechanism [@charness_investment_2008; @fiedler_effect_2017].
-Others chose to intervene directly on the participants.
-For example, @drazkowski_gratitude_2017 found that trust was increased when participants were asked to think about and write down five things that they were grateful for.
-@burnham_friend-or-foe_2000 found that trust was also increased when participants were primed with the concepts of friend and foe.
-
-Whilst these interventions show that it is possible to improve cooperative outcomes at the start of the game, they did not address how to repair a breakdown of trust that might occur due to intentional or accidental non-cooperative actions by the players.
-Indeed, cooperative play in the repeated trust game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor after cooperation has been established, or a return of the trustee below the investment sent.
-Such ruptures of cooperation appear frequently when the trustee suffers from mental health disorders affecting the social domain such as Borderline Personality Disorder [@lieb_borderline_2004].
-In theses situations, BPD trustees fail to engage in trust repairing behavior such as coaxing the investor through sending high return to signal trustworthiness, and this failure may be linked to a failure to perceive their low returns in the game as a violation of social norms [@king-casas_rupture_2008].
-
-In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of interpersonal dysfunction in BPD patients.
-Whilst there is no proven pharmacological therapy for BPD, some forms of psychotherapy such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993], have been clinically validated as efficacious approaches to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
-However, these therapies suffer from a high variability in treatment responses.
-Determining which interventions are effective for particular patients has been very challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
-One promising approach is the study of how specific psychotherapeutic treatment components affect quantitative markers of behavior such as those inferred through computational modelling techniques [@huys_computational_2016; @reiter_neuro-cognitive_2021].
-As such, using specific cognitive probes inspired by therapeutic interventions complemented by computational modelling of behavior in tasks, may allow us to uncover cognitive mechanisms targeted by common forms of psychotherapy.
-This may in turn form the basis for targeting of existing psychotherapies to different individuals.
-
-In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a pre-programmed, one-off low investment sent by an computer investor.
-The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation.
-Participants are given the role of the trustee and are randomly assigned to either a control group or an intervention group.
-They play two instances of the repeated Trust Game facing what they believe are two different players.
-In between games, they either receive a cognitive intervention (intervention condition) or not (control condition, where participants are asked to solve anagrams).
-In reality, participants face the same computerised agent in both instances, which is programmed to play according to an HMM fitted to real players data.
-We explore whether the intervention has an effect on the behaviour of the trustee and whether the learning is transferred to a new repeated Prisoner's Dilemma game when facing a seemingly new player.
-
-```{r dataLoad, include=FALSE }
-d_finished <- readRDS("data/d_finished.RDS")
-```
-
-# Method
-
-## Participants and Design
-
-A total of 318 participants were recruited on the Prolific Academic platform (prolific.co).
-The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years.
-Participants were paid a fixed fee of £5 plus a bonus dependent on their performance.
-The experiment had a 2 (Condition: Intervention or Control) by 2 (Game : Pre or Post Intervention) design, with repeated measures on the first factor.
-Participants were randomly assigned to one of the two levels of the second factor.
-
-## Procedure
-
-```{r timeline, fig.cap = "A) Experiment overview.
-After playing 15 rounds of a repeated trust game (RTG) as trustee, participants were randomized to either receive the control or active intervention.
-They then played the second set of 15 rounds of RTG (again as trustee) to examine intervention effects, and 7 rounds of a repeated prisoner’s dilemma to examine generalization of intervention effects.
-Finally, participants answered questionnaires and were debriefed.", fig.align='center', out.width="80%"}
-
-knitr::include_graphics("figures/timeline.png")
-
-```
-
-<!-- Figure \ref{fig:timeline} shows the timeline of the experiment.
-After reviewing an information sheet about the experiment, participants were informed that there would be three phases to go through, with them facing a different opponent in each phase.
-They would face the same player throughout the first phase, consisting of the "Investment Game" with several rounds.
-This was the moniker used for the repeated trust game, and a total of 15 rounds were played.
-Participants were then randomly assigned to either a control or intervention condition.
--->
-
-<!-- <!-- After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.
-A comprehension quiz on the trust game followed the instructions.
-The first trust game then ensued:  Each round started with an investment stage where the investor decided how much to send to the trustee and that choice was revealed.
-Immediately afterwards, participants were presented with a two-dimensional field to indicate their emotional state on two dimensions: valence, from unpleasant to pleasant (on the horizontal axis) and arousal, from low arousal to high arousal (on the vertical axis).
-After selecting a point on the field, participants were asked to decide how much to send back to the investor using a slider ranging from sending back nothing to sending back the whole (tripled) investment.
-Following that choice, an outcome page summarised both players decisions and showed the total pay-off for each player and the round then concluded.
-At the end of the game, participants were asked to rate the player they were facing on 4 attributes using a scale from 1 to 10: Trustworthiness, friendliness, cooperativeness and selfishness.
--->
-
-<!-- In the second phase of the experiment, participants were informed they would be paired with a different player.
-This phase was similar to the first phase in terms of the game played (RTG) and the number of rounds.
-In all rounds of the RTG, participants gave feedback after seeing the investment received.
-This feedback was given though a two dimensional grid that was either related to their emotional state (degree of valence of arousal) in the Intervention group, or unrelated to the emotional state in the control group (speed of investor's response and magnitude of investment).
-At the end of each RTG, participants were asked to rate how cooperative, selfish, trustworthy and friendly they thought their interaction partner was.
-Details of the two dimensional grid and player ratings are given in the supplement.
--->
-
-<!-- After both trust games,  players were told they would be paired with a new player in the third phase of the experiment.
-This third phase consisted of 7 rounds of the prisoner's dilemma game, facing the new player.
-Throughout all games, players were explicitly told to aim to maximise the number of points as their bonus would depend on the score they accumulated throughout the experiment.
-The total number of rounds was not communicated to the participants in any of the games played.
--->
-
-<!-- After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment.  -->
-
-<!-- <!-- These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016].
--->
-
-<!-- Finally, participants were asked a series of questions around how they played each phase.
-First, they were asked whether they thought they played differently in the second compared to the first phase of the RTG.
-Second, participants had to select whether they thought the opponents they faced were human or computer agents.
-Finally, we revealed to the participants that they faced the same computer agent throughout the RTG.
-We explained that any change in their perception of the opponent or any change in how the opponent played is due to their own change in behavior as the agent was simply reacting to their actions.
-Finally, we asked participants to reveal whether this experiment has taught them anything about how they should behave in social situations.
--->
-
-The experiment as shown in Figure \ref{fig:timeline} began with participants briefed there will be three phases, and that they would face a new opponent in each phase.
-Phase one was a 15 round Trust Game (RTG) in which participants had the role of the trustee, facing the same investor opponent.
-Participants were then assigned to either the control or intervention conditions.
-Phase two was similar to Phase one, with participants being told they faced a new player.
-In both phases, participants were asked for feedback in each round after seeing the investment.
-The nature of the feedback solicited varied by condition, either emotion-related (intervention) or unrelated (control).
-Participants rated their interaction partner on various attributes after each phase.
-More details on these attributes, nature of feedback and exact instructions are found in the supplement.
-Phase three involved 7 rounds of the repeated prisoner's dilemma game (RPD) with a third player.
-Participants were explicitly told to aim to maximise the number of points in all phases.
-The total number of rounds was not communicated to the participants in any of the games played.
-
-Post-experiment, participants completed questionnaires related to mentalising abilities, emotion regulation and BPD traits (see details in supplement).
-They were then quizzed on their game-play, including whether they detected that all opponents were computer agents.
-The reveal explained that they were facing identical AI agents and that any perceived opponent changes were due to participants' own behavior.
-
-## Interventions
-
-The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taking in emotional states [@linehan_dbt_2015].
-Specifically, participants were presented with a low investment and asked to indicate their response.
-They were then invited to consider what their ultimate aim in the game was and whether this response was most likely to achieve their aim.
-The intervention is detailed in the supplementary information.
-
-In the control condition, participants were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
-They provided their answers in a free-form text box.
-The time given to solve the anagrams was the same as that given to respond to questions in the intervention manipulation.
-
-## Design of the AI agents in the RTG and RPD
-
-```{r, include=FALSE}
-Anti_social <-  c(0.1025436430408, 0.1221931236853, 0.1345215238995,
-0.1368182252617, 0.1285592471751, 0.1116014322677, 0.0895041220882,
-0.0663166721334, 0.0453950277118, 0.0287077419587, 0.0167723588011,
-0.0090530028158, 0.0045143317507, 0.0020796744990, 0.0008851094702,
-0.0003480141146, 0.0001264134789, 0.0000424213859, 0.0000131513231,
-0.0000037665630, 0.0000009965755)
-
-Neutral <- c(0.003393529, 0.006930874, 0.013053553, 0.022671228,
-0.036310144, 0.053627606, 0.073039389, 0.091734929, 0.106248217,
-0.113479701, 0.111769796, 0.101517390, 0.085028780, 0.065675083,
-0.046778251, 0.030725245, 0.018610323, 0.010394861, 0.005354126,
-0.002543094, 0.001113881)
-
-Pro_social <- c(0.003162697, 0.001057162, 0.001410197, 0.001881016,
-0.002508877, 0.003346113, 0.004462480, 0.005950950, 0.007935434,
-0.010581067, 0.014107909, 0.018809194, 0.025075644, 0.033427845,
-0.044559370, 0.059394206, 0.079163228, 0.105506029, 0.140606514,
-0.187373417, 0.249680651)
-
-investment <- seq(0:20) -1
-
-response_probs <- as.data.frame(cbind(investment,Anti_social,Neutral,Pro_social)) %>% 
-  rename("low-trust" = "Anti_social", "medium-trust"="Neutral", "high-trust" = "Pro_social") %>%
-  pivot_longer(cols=c("low-trust","medium-trust","high-trust"),
-                    names_to='Investor_state',
-                    values_to='probability') %>% 
-   mutate(across(Investor_state, factor, levels=c("low-trust","medium-trust","high-trust")))
-```
-
-```{r, include=FALSE}
-
-plotinvHMM <- ggplot(response_probs,                            
-       aes(x = investment,
-           y = probability,
-           fill = Investor_state)) +
-  geom_bar(stat = "identity",
-           position = "dodge") + 
-  labs(fill='Latent investor state') + 
-  theme_bw() + 
-  theme(legend.position = "bottom")
-
-```
-
-```{r, include=FALSE}
-
-unhappy_pars <- rbind(c(3.5435248 , 0.0592584), c(0.1611541, 0.4675468), c(0,0)) 
-neutral_pars <- rbind(c(0.8846036, - 0.4394031), c(2.4214322, - 0.0710711), c(0,0))
-happy_pars <- rbind(c(-2.004988 ,- 0.151186), c(-1.2976976 , - 0.1357088), c(0,0))
-
-pars_inv <- list(unhappy_pars, neutral_pars, happy_pars)
-
-plot_HMM_transitions <- function(ns, pars_mat) {
-
-  trans_prob <- data.frame(
-    from = rep(1:ns, each=100*ns),
-    to = rep(1:ns, each=100),
-    ret = seq(-20,60,length=100),
-    probs = 0
-  )
-
-  y <- matrix(0.0,ncol=ns, nrow=100)
-
-  for(from in 1:ns) {
-  pars <- matrix(pars_mat[[from]], ncol=2)
-  # print(pars)
-
-    for(to in 1:ns) {
-        x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"ret"]
-        y[,to] <- exp(pars[to,1] + pars[to,2]*x)
-    }
-    y <- y/rowSums(y)
-
-    for(to in 1:ns) {
-      trans_prob$probs[trans_prob$from == from & trans_prob$to == to] <- y[,to]
-    }
-  }
-
-  df <- as.data.frame(trans_prob) %>% 
-    mutate(from = recode(from, "1" = "low-trust", "2" = "medium-trust", "3" = "high-trust"),
-           to = recode(to, "1" = "low-trust", "2" = "medium-trust", "3" = "high-trust") ) %>% 
-    mutate(across(from, factor, levels=c("low-trust","medium-trust","high-trust"))) %>% 
-    mutate(across(to, factor, levels=c("low-trust","medium-trust","high-trust")))
-
-  ggplot(df,aes(x=ret,y=probs, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) +  labs(x = "Investor's Net Return", y = "Transition probability", color='State Transitioned to') +
-    theme_bw() + theme(legend.position = "bottom")
-
-}
-
-```
-
-```{r, include=FALSE}
-
-plotInvTran <- plot_HMM_transitions(3, pars_inv)
-
-```
-
-```{r HMMPanels, fig.cap="A: Distribution of investments by the artificial investor agent conditional on its latent state as estimated by a three state hidden Markov model fitted to human dyadic play dataset.
-B: Transition function for the HMM investor conditional on its current state and the net return from the previous round of play.", fig.align="center"}
-
-ggpubr::ggarrange(plotinvHMM , plotInvTran, nrow=2, ncol=1, labels = c("A", "B"), common.legend = TRUE, legend = "bottom")
-
-```
-The role of the investor was in reality played by an adaptive artificial agent whose strategy was modelled on the behaviour of human participants taking the role of the investor in the RTG.
-Using data from human dyadic interaction in the 10 round trust game, we estimate a Hidden Markov Model (HMM) to characterise the investor's behavior as emanating from a small number of latent states [@rabiner_hmm_1989].
-In this instance, for both iterations of the repeated trust game, the HMM used was identical: it had three states that can be described as "low-trust", "medium-trust" and "high-trust".
-Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust, as presented in Figure \ref{fig:HMMPanels}.A.
-Transition probabilities between these latent states were modelled as a function of the net return in the previous round conditional on the investor's state as shown in Figure \ref{fig:HMMPanels}.B.
-
-<!-- In order to probe efforts to repair trust, we introduced rounds where the investor deviated from the policy provided by the HMM, and chose to send a low investment in the Trust Game, or chose the non-cooperative action in the Prisoner's Dilemma.
-In the trust games, we programmed the HMM agent to send a very low investment (2 out of 20) to the trustee on specific rounds (round 12 pre-intervention and 13 post-intervention).
-For the repeated Prisoner's Dilemma game, we programmed the agent to choose the non-cooperative action on round 4.
-After each "defection" round, the agents were programmed to proceed their policy from before that round, effectively ignoring the participants' response to their defection.
-For instance, the HMM investor would send an investment in the post defection round that was consistent with the outcome of the round immediately prior to that round.
-For the RPD, the agent would continue to play tit-for-tat, but also ignoring what happened in the defection round, and basing its action on mirroring what the other player did in the round immediately prior to the defection round.
-This ignorance of reactions to the defection rounds was chosen to reflect an accidental defection, with the Investor being open to repair subsequent interaction.
--->
-
-In order to probe efforts to repair trust, we simulated trust breaches in both Trust Games and the Prisoner's Dilemma.
-The AI was programmed to break trust on specific rounds (12 pre-intervention, 13 post-intervention in the Trust Game; round 4 in Prisoner's Dilemma).
-After these "defection" rounds, the AI returned to its previous strategy, disregarding the participant's response to the breach.
-This simulated an accidental defection and a readiness to repair the interaction, providing insights into trust repair dynamics.
-
-<!-- ## Computational analysis of trustee returns -->
-
-<!-- In order to characterise the effect of the intervention on the trustees strategy, we fit a Hidden Markov Model to the percentage returns of the trustees for the RTG data.
-The model allows for switching between latent trustee states over time.
-Hidden Markov models assume that an observable trustee return at time $t$ depends on a latent trustee state at time $t$.
-It is assumed that the latent state at time $t$ depends on the latent state at the previous time $t-1$.
-The model is specified by the state-conditional action distributions (these are provided by the likelihood of the fitted models), an initial state distribution (the distribution over the strategies at the initial round), and the state-transition probabilities (probability of switching from one state/strategy to another).
-Initial state probabilities and the transition probabilities were estimated with the depmixS4 package [@visser_depmixs4_2021].
--->
-
-## Analysis of participants returns in the RTG
-
-To explore whether participants behaved differently after the intervention compared to the control group over all rounds, we estimate a linear-mixed effects model as implemented in the R package "afex" [@singmann_afex_2022], with fixed effects for Condition (intervention or control), Game-number (pre- or post-intervention) and Investment, as well as interactions between Condition and both Investment and Game-number, and participant-wise random intercepts and random slopes for Game-number.
-More complex models with additional random effects provided could not be estimated reliably.
-For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
-We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
-
-To model participants returns in the RTG across games and conditions, we fit various hidden Markov models to participants returns using the depmixS4 package [@visser_depmixs4_2021].
-The transition between latent states is assumed to depend on the investment received and a dummy variable to characterise the group that the participant belongs to.
-Details on how the models are constructed as well as the various contrast codes used for the dummy variables are found in the supplement.
-We fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978-1] to select the best model.
-
-# Behavioral results
-
-<!-- Our investment levels are clearly comparable.
-Our random matching condition is the most directly comparable to Berg et al., (1995) and Charness et al., (2008), both of whom used random matching.
-Our investment averages 4.97 out of 10 in the individual feedback condition, which falls right in between the investment level of 5.16 documented by Berg et al., (1995) and the 3.73 documented by Charness et al., (2008).
-The amount returned in the individual feedback condition with random matching is 5.61, which is slightly higher than the amounts returned in Berg et al., (1995) of 3.73 and Charness et al., (2008) of 4.65.
-The 19% return rate is comparable to results in similar designs.
-In an almost identical design, Fiedler et al., (2011) report a 17% return rate by responders.
-This is similar to our finding.
--->
-
-```{r dataClean, include=FALSE}
-# Filter only trust rounds and create % returns and investments
-
-avg_ret_df <- d_finished %>%
-  dplyr::select(id, condition.f,roundType,investment,returns,roundNum,gameNum.f,BPD_trait,PBOR_score,DERS_score,RFQ_c,RFQ_u) %>% 
-  mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing"))%>%
-  filter(roundType=="trust",!is.na(roundNum)) %>% 
-  mutate(roundNum = as.numeric(as.character(roundNum))) %>%
-  mutate(inv_scaled = scale(investment)) %>% 
-  mutate(inv_pct = investment/20, ret_pct = returns/(3*investment), ret_pct_0 = ifelse(investment==0,0,returns/(3*investment)))  %>% 
-  # Creating Quartiles of % returns by participant over BOTH TRUST GAMES
-  group_by(id) %>% 
-  mutate(mean_pct_ret = mean(ret_pct), mean_abs_ret = mean(returns), mean_inv = mean(investment)) %>%
-  ungroup() %>% 
-  mutate(Quart_pct_ret = ntile(mean_pct_ret,4),
-         Quart_abs_ret = ntile(mean_abs_ret,4),
-         Quart_inv     = ntile(mean_inv, 4))
-
-# %>%
-#   filter(complete.cases(.))   # <- one player had NA in one round as a return, so we exclude him from analysis.
-
-# Number of people left for analysis. 
-nrow(avg_ret_df %>% filter(condition.f == "intervention"))/30
-nrow(avg_ret_df %>% filter(condition.f == "control"))/30
-
-# average investment for first 10 rounds pre intervention
-avg_pct <- avg_ret_df %>% filter(roundNum < 11 , gameNum.f == "pre") %>% summarise(avg_inv = mean(inv_pct), avg_ret = mean(ret_pct, na.rm=TRUE))
-```
-
-Average investments and returns prior to the defection round (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
-Estimated marginal means of percentage returns from fitting the mixed effects model specified in the methods section, as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.A.
-
-<!-- Investments averaged `r round(avg_pct$avg_inv,3)*100` $\%$ of endowment which is less than the $63.2\%$ documented by @fiedler_social_2011 and higher than the $37.3%$ documented by @charness_investment_2008, although the latter used repeated one shot games with random matching.
-Returns averaged `r round(avg_pct$avg_ret,3)*100` $\%$  of the total yield (3x investment sent), which is higher than the $35\%$ found in the same setting in @fiedler_social_2011.
--->
-
-```{r gamesPlot, echo=FALSE, fig.cap="Average and standard errors of the trustee's return as a percentage of the multiplied investment received for each round and for both conditions.
-The red line shows the returns pre-manipulation and the blue line post-manipulation.We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel",fig.align="center", fig.width=6, fig.height = 4}
-
-# colors <- c("investment" = "blue", "returns" = "red")
-# 
-# ggplot(avg_ret_df,aes(x=as.factor(roundNum),group = 1)) +
-#   stat_summary(fun = "mean", geom = "line", aes(y=returns, color ="returns")) +
-#   stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=returns) ) +
-#   stat_summary(fun = "mean", geom = "line", alpha =0.4,aes(y=investment, color = "investment")) +
-#   stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=investment) ) +
-#   facet_wrap(~condition.f*gameNum.f) +
-#   labs(x = "Round",
-#        y = "Investment / Return",
-#        color = "Legend") +
-#   scale_color_manual(values = colors) +
-#   theme_bw() +
-#   theme(legend.position = "bottom")
-
-# Alternative chart with pre vs post percentage returns in one panel as suggested by QH.
-
-ggplot(avg_ret_df ,aes(x=as.factor(roundNum),group=gameNum.f, color = gameNum.f)) +
-  stat_summary(fun = "mean", geom = "line", aes(y=ret_pct)) +
-  stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=ret_pct) )+
-  labs(x = "Round",
-       y = "Percentage Return",
-       color = "Game") +
-  # ylab("Percentage Return") +
-  # xlab("Round") +
-  theme_bw() +
-  theme(legend.position = "bottom") +
-  facet_wrap(~condition.f)
-
-```
-
-```{r, include=FALSE, cache=TRUE}
-
-mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), avg_ret_df, REML= TRUE)
-anova(mod_returns_pct)
-summary(mod_returns_pct)
-
-prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
-
-cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
-```
-
-```{r, include=FALSE}
-pctRet_all <- afex::afex_plot(mod_returns_pct, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
-            mapping = c("linetype", "shape", "fill"),
-            data_geom = geom_violin, 
-            data_arg = list(width = 0.5),
-            factor_levels = list(gameNum.f = c("Pre", "Post")), legend_title = "Condition") + 
-  theme_bw() + 
-  labs(y = "Percentage Return", x = "Game") + 
-  ggtitle("All rounds percentage returns") + 
-  theme(plot.title = element_text(size = 10)) +
-  theme(legend.position = "bottom")
-
-```
-
-<!-- If the intervention has an effect, then we should expect a higher increase in returns after the intervention compared to the control condition, which should be evident from an interaction between Condition (intervention vs control) and Game-number (pre- vs post-manipulation).
-Therefore, the variable of interest here is the interaction between Condition and Game-number.
--->
-
-We find an interaction effect between Condition (intervention vs.
-control) and Game-number (pre- vs.
-post-manipulation) ($F(1,314.2) = 26.9, p < 0.001$).
-Post-hoc tests show that there was an increase in the percentage returned in the intervention group (`r papaja::apa_print(prepost_bycond)$statistic$Intervention_Pre_post`) but not in the control group (`r papaja::apa_print(prepost_bycond)$statistic$Control_Pre_post`).
-We also found a significant main effect for Condition ( $F(1,315.31) = 9.52, p = 0.002)$), such that the intervention group had higher percentage returns than the control group.
-There was also a significant main effect of Investment( $F(1,9208) = 373.6, p < 0.001$) such that higher investments were associated with higher percentage returns.
-
-There was an interaction effect of Investment by Condition ($F(1,9207) =45.38, p < 0.001$), such that the positive effect of investment on percentage returns was greater in the control group than in the intervention group.
-This suggests that the higher returns we see in the intervention group are not simply due to higher investments.
-Finally, we find a three way interaction between Game-number, Condition and Investment ($F(1,8988)= 24.6, p < 0.001$), showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game-number.
-
-```{r, include=FALSE, cache=TRUE}
-mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| id), avg_ret_df )
-summary(mod_invs)
-anova(mod_invs)
-
-# pairs(emmeans::emmeans(mod_invs, c("condition.f"), by = "gameNum.f" ))
-# 
-# pairs(emmeans::emmeans(mod_invs,c("gameNum.f") , by = c("condition.f")))
-# 
-# pairs(emmeans::emmeans(mod_invs, c("gameNum.f")))
-# pairs(emmeans::emmeans(mod_invs, c("condition.f")))
-
-```
-
-```{r, include=FALSE}
-
-inv_all <- afex_plot(mod_invs, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
-            mapping = c("linetype", "shape", "fill"),
-            data_geom = geom_violin,
-            data_arg = list(width = 0.5),
-            factor_levels = list(gameNum.f = c("Pre", "Post")), 
-            legend_title = "Condition") + 
-  theme_bw() + 
-  ggtitle("All rounds investments") +
-  labs(y = "HMM Investment", x = "Game") + 
-  theme(plot.title = element_text(size = 10)) +
-  theme(legend.position = "bottom")
-
-```
-
-The HMM agent exhibited a differentiated behavior between games and conditions.
-When examining the HMM agent investments, we fit a linear-mixed effects model, with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number.
-We find a main effect for both Condition ($F(1,317) = 8.7, p = 0.003$) and Game-number($F(1,317) = 8.3, p = 0.004$).
-As can be seen in Figure \ref{fig:violinPanels}.D, investment was higher in the intervention compared to the control condition across games ($p=0.003$).
-Across conditions, investment was also higher in the second game compared to the first ($p=0.003$).
-
-In summary, participants in the control group sent back **lower** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$Control_Pre_post`) despite the HMM investor sending, on average higher investments.
-Those in the intervention group returned **higher** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$Intervention_Pre_post`), with the investor also sending higher investments.
-These higher returns in the intervention group compared to the control group were not purely driven by reciprocity towards higher investments since we find this interaction effect whilst controlling for investments in our model of participants returns.
-
-## Looking at pre- and post-defection trials only
-
-```{r, include=FALSE, cache=TRUE}
-# ALL ROUNDS BEFORE DEFECTION TRIAL
-pre_int_data <- avg_ret_df %>% filter(roundType=="trust",!is.na(gameNum.f),(roundNum < 12 & gameNum.f =="pre")| (roundNum < 13 & gameNum.f =="post"))
-
-mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), pre_int_data, REML= TRUE)
-anova(mod_returns_pre)
-summary(mod_returns_pre)
-
-pairs_pre_int <- pairs(emmeans::emmeans(mod_returns_pre, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400, reverse=TRUE))
-
-```
-
-We restrict our analysis to the rounds prior to the pre-programmed defection (rounds 1 to 11 pre-manipulation and 1 to 12 post-manipulation) and fit the same linear mixed effects model to percentage returns as the one for the full data.
-Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.B.
-We do find an interaction effect between Condition and Game number ($F(1,317.99) = 17.1, p < 0.001$).
-This was due to an increase in the percentage returned pre low-investment trial in the intervention condition (`r apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`) but not in the control group (`r apa_print(pairs_pre_int)$full_result$Control_Pre_post`).
-This indicates that participants were sending back higher returns in the intervention condition but not in the control condition even before the defection trial.
-
-```{r, include=F}
-pctRet_pre <- afex_plot(mod_returns_pre, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
-            mapping = c("linetype", "shape", "fill"),
-            data_geom = geom_violin,
-            data_arg = list(width = 0.5),
-            factor_levels = list(gameNum.f = c("Pre", "Post")), 
-            legend_title = "Condition") + 
-  theme_bw() + 
-  labs(y = "Percentage Return", x = "Game") + 
-  ggtitle("Pre defection trials percentage returns")+
-  theme(plot.title = element_text(size = 10)) +
-  theme(legend.position = "bottom")
-```
-
-The interventions focused on repairing cooperation in the wake of a transgressive action by the investor.
-To assess the effect of the intervention, we can therefore consider the percentage return after the "transgression" trials.
-We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
-These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).
-
-```{r, include =FALSE}
-
-# Defection trial only 
-coax_data <- avg_ret_df %>%  filter(roundType=="trust",!is.na(gameNum.f),(roundNum == "12" & gameNum.f =="pre")| (roundNum == "13" & gameNum.f =="post"))
-
-coax_data %>% group_by(gameNum.f, condition.f) %>% summarise(avg_inv = mean(investment),avg_return = mean(returns))
-
-# ALL ROUNDS AFTER DEFECTION TRIAL (INCLUSIVE)
-post_coax_data <- avg_ret_df %>% filter(roundType=="trust",!is.na(gameNum.f),(roundNum >= 12 & gameNum.f =="pre")| (roundNum >= 13 & gameNum.f =="post"))
-
-post_coax_data %>% group_by(gameNum.f, condition.f) %>% summarise(avg_inv = mean(investment),avg_return = mean(returns))
-
-```
-
-```{r, include=FALSE, cache=TRUE}
-
-mod_postcoax_trust <- mixed(ret_pct ~ gameNum.f*condition.f*inv_scaled  + ( 1 + gameNum.f|id), post_coax_data)
-anova(mod_postcoax_trust)
-
-postcoax_bygame <- emmeans::emmeans(mod_postcoax_trust, ~gameNum.f, pbkrtest.limit = 9400)
-postcoax_bycond <- emmeans::emmeans(mod_postcoax_trust, ~condition.f, pbkrtest.limit = 9400)
-
-postcoax_interaction <- emmeans::emmeans(mod_postcoax_trust, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400)
-postcoax_interaction
-
-pairs(emmeans::emmeans(mod_postcoax_trust, c("gameNum.f"), by = "condition.f"))
-```
-
-```{r, include=FALSE}
-pctRet_post <- afex_plot(mod_postcoax_trust, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
-            mapping = c("linetype", "shape", "fill"),
-            data_geom = geom_violin,
-            data_arg = list(width = 0.5),
-            factor_levels = list(gameNum.f = c("Pre", "Post")), 
-            legend_title = "Condition") + 
-  theme_bw() + 
-  labs(y = "Percentage Return", x = "Game") + 
-  ggtitle("Post defection trials percentage returns")+
-  theme(plot.title = element_text(size = 10)) +
-  theme(legend.position = "bottom")
-```
-
-```{r violinPanels, fig.cap="A: Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition.
-B: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
-C: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.
-D: Marginal means and distributions of investments over all rounds for HMM agents playing the role of the investor, by Game number and Condition", fig.align="center", fig.width=6, fig.height = 6}
-
-ggpubr::ggarrange(pctRet_all, pctRet_pre, pctRet_post, inv_all, nrow=2, ncol=2, labels = c("A", "B", "C", "D"), common.legend = TRUE, legend = "bottom")
-```
-
-Figure \ref{fig:violinPanels}.C shows the marginal means of trustee returns and their distribution by Game-number and Condition.
-There was a significant interaction between Game-number and Condition.
-Participants sent back lower returns between games in the control condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`), but no such difference in the intervention condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`).
-
-<!-- We found a main effect of Condition with returns on the intervention group higher than returns in the control group (`r apa_print(pairs(postcoax_bycond))$full_result`).
-We also found a main effect of Game-number, with returns higher for the pre-manipulation game compared to the post-manipulation game  (`r apa_print(pairs(postcoax_bygame))$full_result`).
--->
-
-## Emotion self-reports
-
-```{r, include=TRUE}
-
-# Get Emotions on x axis per round (valence)
-emo.x <- d_finished %>% 
-  mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>% 
-  dplyr::select(id,roundType,condition.f,contains("emotionGrid")) %>% 
-  dplyr::filter(roundType=="trust") %>% dplyr::select (-contains(".y") ) %>% pivot_longer(cols=contains(".x"), names_to = c("gameNumber","roundNum"), names_pattern ="return_trust_emotionGrid_(.*)_(.*)[.]x", values_to = "emo_coord_x") %>%
-  distinct()
-
-#Get emotions on y axis (arousal)
-emo.y <- d_finished %>%
-  mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>%
-  dplyr::select(id,roundType,condition.f,contains("emotionGrid")) %>% 
-  dplyr::filter(roundType=="trust") %>% dplyr::select(-contains(".x") ) %>% pivot_longer(cols=contains(".y"), names_to = c("gameNumber","roundNum"), names_pattern ="return_trust_emotionGrid_(.*)_(.*)[.]y", values_to = "emo_coord_y") %>%
-  distinct()
-
-# put emotions in one dataframe
-full_emo <- full_join(emo.x,emo.y, by=c("id", "gameNumber","roundNum","roundType", "condition.f"))  %>% 
-  mutate(roundNum=as.numeric(as.character(roundNum))) %>% 
-  mutate(gameNum.f = factor(gameNumber,labels = c("pre","post"),levels=c("1","2"))) %>% 
-  dplyr::select(-c("roundType","gameNumber")) %>% 
-  # group_by(condition.f) %>% 
-  mutate(emo_scaled_x = scale(emo_coord_x), emo_scaled_y= -scale(emo_coord_y))    # <--- SCALING and reversing Y coordinates (0,0 is top left)
-
-#merge with returns dataframe
-full_dat <- full_join(avg_ret_df, full_emo, by = c("id","condition.f","gameNum.f","roundNum" )) %>% filter(complete.cases(.))
-#nrow(full_dat)
-
-datCoax <- full_dat %>% filter(condition.f=="intervention")
-datCtrl <- full_dat %>% filter(condition.f=="control")
-
-```
-
-```{r emoPlotCoax, fig.cap="Self-reported emotion valence and arousal as well as investment z-scores for each round of the repeated Trust Game averaged across participants in the intervention condition only.",fig.align="center", fig.width=6, fig.height = 4}
-
-# colors <- c("Investment" = "blue", "Valence" = "red", "Arousal" = "green")
-# 
-# ggplot(datCoax,aes(x=roundNum)) + 
-#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_x), color = "red") + 
-#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_y), color = "green") + 
-#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=scale(investment)), color = "blue") + 
-#   scale_color_manual(name = " ",values = colors, labels = c("Investment", "Emotion valence", "Emotion arousal")) +
-#   labs(x = "Round", y="Series Z-score") +
-#   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
-#   facet_grid(cols = vars(gameNum.f)) +
-#   theme_bw() + 
-#   theme(legend.position = "bottom")
-#
-
-# # BOTH IN ONE GRAPH 
-# library(ggplot2)
-# 
-# # Define the colors in alphabetical order
-# colors <- c("Arousal" = "green", "Investment" = "blue", "Valence" = "red")
-# 
-# # Plot 'pre'
-# p <- ggplot(datCoax[datCoax$gameNum.f == 'pre', ], aes(x=roundNum)) + 
-#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_x, color = "Valence", linetype = "pre")) + 
-#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_y, color = "Arousal", linetype = "pre")) + 
-#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=inv_scaled, color = "Investment", linetype = "pre")) +
-# # Plot 'post'
-#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_x, color = "Valence", linetype = "post")) + 
-#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_y, color = "Arousal", linetype = "post")) + 
-#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=inv_scaled, color = "Investment", linetype = "post")) +
-#   labs(x = "Round", y="Series Z-score") +
-#   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
-#   scale_color_manual(name = " ", values = colors, labels = c("Emotion arousal", "Investment", "Emotion valence")) +
-#   scale_linetype_manual(values = c("pre" = "dotted", "post" = "solid"), labels = c("Pre", "Post")) +
-#   theme_bw() + 
-#   theme(legend.position = "bottom")
-# 
-# # Print the plot
-# print(p)
-
-#################### two panels for before and after defection 
-library(ggplot2)
-
-# Define the colors in alphabetical order
-colors <- c("Arousal" = "green", "Investment" = "blue", "Valence" = "red")
-
-# Create a new variable to categorize the rounds
-datCoax$roundGroup <- ifelse(datCoax$roundNum <= 10, "Rounds 1-10", "Rounds 11-15")
-
-# Plot 'pre'
-p <- ggplot(datCoax[datCoax$gameNum.f == 'pre', ], aes(x=roundNum)) + 
-  stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_x, color = "Valence", linetype = "a_Pre")) + 
-  stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_y, color = "Arousal", linetype = "a_Pre")) + 
-  stat_summary(fun = "mean", geom = "line", group =1, aes(y=inv_scaled, color = "Investment", linetype = "a_Pre")) +
-# Plot 'post'
-  stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_x, color = "Valence", linetype = "b_Post")) + 
-  stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_y, color = "Arousal", linetype = "b_Post")) + 
-  stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=inv_scaled, color = "Investment", linetype = "b_Post")) +
-  labs(x = "Round", y="Series Z-score") +
-  geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
-  scale_color_manual(name = " ", values = colors, labels = c("Emotion arousal", "Investment", "Emotion valence")) +
-  scale_linetype_manual(values = c("a_Pre" = "dotted", "b_Post" = "solid"), labels = c("Pre", "Post")) +
-  scale_x_continuous(breaks = 1:max(datCoax$roundNum)) +
-  facet_wrap(~roundGroup, scales = "free_x") +
-  theme_bw() + 
-  theme(legend.position = "bottom")
-
-# Print the plot
-print(p)
-
-```
-
-A key aspect of effective interventions is the emotional change.
-We examined emotion self-reports through fitting a linear mixed effects model to both emotion dimensions (valence and arousal) for the intervention group to explore whether the intervention changed the emotional appraisal of the investment, with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
-
-Higher investments were associated with more positive emotions ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$), while positive emotions declined between the two games ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
-However, there was no evidence that emotional reaction to the investment was lessened after the intervention.
-This means that participants in the intervention condition returned higher amounts post-intervention despite the emotional reaction to the lower investment being largely unchanged.
-
-<!-- Figure \ref{fig:emoPlotCoax} shows the average, across participants *in the intervention condition*, of emotion valence, the degree of arousal as well as the HMM's investment z-scores.
-We find a significant positive correlation between the two emotion axis ($r=0.52, p < 0.001$) as well as between valence and Investment ($r=0.47, p < 0.001$), and arousal and Investment ($r=0.50, p < 0.001$).
--->
-
-```{r, include=FALSE}
-
-mod_emo_x <- mixed( emo_scaled_x ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
-summary(mod_emo_x)
-anova(mod_emo_x)
-
-modVal <- emmeans::emmeans(mod_emo_x, ~gameNum.f)
-pairs(modVal)
-
-mod_emo_y <- mixed( emo_scaled_y ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
-summary(mod_emo_y)
-anova(mod_emo_y)
-
-modArousal <- emmeans::emmeans(mod_emo_y, ~gameNum.f)
-pairs(modArousal)
-
-# afex_plot(mod_emo_x, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
-#             data_geom = geom_violin, 
-#             data_arg = list(width = 0.5))
-#
-
-# library(GGally)
-# ggpairs(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,inv_scaled))
-
-cor(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,investment))
-cor.test(datCoax$emo_scaled_x, datCoax$emo_scaled_y)
-```
-
-<!-- For emotional valence, we find a main effect of Investment ($F(1,4664) = 2902, p < 0.001$), with higher investment leading to more positive emotions.
-We also find a main effect for Game-number, due to the reported emotional valence of investments decreasing significantly after the intervention ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
-For emotional arousal, fitting a similar mixed effects model we find only a main effect of Investment  ($F(1,4668.4) = 1919, p < 0.001$) with higher investment leading to higher arousal.
-These effects are still present if we exclude the defection trial.
-We did not find any interaction between emotional valence or arousal and the investment, which would indicate a moderating effect of the intervention on the reaction to investments.
--->
-
-## Player rating
-
-<!-- One possible reason of the differentiated returns post manipulation between conditions is that participants had a different perception of the investor, post-manipulation, in the control condition compared to the control condition.
-To explore this possibility, we can determine whether participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention) using the players ratings they had to submit at the end of each game.
-To analyse the participants rating of their opponents, we used a linear mixed-effects model for each of the four players ratings (cooperativeness, selfishness, trustworthiness, friendliness) with fixed effects for Game-number (pre or post manipulation) and Condition (intervention or control), as well as interaction between condition and Game-number, and participant-wise random intercepts.
--->
-
-```{r, include=FALSE}
-
-# Pivot longer ratings on each attribute 
-df_coop <- d_finished %>% dplyr::select(id,condition.f,contains("cooperative")) %>%  
-  pivot_longer(cols=contains("cooperative"), names_to = c("gameNumber"), names_pattern ="rating_cooperative_(.*)", values_to = "rating_coop") %>% distinct()
-
-df_selfish <- d_finished %>% dplyr::select(id,condition.f,contains("selfish")) %>% 
-  pivot_longer(cols=contains("selfish"), names_to = c("gameNumber"), names_pattern ="rating_selfish_(.*)", values_to = "rating_selfish") %>% distinct
-
-df_trustworthy <- d_finished %>% dplyr::select(id,condition.f,contains("trustworthy")) %>% 
-  pivot_longer(cols=contains("trustworthy"), names_to = c("gameNumber"), names_pattern ="rating_trustworthy_(.*)", values_to = "rating_trustworthy") %>% distinct()
-
-df_friendly  <-  d_finished %>% dplyr::select(id,condition.f,contains("friendly")) %>% 
-  pivot_longer(cols=contains("friendly"), names_to = c("gameNumber"), names_pattern ="rating_friendly_(.*)", values_to = "rating_friendly") %>%  distinct()
-
-#merge all data frames together
-datRatings <- list(df_coop, df_selfish,df_trustworthy, df_friendly) %>% 
-              reduce(full_join, by=c('id','gameNumber','condition.f') ) %>% 
-              mutate(gameNum.f = factor(gameNumber,labels = c("pre","post"),levels=c("1","2")))
-
-# Group means for each rating 
-mu <- datRatings %>% group_by(gameNum.f, condition.f) %>% summarise(mean_coop = mean(rating_coop),
-                                                  mean_selfish = mean(rating_selfish),
-                                                  mean_trustworthy = mean(rating_trustworthy),
-                                                  mean_friendly = mean(rating_friendly)
-                                                  )
-```
-
-```{r, include=FALSE}
-
-# Cooperative
-coop_mod <- mixed(rating_coop ~ gameNum.f*condition.f + (1 | id), datRatings)
-summary(coop_mod)
-
-pairs(emmeans::emmeans(coop_mod, c("gameNum.f"), by = "condition.f"))
-
-#Selfish
-self_mod <- mixed(rating_selfish ~ gameNum.f*condition.f + (1 | id), datRatings)
-summary(self_mod)
-pairs(emmeans::emmeans(self_mod, c("gameNum.f"), by = "condition.f"))
-
-#Trustworthy 
-trust_mod <- mixed(rating_trustworthy ~ gameNum.f*condition.f + (1 | id), datRatings)
-summary(trust_mod)
-pairs(emmeans::emmeans(trust_mod, c("gameNum.f"), by = "condition.f"))
-
-#Friendly
-friend_mod <- mixed(rating_friendly ~ gameNum.f*condition.f + (1 | id), datRatings)
-summary(friend_mod)
-pairs(emmeans::emmeans(friend_mod, c("gameNum.f"), by = "condition.f"))
-
-# Conduction t-tests 
-# t.test(rating_coop ~ gameNumber, data = datRatingsCoax, paired = TRUE)
-# t.test(rating_selfish ~ gameNumber, data = datRatingsCoax, paired = TRUE)
-# t.test(rating_trustworthy ~ gameNumber, data = datRatingsCoax, paired = TRUE)
-# t.test(rating_friendly ~ gameNumber, data = datRatingsCoax, paired = TRUE)
-
-```
-
-<!-- showed a main effect of Game-number on all attributes, with participants rating the second player as less cooperative (∆M = 0.42, 95% CI [0.15, 0.69], t(317.00) = 3.10, p = .002), less trustworthy (∆M = 0.43, 95% CI [0.16, 0.70], t(317.00) = 3.19, p = .002), less friendly (∆M = 0.40, 95% CI [0.17, 0.64], t(317.00) = 3.36, p = .001) and more selfish(∆M = −0.36, 95% CI [−0.61, −0.10], t(317.00) = −2.76, p = .006).
-Importantly, there was a main effect of Condition , with participants in the intervention condition rated players higher than those in the control condition on cooperativeness (∆M = 0.40, 95% CI [0.00, 0.80], t(317.00) = 1.95, p = .052) and lower on selfishness (∆M = −0.41, 95% CI [−0.80, −0.02], t(317.00) = −2.04, p = .042).
-There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
--->
-
-Participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention).
-The players ratings submitted at the end of each game showed a main effect of Game-number on all attributes, with participants rating the second player as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result`) and more selfish(`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result`).
-We also find a main effect of Condition as participants in the intervention condition rated players higher than those in the control condition on cooperativeness (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("condition.f"))))$full_result`) and lower on selfishness (`r apa_print(pairs(emmeans::emmeans(self_mod, c("condition.f"))))$full_result`).
-There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
-
-<!-- However, breaking down the interaction term by Condition, we find that participants rated the post-intervention player significantly lower on all positive attributes and higher on the negative one (selfish).
-There was no such difference in player ratings the control condition.
--->
-
-## Transfer to the Prisoner's Dilemma Game
-
-```{r, include=FALSE}
-
-PD_data <- d_finished %>%
-  mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>%
-  dplyr::select(id, condition.f,roundType,roundNum, PDoption,PDchoice, AiChoicePD,gameNum.f, PBOR_score) %>% 
-                          filter(roundType == "PD",!is.na(roundNum)) %>% 
-                          dplyr::mutate(coop = ifelse(PDchoice=="cooperate",1,0),phase = ifelse(roundNum <= 4, 0,1))
-
-# Average cooperation rates per round
-#PD_data %>% group_by(roundNum, condition.f) %>% summarise(coopRate = mean(coop))
-```
-
-```{r PDCoop, include=FALSE, fig.cap="Mean and standard error of the rate at which the cooperative action was chosen by the participants for each round of the repeated Prisoner's Dilemma game.
-Round 4 is where we programmed the Tit-for-Tat agent to defect, which explains the lower cooperation rate we see in round 5 onwards",fig.align="center", fig.width=6, fig.height =3}
-# plot of cooperation rates per round
-ggplot(PD_data,aes(x=roundNum,group = 1)) + 
-  stat_summary(fun = "mean", geom = "line", aes(y=coop), color ="red") + 
-  stat_summary(fun.data = "mean_se", geom = "errorbar",alpha =0.3, width = 0.2, aes(y=coop) ) + 
-  facet_grid(~ condition.f) +
-  xlab("Round") + 
-  ylab("Cooperation rate (%)") +
-  scale_x_continuous(breaks = round(seq(1,10, by = 1),1)) + 
-  theme_bw()
-
-```
-
-```{r, include=FALSE}
-
-ipd_mod <- mixed(coop ~ condition.f * phase + (1 |id), data= PD_data, method = "LRT", family= "binomial") 
-summary(ipd_mod)
-
-ipd_mod_r5 <- glm(coop ~ condition.f, data= PD_data%>% filter(roundNum >= 5)) 
-summary(ipd_mod_r5)
-
-```
-
-We next asked whether the coaxing behavior induced by the intervention generalized to the RPD.
-Across participants, we look at the rate at which the cooperative action was chosen in each round.
-Using a logistic mixed-effects model with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, we found no evidence for a different cooperation rate in the intervention condition compared to the control condition.
-We also found no difference in cooperation rates post defection trial between conditions.
-
-## Self report and debrief questionnaires
-
-```{r, include=FALSE}
-########### HOW DO PBOR SCORES affect returns and intervention effect ?########
-
-avg_ret_df <- avg_ret_df %>% mutate(PBOR_scaled = scale(PBOR_score), DERS_scaled = scale(DERS_score), RFQc_scaled = scale(RFQ_c))
-
-# these are repeated measures here, so not independent. need to used mixed effects model.
-mixed_PBOR_pct <- afex::mixed(ret_pct ~ PBOR_scaled*gameNum.f*condition.f + investment + (1 | id ), data= avg_ret_df)
-summary(mixed_PBOR_pct)
-
-# At average value of PBOR score  
-emmeans(mixed_PBOR_pct, pairwise ~ PBOR_scaled * condition.f )
-
-## Looking at difference between average returns across rounds
-#scoreDAT <- avg_ret_df %>% dplyr::select(id,diff_pctRet, PBOR_scaled, DERS_scaled, RFQ_c, condition.f) %>% unique()
-
-```
-
-```{r, include=FALSE}
-# Install the 'psych' package if you haven't already
-if (!requireNamespace("psych", quietly = TRUE)) {
-  install.packages("psych")
-}
-
-# Load the 'psych' package
-library(psych)
-
-questionnaires <- avg_ret_df %>% group_by(id) %>% dplyr::select(PBOR_score,DERS_score,RFQ_c) %>% unique() %>% ungroup()
-# Perform EFA
-efa_result <- fa(questionnaires %>% dplyr::select(PBOR_score,DERS_score,RFQ_c), nfactors = 2, fm = "minres", rotate = "varimax")
-# Print the EFA result
-print(efa_result)
-
-```
-
-We find no interaction effect of the questionnaire scores with the Condition variable, nor a main effect of the questionnaire scores on participants returns in the RTG.
-
-```{r, include=FALSE}
-turing <- read_csv("data/turing.csv")
-colnames(turing) <- c("responses", "category")
-
-turing  %>%
-    group_by(category) %>%
-    summarize(count = n()) %>%
-    mutate(percentage = count / sum(count) * 100) %>%
-    dplyr::select(category, percentage)
-
-```
-
-When asked whether they thought their opponent was Human or not, $40$% of participants thought they were either facing a human or were not sure of the nature of the opponent.
-Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behavior.
-
-# HMM analysis of participant returns
-
-```{r, include=FALSE}
-
-# Removing player whose return was not properly recorded by data (NA in one of the rounds) so as to run depmixS4
-id_with_na <-  as.character(avg_ret_df[is.na(avg_ret_df$returns),"id"])
-
-# Create return percentage bins Bins
-avg_ret_df <- avg_ret_df %>%
-  filter(id != id_with_na) %>% 
-  mutate(game_id = rep(1:636, each=15)) %>%
-  group_by(game_id) %>%
-  mutate(next_investment = lead(investment, default=0),
-         investment_bin = cut(investment, breaks = c(-1,2.5,7.5,12.5,17.5,21)),  
-         return_pct_bin = cut(ret_pct_0, breaks = c(-.1,.16,.33,.50,.66,0.84,1.1)),  # 0, 1/6, 2/6, 3/6,...
-         intervention_ctrst = factor(ifelse(gameNum.f=="pre", 0,ifelse(condition.f=="control",1,2))),
-         ctrl_only_ctrst = factor(ifelse(gameNum.f=="post" && condition.f=="control", 1,0)),
-         coax_only_ctrst = factor(ifelse(gameNum.f=="post" && condition.f=="intervention", 1,0)),
-         pre_post_ctrst = factor(ifelse(gameNum.f=="post", 1,0)))  %>% 
-  ungroup()
-# We put factor as otherwise R thinks that it's a linear variable. We want the first level to be reference group, 0. Default uses that.
-
-priordat <- avg_ret_df %>% filter(roundNum==1)
-
-############### HMM support functions   #########################
-
-# order the states of the HMM to allow it to order them as low ret/mid/ret/high ret. 
-label_switch <- function(mod,labels) {
-  # labels is vector, first element is new label for original state 1, second is new label for original state 2, etc.
-  if(!is(mod,"depmix") || !is(mod,"depmix.fitted")) stop("this function is for depmix models")
-  n_states <- mod@nstates
-  if(length(labels) != n_states || length(unique(labels)) != n_states || !(all(labels) %in% 1:n_states)) {
-    stop("labels needs to be a vector of unique integers between 1 and", n_states)
-  }
-  inv_labels <- sapply(1:n_states,function(x) which(labels == x))
-  tmp <- mod
-  # relabel prior
-  ppars <- getpars(mod@prior)
-  fpars <- getpars(mod@prior,which="fixed")
-  out_pars <- as.numeric(t(matrix(ppars,nrow=length(ppars)/n_states,byrow = TRUE)[,inv_labels]))
-  out_fixed <- as.logical(t(matrix(fpars,nrow=length(fpars)/n_states,byrow = TRUE)[,inv_labels]))
-  if(!tmp@prior@family$link=="identity") tmp@prior@family$base <- labels[tmp@prior@family$base]
-  # relabel transition
-  for(i in 1:n_states) {
-    ppars <- getpars(mod@transition[[inv_labels[i]]])
-    fpars <- getpars(mod@transition[[inv_labels[i]]],which="fixed")
-    out_pars <- c(out_pars,as.numeric(t(matrix(ppars,nrow=length(ppars)/n_states,byrow = TRUE)[,inv_labels])))
-    out_fixed <- c(out_fixed,as.logical(t(matrix(fpars,nrow=length(fpars)/n_states,byrow = TRUE)[,inv_labels])))
-    tmp@transition[[i]] <- mod@transition[[inv_labels[i]]]
-    if(!tmp@transition[[i]]@family$link=="identity") tmp@transition[[i]]@family$base <- labels[tmp@transition[[i]]@family$base]
-    #out_pars <- c(out_pars,getpars(mod@transition[[inv_labels[i]]]))
-  }
-  # relabel response
-  for(i in 1:n_states) {
-    out_pars <- c(out_pars,unlist(lapply(mod@response[[inv_labels[i]]],getpars)))
-    out_fixed <- c(out_fixed,unlist(lapply(mod@response[[inv_labels[i]]],getpars,which="fixed")))
-  }
-  tmp <- setpars(tmp,out_fixed,which="fixed")
-  tmp <- setpars(tmp,out_pars)
-  if(is(tmp,"depmix.fitted")) tmp@posterior <- viterbi(tmp)
-  return(tmp)
-}
-
-# ORDERING STATES
-order_mod_gauss <- function(mod) {
-  ns <- nstates(mod)
-  sum <- rep(0.0,ns)
-  for(i in 1:ns) {
-    # Expected return in each state calculation 
-    sum[i] = mod@response[[i]][[1]]@parameters$mu
-  }
-  # reordering the states
-  mod <- label_switch(mod, rank(sum))
-  return(mod)
-}
-
-```
-
-```{r, include=F}
-# define a response class which only contains the standard slots, no additional slots
-setClass("discgaus", contains="response", slots=c(breaks="numeric"))
-
-# define a generic for the method defining the response class
-
-setGeneric("discgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("discgaus"))
-
-# define the method that creates the response class
-
-setMethod("discgaus", 
-          signature(y="ANY"), 
-          function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), ...) {
-            y <- matrix(y,length(y))
-            x <- matrix(1)
-            parameters <- list()
-            npar <- 2
-            if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
-            if(!is.null(pstart)) {
-              if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
-              parameters$mu <- pstart[1]
-              parameters$sigma <- pstart[2]
-            }
-            mod <- new("discgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, breaks=breaks)
-            mod
-          }
-)
-
-setMethod("show","discgaus",
-          function(object) {
-            cat("Gaussian with discrete support\n")
-            cat("Parameters: \n")
-            cat("mu: ", object@parameters$mu, "\n")
-            cat("sigma: ", object@parameters$sigma, "\n")
-          }
-)
-
-setMethod("dens","discgaus",
-          function(object,log=FALSE) {
-            p <- pnorm(object@breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@breaks[-length(object@breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
-            if(log) return(log(p[as.numeric(cut(object@y, breaks=object@breaks))])) else return(p[as.numeric(cut(object@y, breaks=object@breaks))])
-          }
-)
-
-setMethod("setpars","discgaus",
-          function(object, values, which="pars", ...) {
-            npar <- npar(object)
-            if(length(values)!=npar) stop("length of 'values' must be",npar)
-            # determine whether parameters or fixed constraints are being set
-            nms <- names(object@parameters)
-            switch(which,
-                   "pars"= {
-                     object@parameters$mu <- values[1]
-                     object@parameters$sigma <- values[2]
-                   },
-                   "fixed" = {
-                     object@fixed <- as.logical(values)
-                   }
-            )
-            names(object@parameters) <- nms
-            return(object)
-          }
-)
-
-setMethod("getpars","discgaus",
-          function(object,which="pars",...) {
-            switch(which,
-                   "pars" = {
-                     parameters <- numeric()
-                     parameters <- unlist(object@parameters)
-                     pars <- parameters
-                   },
-                   "fixed" = {
-                     pars <- object@fixed
-                   }
-            )
-            return(pars)
-          }
-)
-
-setMethod("fit","discgaus",
-          function(object,w) {
-            if(missing(w)) w <- NULL
-            if(!is.null(w)) {
-              negLL <- function(pars) {
-                object <- setpars(object, c(pars[1], exp(pars[2])))
-                -sum(w*log(dens(object)))
-              }
-            } else {
-              negLL <- function(pars) {
-                object <- setpars(object, c(pars[1], exp(pars[2])))
-                -sum(log(dens(object)))
-              }
-            }
-            pars <- optim(c(object@parameters$mu, log(object@parameters$sigma)), fn=negLL)$par
-            object <- setpars(object,c(pars[1], exp(pars[2])))
-            object
-          }
-)
-
-setClass("truncdiscgaus", contains="discgaus", slots=c(min="numeric", max="numeric"))
-
-setMethod("dens","truncdiscgaus",
-          function(object,log=FALSE) {
-            breaks <- c(object@min, object@breaks[object@breaks > object@min & object@breaks < object@max], object@max)
-            p <- pnorm(breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(breaks[-length(breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
-            p <- p/sum(p)
-            if(log) return(log(p[as.numeric(cut(object@y, breaks=object@breaks))])) else return(p[as.numeric(cut(object@y, breaks=object@breaks))])
-          }
-)
-
-setGeneric("truncdiscgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("truncdiscgaus"))
-
-setMethod("truncdiscgaus", 
-          signature(y="ANY"), 
-          function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), min=0, max=20, ...) {
-            y <- matrix(y,length(y))
-            x <- matrix(1)
-            parameters <- list()
-            npar <- 2
-            if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
-            if(!is.null(pstart)) {
-              if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
-              parameters$mu <- pstart[1]
-              parameters$sigma <- pstart[2]
-            }
-            mod <- new("truncdiscgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, breaks=breaks, min=min, max=max)
-            mod
-          }
-)
-
-order_mod_gauss <- function(mod) {
-  ns <- nstates(mod)
-  sum <- rep(0.0,ns)
-  for(i in 1:ns) {
-    # Expected return in each state calculation 
-    sum[i] = mod@response[[i]][[1]]@parameters$mu
-  }
-  # reordering the states
-  mod <- label_switch(mod, rank(sum))
-  return(mod)
-}
-
-# define a response class which only contains the standard slots, no additional slots
-setClass("vtdgaus", contains="response", slots=c(yield="numeric"))
-
-# define a generic for the method defining the response class
-
-setGeneric("vtdgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("vtdgaus"))
-
-# define the method that creates the response class
-
-setMethod("vtdgaus", 
-          signature(y="ANY"), 
-          function(y, yield, pstart=NULL,fixed=NULL, ...) {
-            y <- matrix(y,length(y))
-            x <- matrix(1)
-            parameters <- list()
-            npar <- 2
-            if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
-            if(!is.null(pstart)) {
-              if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
-              parameters$mu <- pstart[1]
-              parameters$sigma <- pstart[2]
-            } else {
-              parameters <- list(mu=.5,sigma=1)
-            }
-            mod <- new("vtdgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, yield=yield)
-            mod
-          }
-)
-
-setMethod("show","vtdgaus",
-  function(object) {
-    cat("Gaussian with variable discrete support for percentage responses\n")
-    cat("Parameters: \n")
-    cat("mu: ", object@parameters$mu, "\n")
-    cat("sigma: ", object@parameters$sigma, "\n")
-  }
-)
-
-setMethod("dens","vtdgaus",
-  function(object,log=FALSE) {
-      # determine cuts for pnorm based on 
-      p <- pnorm(sapply(object@y + .5*(1/object@yield),function(x) min(x,1.001)), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(sapply(object@y - .5*(1/object@yield),function(x) max(x,-0.001)), mean = object@parameters$mu, sd = object@parameters$sigma)
-      norm <- (pnorm(1 + .001, mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(-0.001, mean = object@parameters$mu, sd = object@parameters$sigma))
-      p <- p/norm
-      # alternatively, normalize factor based on size of cuts
-      #p <- pnorm(object@y + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@y - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma)
-      #p <- p/(pnorm(1 + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(0 - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma))
-    # probability when yield == 0 is always 1 
-      p[object@yield == 0] <- 1
-      if(log) return(log(p)) else return(p)
-    }
-)
-
-setMethod("setpars","vtdgaus",
-          function(object, values, which="pars", ...) {
-            npar <- npar(object)
-            if(length(values)!=npar) stop("length of 'values' must be",npar)
-            # determine whether parameters or fixed constraints are being set
-            nms <- names(object@parameters)
-            switch(which,
-                   "pars"= {
-                     object@parameters$mu <- values[1]
-                     object@parameters$sigma <- values[2]
-                   },
-                   "fixed" = {
-                     object@fixed <- as.logical(values)
-                   }
-            )
-            names(object@parameters) <- nms
-            return(object)
-          }
-)
-
-setMethod("getpars","vtdgaus",
-          function(object,which="pars",...) {
-            switch(which,
-                   "pars" = {
-                     parameters <- numeric()
-                     parameters <- unlist(object@parameters)
-                     pars <- parameters
-                   },
-                   "fixed" = {
-                     pars <- object@fixed
-                   }
-            )
-            return(pars)
-          }
-)
-
-setMethod("fit","vtdgaus",
-          function(object,w) {
-            if(missing(w)) w <- NULL
-            if(!is.null(w)) {
-              negLL <- function(pars) {
-                object <- setpars(object, c(pars[1], exp(pars[2])))
-                -sum(w*log(dens(object)))
-              }
-            } else {
-              negLL <- function(pars) {
-                object <- setpars(object, c(pars[1], exp(pars[2])))
-                -sum(log(dens(object)))
-              }
-            }
-            pars <- optim(c(object@parameters$mu, log(object@parameters$sigma)), fn=negLL)$par
-            object <- setpars(object,c(pars[1], exp(pars[2])))
-            object
-          }
-)
-```
-
-```{r, include=F}
-priordat <- avg_ret_df %>% filter(roundNum==1)
-n_state_min <- 2
-n_state_max <- 7
-
-trust_simple <- trust_ctrl <- trust_coax <- trust_fullCtrst <- trust_prePost <- list()
-
-# HMMs based on bins
-for(i in n_state_min:n_state_max) {
-
-  trust_simple[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-
-  trust_ctrl[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*ctrl_only_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-
-  trust_coax[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*coax_only_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-
-  trust_fullCtrst[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*intervention_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-
-  trust_prePost[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*pre_post_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-
-}
-
-# vtdgaus no contrasts
-simple_HMMs <- ctrl_HMMs <- coax_HMMs <- fullCtrst_HMMs <- prePost_HMMs <- list()
-
-for(i in n_state_min:n_state_max) {
-
-  rModels <- rep(list(list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment))),each=i)
-
-  simple_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_simple[[i]]@transition,prior=trust_simple[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)
-
-  ctrl_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_ctrl[[i]]@transition,prior=trust_ctrl[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)
-
-  coax_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_coax[[i]]@transition,prior=trust_coax[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)
-
-  fullCtrst_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_fullCtrst[[i]]@transition,prior=trust_fullCtrst[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)
-
-  prePost_HMMs[[i]] <- makeDepmix(response=rModels,transition=trust_prePost[[i]]@transition,prior=trust_prePost[[i]]@prior, ntimes = rep(15,636), homogeneous=FALSE)
-
-}
-```
-
-```{r, include=FALSE}
-
-# fittedSimple <- fittedCoax  <- fittedCtrl  <- fittedFullCtrst  <- fittedPrePost  <- list()
-# # increase default in multistart from 10 to 20. or set the same seed for every model
-# 
-# set.seed(20221028)
-# for(i in n_state_min:n_state_max) {
-# 
-#   fittedSimple[[i]] <- multistart(simple_HMMs[[i]],nstart=20)
-# }
-# save(fittedSimple, file="fittedSimple.RData")
-# ##############################
-# 
-# set.seed(20221028)
-# for(i in n_state_min:n_state_max) {
-#   fittedCtrl[[i]] <- multistart(ctrl_HMMs[[i]],nstart=20)
-# }
-# save(fittedCtrl, file="fittedCtrl.RData")
-# ##############################
-# 
-# set.seed(20221028)
-# for(i in n_state_min:n_state_max) {
-#   fittedCoax[[i]] <- multistart(coax_HMMs[[i]],nstart=20)
-# }
-# save(fittedCoax, file="fittedCoax.RData")
-# ##############################
-# 
-# set.seed(20221028)
-# for(i in n_state_min:n_state_max) {
-#   fittedPrePost[[i]] <- multistart(prePost_HMMs[[i]],nstart=20)
-# }
-# save(fittedPrePost, file="fittedPrePost.RData")
-# #############################
-# 
-# 
-# 
-# for(i in n_state_min:n_state_max) {
-#   fittedFullCtrst[[i]] <- multistart(fullCtrst_HMMs[[i]],nstart=20)
-# }
-# save(fittedFullCtrst, file="fittedFullCtrst.RData")
-# ###############################
-
-```
-
-```{r, include=FALSE}
-
-# THE CODE BELOW WAS NOT USED; ALL CONVERGED. PUT IT HERE IN CASE IT IS NEEDED LATER ON.
-# library(depmixS4)
-# 
-# load("data/fittedSimple.RData")
-# load("data/fittedCtrl.RData")
-# load("data/fittedCoax.RData")
-# load("data/fittedFullCtrst.RData")
-# load("data/fittedPrePost.RData")
-# load("data/newFull.RData")
-# 
-# has_converged <- function(object, numeric = TRUE){
-#   msg <- object@message
-#   if(numeric) as.integer(grepl("converged", msg)) else 0
-# }
-# 
-# 
-# fit_until_convergence <- function(fitted_model, max_iterations=2) {
-#   cat(fitted_model@nstates)
-#   iterations <- 0
-#   converged <- has_converged(fitted_model)
-#   
-#   while (!converged && iterations < max_iterations) {
-#     # Use parameters from the fitted model as initial parameters
-#     initial_params <- getpars(fitted_model)
-#     new_model <- setpars(fitted_model, initial_params)
-#     
-#     # Refit the model
-#     fitted_model <- fit(new_model)
-#     converged <- has_converged(fitted_model)
-#     iterations <- iterations + 1
-#   }
-#   
-#   if (converged) {
-#     cat("NS = ", fitted_model@nstates,"Convergence has been reached.\n")
-#     flush.console()
-#     return(fitted_model)
-#   } else {
-#     cat("Maximum iterations reached. Convergence has not been reached.\n")
-#     flush.console()
-#     return(fitted_model)
-#   }
-# }
-# 
-# 
-# run_parallel_fitting <- function(mods_vec,num_cores = 5) {
-#   # Set up the parallel backend
-#   my.cluster <- parallel::makeCluster(num_cores, type = "PSOCK")
-#   doParallel::registerDoParallel(cl = my.cluster)
-#   
-#   # Export the fit_until_convergence function to the workers
-#   parallel::clusterExport(my.cluster, "fit_until_convergence")
-#   parallel::clusterExport(my.cluster, "has_converged")
-# 
-#   # Run the loop in parallel using foreach
-#   converged_mods_vec <- foreach(mod = mods_vec, .packages = c("depmixS4"), .combine = "c") %dopar% {
-#     cat(mod@nstates)
-#     fit_until_convergence(mod)
-#   }
-# 
-#   # Stop the parallel backend
-#   parallel::stopCluster(my.cluster)
-#   return(converged_mods_vec)
-# }
-# 
-# 
-# sapply(fittedSimple[2:7],has_converged)
-# sapply(fittedCtrl[2:7],has_converged)
-# sapply(fittedCoax[2:7],has_converged)
-# sapply(fittedFullCtrst[2:7],has_converged)
-# sapply(fittedPrePost[2:7],has_converged)
-# sapply(newFull[2:7],has_converged)
-
-```
-
-```{r, include=FALSE}
-# # The full contrast model convergence was not attained. Here we use parameters of fitted PrePost model as initial values of the FullContrast model to speed up fitting and aim for faster convergence.
-
-# newFull <- fittedFullCtrst
-# for (ns in n_state_min :n_state_max){
-# 
-#   fmod <- fittedPrePost[[ns]]
-#   origin_pars <- getpars(fmod)
-#   numCovTr <- 4
-#   numCovIn <- 2
-#   
-#   # create a new vector which has the right number of pars for the full contrast model. 
-#   new_pars <- c(origin_pars[1:(ns*2)])
-#   # from is state we are transitioning from 
-#   for(from in 1:ns) {
-#   mat <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
-#   new_mat <- mat[,c(1:2,3,3,4,4)]
-#   new_pars <- c(new_pars,as.numeric(new_mat))
-#   }
-#   
-#   new_pars <- c(new_pars,origin_pars[(ns*numCovIn + 1 + (ns - 1)*numCovTr*ns + numCovTr*ns):length(origin_pars)])
-#   
-#   newFull[[ns]] <- setpars(newFull[[ns]],new_pars)
-#   newFull[[ns]] <- fit(newFull[[ns]], emcontrol= em.control(maxit = 1000,random.start = FALSE))
-# }
-# 
-# save(newFull, file="newFull.RData")
-
-```
-
-```{r, include=FALSE}
-
-load("data/fittedSimple.RData")
-load("data/fittedCtrl.RData")
-load("data/fittedCoax.RData")
-load("data/fittedFullCtrst.RData")
-load("data/fittedPrePost.RData")
-load("data/newFull.RData")
-
-BICs_simple <- BICs_Ctrl <- BICs_Coax <- BICs_FullCtrst <- BICs_PrePost <-  BICs_newFull <- list()
-for(i in n_state_min:n_state_max) {
-  BICs_simple[[i]] <- BIC(fittedSimple[[i]]) 
-  BICs_Ctrl[[i]] <- BIC(fittedCtrl[[i]])
-  BICs_Coax[[i]] <- BIC(fittedCoax[[i]]) 
-  BICs_FullCtrst[[i]] <- BIC(fittedFullCtrst[[i]]) 
-  BICs_PrePost[[i]] <- BIC(fittedPrePost[[i]]) 
-  BICs_newFull[[i]] <- BIC(newFull[[i]])
-
-}
-
-print("SIMPLE HMM models")
-BICs_simple
-
-print("HMM with contrast on post Control vs others")
-BICs_Ctrl
-
-print("HMM with contrast on post Coax vs others")
-BICs_Coax
-
-print("HMM with Pre vs Post Contrast")
-BICs_PrePost
-
-print("HMM with contrast levels Pre, Post Control and Post Coaxing")
-BICs_FullCtrst
-
-print("HMM with contrast levels Pre, Post Control and Post Coaxing, new fitting")
-BICs_newFull
-
-df_bics <- cbind(2:7,as.numeric(BICs_simple[2:7]), as.numeric(BICs_Ctrl[2:7]),as.numeric(BICs_Coax[2:7]), as.numeric(BICs_PrePost[2:7]), as.numeric(BICs_newFull[2:7]))
-df_bics
-
-```
-
-```{r, include=FALSE}
-library(knitr)
-library(kableExtra)
-
-# Create a data frame for the models
-models <- data.frame(
-  Model = c("HMM-inv", "HMM-prepost", "HMM-coax", "HMM-ctrl", "HMM-full"),
-  Pre_Intervention =  c(0, -1, -1, -1, -1),
-  Post_Intervention = c(0, 1, 1, -1, 2),
-  Pre_Control =       c(0, -1, -1, -1, -1),
-  Post_Control =      c(0, 1, -1, 1, 1)
-)
-
-# Create a table
-models %>%
-  kable("pipe", caption = "Models and their Contrasts") %>%
-  kable_styling()
-
-```
-
-```{r table-BICs-coax, include =FALSE, warning = FALSE, echo=FALSE, ft.align="center", tab.id='table-BICs-coax', label='table-BICs-coax'}
-
-data.frame(df_bics) %>% 
-  `colnames<-` (c("Number of states","HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost","HMM-full")) %>%
-  mutate_if(is.numeric, format, digits=4,nsmall = 0, big.mark = ",") %>% 
-  knitr::kable(.,booktabs = TRUE,
-  caption = 'Table of BICs for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>% kable_styling(latex_options="scale_down")
-```
-
-We analyzed participants' behavior differences in the intervention versus control conditions using hidden Markov models (HMM).
-Five models were used: "HMM-inv" assumed transition states depended solely on investment, ignoring game number and condition.
-"HMM-prepost" contrasted Pre and Post Intervention.
-"HMM-coax" contrasted post-intervention with pre-intervention and both control conditions.
-"HMM-ctrl" contrasted post-control with pre-control and both intervention conditions.
-"HMM-full" grouped pre-control and pre-intervention as one, with separate groups for post-control and post-intervention.
-Models were fitted using 2 to 7 states, selecting the lowest BIC.
-Generally, 5-7 state models best explained the data.
-A likelihood ratio test compared the models' goodness of fit, contrasting the complex HMM-full model with nested models equating behavior in certain stages and conditions.
-
-<!-- Table \ref{tab:table-BICs-coax} shows the BICs of the various fitted models for an assumed number of states between 2 and 7.
-For a simple model without any contrasts (HMM-inv) and a model with post-control only contrast (HMM-ctrl) we find a 6-state model to be best fitting.
-If the contrast is between the post-intervention group and all the other groups (HMM-coax), then a 7 state model is best fitting.
-When the contrast is comparing only pre and post Intervention groups (HMM-prepost), a 5 state model fits best.
-Finally, when we distinguish between pre-manipulation, post-control and post-intervention (HMM-full), we find that a 5 state model fits best.
-Since we only fit models between 2 and 7 states, it is possible that for those where we find the 7 state model to be best fitting, models with a higher number of states could fit the data better.
-We decided to stop at 7 states for computational cost reasons and because the interpretation of models with a higher number of states becomes complex.
--->
-
-```{r, include=FALSE}
-summary(fittedSimple[[5]])
-
-logLik(fittedSimple[[5]])
-logLik(fittedCtrl[[5]])
-logLik(fittedCoax[[5]])
-logLik(fittedPrePost[[5]])
-# logLik(fittedFullCtrst[[5]])
-logLik(newFull[[5]])
-
-# Nested model comparison for 5 states, with and without intervention contrast. llratio test shows no effect, meaning interaction term addition does not change goodness of fit of model. 
-llratio(newFull[[5]], fittedSimple[[5]])
-
-llratio(fittedCtrl[[5]],fittedSimple[[5]])
-llratio(fittedCoax[[5]],fittedSimple[[5]])
-llratio(fittedPrePost[[5]],fittedSimple[[5]])
-
-llratio(newFull[[5]],fittedCtrl[[5]])
-llratio(newFull[[5]],fittedCoax[[5]])
-llratio(newFull[[5]],fittedPrePost[[5]])
-
-```
-
-In order to compare the goodness of fit of the various models, we test the relative likelihood of models using a likelihood ratio test.
-This procedure is useful to compare the most complex model (HMM-full, which allows for differences between pre-intervention and the two conditions post-intervention) to nested models which equate behaviour in some if the stages and conditions.
-
-<!-- We start by comparing HMM-full with HMM-inv.
-We find that HMM-full fits the data better than HMM-inv ($\chi^2(84) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
-Likewise HMM-ctrl fits better than HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedCtrl[[5]]))) , 2)`$, $p < .001$).
-The same is true for HMM-coax compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedCoax[[5]]))) , 2)`$, $p < .001$) and HMM-prepost compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedPrePost[[5]]))) , 2)`$, $p < .001$).
-HMM-inv being the worst fitting model compared to the others indicates the existence of differentiated behavior pre vs post manipulation and/or between the control and intervention groups.
--->
-
-Using likelihood ratio tests, we find that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCtrl[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCoax[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedPrePost[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
-This is consistent with a differentiated behavior of the trustees between all three groups: the post-intervention group, the post-control group and the pre-manipulation group.
-
-<!--    ORDER THE STATES    -->
-
-```{r, include=FALSE}
-tr_fdmod_5 <- order_mod_gauss(newFull[[5]])
-```
-
-```{r, include=FALSE}
-
-state1 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[1]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-state2 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[2]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-state3 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[3]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-state4 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[4]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-state5 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[5]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-returns <- seq(0.025,0.975,length=20)
-
-response_best_mod <- as.data.frame(cbind(returns,state1,state2,state3,state4,state5)) %>% 
-  pivot_longer(cols=c("state1","state2","state3","state4","state5"),
-                    names_to='Trustee_state',
-                    values_to='probability')
-
-```
-
-<!-- Using the best fitting model according to likelihood ratio tests (HMM-full), Figure \ref{fig:trusteeHMMPlot} shows the distribution of the participants' returns conditional on the latent state they are in.
-The states are ordered based on the mean of the Gaussian distribution fitted to the response (percentage return).
-State 1 represents the state in which the returns have have the lowest underlying mean, and state 5 is the state in which the returns have the highest underlying mean.
-The higher the state number the more pro-social the policy adopted.
-More specifically, state 1 can be thought of as a non-cooperative state in which returns are low and close to 0, meaning that the trustee is keeping most of the tripled investment.
-State 2 is a state where the average return is around the investment sent and can be interpreted as a cautious state in which the return on trust is small.
-States 3, 4 and 5 are increasingly cooperative states.
-For instance, in state 5, the average return is close to two thirds of the tripled investment, meaning the trustee is keeping an amount similar to the investment that was sent and returning to the investor double the investment.
--->
-
-<!-- Figure \ref{fig:plotTransitionsDiscGaus} shows the transition between states as a function of the investment received for each group (pre-manipulation, post-control and post-intervention) using results from the best fitting model: HMM-full.
-The best fitting HMM model has multiple states and a high number of parameters.
-We can nonetheless focus on particular states linked to the breakdown and repair of cooperation.
-For instance, focusing on the transition functions to state 1 (the lowest return state with returns close to 0) from higher return states, we can compare the  post-control group to the post-intervention group.
-The red line representing the probability of transitioning to the low-return state 1 when the investment is close to 0 is lower in the intervention group compared to the control group when the trustee is in a relatively pro-social state (states 3 to 5).
-This is pointing towards more "forgiving" behavior where participants in the intervention group were less likely to transition to this anti-social state compared to the control group.
--->
-
-Using the HMM-full model, we can retrieve participants' return distributions based on their latent states (Figures \ref{fig:postStatesBestMod}.A) and transition probabilities between these states (Figure \ref{fig:plotTransitionsDiscGaus}).
-The states are ranked by mean return, with State 1 having the lowest mean return and State 5 the highest.
-A higher state number indicates a more pro-social policy.
-We focused on states related to cooperation's breakdown and repair.
-We compared the transition probabilities between states when the investment is low for post-control and post-intervention groups.
-Figure \ref{fig:plotTransitionsDiscGaus} suggests that the intervention group is more forgiving of low investments, as they are less likely to shift to an anti-social state when faced with defection compared to the control group.
-
-```{r, include=FALSE}
-
-plot_state_transitions <- function(fmod, numCovIn, numCovTr) {
-
-  #print(getpars(fmod))
-  ns <- nstates(fmod)
-
-  trans_prob <- data.frame(
-    from = rep(1:ns, each=100*ns),
-    to = rep(1:ns, each=100),
-    investment = seq(0,20,length=100),
-    prob_pre = 0,
-    prob_ctrl = 0,
-    prob_coax =0
-  )
-
-  y0 <- matrix(0.0,ncol=ns, nrow=100)
-  y1 <- matrix(0.0,ncol=ns, nrow=100)
-  y2 <- matrix(0.0,ncol=ns, nrow=100)
-
-  for(from in 1:ns) {
-  pars <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
-  #print(pars)
-
-    for(to in 1:ns) {
-        x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"investment"]
-        y0[,to] <- exp(pars[to,1] + pars[to,2]*x)
-        #ctrst 2 = 1, post intervention vs pre
-        y2[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,3]*1 + pars[to,5]*x )
-        #ctrst 1 = 1, post control vs pre
-        y1[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,4]*1 + pars[to,6]*x )
-    }
-    y0 <- y0/rowSums(y0)
-    y1 <- y1/rowSums(y1)
-    y2 <- y2/rowSums(y2)
-
-    for(to in 1:ns) {
-      trans_prob$prob_pre[trans_prob$from == from & trans_prob$to == to] <- y0[,to]
-      trans_prob$prob_ctrl[trans_prob$from == from & trans_prob$to == to] <- y1[,to]
-      trans_prob$prob_coax[trans_prob$from == from & trans_prob$to == to] <- y2[,to]
-    }
-  }
-
-  saveRDS(trans_prob, "data/trans_prob.RDS")
-
-  return(trans_prob)
-
-  #  p_pre <- ggplot(trans_prob,aes(x=investment,y=prob_pre, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function pre manipulation") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # p_ctrl <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post control") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # p_coax <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post intervention") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # grid.arrange(p_pre, p_ctrl,p_coax, nrow=3, ncol=1)
-
-}
-
-# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
-
-```
-
-```{r,include=F}
-
-trans_prob <- readRDS("data/trans_prob.RDS")
-
-ctrl_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + 
-  geom_line() + 
-  geom_line(aes(y=prob_pre),linetype="dotted") +
-  facet_wrap(~from) + 
-  ylim(c(0,1)) + 
-  ggtitle("Transition function pre- and post-control manipulation") + 
-  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
-  theme_bw()
-
-coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
-  geom_line() + 
-  geom_line(aes(y=prob_pre),linetype="dotted") +
-  facet_wrap(~from) + 
-  ylim(c(0,1)) + 
-  ggtitle("Transition function pre- and post-intervention manipulation") + 
-  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
-  theme_bw()
-
-```
-
-```{r plotTransitionsDiscGaus, fig.cap="Transition function for the HMM-full trustee model.
-Each panel represents the state transitioned from, and each color the state transitioned to.
-Solid lines show estimated transition probabillities post-manipulation.
-Dotted lines show the same probabilities prior to the manipulation",fig.align="center", fig.width=6, fig.height = 7 }
-
-grid.arrange(ctrl_pre_plot , coax_pre_plot , nrow=2, ncol=1)
-
-# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
-
-```
-
-<!-- To explore the differences in transition probabilities between the control and coaxing conditions, we can choose an investment and compare the probabilities of transitioning between States.
-For instance, in case the trustee is low in trustworthiness (State 1), and the investor sends an average amount, we can compare the likelihood of the trustee transitioning away from the low trustworthiness state.
-Assuming an investment of 10 (half the endowment), The trustee remains in State 1 with around $85\%$ probability in the control condition, but only $67\%$ probability after the coaxing intervention.
-Likewise, assuming the trustee is in State 4, and receiving a low investment of 2, there is a much lower probability ($0.2\%$) of transitioning to low trustworthiness state in the coaxing condition compared to the control condition ($21\%$).
--->
-
-```{r, include = FALSE}
-set.seed(20221010)
-# Get investor posterior states from model and add to data table
-
-# mention we are using local decoding (refer to the book). 
-predTrStates <- posterior(tr_fdmod_5, type="local")
-avg_ret_df$TrState <-  factor(predTrStates, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))
-
-# avg_ret_df$TrState <-  factor(predTrStates, levels= c(5,4,3,2,1),labels=c("5","4","3","2","1"))
-
-# predTrStates <- posterior(tr_fdmod_5)
-# avg_ret_df$TrState <-  factor(predTrStates$state, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))
-
-library(dplyr)
-temp_df <- avg_ret_df %>% dplyr::select(roundNum,investment,returns, next_investment, TrState)
-```
-
-```{r, include=FALSE}
-
-trusteeHMMPlot <- ggplot(response_best_mod,                            
-       aes(x = returns,
-           y = probability,
-           fill = Trustee_state)) +
-  geom_bar(stat = "identity",
-           position = "dodge") + 
-  labs(fill='Latent trustee State') +
-  theme_bw() + 
-  theme(legend.position = "bottom")
-
-# investor real state distribution (posterior)
-postHMM <- ggplot(avg_ret_df %>% dplyr::filter(gameNum.f=="post")) +
-  geom_bar(aes(x = roundNum, group = TrState, fill = TrState),  position = position_stack(reverse = TRUE)) + 
-  facet_wrap(~condition.f) +  
-  labs(x = "Round", fill='Posterior trustee state') +
-  theme_bw() +
-  theme(legend.position = "bottom")
-
-```
-
-```{r postStatesBestMod,  echo=FALSE, fig.cap = "A: Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model.
-The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social.
-B: Distribution of posterior trustee states post manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.", fig.align="center", fig.height = 8}
-
-ggpubr::ggarrange(trusteeHMMPlot , postHMM , nrow=2, ncol=1,labels = c("A", "B"),common.legend = FALSE)
-
-```
-
-```{r, include= F}
-
-props_df_5 <- avg_ret_df %>% 
-  filter(gameNum.f=="post", roundNum== 5) %>% 
-  group_by(condition.f,TrState) %>% 
-  summarise(n = n()) %>%
-  mutate(freq = n / sum(n))
-
-prop.test(c(11,29), c(159,159))
-
-props_df_14 <- avg_ret_df %>% 
-  filter(gameNum.f=="post", roundNum== 14) %>% 
-  group_by(condition.f,TrState) %>% 
-  summarise(n = n()) %>%
-  mutate(freq = n / sum(n))
-
-prop.test(c(35,68), c(159,159))
-
-props_df_13 <- avg_ret_df %>% 
-  filter(gameNum.f=="post", roundNum== 13) %>% 
-  group_by(condition.f,TrState) %>% 
-  summarise(n = n()) %>%
-  mutate(freq = n / sum(n))
-
-# compare proportions in state 1 in round 13 between conditions
-prop.test(c(48,72), c(159,159))
-
-# compare proportions in states 4 and 5  in round 13 between conditions
-prop.test(c(48,18), c(159,159))
-
-# props_df_12 <- avg_ret_df %>% 
-#   filter(gameNum.f=="post", roundNum== 12) %>% 
-#   group_by(condition.f,TrState) %>% 
-#   summarise(n = n()) %>%
-#   mutate(freq = n / sum(n))
-
-```
-
-To quantitatively explore the differences in transition probabilities between the control and intervention conditions, we can estimate from the model, using local decoding methods from the depmixS4 package [@visser_depmixs4_2021], the most likely posterior state of the trustee participants by round given the actions they have taken.
-Figure \ref{fig:postStatesBestMod}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
-For instance, in round 5, state 1 was the most likely posterior state for only $7$% of participants in the intervention condition compared to $24$% in the control condition ($\chi^2(1) = 8.26, p < 0.01$).
-For the post-defection trial after the intervention (round 14), state 1 was the most likely state for only $22$% of participants in the intervention condition compared to $43$% in the control condition ($\chi^2(1) = 14.70, p < 0.001$).
-
-The posteriors also suggest that a non-negligible proportion of participants in the intervention condition did not exhibit a behaviour consistent with the goal of the intervention as they were still best fit by low-return states post intervention.
-For instance, focusing on round 13 post defection $30.2$% of those in the intervention condition were most likely to be in the least pro-social state 1.
-These differences can be seen as an indication of important heterogeneity in the effectiveness of the intervention.
-
-```{r, include=FALSE}
-# library(depmixS4)
-# 
-# n_bootstraps <- 1  # number of bootstrap resamples
-# bootstrap_estimates <- matrix(NA, nrow=n_bootstraps, ncol=1)  # to store bootstrap estimates
-# 
-# ns <- 3
-# numCovIn <- 2
-# numCovTr <- 6
-# from <- 3
-# to <- 1
-# 
-# for (i in 1:n_bootstraps) {
-#   # create a bootstrap resample of the data
-#   #bootstrap_data <- data[sample(nrow(data), replace=TRUE), ]
-#   bootstrap_data <- avg_ret_df %>% filter(id %in% sample(id,replace=TRUE))
-#   
-#   rModels <- rep(list(list(vtdgaus(y=bootstrap_data$ret_pct_0,yield=3*bootstrap_data$investment))),each=ns)
-#   
-#   simple_mod <- depmix(ret_pct ~ 1, data = bootstrap_data, nstates = ns, transition = ~ next_investment*intervention_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-#   
-#   
-#   # fit the model to the bootstrap resample
-# 
-#   model <- makeDepmix(response=rModels, transition = simple_mod@transition , prior = simple_mod@prior, initdata=priordat, ntimes = rep(15,636), homogeneous=FALSE)
-#   
-#   cat("two")
-#   # trust_fullCtrst[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*intervention_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-#   
-#   
-# 
-#   fit <- fit(model)
-#   cat("post-fit")
-# 
-#   # store the estimates
-#   #bootstrap_estimates[i, ] <- getpars(fit)
-#   
-#   pars <- matrix(getpars(fit)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
-#   
-#    bootstrap_estimates[i, ] <- pars[to,3]
-#   
-# }
-# 
-# # calculate 95% confidence intervals
-# ci_lower <- apply(bootstrap_estimates, 2, function(x) quantile(x, 0.025))
-# ci_upper <- apply(bootstrap_estimates, 2, function(x) quantile(x, 0.975))
-# 
-# # print the confidence intervals
-# print(ci_lower)
-# print(ci_upper)
-
-```
-
-# Discussion
-
-In this experiment, we made human participants face artificial computer agents endowed with the ability to transition between latent states and react to the participants' returns.
-The number of states, the policy in each state as well as the way these agents transitioned between states was based on estimating a hidden Markov model to behaviour from real human participants.
-On average, we saw the emergence of cooperative behavior with investment and returns in line with what is reported in human dyadic interaction in the repeated trust game [@charness_investment_2008; @fiedler_social_2011].
-The emergence of cooperative behavior and participant's uncertainty about whether they were facing human or artificial opponents, point to the potential of these agents to mimic human behavior in economic games whilst offering a higher degree of experimental control.
-
-The intervention's aim was to articulate the effect of acting on impulse in case of a transgressive action from the investor in the form of a one-off low investment.
-When the agent defected as programmed, yielding a situation similar to the one presented in the intervention, the intervention led to higher percentage returns post defection compared to the control group, as intended.
-Participants emotional reactions to the received investment, we similar pre and post-intervention, so the higher returns were produced despite participants having the same emotional reaction.
-This might indicate that the intervention achieved its goal of encouraging participants to respond in a non-impulsive, considered way, overriding the emotional urge to retaliate.
-
-What was also notable was that the intervention led to generally higher returns post-intervention, even before the defection trial.
-This could be for a number of reasons.
-One possibility is that participants simply learned that by returning more, the investment on the next trial would be higher.
-However, this explanation is unlikely, as we did not see a similar increase in percentage returns in the control condition.
-Another possibility is that, on average, the second player they faced invested more, which prompted positive reciprocity in the human trustees.
-As all players were programmed in the same way, any difference would be due to participant's actions.
-Further, participants rated both players similarly on relevant attributes of cooperativeness and trust.
-The higher returns are thus unlikely to be driven by different beliefs about the investor.
-A likely explanation for overall higher trustworthiness, as measured by higher percentage return post investment, is that participants, on average, interpreted the intervention message as an argument for more pro-social behavior, irrespective of the investor's actions.
-
-It is also noteworthy that there were important individual differences in the percentage return changes post vs.
-pre intervention, which can be seen as a proxy for the intervention effectiveness.
-Some participants might not have been convinced by the intervention's message and decided to reduce their returns both pre and post defection in the second trust game, while others increased their returns in both phases.
-This raises important questions for the measurement of intervention effectiveness.
-Recent work has shed light on the important heterogeneity inherent in how disorders are categorised: This heterogeneity arises from the view that mental health problems should be viewed as complex systems, or interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017].
-This view was used to justify computational psychiatry's difficulty in establishing differential and reliable predictors of likely treatment responses [@hitchcock_computational_2022].
-But if a healthy group's reaction to a relatively explicit intervention is itself heterogeneous as we have shown in this experiment, then the issue of variable treatment responses might the result of the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself.
-As such, a rigorous exploration of the determinants of inter-individual differences to an intervention in the general patient population is required.
-
-In our case, judging by the inter-individual heterogeneity in responses, some people may not have been convinced that a coaxing behavior was a good way to establish long term cooperative outcomes, and their need to “punish” the other player for their low investment may have been more pertinent than what we suggested.
-This was also evident from the participants' replies to a question about whether they would change their behavior, just after seeing the intervention manipulation.
-An important avenue is to explore the role of emotion in decision making in such situations.
-We could aim to measure emotional reactions more accurately and explore whether specific emotions mediate the relationship between the investment received and the decision of what proportion to return.
-Measuring the emotions using the two axes of valence and arousal could be improved: Results indicate that these concepts may not have been well understood by participants since we would not expect to see low arousal after the pre-programmed defection of the investor.
-
-The effect of this short intervention was not transferred to the Repeated Prisoner's Dilemma game.
-In this game, the rate at which the cooperative option was chosen was not significantly different between the control and intervention groups, both pre and post defection.
-Since the prisoner's dilemma is a very popular economic game, it is possible that participants had strong prior preferences towards which strategy they would adopt, irrespective of whether or not they received the intervention.
-As such, this paradigm might not be the best test case for knowledge transfer.
-For those that took on the intervention message and showed coaxing behavior in the second trust game, the fact that the investor still defected in the final rounds might have reinforced the idea that not reciprocating negative behavior is a losing strategy after all.
-
-Overall, it is remarkable that such a short intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments can lead to such differentiated behavior.
-In future studies, we aim to explore the effects of different cognitive interventions and improve the experimental design in multiple ways.
-First, the intervention could benefit from being more interactive medium, with visual inputs such as cartoons and videos, rather than pure text which can be cumbersome to read and lead to lower engagement.
-Second, we selected trustees from the general population, which might not suffer from the inability or unwillingness to repair relationships due to accidental breakdown of trust that characterises some mental health disorders such as BPD.
-As such, it would be interesting to contrast these results with findings from experiments involving trustees that are selected from patient populations known to suffer from difficulties in maintaining or repairing cooperative interactions.
-Third, as we explained above, the choice of the task to measure transfer of intervention learning could be made better by involving less popular paradigms.
-The high popularity of the Prisoner's Dilemma and the strategy of playing tit-for-tat may have resulted in a strong prior on which strategy to adopt in this game irrespective of the intervention.
-We believed that asking people about how they felt in the control condition might have affected how they behaved and might constitute an intervention in itself.
-However, being able to compare the differential impact of the intervention on the emotional interpretation of the opponent action between an intervention and control conditions could lead to insights on the mechanism through which the intervention affects the emotional reaction to the opponent's actions.
-
-# Conclusion
-
-We explored the effect of a short cognitive intervention on the behavior of human trustees facing adaptive artificial agents endowed with multiple latent behavioral states.
-Each state defines different levels of a cooperative response with the agent able to transition between these states based on the behavior of the human opponent.
-Feedback from participants indicated that these agents were sometimes perceived as humans.
-Their strategy led to emergent cooperative behavior when playing the repeated trust game with human players.
-The intervention, promoting a less impulsive reaction to transgressive actions, led to coaxing behavior and less negative reciprocity when the investor sent a very low investment.
-It also led to more trustworthy behavior prior to the pre-programmed defection trial and to coaxing behavior after defection.
-Whilst this intervention effect varied between participants and generally was not transferred to a new game, an HMM analysis of participant's play post intervention showed differentiated patterns of transitions between latent states, indicating a change in the effect of the opponent action on the probability of transitioning between latent mental states.
-
-# References

### 2023-06-07 article.Rmd
started changes

@@
 require(knitr)
-require(citr)
+#require(citr)
 require(bookdown)
@@
 
-At the core of social interaction is figuring out the goals, intentions, and decision-making process of the interaction partner.
-This inference is however fraught with uncertainty, as we cannot reasonably observe these features without prior knowledge of the person.
-Absent a history of interaction, one needs to decide whether to take the risk of trusting others.
+Determining the other's goals, intentions, and decision-making process is fundamental to successful social interaction.
+This inference is however fraught with uncertainty, as we cannot directly observe these features, and may need extensive prior knowledge of the person.
+Absent a history of interaction, one may decide to trust the other's goals and intentions are aligned with one's own.
 The challenge of trust is that it is by construction a risky endeavour.
-For example, if we deem a person trustworthy, we might decide to take the risk of investing in the relationship hoping for a collaborative outcome.
-If we misplace our trust, this can come at a high cost to us.
+If we deem a person trustworthy, we might take the risk of investing in the relationship, hoping for a collaborative outcome.
+If this trust is misplaced, it can come at a high cost.
 Not trusting others is also risky since opportunities for cooperation may be foregone.
@@
 Evidence from the literature emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016 ; @meng_multilevel_2014].
-It affects the health status of individuals through reinforcing social support networks, maintaining community norms and facilitating collective action.
+It affects the health status of individuals by reinforcing social support networks, maintaining community norms and facilitating collective action.
 Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders.
@@
 A well-established paradigm in the study of trust is the repeated trust game [@joyce_trust_1995].
-To encourage the emergence and maintenance of trust in this setting, some studies focused on modifying the game mechanism [@charness_investment_2008; @fiedler_effect_2017].
+In this game, the "investor" decides how much of an endowment to send to the other player (the "trustee").
+The amount that is sent is tripled and the trustee decides, in return, how much of the tripled amount to send back to the investor.
+To encourage the emergence and maintenance of trust in this setting, some studies focused on modifying the game mechanism, for example by introducing a third-party who monitors the actions of the other players [@charness_investment_2008; @fiedler_effect_2017].
 Others chose to intervene directly on the participants.
@@
 
-Whilst these interventions show that it is possible to improve cooperative outcomes at the start of the game, they did not address how to repair a breakdown of trust that might occur due to intentional or accidental non-cooperative actions by the players.
-Indeed, cooperative play in the repeated trust game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor after cooperation has been established, or a return of the trustee below the investment sent.
-Such ruptures of cooperation appear frequently when the trustee suffers from mental health disorders affecting the social domain such as Borderline Personality Disorder [@lieb_borderline_2004].
-In theses situations, BPD trustees fail to engage in trust repairing behavior such as coaxing the investor through sending high return to signal trustworthiness, and this failure may be linked to a failure to perceive their low returns in the game as a violation of social norms [@king-casas_rupture_2008].
-
-In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of interpersonal dysfunction in BPD patients.
-Whilst there is no proven pharmacological therapy for BPD, some forms of psychotherapy such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993], have been clinically validated as efficacious approaches to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
-However, these therapies suffer from a high variability in treatment responses.
-Determining which interventions are effective for particular patients has been very challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
+Whilst these interventions show that it is possible to improve cooperative outcomes at the start of the game, they do not address how to repair a breakdown of trust that might occur due to intentional or accidental non-cooperative actions by the players.
+Cooperative play in the repeated trust game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor or a return of the trustee below the investment sent [@bendor_when_1991].
+Such ruptures of cooperation appear frequently when the trustee suffers from social disorders such as Borderline Personality Disorder [BPD; @lieb_borderline_2004].
+In theses situations, BPD trustees fail to engage in trust repairing behaviours such as coaxing the investor by signalling trustworthiness via sending high returns.
+This failure may be linked to the misperception that their low returns in the game are not violating social norms [@king-casas_rupture_2008].
+
+In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of social dysfunction in BPD patients.
+Whilst there is no proven pharmacological therapy for BPD, psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] are proven to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
+However, response to these treatments is highly variable, and determining which interventions are effective for particular patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
 One promising approach is the study of how specific psychotherapeutic treatment components affect quantitative markers of behavior such as those inferred through computational modelling techniques [@huys_computational_2016; @reiter_neuro-cognitive_2021].

### 2023-06-13 article.Rmd
further edits

@@
 In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of social dysfunction in BPD patients.
-Whilst there is no proven pharmacological therapy for BPD, psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] are proven to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
+Whilst there is no proven pharmacological therapy for BPD, psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
 However, response to these treatments is highly variable, and determining which interventions are effective for particular patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
-One promising approach is the study of how specific psychotherapeutic treatment components affect quantitative markers of behavior such as those inferred through computational modelling techniques [@huys_computational_2016; @reiter_neuro-cognitive_2021].
-As such, using specific cognitive probes inspired by therapeutic interventions complemented by computational modelling of behavior in tasks, may allow us to uncover cognitive mechanisms targeted by common forms of psychotherapy.
-This may in turn form the basis for targeting of existing psychotherapies to different individuals.
-
-In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a pre-programmed, one-off low investment sent by an computer investor.
+One promising approach is the study of how specific components of psychotherapeutic treatment affect quantitative markers of behaviour such as those inferred through computational models [@huys_computational_2016; @reiter_neuro-cognitive_2021].
+Combining the use of specific cognitive probes inspired by therapeutic interventions and computational models of behaviour may allow us to uncover the cognitive mechanisms targeted by common forms of psychotherapy.
+In turn, this may provide the basis for choosing effective psychotherapeutic interventions for given individuals.
+
+In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a one-off low investment sent by an computerised investor.
 The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation.
-Participants are given the role of the trustee and are randomly assigned to either a control group or an intervention group.
-They play two instances of the repeated Trust Game facing what they believe are two different players.
-In between games, they either receive a cognitive intervention (intervention condition) or not (control condition, where participants are asked to solve anagrams).
-In reality, participants face the same computerised agent in both instances, which is programmed to play according to an HMM fitted to real players data.
-We explore whether the intervention has an effect on the behaviour of the trustee and whether the learning is transferred to a new repeated Prisoner's Dilemma game when facing a seemingly new player.
+Participants are given the role of the trustee and are randomly assigned to either a control or intervention group.
+They play two instances of the repeated trust game with two different investors.
+After the first instance of the game, they either receive a cognitive intervention (intervention condition) or perform an unrelated task solving anagrams (control condition).
+In reality, participants face the same computerised agent in both instances, which is programmed to play according to a hidden Markov model fitted to real players' data.
+We explore whether the intervention has an effect on the behaviour of the human trustee and whether this effect transfers to a different game (repeated Prisoner's Dilemma) and facing a seemingly new player.
 
@@
 The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years.
-Participants were paid a fixed fee of £5 plus a bonus dependent on their performance.
-The experiment had a 2 (Condition: Intervention or Control) by 2 (Game : Pre or Post Intervention) design, with repeated measures on the first factor.
-Participants were randomly assigned to one of the two levels of the second factor.
-
-## Procedure
-
-```{r timeline, fig.cap = "A) Experiment overview.
-After playing 15 rounds of a repeated trust game (RTG) as trustee, participants were randomized to either receive the control or active intervention.
-They then played the second set of 15 rounds of RTG (again as trustee) to examine intervention effects, and 7 rounds of a repeated prisoner’s dilemma to examine generalization of intervention effects.
-Finally, participants answered questionnaires and were debriefed.", fig.align='center', out.width="80%"}
-
-knitr::include_graphics("figures/timeline.png")
-
-```
-
-<!-- Figure \ref{fig:timeline} shows the timeline of the experiment.
-After reviewing an information sheet about the experiment, participants were informed that there would be three phases to go through, with them facing a different opponent in each phase.
-They would face the same player throughout the first phase, consisting of the "Investment Game" with several rounds.
-This was the moniker used for the repeated trust game, and a total of 15 rounds were played.
-Participants were then randomly assigned to either a control or intervention condition.
--->
-
-<!-- <!-- After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.
-A comprehension quiz on the trust game followed the instructions.
-The first trust game then ensued:  Each round started with an investment stage where the investor decided how much to send to the trustee and that choice was revealed.
-Immediately afterwards, participants were presented with a two-dimensional field to indicate their emotional state on two dimensions: valence, from unpleasant to pleasant (on the horizontal axis) and arousal, from low arousal to high arousal (on the vertical axis).
-After selecting a point on the field, participants were asked to decide how much to send back to the investor using a slider ranging from sending back nothing to sending back the whole (tripled) investment.
-Following that choice, an outcome page summarised both players decisions and showed the total pay-off for each player and the round then concluded.
-At the end of the game, participants were asked to rate the player they were facing on 4 attributes using a scale from 1 to 10: Trustworthiness, friendliness, cooperativeness and selfishness.
--->
-
-<!-- In the second phase of the experiment, participants were informed they would be paired with a different player.
-This phase was similar to the first phase in terms of the game played (RTG) and the number of rounds.
-In all rounds of the RTG, participants gave feedback after seeing the investment received.
-This feedback was given though a two dimensional grid that was either related to their emotional state (degree of valence of arousal) in the Intervention group, or unrelated to the emotional state in the control group (speed of investor's response and magnitude of investment).
-At the end of each RTG, participants were asked to rate how cooperative, selfish, trustworthy and friendly they thought their interaction partner was.
-Details of the two dimensional grid and player ratings are given in the supplement.
--->
-
-<!-- After both trust games,  players were told they would be paired with a new player in the third phase of the experiment.
-This third phase consisted of 7 rounds of the prisoner's dilemma game, facing the new player.
-Throughout all games, players were explicitly told to aim to maximise the number of points as their bonus would depend on the score they accumulated throughout the experiment.
-The total number of rounds was not communicated to the participants in any of the games played.
--->
-
-<!-- After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment.  -->
-
-<!-- <!-- These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016].
--->
-
-<!-- Finally, participants were asked a series of questions around how they played each phase.
-First, they were asked whether they thought they played differently in the second compared to the first phase of the RTG.
-Second, participants had to select whether they thought the opponents they faced were human or computer agents.
-Finally, we revealed to the participants that they faced the same computer agent throughout the RTG.
-We explained that any change in their perception of the opponent or any change in how the opponent played is due to their own change in behavior as the agent was simply reacting to their actions.
-Finally, we asked participants to reveal whether this experiment has taught them anything about how they should behave in social situations.
--->
-
-The experiment as shown in Figure \ref{fig:timeline} began with participants briefed there will be three phases, and that they would face a new opponent in each phase.
-Phase one was a 15 round Trust Game (RTG) in which participants had the role of the trustee, facing the same investor opponent.
-Participants were then assigned to either the control or intervention conditions.
-Phase two was similar to Phase one, with participants being told they faced a new player.
-In both phases, participants were asked for feedback in each round after seeing the investment.
-The nature of the feedback solicited varied by condition, either emotion-related (intervention) or unrelated (control).
-Participants rated their interaction partner on various attributes after each phase.
-More details on these attributes, nature of feedback and exact instructions are found in the supplement.
-Phase three involved 7 rounds of the repeated prisoner's dilemma game (RPD) with a third player.
-Participants were explicitly told to aim to maximise the number of points in all phases.
-The total number of rounds was not communicated to the participants in any of the games played.
-
-Post-experiment, participants completed questionnaires related to mentalising abilities, emotion regulation and BPD traits (see details in supplement).
-They were then quizzed on their game-play, including whether they detected that all opponents were computer agents.
-The reveal explained that they were facing identical AI agents and that any perceived opponent changes were due to participants' own behavior.
-
-## Interventions
-
-The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taking in emotional states [@linehan_dbt_2015].
-Specifically, participants were presented with a low investment and asked to indicate their response.
-They were then invited to consider what their ultimate aim in the game was and whether this response was most likely to achieve their aim.
-The intervention is detailed in the supplementary information.
-
-In the control condition, participants were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
-They provided their answers in a free-form text box.
-The time given to solve the anagrams was the same as that given to respond to questions in the intervention manipulation.
-
-## Design of the AI agents in the RTG and RPD
+Participants were paid a fixed fee of £5 plus a bonus payment dependent on their performance.<!--MS: state average bonus--> The experiment had a 2 (Condition: Intervention or Control) by 3 (Game: Trust-Game Pre Intervention, Trust-Game Post Intervention, Prisoner's Dilemma Post Intervention) design, with repeated measures on the second factor.
+Participants were randomly assigned to one of the two levels of the first factor.
+
+## Tasks and Measures
+
+### Repeated Trust Game
+
+Participants played a 15-round repeated trust game [@joyce_trust_1995] in the trustee role against a computer-programmed investor.
+On each round the investor was endowed with 20 units and decided how much of that endowment to invest.
+This investment is tripled and the trustee then decides how to split this amount between them and the investor.
+If the trustee returns more than one third of the amount, the investor makes a gain.
+The Nash equilibrium for a single-round version is for the investor to send nothing.
+In the repeated version, rewards for both players are maximised if they build trust and share the benefits of the the investment multiplied by three.
+An investor who has been rewarded for taking the risk of sending an investment is more likely to invest more on future rounds.
+An investor obtaining a low return on their investment may choose to reduce future investment and thereby reduce both players’ gains.
 
@@
 ```
-The role of the investor was in reality played by an adaptive artificial agent whose strategy was modelled on the behaviour of human participants taking the role of the investor in the RTG.
-Using data from human dyadic interaction in the 10 round trust game, we estimate a Hidden Markov Model (HMM) to characterise the investor's behavior as emanating from a small number of latent states [@rabiner_hmm_1989].
-In this instance, for both iterations of the repeated trust game, the HMM used was identical: it had three states that can be described as "low-trust", "medium-trust" and "high-trust".
-Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust, as presented in Figure \ref{fig:HMMPanels}.A.
-Transition probabilities between these latent states were modelled as a function of the net return in the previous round conditional on the investor's state as shown in Figure \ref{fig:HMMPanels}.B.
-
-<!-- In order to probe efforts to repair trust, we introduced rounds where the investor deviated from the policy provided by the HMM, and chose to send a low investment in the Trust Game, or chose the non-cooperative action in the Prisoner's Dilemma.
-In the trust games, we programmed the HMM agent to send a very low investment (2 out of 20) to the trustee on specific rounds (round 12 pre-intervention and 13 post-intervention).
-For the repeated Prisoner's Dilemma game, we programmed the agent to choose the non-cooperative action on round 4.
-After each "defection" round, the agents were programmed to proceed their policy from before that round, effectively ignoring the participants' response to their defection.
-For instance, the HMM investor would send an investment in the post defection round that was consistent with the outcome of the round immediately prior to that round.
-For the RPD, the agent would continue to play tit-for-tat, but also ignoring what happened in the defection round, and basing its action on mirroring what the other player did in the round immediately prior to the defection round.
-This ignorance of reactions to the defection rounds was chosen to reflect an accidental defection, with the Investor being open to repair subsequent interaction.
--->
-
-In order to probe efforts to repair trust, we simulated trust breaches in both Trust Games and the Prisoner's Dilemma.
-The AI was programmed to break trust on specific rounds (12 pre-intervention, 13 post-intervention in the Trust Game; round 4 in Prisoner's Dilemma).
-After these "defection" rounds, the AI returned to its previous strategy, disregarding the participant's response to the breach.
-This simulated an accidental defection and a readiness to repair the interaction, providing insights into trust repair dynamics.
-
-<!-- ## Computational analysis of trustee returns -->
-
-<!-- In order to characterise the effect of the intervention on the trustees strategy, we fit a Hidden Markov Model to the percentage returns of the trustees for the RTG data.
-The model allows for switching between latent trustee states over time.
-Hidden Markov models assume that an observable trustee return at time $t$ depends on a latent trustee state at time $t$.
-It is assumed that the latent state at time $t$ depends on the latent state at the previous time $t-1$.
-The model is specified by the state-conditional action distributions (these are provided by the likelihood of the fitted models), an initial state distribution (the distribution over the strategies at the initial round), and the state-transition probabilities (probability of switching from one state/strategy to another).
-Initial state probabilities and the transition probabilities were estimated with the depmixS4 package [@visser_depmixs4_2021].
--->
-
-## Analysis of participants returns in the RTG
+
+The strategy of the computerised investor was modelled on behaviour of human investors in a 10-round RTG.<!-- reference to data -->.
+Using this data, we estimated a hidden Markov model (HMM) on investors' behaviour with three latent states, reflecting "low-trust", "medium-trust", or "high-trust".
+Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust (Figure \ref{fig:HMMPanels}.A).
+Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of the net return in the previous round (see Figure \ref{fig:HMMPanels}.B).
+
+In order to probe efforts to repair trust, the computerised agent was programmed to provide a low return on round 12 pre-intervention or 13 post-intervention.
+On all other rounds, the agent's actions were derived from the HMM (disregarding the participant's response on round 12).
+
+### Repeated Prisoner's Dillema
+
+Participants played 7 rounds of a repeated Prisoner's Dilemma.
+In each round, participants could choose a cooperative action with a a reward of 5 if the player also cooperated and the a reward of 1 if not, or a non-cooperative action that would yield a 7 points if the other person chooses the cooperative action and 2 points if not.
+The Nash equilibrium for a single-round version is to choose the non-cooperative action.
+
+The computerised agent was programmed to act according to a tit-For-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
+On round 4, the agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
+
+## Intervention
+
+The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taking in emotional states [@linehan_dbt_2015].
+Specifically, participants were presented with a low investment and asked to indicate their response.
+They were then invited to consider what their ultimate aim in the game was and whether this response was most likely to achieve their aim.
+The intervention is detailed in the supplementary information.
+
+In the control condition, participants were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
+They provided their answers in a free-form text box.
+The time given to solve the anagrams was the same as that given to respond to questions in the intervention manipulation.
+
+## Procedure
+
+```{r timeline, fig.cap = "Experiment overview.
+After playing 15 rounds of a repeated trust game (RTG) as trustee, participants were randomized to either receive the control or active intervention.
+They then played the second set of 15 rounds of RTG (again as trustee) to examine intervention effects, and 7 rounds of a repeated Prisoner’s Dilemma to examine generalization of intervention effects.
+Finally, participants answered questionnaires and were debriefed.", fig.align='center', out.width="80%"}
+
+knitr::include_graphics("figures/timeline.png")
+
+```
+
+<!-- Figure \ref{fig:timeline} shows the timeline of the experiment.
+After reviewing an information sheet about the experiment, participants were informed that there would be three phases to go through, with them facing a different opponent in each phase.
+They would face the same player throughout the first phase, consisting of the "Investment Game" with several rounds.
+This was the moniker used for the repeated trust game, and a total of 15 rounds were played.
+Participants were then randomly assigned to either a control or intervention condition.
+-->
+
+<!-- <!-- After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.
+A comprehension quiz on the trust game followed the instructions.
+The first trust game then ensued:  Each round started with an investment stage where the investor decided how much to send to the trustee and that choice was revealed.
+Immediately afterwards, participants were presented with a two-dimensional field to indicate their emotional state on two dimensions: valence, from unpleasant to pleasant (on the horizontal axis) and arousal, from low arousal to high arousal (on the vertical axis).
+After selecting a point on the field, participants were asked to decide how much to send back to the investor using a slider ranging from sending back nothing to sending back the whole (tripled) investment.
+Following that choice, an outcome page summarised both players decisions and showed the total pay-off for each player and the round then concluded.
+At the end of the game, participants were asked to rate the player they were facing on 4 attributes using a scale from 1 to 10: Trustworthiness, friendliness, cooperativeness and selfishness.
+-->
+
+<!-- In the second phase of the experiment, participants were informed they would be paired with a different player.
+This phase was similar to the first phase in terms of the game played (RTG) and the number of rounds.
+In all rounds of the RTG, participants gave feedback after seeing the investment received.
+This feedback was given though a two dimensional grid that was either related to their emotional state (degree of valence of arousal) in the Intervention group, or unrelated to the emotional state in the control group (speed of investor's response and magnitude of investment).
+At the end of each RTG, participants were asked to rate how cooperative, selfish, trustworthy and friendly they thought their interaction partner was.
+Details of the two dimensional grid and player ratings are given in the supplement.
+-->
+
+<!-- After both trust games,  players were told they would be paired with a new player in the third phase of the experiment.
+This third phase consisted of 7 rounds of the prisoner's dilemma game, facing the new player.
+Throughout all games, players were explicitly told to aim to maximise the number of points as their bonus would depend on the score they accumulated throughout the experiment.
+The total number of rounds was not communicated to the participants in any of the games played.
+-->
+
+<!-- After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment.  -->
+
+<!-- <!-- These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016].
+-->
+
+<!-- Finally, participants were asked a series of questions around how they played each phase.
+First, they were asked whether they thought they played differently in the second compared to the first phase of the RTG.
+Second, participants had to select whether they thought the opponents they faced were human or computer agents.
+Finally, we revealed to the participants that they faced the same computer agent throughout the RTG.
+We explained that any change in their perception of the opponent or any change in how the opponent played is due to their own change in behavior as the agent was simply reacting to their actions.
+Finally, we asked participants to reveal whether this experiment has taught them anything about how they should behave in social situations.
+-->
+
+At the start of the experiment (Figure \ref{fig:timeline}), participants provided informed consent and were instructed the study would consist of three phases in which they would face a different other player.
+Participants were told their goal was to maximise the number of points in all phases.
+They were not told the number of rounds of each phase.
+Phase one was a 15 round repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
+On each round, after being informed about the amount sent by the investor, participants were asked to provide feedback, with participants in the Intervention condition rating their feeling in terms of valence (from negative to positive) and arousal (from low to high), and participants in the Control condition rating the investment in terms of speed (from slow to fast) and magnitude (from low to high).
+These ratings were made by indicating a point on a two-dimensional grid.
+Participants then decided on how much of the tripled investment to return to the investor, before continuing to the next round.
+After completing 15 rounds of the RTG, participants rated how cooperative, selfish, trustworthy and friendly they perceived their interaction partner (all on a scale from 1 to 10).
+After phase one, participants in the intervention condition completed the intervention, and participants in the control condition solved anagrams.
+Subsequent phase two was similar to phase one, with participants being told they would face a new player.
+Phase three consisted of 7 rounds of the repeated prisoner's dilemma game (RPD), with participants informed they would face a third player.
+Participants then completed questionnaires related to mentalising abilities (RFQ8), emotion regulation (DERS), and BPD traits (PAI-BOR).<!-- MS: need to include references for these scales --> They were then asked about the strategy in the games, as well as whether they thought the other players were human or computer agents.
+They were then debriefed and thanked for their participation.
+
+## Statistical analysis
 
@@
 
-To model participants returns in the RTG across games and conditions, we fit various hidden Markov models to participants returns using the depmixS4 package [@visser_depmixs4_2021].
+To model participants' returns in the RTG across games and conditions, we fit various hidden Markov models to participants' returns using the depmixS4 package [@visser_depmixs4_2021] for R.
 The transition between latent states is assumed to depend on the investment received and a dummy variable to characterise the group that the participant belongs to.
-Details on how the models are constructed as well as the various contrast codes used for the dummy variables are found in the supplement.
+Details on how the models are constructed can be found in the supplement.
 We fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978-1] to select the best model.
 
-# Behavioral results
+# Behavioural results
 
@@
 
-Average investments and returns prior to the defection round (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
-Estimated marginal means of percentage returns from fitting the mixed effects model specified in the methods section, as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.A.
+Average investments and returns prior to the "defection round" (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
+
+<!--
+Estimated marginal means of percentage returns from fitting the mixed effects model specified in the methods section, as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.A.-->
 
@@
 
-mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), avg_ret_df, REML= TRUE)
+mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), avg_ret_df, REML= TRUE, method="KR")
 anova(mod_returns_pct)
@@
 
+<!-- MS: double check statistics; I get different df when using KR in mixed -->
+Mixed-effects analysis shows a significant main effect of Condition (intervention vs.
+control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f` <!--$F(1,315.31) = 9.52$, $p = .002$-->, with higher percentage returns in the intervention compared to the control condition.
+Importantly, we also find an interaction between Condition and Game-number (pre- vs.
+post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f` <!--$F(1,314.2) = 26.9$, $p < .001$-->.
+Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:violinPanels}.A).
+This indicates the intervention was effective in increasing cooperative behaviour.
+There was also a significant main effect of Investment, `r papaja::apa_print(mod_returns_pct)$full_result$inv_scaled` <!--$F(1,9208) = 373.6$, $p < 0.001$-->, such that higher investments were associated with higher percentage returns.
+An Investment by Condition interaction, `r papaja::apa_print(mod_returns_pct)$full_result$condition_f_inv_scaled` <!--$F(1,9207) = 45.38$, $p < .001$-->, indicates the positive effect of investment on percentage returns was greater in the control than intervention condition.
+<!-- This suggests that the higher returns we see in the intervention group are not simply due to higher investments.--> There was also an Investment by Game-number interaction, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_inv_scaled`.
+Finally, we find a three way interaction between Game-number, Condition and Investment, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f_inv_scaled`, <!--($F(1,8988)= 24.6, p < 0.001$),--> showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game-number.
+
+<!--
+group had higher percentage returns than the control group.
 We find an interaction effect between Condition (intervention vs.
@@
 
+-->
+
 ```{r, include=FALSE, cache=TRUE}
-mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| id), avg_ret_df )
+mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| id), avg_ret_df, method="KR")
 summary(mod_invs)
 anova(mod_invs)
+
+#cond_effect_inv <- pairs(emmeans::emmeans(mod_invs, c("condition.f"), by = "gameNum.f", pbkrtest.limit = 9570))
 
@@
 
-The HMM agent exhibited a differentiated behavior between games and conditions.
-When examining the HMM agent investments, we fit a linear-mixed effects model, with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number.
-We find a main effect for both Condition ($F(1,317) = 8.7, p = 0.003$) and Game-number($F(1,317) = 8.3, p = 0.004$).
-As can be seen in Figure \ref{fig:violinPanels}.D, investment was higher in the intervention compared to the control condition across games ($p=0.003$).
-Across conditions, investment was also higher in the second game compared to the first ($p=0.003$).
-
-In summary, participants in the control group sent back **lower** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$Control_Pre_post`) despite the HMM investor sending, on average higher investments.
-Those in the intervention group returned **higher** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$Intervention_Pre_post`), with the investor also sending higher investments.
-These higher returns in the intervention group compared to the control group were not purely driven by reciprocity towards higher investments since we find this interaction effect whilst controlling for investments in our model of participants returns.
-
-## Looking at pre- and post-defection trials only
+We next analysed HMM agent investments via a linear-mixed effects model with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number.
+This shows a main effect of Condition, `r papaja::apa_print(mod_invs)$full_result$condition_f`<!--$F(1,317) = 8.7$, $p = .003$-->, and Game-number, `r papaja::apa_print(mod_invs)$full_result$gameNum_f`<!--$F(1,317) = 8.3$, $p = .004$-->.
+As can be seen in Figure \ref{fig:violinPanels}.B, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
+
+Taken together, we find that participants in the control condition sent *lower* percentage returns in the second game, despite the HMM investor sending on average higher investments in the second game.
+Those in the intervention group returned *higher* percentage returns in the second game, with the investor also sending higher investments.
+These higher returns in the intervention group compared to the control group were not purely driven by reciprocity towards higher investments, since we find a Condition by Game-number interaction whilst controlling for investment in the model, and a reduced effect of Investment in the Intervention condition.
+<!-- since we find this interaction effect whilst controlling for investments in our model of participants returns.-->
+
+<!-- ## Looking at pre- and post-defection trials only -->
 
@@
 
-mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), pre_int_data, REML= TRUE)
+mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), pre_int_data, REML= TRUE, method="KR")
 anova(mod_returns_pre)
@@
 
-We restrict our analysis to the rounds prior to the pre-programmed defection (rounds 1 to 11 pre-manipulation and 1 to 12 post-manipulation) and fit the same linear mixed effects model to percentage returns as the one for the full data.
+We next analysed returns separately for rounds prior to the pre-programmed defection (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
+Applying the same mixed effects model as before to returns before defection, largely replicates results over all trials.
+Full results are provided in the supplement.
+Participants in the intervention condition increased their returns in the second game, `r papaja::apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`.
+There was no evidence that participants in the control condition changed their returns in pre-defection trials between the two phases of the RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
+
+<!--
+investments Analysis  and fit the same linear mixed effects model to percentage returns as the one for the full data.
 Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.B.
@@
 This indicates that participants were sending back higher returns in the intervention condition but not in the control condition even before the defection trial.
+-->
 
@@
 
-The interventions focused on repairing cooperation in the wake of a transgressive action by the investor.
-To assess the effect of the intervention, we can therefore consider the percentage return after the "transgression" trials.
-We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
-These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).
-
 ```{r, include =FALSE}
@@
 ```{r violinPanels, fig.cap="A: Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition.
-B: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
-C: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.
-D: Marginal means and distributions of investments over all rounds for HMM agents playing the role of the investor, by Game number and Condition", fig.align="center", fig.width=6, fig.height = 6}
-
-ggpubr::ggarrange(pctRet_all, pctRet_pre, pctRet_post, inv_all, nrow=2, ncol=2, labels = c("A", "B", "C", "D"), common.legend = TRUE, legend = "bottom")
-```
-
-Figure \ref{fig:violinPanels}.C shows the marginal means of trustee returns and their distribution by Game-number and Condition.
-There was a significant interaction between Game-number and Condition.
-Participants sent back lower returns between games in the control condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`), but no such difference in the intervention condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`).
+B: Marginal means and distributions of investments over all rounds for HMM investors, by Game number and Condition.
+C: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
+D: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.", fig.align="center", fig.width=6, fig.height = 6}
+
+ggpubr::ggarrange(pctRet_all, inv_all, pctRet_pre, pctRet_post, nrow=2, ncol=2, labels = c("A", "B", "C", "D"), common.legend = TRUE, legend = "bottom")
+```
+
+The intervention focused on repairing cooperation after a "transgressive action" by the investor.
+To assess whether the intervention succeeded, we next considered the returns by participants after the pre-programmed transgression (Figure \ref{fig:violinPanels}.D).
+<!-- We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
+These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).
+-->
+<!-- Figure \ref{fig:violinPanels}.D shows the marginal means of trustee returns and their distribution by Game-number and Condition.--> A mixed-model analysis shows similar results to those of the model applied to all returns (see SI for full results).
+The was again a significant interaction between Condition and Game-number and Condition.
+Participants in the control condition decreased their post-transgression returns from the first to the second phase of the RTG, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
+There was no change for participants in the intervention condition, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`.
+So, whilst the intervention did not appear to move participants to increase their returns after a transgression by the investor, it may have countered the decrease in returns showed by participants in the control condition.
 
@@
 datCoax$roundGroup <- ifelse(datCoax$roundNum <= 10, "Rounds 1-10", "Rounds 11-15")
+
+# p <- datCoax %>%
+#   ggplot(aes(x=roundNum)) + stat_summary(fun = "mean", geom = "line", aes(y=emo_scaled_x, color = "Valence")) + stat_summary(fun = "mean", geom = "line", aes(y=emo_scaled_y, color = "Arousal")) + stat_summary(fun = "mean", geom = "line", aes(y=inv_scaled, color = "Investment")) + facet_wrap(~gameNum_f, scales = "free_x")
 
@@
 
+<!-- Figure \ref{fig:emoPlotCoax} shows the average, across participants *in the intervention condition*, of emotion valence, the degree of arousal as well as the HMM's investment z-scores.
+We find a significant positive correlation between the two emotion axis ($r=0.52, p < 0.001$) as well as between valence and Investment ($r=0.47, p < 0.001$), and arousal and Investment ($r=0.50, p < 0.001$).
+-->
+
+```{r, include=FALSE}
+
+mod_emo_x <- mixed( emo_scaled_x ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), data=datCoax, method="KR")
+summary(mod_emo_x)
+anova(mod_emo_x)
+
+modVal <- emmeans::emmeans(mod_emo_x, ~gameNum.f)
+pairs(modVal)
+
+mod_emo_y <- mixed( emo_scaled_y ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
+summary(mod_emo_y)
+anova(mod_emo_y)
+
+modArousal <- emmeans::emmeans(mod_emo_y, ~gameNum.f)
+pairs(modArousal)
+
+# afex_plot(mod_emo_x, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
+#             data_geom = geom_violin, 
+#             data_arg = list(width = 0.5))
+#
+
+# library(GGally)
+# ggpairs(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,inv_scaled))
+
+cor(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,investment))
+cor.test(datCoax$emo_scaled_x, datCoax$emo_scaled_y)
+```
+
+Participants in the intervention condition rated their emotion on valence (negative to positive) and arousal (low to high) after each investment.
+To assess the impact of the intervention on these emotional reactions, we used linear mixed-effects models (one for valence, and one for arousal) with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
+This showed that higher investments were associated with more positive emotions, `r papaja::apa_print(mod_emo_x)$full_result$scaleinvestment`, and higher arousal, `r papaja::apa_print(mod_emo_y)$full_result$scaleinvestment`.
+<!-- ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$)--> In addition, the positiveness of emotion declined between the two games, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f`, as did arousal, `r papaja::apa_print(mod_emo_y)$full_result$gameNum_f`.
+There was no indication that the effect of the investment on either aspect of emotion was affected by the intervention, as there was no interaction between Investment and Game-number on valence, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f_scaleinvestment`, or arousal, `papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment`.
+This indicates that participants in the intervention condition returned higher amounts post-intervention despite their emotional reaction to investments remaining largely the same.
+
+<!--
 A key aspect of effective interventions is the emotional change.
@@
 This means that participants in the intervention condition returned higher amounts post-intervention despite the emotional reaction to the lower investment being largely unchanged.
-
-<!-- Figure \ref{fig:emoPlotCoax} shows the average, across participants *in the intervention condition*, of emotion valence, the degree of arousal as well as the HMM's investment z-scores.
-We find a significant positive correlation between the two emotion axis ($r=0.52, p < 0.001$) as well as between valence and Investment ($r=0.47, p < 0.001$), and arousal and Investment ($r=0.50, p < 0.001$).
--->
-
-```{r, include=FALSE}
-
-mod_emo_x <- mixed( emo_scaled_x ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
-summary(mod_emo_x)
-anova(mod_emo_x)
-
-modVal <- emmeans::emmeans(mod_emo_x, ~gameNum.f)
-pairs(modVal)
-
-mod_emo_y <- mixed( emo_scaled_y ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
-summary(mod_emo_y)
-anova(mod_emo_y)
-
-modArousal <- emmeans::emmeans(mod_emo_y, ~gameNum.f)
-pairs(modArousal)
-
-# afex_plot(mod_emo_x, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
-#             data_geom = geom_violin, 
-#             data_arg = list(width = 0.5))
-#
-
-# library(GGally)
-# ggpairs(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,inv_scaled))
-
-cor(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,investment))
-cor.test(datCoax$emo_scaled_x, datCoax$emo_scaled_y)
-```
+-->
 
@@
 
-## Player rating
+## Evaluation of the investor
 
@@
 
+Participants rated the HMM investor in the second game as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result`) and more selfish (`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result`), than the HMM investor in the first game.
+Participants in the intervention condition rated players higher than those in the control condition on cooperativeness (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("condition.f"))))$full_result`) and lower on selfishness (`r apa_print(pairs(emmeans::emmeans(self_mod, c("condition.f"))))$full_result`).
+There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
+
+<!--
 Participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention).
@@
 There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
+-->
 
@@
 
-## Transfer to the Prisoner's Dilemma Game
+## Transfer to the repeated Prisoner's Dilemma game
 
@@
 
-We next asked whether the coaxing behavior induced by the intervention generalized to the RPD.
-Across participants, we look at the rate at which the cooperative action was chosen in each round.
-Using a logistic mixed-effects model with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, we found no evidence for a different cooperation rate in the intervention condition compared to the control condition.
-We also found no difference in cooperation rates post defection trial between conditions.
+We next asked whether the intervention had any discernible effect on participants' behaviour in a different, repeated Prisoner's Dilemma game.
+Predicting the probability of a cooperative action with a logistic mixed-effects regression model, with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, showed a decline in cooperation after defection by the other player, `r papaja::apa_print(ipd_mod)$full_result$phase`, but no evidence for a different cooperation rate in the intervention condition compared to the control condition, `r `papaja::apa_print(ipd_mod)$full_result$condition_f`, or a different response to defection between the conditions, `r papaja::apa_print(ipd_mod)$full_result$condition_f_phase`.
+<!-- We also found no difference in cooperation rates post defection trial between conditions.-->
 
 ## Self report and debrief questionnaires
+
+<!-- MS: This section doesn't say much.
+It could be reasonable to include questionnaire scores in the main analyses throughout (e.g.
+does BPD trait have an effect or moderate any other effects?
+IF not, a statement somewhere that the scales didn't have an effect, and showing results of accompanying analyses in SI would be fine -->
 

### 2023-06-30 article.Rmd
Final edits

@@
   - Ismail Guennouni
-  - Maarten Speekenbrink
   - Quentin Huys
   - Samuel Dupret
+  - Maarten Speekenbrink
 
@@
 
-Average investments and returns prior to the "defection round" (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
-
 <!--
@@
 ```
-
 ```{r, include=FALSE, cache=TRUE}
@@
 ```
-
 ```{r, include=FALSE}
@@
 <!-- MS: double check statistics; I get different df when using KR in mixed -->
-Mixed-effects analysis shows a significant main effect of Condition (intervention vs.
-control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f` <!--$F(1,315.31) = 9.52$, $p = .002$-->, with higher percentage returns in the intervention compared to the control condition.
-Importantly, we also find an interaction between Condition and Game-number (pre- vs.
-post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f` <!--$F(1,314.2) = 26.9$, $p < .001$-->.
+
+Average investments and returns prior to the "defection round" (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
+Mixed-effects analysis on the returns shows a significant main effect of Condition (intervention vs.
+control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f`<!--$F(1,315.31) = 9.52$, $p = .002$-->, with higher percentage returns in the intervention compared to the control condition.
+Importantly, we also find an interaction between Condition and Game (RTG pre- vs.
+post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f`<!--$F(1,314.2) = 26.9$, $p < .001$-->.
 Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:violinPanels}.A).
 This indicates the intervention was effective in increasing cooperative behaviour.
-There was also a significant main effect of Investment, `r papaja::apa_print(mod_returns_pct)$full_result$inv_scaled` <!--$F(1,9208) = 373.6$, $p < 0.001$-->, such that higher investments were associated with higher percentage returns.
-An Investment by Condition interaction, `r papaja::apa_print(mod_returns_pct)$full_result$condition_f_inv_scaled` <!--$F(1,9207) = 45.38$, $p < .001$-->, indicates the positive effect of investment on percentage returns was greater in the control than intervention condition.
-<!-- This suggests that the higher returns we see in the intervention group are not simply due to higher investments.--> There was also an Investment by Game-number interaction, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_inv_scaled`.
-Finally, we find a three way interaction between Game-number, Condition and Investment, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f_inv_scaled`, <!--($F(1,8988)= 24.6, p < 0.001$),--> showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game-number.
+There was also a significant main effect of Investment, `r papaja::apa_print(mod_returns_pct)$full_result$inv_scaled`<!--$F(1,9208) = 373.6$, $p < 0.001$-->, such that higher investments were associated with higher percentage returns.
+An Investment by Condition interaction, `r papaja::apa_print(mod_returns_pct)$full_result$condition_f_inv_scaled`<!--$F(1,9207) = 45.38$, $p < .001$-->, indicates the positive effect of investment on percentage returns was greater in the control than intervention condition.
+<!-- This suggests that the higher returns we see in the intervention group are not simply due to higher investments.--> There was also an Investment by Game interaction, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_inv_scaled`.
+Finally, we find a three way interaction between Game, Condition and Investment, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f_inv_scaled`<!--($F(1,8988)= 24.6, p < 0.001$),-->, showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game (pre- vs post intervention).
 
@@
 
-We next analysed HMM agent investments via a linear-mixed effects model with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number.
-This shows a main effect of Condition, `r papaja::apa_print(mod_invs)$full_result$condition_f`<!--$F(1,317) = 8.7$, $p = .003$-->, and Game-number, `r papaja::apa_print(mod_invs)$full_result$gameNum_f`<!--$F(1,317) = 8.3$, $p = .004$-->.
+We next analysed HMM agent investments with a linear-mixed effects model with fixed effects for Condition (intervention vs control), Game (pre vs post intervention), as well as interaction between Condition and Game, and participant-wise random intercepts and random slopes for Game.
+This shows a main effect of Condition, `r papaja::apa_print(mod_invs)$full_result$condition_f`<!--$F(1,317) = 8.7$, $p = .003$-->, and Game, `r papaja::apa_print(mod_invs)$full_result$gameNum_f`<!--$F(1,317) = 8.3$, $p = .004$-->.
 As can be seen in Figure \ref{fig:violinPanels}.B, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
 
-Taken together, we find that participants in the control condition sent *lower* percentage returns in the second game, despite the HMM investor sending on average higher investments in the second game.
-Those in the intervention group returned *higher* percentage returns in the second game, with the investor also sending higher investments.
-These higher returns in the intervention group compared to the control group were not purely driven by reciprocity towards higher investments, since we find a Condition by Game-number interaction whilst controlling for investment in the model, and a reduced effect of Investment in the Intervention condition.
+<!-- Taken together, we find that participants in the control condition sent lower percentage returns in the second game, despite the HMM investor sending on average higher investments in the second game.
+Those in the intervention group returned higher percentage returns in the second game, with the investor also sending higher investments.
+These higher returns in the intervention compared to the control condition were not purely driven by reciprocity towards higher investments, since we find a Condition by Game interaction whilst controlling for investment in the model, and a reduced effect of investment in the intervention condition.
 <!-- since we find this interaction effect whilst controlling for investments in our model of participants returns.-->
@@
 
-We next analysed returns separately for rounds prior to the pre-programmed defection (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
-Applying the same mixed effects model as before to returns before defection, largely replicates results over all trials.
-Full results are provided in the supplement.
+We next analysed returns separately for rounds prior to the pre-programmed transgression (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
+Applying the same mixed effects model as before to returns before the transgression largely replicates the results over all trials.
 Participants in the intervention condition increased their returns in the second game, `r papaja::apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`.
-There was no evidence that participants in the control condition changed their returns in pre-defection trials between the two phases of the RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
+There was no evidence that participants in the control condition changed their returns in pre-transgression trials between the first and second RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
+Full results are provided in the SI.
 
@@
 
-The intervention focused on repairing cooperation after a "transgressive action" by the investor.
-To assess whether the intervention succeeded, we next considered the returns by participants after the pre-programmed transgression (Figure \ref{fig:violinPanels}.D).
-<!-- We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
+<!-- The intervention focused on repairing cooperation after a "transgressive action" by the investor.
+To assess whether the intervention succeeded, we next considered the returns by participants after the pre-programmed transgression (Figure \ref{fig:violinPanels}.D).--> <!-- We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
 These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).
 -->
-<!-- Figure \ref{fig:violinPanels}.D shows the marginal means of trustee returns and their distribution by Game-number and Condition.--> A mixed-model analysis shows similar results to those of the model applied to all returns (see SI for full results).
-The was again a significant interaction between Condition and Game-number and Condition.
-Participants in the control condition decreased their post-transgression returns from the first to the second phase of the RTG, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
-There was no change for participants in the intervention condition, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`.
-So, whilst the intervention did not appear to move participants to increase their returns after a transgression by the investor, it may have countered the decrease in returns showed by participants in the control condition.
+<!-- Figure \ref{fig:violinPanels}.D shows the marginal means of trustee returns and their distribution by Game-number and Condition.--> Applying the same model to the returns after the transgression (see SI for full results), we again find <!-- A mixed-model analysis shows similar results to those of the model applied to all returns (see SI for full results).
+There was again --> a significant interaction between Condition and Game.
+Participants in the control condition decreased their post-transgression returns from the first to the second RTG, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
+There was no significant change for participants in the intervention condition, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`.
+<!-- So, whilst the intervention did not appear to move participants to increase their returns after a transgression by the investor, it may have countered the decrease in returns showed by participants in the control condition.
+-->
+
+Taken together, we find that participants in the control condition sent lower percentage returns in the second game, despite the HMM investor sending on average higher investments in the second game.
+Those in the intervention group returned higher percentage returns in the second game, with the investor also sending higher investments.
+These higher returns in the intervention compared to the control condition were not purely driven by reciprocity towards higher investments, since we found a Condition by Game interaction whilst controlling for investment in the model, and a reduced effect of investment in the intervention condition.
+Whilst the intervention increased participants returns overall, it did not appear to increase participants' returns after the transgression by the other player.
+However, it may have countered the tendency to lower returns after the transgression in the second game compared to the first game, which was shown by participants in the control condition.
 
@@
 Participants in the intervention condition rated their emotion on valence (negative to positive) and arousal (low to high) after each investment.
-To assess the impact of the intervention on these emotional reactions, we used linear mixed-effects models (one for valence, and one for arousal) with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
+To assess the impact of the intervention on these emotional reactions, we used linear mixed-effects models (one for valence, and one for arousal) with fixed effects for Game (pre vs post intervention) and Investment, as well as interaction between Investment and Game, with participant-wide random intercepts and random slopes for Game.
 This showed that higher investments were associated with more positive emotions, `r papaja::apa_print(mod_emo_x)$full_result$scaleinvestment`, and higher arousal, `r papaja::apa_print(mod_emo_y)$full_result$scaleinvestment`.
 <!-- ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$)--> In addition, the positiveness of emotion declined between the two games, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f`, as did arousal, `r papaja::apa_print(mod_emo_y)$full_result$gameNum_f`.
-There was no indication that the effect of the investment on either aspect of emotion was affected by the intervention, as there was no interaction between Investment and Game-number on valence, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f_scaleinvestment`, or arousal, `papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment`.
-This indicates that participants in the intervention condition returned higher amounts post-intervention despite their emotional reaction to investments remaining largely the same.
+There was no indication that the effect of the investment on either aspect of emotion was affected by the intervention, as there was no interaction between Investment and Game on valence, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f_scaleinvestment`, or arousal, `r papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment`.
+This indicates that participants in the intervention condition returned higher amounts post-intervention, despite their emotional reaction to investments remaining largely the same.
 
@@
 Participants in the intervention condition rated players higher than those in the control condition on cooperativeness (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("condition.f"))))$full_result`) and lower on selfishness (`r apa_print(pairs(emmeans::emmeans(self_mod, c("condition.f"))))$full_result`).
-There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
+There was no evidence for an interaction effect between Condition and Game on any of the attributes.
 
@@
 We next asked whether the intervention had any discernible effect on participants' behaviour in a different, repeated Prisoner's Dilemma game.
-Predicting the probability of a cooperative action with a logistic mixed-effects regression model, with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, showed a decline in cooperation after defection by the other player, `r papaja::apa_print(ipd_mod)$full_result$phase`, but no evidence for a different cooperation rate in the intervention condition compared to the control condition, `r `papaja::apa_print(ipd_mod)$full_result$condition_f`, or a different response to defection between the conditions, `r papaja::apa_print(ipd_mod)$full_result$condition_f_phase`.
+Predicting the probability of a cooperative action with a logistic mixed-effects regression model, with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, showed a decline in cooperation after defection by the other player, `r papaja::apa_print(ipd_mod)$full_result$phase`, but no evidence for a different cooperation rate in the intervention condition compared to the control condition, `r `r papaja::apa_print(ipd_mod)$full_result$condition_f`, or a different response to defection between the conditions, `r papaja::apa_print(ipd_mod)$full_result$condition_f_phase`.
+As such, there is no evidence that the intervention affected behaviour in this game.
 <!-- We also found no difference in cooperation rates post defection trial between conditions.-->
@@
 When asked whether they thought their opponent was Human or not, $40$% of participants thought they were either facing a human or were not sure of the nature of the opponent.
-Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behavior.
+Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behaviour.
 
@@
 
-We analyzed participants' behavior differences in the intervention versus control conditions using hidden Markov models (HMM).
-Five models were used: "HMM-inv" assumed transition states depended solely on investment, ignoring game number and condition.
-"HMM-prepost" contrasted Pre and Post Intervention.
-"HMM-coax" contrasted post-intervention with pre-intervention and both control conditions.
-"HMM-ctrl" contrasted post-control with pre-control and both intervention conditions.
-"HMM-full" grouped pre-control and pre-intervention as one, with separate groups for post-control and post-intervention.
-Models were fitted using 2 to 7 states, selecting the lowest BIC.
-Generally, 5-7 state models best explained the data.
-A likelihood ratio test compared the models' goodness of fit, contrasting the complex HMM-full model with nested models equating behavior in certain stages and conditions.
+We used hidden Markov models (HMMs) to further assess differences between the intervention and control condition in participants' reactions to the investor.
+As in the models for the investor, these HMMs assume behaviour is governed by latent states, with participants' switches between states now dependent on the investments made.
+We also allowed for differences between games and conditions in how investments govern state transitions.
+More in particular, we fitted five main models which all regressed state transition probabilities onto investments, as well as on additional contrast-coded predictors for condition and/or game number.
+In the most complex model (HMM-full), the transition probabilities were allowed to differ between all four combinations of game number and condition.
+The HMM-coax model allowed differences between post-intervention and the other three conditions (pre-intervention, pre-control, post-control) assuming these latter were the same.
+Similarly, the HMM-ctrl model allowed differences between post-control and the other three conditions.
+The HMM-prepost model allowed differences between the first and second RGT.
+Finally, the HMM-inv model did not allow transition probabilities to differ between conditions or game numbers, modelling them only as a function of investment.
+As the number of hidden states was unknown, for each model we estimated versions with 2 to 7 states, and used the BIC to select the best fitting model.
+Generally, best fitting models had between 5 to 7 hidden states.
 
@@
 
-```
-
-In order to compare the goodness of fit of the various models, we test the relative likelihood of models using a likelihood ratio test.
-This procedure is useful to compare the most complex model (HMM-full, which allows for differences between pre-intervention and the two conditions post-intervention) to nested models which equate behaviour in some if the stages and conditions.
+llratio(newFull[[6]],fittedCtrl[[6]])
+llratio(newFull[[6]],fittedCoax[[6]])
+llratio(newFull[[6]],fittedPrePost[[6]])
+```
+
+<!-- MS: There seems to be an issue with the likelihoods of the models.
+For example, for 6 states models, the likelihood of the Ctrl and Coax model are higher than for the Full model, but this is theoretically not possible as additional parameters can only increase the likelihood!
+-->
+
+Focussing on models with 5 latent states (which is the optimal number for the HMM-full model), likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCtrl[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCoax[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedPrePost[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
+This is consistent with state transitions differing both due to game number and condition.
 
@@
 
-Using likelihood ratio tests, we find that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCtrl[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCoax[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedPrePost[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
+<!-- Using likelihood ratio tests, we find that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCtrl[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCoax[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedPrePost[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
 This is consistent with a differentiated behavior of the trustees between all three groups: the post-intervention group, the post-control group and the pre-manipulation group.
+-->
 
@@
 
-Using the HMM-full model, we can retrieve participants' return distributions based on their latent states (Figures \ref{fig:postStatesBestMod}.A) and transition probabilities between these states (Figure \ref{fig:plotTransitionsDiscGaus}).
+<!-- MS: I think Figure 6 can be moved to the supplement and perhaps Figure 6.A too. -->
+
+<!-- Using the HMM-full model, we can retrieve participants' return distributions based on their latent states (Figures \ref{fig:postStatesBestMod}.A) and transition probabilities between these states (Figure \ref{fig:plotTransitionsDiscGaus}).
 The states are ranked by mean return, with State 1 having the lowest mean return and State 5 the highest.
@@
 Figure \ref{fig:plotTransitionsDiscGaus} suggests that the intervention group is more forgiving of low investments, as they are less likely to shift to an anti-social state when faced with defection compared to the control group.
+-->
 
@@
 
-To quantitatively explore the differences in transition probabilities between the control and intervention conditions, we can estimate from the model, using local decoding methods from the depmixS4 package [@visser_depmixs4_2021], the most likely posterior state of the trustee participants by round given the actions they have taken.
+Focusing on the best-fitting 5-state HMM-full model, we used a local decoding procedure to assign observations (participants' returns on trials) to latent states.
+The states are ordered by expected return, with state 1 having the lowest mean return and state 5 the highest.
 Figure \ref{fig:postStatesBestMod}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
@@
 For the post-defection trial after the intervention (round 14), state 1 was the most likely state for only $22$% of participants in the intervention condition compared to $43$% in the control condition ($\chi^2(1) = 14.70, p < 0.001$).
+Whilst the posterior states indicate that the intervention was effective, a non-negligible proportion of participants in the intervention condition did not exhibit the coaxing behaviour promoted by the intervention.
+Directly following the low investment in round 13, $30.2$% of participants in the intervention condition were assigned to state 1 with the lowest average returns.
+There is thus clear heterogeneity in the effectiveness of the intervention.
+
+<!-- To quantitatively explore the differences in transition probabilities between the control and intervention conditions, we can estimate from the model, using local decoding methods from the depmixS4 package [@visser_depmixs4_2021], the most likely posterior state of the trustee participants by round given the actions they have taken.
+Figure \ref{fig:postStatesBestMod}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
+For instance, in round 5, state 1 was the most likely posterior state for only $7$% of participants in the intervention condition compared to $24$% in the control condition ($\chi^2(1) = 8.26, p < 0.01$).
+For the post-defection trial after the intervention (round 14), state 1 was the most likely state for only $22$% of participants in the intervention condition compared to $43$% in the control condition ($\chi^2(1) = 14.70, p < 0.001$).
 
@@
 These differences can be seen as an indication of important heterogeneity in the effectiveness of the intervention.
+-->
 
@@
 
-In this experiment, we made human participants face artificial computer agents endowed with the ability to transition between latent states and react to the participants' returns.
-The number of states, the policy in each state as well as the way these agents transitioned between states was based on estimating a hidden Markov model to behaviour from real human participants.
-On average, we saw the emergence of cooperative behavior with investment and returns in line with what is reported in human dyadic interaction in the repeated trust game [@charness_investment_2008; @fiedler_social_2011].
-The emergence of cooperative behavior and participant's uncertainty about whether they were facing human or artificial opponents, point to the potential of these agents to mimic human behavior in economic games whilst offering a higher degree of experimental control.
-
-The intervention's aim was to articulate the effect of acting on impulse in case of a transgressive action from the investor in the form of a one-off low investment.
-When the agent defected as programmed, yielding a situation similar to the one presented in the intervention, the intervention led to higher percentage returns post defection compared to the control group, as intended.
-Participants emotional reactions to the received investment, we similar pre and post-intervention, so the higher returns were produced despite participants having the same emotional reaction.
-This might indicate that the intervention achieved its goal of encouraging participants to respond in a non-impulsive, considered way, overriding the emotional urge to retaliate.
-
-What was also notable was that the intervention led to generally higher returns post-intervention, even before the defection trial.
-This could be for a number of reasons.
-One possibility is that participants simply learned that by returning more, the investment on the next trial would be higher.
-However, this explanation is unlikely, as we did not see a similar increase in percentage returns in the control condition.
-Another possibility is that, on average, the second player they faced invested more, which prompted positive reciprocity in the human trustees.
-As all players were programmed in the same way, any difference would be due to participant's actions.
-Further, participants rated both players similarly on relevant attributes of cooperativeness and trust.
-The higher returns are thus unlikely to be driven by different beliefs about the investor.
-A likely explanation for overall higher trustworthiness, as measured by higher percentage return post investment, is that participants, on average, interpreted the intervention message as an argument for more pro-social behavior, irrespective of the investor's actions.
-
-It is also noteworthy that there were important individual differences in the percentage return changes post vs.
-pre intervention, which can be seen as a proxy for the intervention effectiveness.
-Some participants might not have been convinced by the intervention's message and decided to reduce their returns both pre and post defection in the second trust game, while others increased their returns in both phases.
-This raises important questions for the measurement of intervention effectiveness.
-Recent work has shed light on the important heterogeneity inherent in how disorders are categorised: This heterogeneity arises from the view that mental health problems should be viewed as complex systems, or interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017].
-This view was used to justify computational psychiatry's difficulty in establishing differential and reliable predictors of likely treatment responses [@hitchcock_computational_2022].
-But if a healthy group's reaction to a relatively explicit intervention is itself heterogeneous as we have shown in this experiment, then the issue of variable treatment responses might the result of the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself.
+In this experiment, human participants took the role of trustee in a repeated trust game (RTG) where they faced artificial computer agents who's behaviour was partly determined by participants' returns.
+The behaviour of the artificial investors was determined by a 3-state hidden Markov model (HMM), which was estimated from the behaviour of humans in the RTG in prior research.
+Overall, investments and returns by the artificial and human agents replicated that of human dyads in prior research using the RTG [@charness_investment_2008; @fiedler_social_2011].
+This, together with participants' reported uncertainty about whether they faced a human or artificial investor, shows the potential of using HMM-based artificial agents to mimic human behaviour in economic games, whilst offering a higher degree of experimental control.
+
+The aim of the cognitive intervention was to articulate the potential unwanted effects of acting on impulse after a transgressive action from the investor in the form of a one-off low investment.
+After the intervention, participants send back higher returns compared to before the intervention, and did not decrease their returns after a transgressive action like participants in the control condition did.
+The overall higher returns after the intervention occurred despite participants' emotional reactions to the investments remaining largely the same as before the intervention.
+This indicates the intervention achieved its goal of encouraging participants to respond in a non-impulsive and considered manner, overriding an emotional urge to retaliate.
+
+That participants generally send higher returns to the investor after the intervention is unlikely due to a  general learning effect unrelated to the intervention, as participants in the control condition did not increase their returns.
+Also, as participants in the intervention and control condition faced the same HMM investor, the higher post-intervention returns are not solely due to a difference in investor behaviour.
+As the investor reacts to participants' returns, those who return more will generally see higher investments.
+But this is driven by the magnitude of their returns, not by a change in the strategy of the investor.
+Finally, as participants rated the first and second HMM agent similarly on attributes such as cooperativeness and trust, the increased returns are unlikely to be the result of a more favourable evaluation of the investor.
+Rather, we find it most likely that the increased returns are due to participants inferring from the intervention that pro-social and trustworthy behaviour may generally motivate the investor to send high investments, which can provide more beneficial outcomes to them in the long run.
+
+The effect of the intervention was not transferred to the Repeated Prisoner's Dilemma (RPD) game.
+There was no difference between the intervention and control condition in the rate of cooperation, whether before or after a preprogrammed defection by the artificial agent.
+As the prisoner's dilemma is a popular economic game, it is possible that participants had a strong prior commitment towards the strategy they would adopt, which was not overridden by the intervention.
+The RPD also involves much coarser actions (cooperate vs defect) than the finer-grained returns in the RTG.
+This would make it more difficult to observe more subtle effects of the intervention.
+As such, the RPD might not be the best choice for any knowledge transfer.
+In any case, we can not rule out that the effects of the brief cognitive intervention, which explicitly focused on the RTG, are confined to the RTG.
+Future research will need to assess whether transfer to other games is possible.
+<!-- For those that took on the intervention message and showed coaxing behavior in the second trust game, the fact that the investor still defected in the final rounds might have reinforced the idea that not reciprocating negative behavior is a losing strategy after all.-->
+
+There were clear individual differences in the change of returns between the pre- and post-intervention RTG, which can be seen as a proxy for the effectiveness of the intervention.
+Some participants may not have been convinced that coaxing via high returns was a good way to establish cooperation and decided to reduce their returns in the second trust game.
+Their impulse to “punish” the other player for a transgression may have been too strong to be overridden by the intervention.
+This was also evident from the participants' replies to a question about whether they would change their behaviour, just after receiving the intervention.
+Other participants responded to the intervention and increased their returns.
+<!-- This raises important questions for the measurement of intervention effectiveness.--> Heterogeneity in response to treatment is common in psychiatry and related fields.
+Such heterogeneity may reflect the complex nature of mental health problems, which may be best viewed as complex systems involving interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017].
+This view was used to justify computational psychiatry's difficulty in establishing differential and reliable predictors of likely treatment response [@hitchcock_computational_2022].
+<!-- MS: how do we know participants are healthy?
+-->As we found heterogeneity in reactions to a relatively explicit intervention by relatively healthy participants from the general population.
+is itself heterogeneous as we have shown in this experiment, then the issue of variable treatment responses might the result of the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself.
 As such, a rigorous exploration of the determinants of inter-individual differences to an intervention in the general patient population is required.
-
-In our case, judging by the inter-individual heterogeneity in responses, some people may not have been convinced that a coaxing behavior was a good way to establish long term cooperative outcomes, and their need to “punish” the other player for their low investment may have been more pertinent than what we suggested.
-This was also evident from the participants' replies to a question about whether they would change their behavior, just after seeing the intervention manipulation.
+<!-- In our case, judging by the inter-individual heterogeneity in responses, some people may not have been convinced that coaxing via high returns was a good way to re-establish cooperation after a transgression.
+Their impulse to “punish” the other player for their transgression may have been too strong to be overridden by the intervention.
+This was also evident from the participants' replies to a question about whether they would change their behaviour, just after seeing the intervention manipulation.
 An important avenue is to explore the role of emotion in decision making in such situations.
 We could aim to measure emotional reactions more accurately and explore whether specific emotions mediate the relationship between the investment received and the decision of what proportion to return.
-Measuring the emotions using the two axes of valence and arousal could be improved: Results indicate that these concepts may not have been well understood by participants since we would not expect to see low arousal after the pre-programmed defection of the investor.
-
-The effect of this short intervention was not transferred to the Repeated Prisoner's Dilemma game.
-In this game, the rate at which the cooperative option was chosen was not significantly different between the control and intervention groups, both pre and post defection.
-Since the prisoner's dilemma is a very popular economic game, it is possible that participants had strong prior preferences towards which strategy they would adopt, irrespective of whether or not they received the intervention.
-As such, this paradigm might not be the best test case for knowledge transfer.
-For those that took on the intervention message and showed coaxing behavior in the second trust game, the fact that the investor still defected in the final rounds might have reinforced the idea that not reciprocating negative behavior is a losing strategy after all.
-
-Overall, it is remarkable that such a short intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments can lead to such differentiated behavior.
-In future studies, we aim to explore the effects of different cognitive interventions and improve the experimental design in multiple ways.
-First, the intervention could benefit from being more interactive medium, with visual inputs such as cartoons and videos, rather than pure text which can be cumbersome to read and lead to lower engagement.
+Measuring the emotions using the two axes of valence and arousal could be improved: Results indicate that these concepts may not have been well understood by participants since we would not expect to see low arousal after the pre-programmed defection of the investor.-->
+Overall, we are encouraged that our brief cognitive intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments, can lead to clearly differentiated behaviour.
+In future studies, we aim to explore the effects of improved cognitive interventions to enhance cooperative behaviour.
+We may enhance engagement by making the intervention more interactive and visually appealing, rather than the "dry" textual format used in the experiment.
+It would also be of interest to test such interventions with who suffer from an inability or unwillingness to repair relationships after an accidental breakdown of trust, such as people with Borderline Personality Disorder.
+The relative ease by which online interventions can be assigned, and the opportunity for people to test the effect of their behaviour with artificial, but human-like agents, may pave the way for efficient, low-cost, effective treatment programmes which may help a wide-variety of people overcome detrimental actions in social situations.
+
+<!--
 Second, we selected trustees from the general population, which might not suffer from the inability or unwillingness to repair relationships due to accidental breakdown of trust that characterises some mental health disorders such as BPD.
@@
 However, being able to compare the differential impact of the intervention on the emotional interpretation of the opponent action between an intervention and control conditions could lead to insights on the mechanism through which the intervention affects the emotional reaction to the opponent's actions.
+-->
 
@@
 
-We explored the effect of a short cognitive intervention on the behavior of human trustees facing adaptive artificial agents endowed with multiple latent behavioral states.
+<!-- MS: Don't think we need a conclusion? -->
+
+We explored the effect of a brief cognitive intervention on the behaviour of human trustees facing adaptive artificial investors designed to replicate the behaviour of human investors in the repeated trust game.
 Each state defines different levels of a cooperative response with the agent able to transition between these states based on the behavior of the human opponent.
 Feedback from participants indicated that these agents were sometimes perceived as humans.
-Their strategy led to emergent cooperative behavior when playing the repeated trust game with human players.
+Their strategy led to emergent cooperative behaviour when playing the repeated trust game with human players.
 The intervention, promoting a less impulsive reaction to transgressive actions, led to coaxing behavior and less negative reciprocity when the investor sent a very low investment.

### 2023-06-30 article.Rmd
Final edits

@@
 
-There were clear individual differences in the change of returns between the pre- and post-intervention RTG, which can be seen as a proxy for the effectiveness of the intervention.
+Analysing participants' behaviour with hidden Markov models, we found clear individual differences in how returns changed between the pre- and post-intervention RTG, which can be seen as a proxy for the effectiveness of the intervention.
 Some participants may not have been convinced that coaxing via high returns was a good way to establish cooperation and decided to reduce their returns in the second trust game.

### 2023-07-13 article.Rmd
plot improvements

--- 2023-06-13 article.Rmd
@@
 require(knitr)
-#require(citr)
+require(citr)
 require(bookdown)
@@
 
-Determining the other's goals, intentions, and decision-making process is fundamental to successful social interaction.
-This inference is however fraught with uncertainty, as we cannot directly observe these features, and may need extensive prior knowledge of the person.
-Absent a history of interaction, one may decide to trust the other's goals and intentions are aligned with one's own.
+At the core of social interaction is figuring out the goals, intentions, and decision-making process of the interaction partner.
+This inference is however fraught with uncertainty, as we cannot reasonably observe these features without prior knowledge of the person.
+Absent a history of interaction, one needs to decide whether to take the risk of trusting others.
 The challenge of trust is that it is by construction a risky endeavour.
-If we deem a person trustworthy, we might take the risk of investing in the relationship, hoping for a collaborative outcome.
-If this trust is misplaced, it can come at a high cost.
+For example, if we deem a person trustworthy, we might decide to take the risk of investing in the relationship hoping for a collaborative outcome.
+If we misplace our trust, this can come at a high cost to us.
 Not trusting others is also risky since opportunities for cooperation may be foregone.
@@
 Evidence from the literature emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016 ; @meng_multilevel_2014].
-It affects the health status of individuals by reinforcing social support networks, maintaining community norms and facilitating collective action.
+It affects the health status of individuals through reinforcing social support networks, maintaining community norms and facilitating collective action.
 Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders.
@@
 A well-established paradigm in the study of trust is the repeated trust game [@joyce_trust_1995].
-In this game, the "investor" decides how much of an endowment to send to the other player (the "trustee").
-The amount that is sent is tripled and the trustee decides, in return, how much of the tripled amount to send back to the investor.
-To encourage the emergence and maintenance of trust in this setting, some studies focused on modifying the game mechanism, for example by introducing a third-party who monitors the actions of the other players [@charness_investment_2008; @fiedler_effect_2017].
+To encourage the emergence and maintenance of trust in this setting, some studies focused on modifying the game mechanism [@charness_investment_2008; @fiedler_effect_2017].
 Others chose to intervene directly on the participants.
@@
 
-Whilst these interventions show that it is possible to improve cooperative outcomes at the start of the game, they do not address how to repair a breakdown of trust that might occur due to intentional or accidental non-cooperative actions by the players.
-Cooperative play in the repeated trust game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor or a return of the trustee below the investment sent [@bendor_when_1991].
-Such ruptures of cooperation appear frequently when the trustee suffers from social disorders such as Borderline Personality Disorder [BPD; @lieb_borderline_2004].
-In theses situations, BPD trustees fail to engage in trust repairing behaviours such as coaxing the investor by signalling trustworthiness via sending high returns.
-This failure may be linked to the misperception that their low returns in the game are not violating social norms [@king-casas_rupture_2008].
-
-In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of social dysfunction in BPD patients.
-Whilst there is no proven pharmacological therapy for BPD, psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
-However, response to these treatments is highly variable, and determining which interventions are effective for particular patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
-One promising approach is the study of how specific components of psychotherapeutic treatment affect quantitative markers of behaviour such as those inferred through computational models [@huys_computational_2016; @reiter_neuro-cognitive_2021].
-Combining the use of specific cognitive probes inspired by therapeutic interventions and computational models of behaviour may allow us to uncover the cognitive mechanisms targeted by common forms of psychotherapy.
-In turn, this may provide the basis for choosing effective psychotherapeutic interventions for given individuals.
-
-In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a one-off low investment sent by an computerised investor.
+Whilst these interventions show that it is possible to improve cooperative outcomes at the start of the game, they did not address how to repair a breakdown of trust that might occur due to intentional or accidental non-cooperative actions by the players.
+Indeed, cooperative play in the repeated trust game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor after cooperation has been established, or a return of the trustee below the investment sent.
+Such ruptures of cooperation appear frequently when the trustee suffers from mental health disorders affecting the social domain such as Borderline Personality Disorder [@lieb_borderline_2004].
+In theses situations, BPD trustees fail to engage in trust repairing behavior such as coaxing the investor through sending high return to signal trustworthiness, and this failure may be linked to a failure to perceive their low returns in the game as a violation of social norms [@king-casas_rupture_2008].
+
+In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of interpersonal dysfunction in BPD patients.
+Whilst there is no proven pharmacological therapy for BPD, some forms of psychotherapy such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993], have been clinically validated as efficacious approaches to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
+However, these therapies suffer from a high variability in treatment responses.
+Determining which interventions are effective for particular patients has been very challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
+One promising approach is the study of how specific psychotherapeutic treatment components affect quantitative markers of behavior such as those inferred through computational modelling techniques [@huys_computational_2016; @reiter_neuro-cognitive_2021].
+As such, using specific cognitive probes inspired by therapeutic interventions complemented by computational modelling of behavior in tasks, may allow us to uncover cognitive mechanisms targeted by common forms of psychotherapy.
+This may in turn form the basis for targeting of existing psychotherapies to different individuals.
+
+In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a pre-programmed, one-off low investment sent by an computer investor.
 The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation.
-Participants are given the role of the trustee and are randomly assigned to either a control or intervention group.
-They play two instances of the repeated trust game with two different investors.
-After the first instance of the game, they either receive a cognitive intervention (intervention condition) or perform an unrelated task solving anagrams (control condition).
-In reality, participants face the same computerised agent in both instances, which is programmed to play according to a hidden Markov model fitted to real players' data.
-We explore whether the intervention has an effect on the behaviour of the human trustee and whether this effect transfers to a different game (repeated Prisoner's Dilemma) and facing a seemingly new player.
+Participants are given the role of the trustee and are randomly assigned to either a control group or an intervention group.
+They play two instances of the repeated Trust Game facing what they believe are two different players.
+In between games, they either receive a cognitive intervention (intervention condition) or not (control condition, where participants are asked to solve anagrams).
+In reality, participants face the same computerised agent in both instances, which is programmed to play according to an HMM fitted to real players data.
+We explore whether the intervention has an effect on the behaviour of the trustee and whether the learning is transferred to a new repeated Prisoner's Dilemma game when facing a seemingly new player.
 
@@
 The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years.
-Participants were paid a fixed fee of £5 plus a bonus payment dependent on their performance.<!--MS: state average bonus--> The experiment had a 2 (Condition: Intervention or Control) by 3 (Game: Trust-Game Pre Intervention, Trust-Game Post Intervention, Prisoner's Dilemma Post Intervention) design, with repeated measures on the second factor.
-Participants were randomly assigned to one of the two levels of the first factor.
-
-## Tasks and Measures
-
-### Repeated Trust Game
-
-Participants played a 15-round repeated trust game [@joyce_trust_1995] in the trustee role against a computer-programmed investor.
-On each round the investor was endowed with 20 units and decided how much of that endowment to invest.
-This investment is tripled and the trustee then decides how to split this amount between them and the investor.
-If the trustee returns more than one third of the amount, the investor makes a gain.
-The Nash equilibrium for a single-round version is for the investor to send nothing.
-In the repeated version, rewards for both players are maximised if they build trust and share the benefits of the the investment multiplied by three.
-An investor who has been rewarded for taking the risk of sending an investment is more likely to invest more on future rounds.
-An investor obtaining a low return on their investment may choose to reduce future investment and thereby reduce both players’ gains.
+Participants were paid a fixed fee of £5 plus a bonus dependent on their performance.
+The experiment had a 2 (Condition: Intervention or Control) by 2 (Game : Pre or Post Intervention) design, with repeated measures on the first factor.
+Participants were randomly assigned to one of the two levels of the second factor.
+
+## Procedure
+
+```{r timeline, fig.cap = "A) Experiment overview.
+After playing 15 rounds of a repeated trust game (RTG) as trustee, participants were randomized to either receive the control or active intervention.
+They then played the second set of 15 rounds of RTG (again as trustee) to examine intervention effects, and 7 rounds of a repeated prisoner’s dilemma to examine generalization of intervention effects.
+Finally, participants answered questionnaires and were debriefed.", fig.align='center', out.width="80%"}
+
+knitr::include_graphics("figures/timeline.png")
+
+```
+
+<!-- Figure \ref{fig:timeline} shows the timeline of the experiment.
+After reviewing an information sheet about the experiment, participants were informed that there would be three phases to go through, with them facing a different opponent in each phase.
+They would face the same player throughout the first phase, consisting of the "Investment Game" with several rounds.
+This was the moniker used for the repeated trust game, and a total of 15 rounds were played.
+Participants were then randomly assigned to either a control or intervention condition.
+-->
+
+<!-- <!-- After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.
+A comprehension quiz on the trust game followed the instructions.
+The first trust game then ensued:  Each round started with an investment stage where the investor decided how much to send to the trustee and that choice was revealed.
+Immediately afterwards, participants were presented with a two-dimensional field to indicate their emotional state on two dimensions: valence, from unpleasant to pleasant (on the horizontal axis) and arousal, from low arousal to high arousal (on the vertical axis).
+After selecting a point on the field, participants were asked to decide how much to send back to the investor using a slider ranging from sending back nothing to sending back the whole (tripled) investment.
+Following that choice, an outcome page summarised both players decisions and showed the total pay-off for each player and the round then concluded.
+At the end of the game, participants were asked to rate the player they were facing on 4 attributes using a scale from 1 to 10: Trustworthiness, friendliness, cooperativeness and selfishness.
+-->
+
+<!-- In the second phase of the experiment, participants were informed they would be paired with a different player.
+This phase was similar to the first phase in terms of the game played (RTG) and the number of rounds.
+In all rounds of the RTG, participants gave feedback after seeing the investment received.
+This feedback was given though a two dimensional grid that was either related to their emotional state (degree of valence of arousal) in the Intervention group, or unrelated to the emotional state in the control group (speed of investor's response and magnitude of investment).
+At the end of each RTG, participants were asked to rate how cooperative, selfish, trustworthy and friendly they thought their interaction partner was.
+Details of the two dimensional grid and player ratings are given in the supplement.
+-->
+
+<!-- After both trust games,  players were told they would be paired with a new player in the third phase of the experiment.
+This third phase consisted of 7 rounds of the prisoner's dilemma game, facing the new player.
+Throughout all games, players were explicitly told to aim to maximise the number of points as their bonus would depend on the score they accumulated throughout the experiment.
+The total number of rounds was not communicated to the participants in any of the games played.
+-->
+
+<!-- After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment.  -->
+
+<!-- <!-- These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016].
+-->
+
+<!-- Finally, participants were asked a series of questions around how they played each phase.
+First, they were asked whether they thought they played differently in the second compared to the first phase of the RTG.
+Second, participants had to select whether they thought the opponents they faced were human or computer agents.
+Finally, we revealed to the participants that they faced the same computer agent throughout the RTG.
+We explained that any change in their perception of the opponent or any change in how the opponent played is due to their own change in behavior as the agent was simply reacting to their actions.
+Finally, we asked participants to reveal whether this experiment has taught them anything about how they should behave in social situations.
+-->
+
+The experiment as shown in Figure \ref{fig:timeline} began with participants briefed there will be three phases, and that they would face a new opponent in each phase.
+Phase one was a 15 round Trust Game (RTG) in which participants had the role of the trustee, facing the same investor opponent.
+Participants were then assigned to either the control or intervention conditions.
+Phase two was similar to Phase one, with participants being told they faced a new player.
+In both phases, participants were asked for feedback in each round after seeing the investment.
+The nature of the feedback solicited varied by condition, either emotion-related (intervention) or unrelated (control).
+Participants rated their interaction partner on various attributes after each phase.
+More details on these attributes, nature of feedback and exact instructions are found in the supplement.
+Phase three involved 7 rounds of the repeated prisoner's dilemma game (RPD) with a third player.
+Participants were explicitly told to aim to maximise the number of points in all phases.
+The total number of rounds was not communicated to the participants in any of the games played.
+
+Post-experiment, participants completed questionnaires related to mentalising abilities, emotion regulation and BPD traits (see details in supplement).
+They were then quizzed on their game-play, including whether they detected that all opponents were computer agents.
+The reveal explained that they were facing identical AI agents and that any perceived opponent changes were due to participants' own behavior.
+
+## Interventions
+
+The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taking in emotional states [@linehan_dbt_2015].
+Specifically, participants were presented with a low investment and asked to indicate their response.
+They were then invited to consider what their ultimate aim in the game was and whether this response was most likely to achieve their aim.
+The intervention is detailed in the supplementary information.
+
+In the control condition, participants were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
+They provided their answers in a free-form text box.
+The time given to solve the anagrams was the same as that given to respond to questions in the intervention manipulation.
+
+## Design of the AI agents in the RTG and RPD
 
@@
 ```
-
-The strategy of the computerised investor was modelled on behaviour of human investors in a 10-round RTG.<!-- reference to data -->.
-Using this data, we estimated a hidden Markov model (HMM) on investors' behaviour with three latent states, reflecting "low-trust", "medium-trust", or "high-trust".
-Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust (Figure \ref{fig:HMMPanels}.A).
-Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of the net return in the previous round (see Figure \ref{fig:HMMPanels}.B).
-
-In order to probe efforts to repair trust, the computerised agent was programmed to provide a low return on round 12 pre-intervention or 13 post-intervention.
-On all other rounds, the agent's actions were derived from the HMM (disregarding the participant's response on round 12).
-
-### Repeated Prisoner's Dillema
-
-Participants played 7 rounds of a repeated Prisoner's Dilemma.
-In each round, participants could choose a cooperative action with a a reward of 5 if the player also cooperated and the a reward of 1 if not, or a non-cooperative action that would yield a 7 points if the other person chooses the cooperative action and 2 points if not.
-The Nash equilibrium for a single-round version is to choose the non-cooperative action.
-
-The computerised agent was programmed to act according to a tit-For-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
-On round 4, the agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
-
-## Intervention
-
-The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taking in emotional states [@linehan_dbt_2015].
-Specifically, participants were presented with a low investment and asked to indicate their response.
-They were then invited to consider what their ultimate aim in the game was and whether this response was most likely to achieve their aim.
-The intervention is detailed in the supplementary information.
-
-In the control condition, participants were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
-They provided their answers in a free-form text box.
-The time given to solve the anagrams was the same as that given to respond to questions in the intervention manipulation.
-
-## Procedure
-
-```{r timeline, fig.cap = "Experiment overview.
-After playing 15 rounds of a repeated trust game (RTG) as trustee, participants were randomized to either receive the control or active intervention.
-They then played the second set of 15 rounds of RTG (again as trustee) to examine intervention effects, and 7 rounds of a repeated Prisoner’s Dilemma to examine generalization of intervention effects.
-Finally, participants answered questionnaires and were debriefed.", fig.align='center', out.width="80%"}
-
-knitr::include_graphics("figures/timeline.png")
-
-```
-
-<!-- Figure \ref{fig:timeline} shows the timeline of the experiment.
-After reviewing an information sheet about the experiment, participants were informed that there would be three phases to go through, with them facing a different opponent in each phase.
-They would face the same player throughout the first phase, consisting of the "Investment Game" with several rounds.
-This was the moniker used for the repeated trust game, and a total of 15 rounds were played.
-Participants were then randomly assigned to either a control or intervention condition.
--->
-
-<!-- <!-- After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.
-A comprehension quiz on the trust game followed the instructions.
-The first trust game then ensued:  Each round started with an investment stage where the investor decided how much to send to the trustee and that choice was revealed.
-Immediately afterwards, participants were presented with a two-dimensional field to indicate their emotional state on two dimensions: valence, from unpleasant to pleasant (on the horizontal axis) and arousal, from low arousal to high arousal (on the vertical axis).
-After selecting a point on the field, participants were asked to decide how much to send back to the investor using a slider ranging from sending back nothing to sending back the whole (tripled) investment.
-Following that choice, an outcome page summarised both players decisions and showed the total pay-off for each player and the round then concluded.
-At the end of the game, participants were asked to rate the player they were facing on 4 attributes using a scale from 1 to 10: Trustworthiness, friendliness, cooperativeness and selfishness.
--->
-
-<!-- In the second phase of the experiment, participants were informed they would be paired with a different player.
-This phase was similar to the first phase in terms of the game played (RTG) and the number of rounds.
-In all rounds of the RTG, participants gave feedback after seeing the investment received.
-This feedback was given though a two dimensional grid that was either related to their emotional state (degree of valence of arousal) in the Intervention group, or unrelated to the emotional state in the control group (speed of investor's response and magnitude of investment).
-At the end of each RTG, participants were asked to rate how cooperative, selfish, trustworthy and friendly they thought their interaction partner was.
-Details of the two dimensional grid and player ratings are given in the supplement.
--->
-
-<!-- After both trust games,  players were told they would be paired with a new player in the third phase of the experiment.
-This third phase consisted of 7 rounds of the prisoner's dilemma game, facing the new player.
-Throughout all games, players were explicitly told to aim to maximise the number of points as their bonus would depend on the score they accumulated throughout the experiment.
-The total number of rounds was not communicated to the participants in any of the games played.
--->
-
-<!-- After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment.  -->
-
-<!-- <!-- These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016].
--->
-
-<!-- Finally, participants were asked a series of questions around how they played each phase.
-First, they were asked whether they thought they played differently in the second compared to the first phase of the RTG.
-Second, participants had to select whether they thought the opponents they faced were human or computer agents.
-Finally, we revealed to the participants that they faced the same computer agent throughout the RTG.
-We explained that any change in their perception of the opponent or any change in how the opponent played is due to their own change in behavior as the agent was simply reacting to their actions.
-Finally, we asked participants to reveal whether this experiment has taught them anything about how they should behave in social situations.
--->
-
-At the start of the experiment (Figure \ref{fig:timeline}), participants provided informed consent and were instructed the study would consist of three phases in which they would face a different other player.
-Participants were told their goal was to maximise the number of points in all phases.
-They were not told the number of rounds of each phase.
-Phase one was a 15 round repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
-On each round, after being informed about the amount sent by the investor, participants were asked to provide feedback, with participants in the Intervention condition rating their feeling in terms of valence (from negative to positive) and arousal (from low to high), and participants in the Control condition rating the investment in terms of speed (from slow to fast) and magnitude (from low to high).
-These ratings were made by indicating a point on a two-dimensional grid.
-Participants then decided on how much of the tripled investment to return to the investor, before continuing to the next round.
-After completing 15 rounds of the RTG, participants rated how cooperative, selfish, trustworthy and friendly they perceived their interaction partner (all on a scale from 1 to 10).
-After phase one, participants in the intervention condition completed the intervention, and participants in the control condition solved anagrams.
-Subsequent phase two was similar to phase one, with participants being told they would face a new player.
-Phase three consisted of 7 rounds of the repeated prisoner's dilemma game (RPD), with participants informed they would face a third player.
-Participants then completed questionnaires related to mentalising abilities (RFQ8), emotion regulation (DERS), and BPD traits (PAI-BOR).<!-- MS: need to include references for these scales --> They were then asked about the strategy in the games, as well as whether they thought the other players were human or computer agents.
-They were then debriefed and thanked for their participation.
-
-## Statistical analysis
+The role of the investor was in reality played by an adaptive artificial agent whose strategy was modelled on the behaviour of human participants taking the role of the investor in the RTG.
+Using data from human dyadic interaction in the 10 round trust game, we estimate a Hidden Markov Model (HMM) to characterise the investor's behavior as emanating from a small number of latent states [@rabiner_hmm_1989].
+In this instance, for both iterations of the repeated trust game, the HMM used was identical: it had three states that can be described as "low-trust", "medium-trust" and "high-trust".
+Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust, as presented in Figure \ref{fig:HMMPanels}.A.
+Transition probabilities between these latent states were modelled as a function of the net return in the previous round conditional on the investor's state as shown in Figure \ref{fig:HMMPanels}.B.
+
+<!-- In order to probe efforts to repair trust, we introduced rounds where the investor deviated from the policy provided by the HMM, and chose to send a low investment in the Trust Game, or chose the non-cooperative action in the Prisoner's Dilemma.
+In the trust games, we programmed the HMM agent to send a very low investment (2 out of 20) to the trustee on specific rounds (round 12 pre-intervention and 13 post-intervention).
+For the repeated Prisoner's Dilemma game, we programmed the agent to choose the non-cooperative action on round 4.
+After each "defection" round, the agents were programmed to proceed their policy from before that round, effectively ignoring the participants' response to their defection.
+For instance, the HMM investor would send an investment in the post defection round that was consistent with the outcome of the round immediately prior to that round.
+For the RPD, the agent would continue to play tit-for-tat, but also ignoring what happened in the defection round, and basing its action on mirroring what the other player did in the round immediately prior to the defection round.
+This ignorance of reactions to the defection rounds was chosen to reflect an accidental defection, with the Investor being open to repair subsequent interaction.
+-->
+
+In order to probe efforts to repair trust, we simulated trust breaches in both Trust Games and the Prisoner's Dilemma.
+The AI was programmed to break trust on specific rounds (12 pre-intervention, 13 post-intervention in the Trust Game; round 4 in Prisoner's Dilemma).
+After these "defection" rounds, the AI returned to its previous strategy, disregarding the participant's response to the breach.
+This simulated an accidental defection and a readiness to repair the interaction, providing insights into trust repair dynamics.
+
+<!-- ## Computational analysis of trustee returns -->
+
+<!-- In order to characterise the effect of the intervention on the trustees strategy, we fit a Hidden Markov Model to the percentage returns of the trustees for the RTG data.
+The model allows for switching between latent trustee states over time.
+Hidden Markov models assume that an observable trustee return at time $t$ depends on a latent trustee state at time $t$.
+It is assumed that the latent state at time $t$ depends on the latent state at the previous time $t-1$.
+The model is specified by the state-conditional action distributions (these are provided by the likelihood of the fitted models), an initial state distribution (the distribution over the strategies at the initial round), and the state-transition probabilities (probability of switching from one state/strategy to another).
+Initial state probabilities and the transition probabilities were estimated with the depmixS4 package [@visser_depmixs4_2021].
+-->
+
+## Analysis of participants returns in the RTG
 
@@
 
-To model participants' returns in the RTG across games and conditions, we fit various hidden Markov models to participants' returns using the depmixS4 package [@visser_depmixs4_2021] for R.
+To model participants returns in the RTG across games and conditions, we fit various hidden Markov models to participants returns using the depmixS4 package [@visser_depmixs4_2021].
 The transition between latent states is assumed to depend on the investment received and a dummy variable to characterise the group that the participant belongs to.
-Details on how the models are constructed can be found in the supplement.
+Details on how the models are constructed as well as the various contrast codes used for the dummy variables are found in the supplement.
 We fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978-1] to select the best model.
 
-# Behavioural results
+# Behavioral results
 
@@
 
-Average investments and returns prior to the "defection round" (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
-
-<!--
-Estimated marginal means of percentage returns from fitting the mixed effects model specified in the methods section, as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.A.-->
+Average investments and returns prior to the defection round (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
+Estimated marginal means of percentage returns from fitting the mixed effects model specified in the methods section, as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.A.
 
@@
 
-ggplot(avg_ret_df ,aes(x=as.factor(roundNum),group=gameNum.f, color = gameNum.f)) +
-  stat_summary(fun = "mean", geom = "line", aes(y=ret_pct)) +
-  stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=ret_pct) )+
+ggplot(avg_ret_df, aes(x=as.factor(roundNum), y=ret_pct, group=gameNum.f, color = gameNum.f)) +
+  stat_summary(fun = mean, geom = "line") +
+  stat_summary(fun.data = mean_se, geom = "ribbon", aes(ymin=..ymin.., ymax=..ymax..), 
+               alpha = 0.3, fill = "grey", linetype = 0) +
   labs(x = "Round",
@@
        color = "Game") +
-  # ylab("Percentage Return") +
-  # xlab("Round") +
   theme_bw() +
   theme(legend.position = "bottom") +
-  facet_wrap(~condition.f)
+  facet_wrap(~condition.f) +
+  scale_color_manual(values = c("darkblue", "green"))
+
+```
+
+<!-- Plotting individual differences   -->
+```{r, include =F}
+ret_post_int <- avg_ret_df %>% filter(roundNum == 13 , gameNum.f == "post")
+
+# plot(jitter(ret_post_int$returns), main="Jitter Plot", ylab="Returns", pch=19, col="blue")
+# plot(ecdf(ret_post_int$returns), main="ECDF", xlab="Returns", ylab="Cumulative Probability")
+# 
+# ggplot(ret_post_int , aes(x = "", y = returns)) +
+#   geom_violin(fill="lightblue") +
+#   geom_boxplot(width=0.1, fill="white") +
+#   theme_minimal() +
+#   labs(x = NULL, y = "Returns", title = "Violin plot")
+
+library(ggplot2)
+ggplot(ret_post_int, aes(x = "", y = ret_pct)) +
+  geom_violin(fill="lightblue") +
+  geom_jitter(width = 0.2, height = 0.02, size = 1, col = "black") +
+  geom_hline(yintercept = 0.33, color = "red", linetype = "dashed") +
+  theme_bw() +
+  facet_wrap(~condition.f) +
+  labs(x = NULL, y = "% Return", title = "")
 
@@
 
-mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), avg_ret_df, REML= TRUE, method="KR")
+mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), avg_ret_df, REML= TRUE)
 anova(mod_returns_pct)
@@
 
-<!-- MS: double check statistics; I get different df when using KR in mixed -->
-Mixed-effects analysis shows a significant main effect of Condition (intervention vs.
-control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f` <!--$F(1,315.31) = 9.52$, $p = .002$-->, with higher percentage returns in the intervention compared to the control condition.
-Importantly, we also find an interaction between Condition and Game-number (pre- vs.
-post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f` <!--$F(1,314.2) = 26.9$, $p < .001$-->.
-Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:violinPanels}.A).
-This indicates the intervention was effective in increasing cooperative behaviour.
-There was also a significant main effect of Investment, `r papaja::apa_print(mod_returns_pct)$full_result$inv_scaled` <!--$F(1,9208) = 373.6$, $p < 0.001$-->, such that higher investments were associated with higher percentage returns.
-An Investment by Condition interaction, `r papaja::apa_print(mod_returns_pct)$full_result$condition_f_inv_scaled` <!--$F(1,9207) = 45.38$, $p < .001$-->, indicates the positive effect of investment on percentage returns was greater in the control than intervention condition.
-<!-- This suggests that the higher returns we see in the intervention group are not simply due to higher investments.--> There was also an Investment by Game-number interaction, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_inv_scaled`.
-Finally, we find a three way interaction between Game-number, Condition and Investment, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f_inv_scaled`, <!--($F(1,8988)= 24.6, p < 0.001$),--> showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game-number.
-
-<!--
-group had higher percentage returns than the control group.
 We find an interaction effect between Condition (intervention vs.
@@
 
--->
-
 ```{r, include=FALSE, cache=TRUE}
-mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| id), avg_ret_df, method="KR")
+mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| id), avg_ret_df )
 summary(mod_invs)
 anova(mod_invs)
-
-#cond_effect_inv <- pairs(emmeans::emmeans(mod_invs, c("condition.f"), by = "gameNum.f", pbkrtest.limit = 9570))
 
@@
 
-We next analysed HMM agent investments via a linear-mixed effects model with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number.
-This shows a main effect of Condition, `r papaja::apa_print(mod_invs)$full_result$condition_f`<!--$F(1,317) = 8.7$, $p = .003$-->, and Game-number, `r papaja::apa_print(mod_invs)$full_result$gameNum_f`<!--$F(1,317) = 8.3$, $p = .004$-->.
-As can be seen in Figure \ref{fig:violinPanels}.B, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
-
-Taken together, we find that participants in the control condition sent *lower* percentage returns in the second game, despite the HMM investor sending on average higher investments in the second game.
-Those in the intervention group returned *higher* percentage returns in the second game, with the investor also sending higher investments.
-These higher returns in the intervention group compared to the control group were not purely driven by reciprocity towards higher investments, since we find a Condition by Game-number interaction whilst controlling for investment in the model, and a reduced effect of Investment in the Intervention condition.
-<!-- since we find this interaction effect whilst controlling for investments in our model of participants returns.-->
-
-<!-- ## Looking at pre- and post-defection trials only -->
+The HMM agent exhibited a differentiated behavior between games and conditions.
+When examining the HMM agent investments, we fit a linear-mixed effects model, with fixed effects for Condition (intervention or control), Game-number (pre or post intervention), as well as interaction between Condition and Game-number, and participant-wise random intercepts and random slopes for Game-number.
+We find a main effect for both Condition ($F(1,317) = 8.7, p = 0.003$) and Game-number($F(1,317) = 8.3, p = 0.004$).
+As can be seen in Figure \ref{fig:violinPanels}.D, investment was higher in the intervention compared to the control condition across games ($p=0.003$).
+Across conditions, investment was also higher in the second game compared to the first ($p=0.003$).
+
+In summary, participants in the control group sent back **lower** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$Control_Pre_post`) despite the HMM investor sending, on average higher investments.
+Those in the intervention group returned **higher** percentage returns in the second game (`r apa_print(prepost_bycond)$full_result$Intervention_Pre_post`), with the investor also sending higher investments.
+These higher returns in the intervention group compared to the control group were not purely driven by reciprocity towards higher investments since we find this interaction effect whilst controlling for investments in our model of participants returns.
+
+## Looking at pre- and post-defection trials only
 
@@
 
-mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), pre_int_data, REML= TRUE, method="KR")
+mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), pre_int_data, REML= TRUE)
 anova(mod_returns_pre)
@@
 
-We next analysed returns separately for rounds prior to the pre-programmed defection (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
-Applying the same mixed effects model as before to returns before defection, largely replicates results over all trials.
-Full results are provided in the supplement.
-Participants in the intervention condition increased their returns in the second game, `r papaja::apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`.
-There was no evidence that participants in the control condition changed their returns in pre-defection trials between the two phases of the RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
-
-<!--
-investments Analysis  and fit the same linear mixed effects model to percentage returns as the one for the full data.
+We restrict our analysis to the rounds prior to the pre-programmed defection (rounds 1 to 11 pre-manipulation and 1 to 12 post-manipulation) and fit the same linear mixed effects model to percentage returns as the one for the full data.
 Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.B.
@@
 This indicates that participants were sending back higher returns in the intervention condition but not in the control condition even before the defection trial.
--->
 
@@
 
+The interventions focused on repairing cooperation in the wake of a transgressive action by the investor.
+To assess the effect of the intervention, we can therefore consider the percentage return after the "transgression" trials.
+We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
+These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).
+
 ```{r, include =FALSE}
@@
 ```{r violinPanels, fig.cap="A: Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition.
-B: Marginal means and distributions of investments over all rounds for HMM investors, by Game number and Condition.
-C: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
-D: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.", fig.align="center", fig.width=6, fig.height = 6}
-
-ggpubr::ggarrange(pctRet_all, inv_all, pctRet_pre, pctRet_post, nrow=2, ncol=2, labels = c("A", "B", "C", "D"), common.legend = TRUE, legend = "bottom")
-```
-
-The intervention focused on repairing cooperation after a "transgressive action" by the investor.
-To assess whether the intervention succeeded, we next considered the returns by participants after the pre-programmed transgression (Figure \ref{fig:violinPanels}.D).
-<!-- We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
-These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).
--->
-<!-- Figure \ref{fig:violinPanels}.D shows the marginal means of trustee returns and their distribution by Game-number and Condition.--> A mixed-model analysis shows similar results to those of the model applied to all returns (see SI for full results).
-The was again a significant interaction between Condition and Game-number and Condition.
-Participants in the control condition decreased their post-transgression returns from the first to the second phase of the RTG, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
-There was no change for participants in the intervention condition, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`.
-So, whilst the intervention did not appear to move participants to increase their returns after a transgression by the investor, it may have countered the decrease in returns showed by participants in the control condition.
+B: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
+C: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.
+D: Marginal means and distributions of investments over all rounds for HMM agents playing the role of the investor, by Game number and Condition", fig.align="center", fig.width=6, fig.height = 6}
+
+ggpubr::ggarrange(pctRet_all, pctRet_pre, pctRet_post, inv_all, nrow=2, ncol=2, labels = c("A", "B", "C", "D"), common.legend = TRUE, legend = "bottom")
+```
+
+Figure \ref{fig:violinPanels}.C shows the marginal means of trustee returns and their distribution by Game-number and Condition.
+There was a significant interaction between Game-number and Condition.
+Participants sent back lower returns between games in the control condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`), but no such difference in the intervention condition (`r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`).
 
@@
 datCoax$roundGroup <- ifelse(datCoax$roundNum <= 10, "Rounds 1-10", "Rounds 11-15")
-
-# p <- datCoax %>%
-#   ggplot(aes(x=roundNum)) + stat_summary(fun = "mean", geom = "line", aes(y=emo_scaled_x, color = "Valence")) + stat_summary(fun = "mean", geom = "line", aes(y=emo_scaled_y, color = "Arousal")) + stat_summary(fun = "mean", geom = "line", aes(y=inv_scaled, color = "Investment")) + facet_wrap(~gameNum_f, scales = "free_x")
 
@@
 
+A key aspect of effective interventions is the emotional change.
+We examined emotion self-reports through fitting a linear mixed effects model to both emotion dimensions (valence and arousal) for the intervention group to explore whether the intervention changed the emotional appraisal of the investment, with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
+
+Higher investments were associated with more positive emotions ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$), while positive emotions declined between the two games ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
+However, there was no evidence that emotional reaction to the investment was lessened after the intervention.
+This means that participants in the intervention condition returned higher amounts post-intervention despite the emotional reaction to the lower investment being largely unchanged.
+
 <!-- Figure \ref{fig:emoPlotCoax} shows the average, across participants *in the intervention condition*, of emotion valence, the degree of arousal as well as the HMM's investment z-scores.
@@
 
-mod_emo_x <- mixed( emo_scaled_x ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), data=datCoax, method="KR")
+mod_emo_x <- mixed( emo_scaled_x ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
 summary(mod_emo_x)
@@
 ```
-
-Participants in the intervention condition rated their emotion on valence (negative to positive) and arousal (low to high) after each investment.
-To assess the impact of the intervention on these emotional reactions, we used linear mixed-effects models (one for valence, and one for arousal) with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
-This showed that higher investments were associated with more positive emotions, `r papaja::apa_print(mod_emo_x)$full_result$scaleinvestment`, and higher arousal, `r papaja::apa_print(mod_emo_y)$full_result$scaleinvestment`.
-<!-- ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$)--> In addition, the positiveness of emotion declined between the two games, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f`, as did arousal, `r papaja::apa_print(mod_emo_y)$full_result$gameNum_f`.
-There was no indication that the effect of the investment on either aspect of emotion was affected by the intervention, as there was no interaction between Investment and Game-number on valence, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f_scaleinvestment`, or arousal, `papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment`.
-This indicates that participants in the intervention condition returned higher amounts post-intervention despite their emotional reaction to investments remaining largely the same.
-
-<!--
-A key aspect of effective interventions is the emotional change.
-We examined emotion self-reports through fitting a linear mixed effects model to both emotion dimensions (valence and arousal) for the intervention group to explore whether the intervention changed the emotional appraisal of the investment, with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
-
-Higher investments were associated with more positive emotions ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$), while positive emotions declined between the two games ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
-However, there was no evidence that emotional reaction to the investment was lessened after the intervention.
-This means that participants in the intervention condition returned higher amounts post-intervention despite the emotional reaction to the lower investment being largely unchanged.
--->
 
@@
 
-## Evaluation of the investor
+## Player rating
 
@@
 
-Participants rated the HMM investor in the second game as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result`) and more selfish (`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result`), than the HMM investor in the first game.
-Participants in the intervention condition rated players higher than those in the control condition on cooperativeness (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("condition.f"))))$full_result`) and lower on selfishness (`r apa_print(pairs(emmeans::emmeans(self_mod, c("condition.f"))))$full_result`).
-There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
-
-<!--
 Participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention).
@@
 There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
--->
 
@@
 
-## Transfer to the repeated Prisoner's Dilemma game
+## Transfer to the Prisoner's Dilemma Game
 
@@
 
-We next asked whether the intervention had any discernible effect on participants' behaviour in a different, repeated Prisoner's Dilemma game.
-Predicting the probability of a cooperative action with a logistic mixed-effects regression model, with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, showed a decline in cooperation after defection by the other player, `r papaja::apa_print(ipd_mod)$full_result$phase`, but no evidence for a different cooperation rate in the intervention condition compared to the control condition, `r `papaja::apa_print(ipd_mod)$full_result$condition_f`, or a different response to defection between the conditions, `r papaja::apa_print(ipd_mod)$full_result$condition_f_phase`.
-<!-- We also found no difference in cooperation rates post defection trial between conditions.-->
+We next asked whether the coaxing behavior induced by the intervention generalized to the RPD.
+Across participants, we look at the rate at which the cooperative action was chosen in each round.
+Using a logistic mixed-effects model with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, we found no evidence for a different cooperation rate in the intervention condition compared to the control condition.
+We also found no difference in cooperation rates post defection trial between conditions.
 
 ## Self report and debrief questionnaires
-
-<!-- MS: This section doesn't say much.
-It could be reasonable to include questionnaire scores in the main analyses throughout (e.g.
-does BPD trait have an effect or moderate any other effects?
-IF not, a statement somewhere that the scales didn't have an effect, and showing results of accompanying analyses in SI would be fine -->
 
@@
     to = rep(1:ns, each=100),
-    investment = seq(0,20,length=100),
+    investment = seq(0,8,length=100),
     prob_pre = 0,
@@
 
-# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
+plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
 
@@
 
-coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
-  geom_line() + 
-  geom_line(aes(y=prob_pre),linetype="dotted") +
+# coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
+#   geom_line() + 
+#   geom_line(aes(y=prob_pre),linetype="dotted") +
+#   facet_wrap(~from) + 
+#   ylim(c(0,1)) + 
+#   ggtitle("Transition function pre- and post-intervention manipulation") + 
+#   labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
+#   theme_bw()
+
+coax_pre_plot <- ggplot(trans_prob,aes(x=investment)) + 
+  geom_line(aes(y=prob_coax, colour = as.factor(to), linetype="Post-intervention")) + 
+  geom_line(aes(y=prob_pre, colour = as.factor(to), linetype="Pre-intervention")) +
   facet_wrap(~from) + 
@@
   ggtitle("Transition function pre- and post-intervention manipulation") + 
-  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
+  labs(x = "Investment", y = "Transition probability", color='State Transitioned to', linetype = "Line Type") + 
+  scale_linetype_manual(values = c("Post-intervention" = "solid", "Pre-intervention" = "dotted")) +
   theme_bw()

### 2023-08-14 article.Rmd
cleaning up MS edits

--- 2023-06-30 article.Rmd
@@
 
-The strategy of the computerised investor was modelled on behaviour of human investors in a 10-round RTG.<!-- reference to data -->.
+The strategy of the computerised investor was modelled on behaviour of human investors in a 10-round RTG <!-- reference to data -->.
 Using this data, we estimated a hidden Markov model (HMM) on investors' behaviour with three latent states, reflecting "low-trust", "medium-trust", or "high-trust".
@@
 
-In order to probe efforts to repair trust, the computerised agent was programmed to provide a low return on round 12 pre-intervention or 13 post-intervention.
-On all other rounds, the agent's actions were derived from the HMM (disregarding the participant's response on round 12).
+In order to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 pre-intervention and 13 post-intervention.
+On all other rounds, the agent's actions were derived from the HMM (disregarding the participant's response on pre-programmed low investment rounds).
 
@@
 Participants played 7 rounds of a repeated Prisoner's Dilemma.
-In each round, participants could choose a cooperative action with a a reward of 5 if the player also cooperated and the a reward of 1 if not, or a non-cooperative action that would yield a 7 points if the other person chooses the cooperative action and 2 points if not.
+In each round, participants could choose between: a cooperative action with a reward of 5 if the player also cooperated and a reward of 1 if not, or a non-cooperative action that would yield a 7 points if the other person chooses the cooperative action and 2 points if not.
 The Nash equilibrium for a single-round version is to choose the non-cooperative action.
 
-The computerised agent was programmed to act according to a tit-For-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
+The computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
 On round 4, the agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
@@
 
-The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taking in emotional states [@linehan_dbt_2015].
+The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taken in emotional states [@linehan_dbt_2015].
 Specifically, participants were presented with a low investment and asked to indicate their response.
@@
 Phase three consisted of 7 rounds of the repeated prisoner's dilemma game (RPD), with participants informed they would face a third player.
-Participants then completed questionnaires related to mentalising abilities (RFQ8), emotion regulation (DERS), and BPD traits (PAI-BOR).<!-- MS: need to include references for these scales --> They were then asked about the strategy in the games, as well as whether they thought the other players were human or computer agents.
+Participants then completed questionnaires related to mentalising abilities, emotion regulation, and BPD traits (see the supplement for details).
+They were then asked about the strategy in the games, as well as whether they thought the other players were human or computer agents.
 They were then debriefed and thanked for their participation.
@@
 # Behavioural results
-
-<!-- Our investment levels are clearly comparable.
-Our random matching condition is the most directly comparable to Berg et al., (1995) and Charness et al., (2008), both of whom used random matching.
-Our investment averages 4.97 out of 10 in the individual feedback condition, which falls right in between the investment level of 5.16 documented by Berg et al., (1995) and the 3.73 documented by Charness et al., (2008).
-The amount returned in the individual feedback condition with random matching is 5.61, which is slightly higher than the amounts returned in Berg et al., (1995) of 3.73 and Charness et al., (2008) of 4.65.
-The 19% return rate is comparable to results in similar designs.
-In an almost identical design, Fiedler et al., (2011) report a 17% return rate by responders.
-This is similar to our finding.
--->
 
@@
 
-<!--
-Estimated marginal means of percentage returns from fitting the mixed effects model specified in the methods section, as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.A.-->
-
-<!-- Investments averaged `r round(avg_pct$avg_inv,3)*100` $\%$ of endowment which is less than the $63.2\%$ documented by @fiedler_social_2011 and higher than the $37.3%$ documented by @charness_investment_2008, although the latter used repeated one shot games with random matching.
-Returns averaged `r round(avg_pct$avg_ret,3)*100` $\%$  of the total yield (3x investment sent), which is higher than the $35\%$ found in the same setting in @fiedler_social_2011.
--->
-
 ```{r gamesPlot, echo=FALSE, fig.cap="Average and standard errors of the trustee's return as a percentage of the multiplied investment received for each round and for both conditions.
@@
 ```
+
 ```{r, include=FALSE, cache=TRUE}
@@
 ```
+
 ```{r, include=FALSE}
@@
 
-<!-- If the intervention has an effect, then we should expect a higher increase in returns after the intervention compared to the control condition, which should be evident from an interaction between Condition (intervention vs control) and Game-number (pre- vs post-manipulation).
-Therefore, the variable of interest here is the interaction between Condition and Game-number.
--->
-
 <!-- MS: double check statistics; I get different df when using KR in mixed -->
@@
 post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f`<!--$F(1,314.2) = 26.9$, $p < .001$-->.
-Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:violinPanels}.A).
+Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:violinPanels}.A).
 This indicates the intervention was effective in increasing cooperative behaviour.
@@
 Finally, we find a three way interaction between Game, Condition and Investment, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f_inv_scaled`<!--($F(1,8988)= 24.6, p < 0.001$),-->, showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game (pre- vs post intervention).
-
-<!--
-group had higher percentage returns than the control group.
-We find an interaction effect between Condition (intervention vs.
-control) and Game-number (pre- vs.
-post-manipulation) ($F(1,314.2) = 26.9, p < 0.001$).
-Post-hoc tests show that there was an increase in the percentage returned in the intervention group (`r papaja::apa_print(prepost_bycond)$statistic$Intervention_Pre_post`) but not in the control group (`r papaja::apa_print(prepost_bycond)$statistic$Control_Pre_post`).
-We also found a significant main effect for Condition ( $F(1,315.31) = 9.52, p = 0.002)$), such that the intervention group had higher percentage returns than the control group.
-There was also a significant main effect of Investment( $F(1,9208) = 373.6, p < 0.001$) such that higher investments were associated with higher percentage returns.
-
-There was an interaction effect of Investment by Condition ($F(1,9207) =45.38, p < 0.001$), such that the positive effect of investment on percentage returns was greater in the control group than in the intervention group.
-This suggests that the higher returns we see in the intervention group are not simply due to higher investments.
-Finally, we find a three way interaction between Game-number, Condition and Investment ($F(1,8988)= 24.6, p < 0.001$), showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game-number.
-
--->
 
@@
 
-<!-- Taken together, we find that participants in the control condition sent lower percentage returns in the second game, despite the HMM investor sending on average higher investments in the second game.
-Those in the intervention group returned higher percentage returns in the second game, with the investor also sending higher investments.
-These higher returns in the intervention compared to the control condition were not purely driven by reciprocity towards higher investments, since we find a Condition by Game interaction whilst controlling for investment in the model, and a reduced effect of investment in the intervention condition.
-<!-- since we find this interaction effect whilst controlling for investments in our model of participants returns.-->
-
-<!-- ## Looking at pre- and post-defection trials only -->
-
 ```{r, include=FALSE, cache=TRUE}
@@
 There was no evidence that participants in the control condition changed their returns in pre-transgression trials between the first and second RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
-Full results are provided in the SI.
-
-<!--
-investments Analysis  and fit the same linear mixed effects model to percentage returns as the one for the full data.
-Estimated marginal means of percentage returns as well as the distribution of the returns for participants across all trials are presented in Figure \ref{fig:violinPanels}.B.
-We do find an interaction effect between Condition and Game number ($F(1,317.99) = 17.1, p < 0.001$).
-This was due to an increase in the percentage returned pre low-investment trial in the intervention condition (`r apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`) but not in the control group (`r apa_print(pairs_pre_int)$full_result$Control_Pre_post`).
-This indicates that participants were sending back higher returns in the intervention condition but not in the control condition even before the defection trial.
--->
+Full results are provided in the supplement.
 
@@
 
-<!-- The intervention focused on repairing cooperation after a "transgressive action" by the investor.
-To assess whether the intervention succeeded, we next considered the returns by participants after the pre-programmed transgression (Figure \ref{fig:violinPanels}.D).--> <!-- We fit the same linear mixed effects model to percentage returns as the one for the full data while restricting the data to rounds 12 to 15 in the first game, and 13 to 15 in the second game.
-These trials represent all trials after the pre-programmed defection of the investor (low investment of $2$) until the end of the game (round 15).
--->
-<!-- Figure \ref{fig:violinPanels}.D shows the marginal means of trustee returns and their distribution by Game-number and Condition.--> Applying the same model to the returns after the transgression (see SI for full results), we again find <!-- A mixed-model analysis shows similar results to those of the model applied to all returns (see SI for full results).
-There was again --> a significant interaction between Condition and Game.
+Applying the same model to the returns after the transgression (see the supplement for full results), we again find a significant interaction between Condition and Game.
 Participants in the control condition decreased their post-transgression returns from the first to the second RTG, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
 There was no significant change for participants in the intervention condition, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`.
-<!-- So, whilst the intervention did not appear to move participants to increase their returns after a transgression by the investor, it may have countered the decrease in returns showed by participants in the control condition.
--->
+When questionnaire scores for borderline traits, mentalising and emotion regulation abilities were added as explanatory variables, we found no interaction effect of these questionnaire scores with the Condition variable, nor a main effect of the questionnaire scores on participants returns in the RTG.
 
@@
 However, it may have countered the tendency to lower returns after the transgression in the second game compared to the first game, which was shown by participants in the control condition.
-
-<!-- We found a main effect of Condition with returns on the intervention group higher than returns in the control group (`r apa_print(pairs(postcoax_bycond))$full_result`).
-We also found a main effect of Game-number, with returns higher for the pre-manipulation game compared to the post-manipulation game  (`r apa_print(pairs(postcoax_bygame))$full_result`).
--->
 
@@
 ```{r emoPlotCoax, fig.cap="Self-reported emotion valence and arousal as well as investment z-scores for each round of the repeated Trust Game averaged across participants in the intervention condition only.",fig.align="center", fig.width=6, fig.height = 4}
-
-# colors <- c("Investment" = "blue", "Valence" = "red", "Arousal" = "green")
-# 
-# ggplot(datCoax,aes(x=roundNum)) + 
-#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_x), color = "red") + 
-#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=emo_scaled_y), color = "green") + 
-#   stat_summary(fun = "mean", geom = "line",group =1, aes(y=scale(investment)), color = "blue") + 
-#   scale_color_manual(name = " ",values = colors, labels = c("Investment", "Emotion valence", "Emotion arousal")) +
-#   labs(x = "Round", y="Series Z-score") +
-#   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
-#   facet_grid(cols = vars(gameNum.f)) +
-#   theme_bw() + 
-#   theme(legend.position = "bottom")
-#
-
-# # BOTH IN ONE GRAPH 
-# library(ggplot2)
-# 
-# # Define the colors in alphabetical order
-# colors <- c("Arousal" = "green", "Investment" = "blue", "Valence" = "red")
-# 
-# # Plot 'pre'
-# p <- ggplot(datCoax[datCoax$gameNum.f == 'pre', ], aes(x=roundNum)) + 
-#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_x, color = "Valence", linetype = "pre")) + 
-#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=emo_scaled_y, color = "Arousal", linetype = "pre")) + 
-#   stat_summary(fun = "mean", geom = "line", group =1, aes(y=inv_scaled, color = "Investment", linetype = "pre")) +
-# # Plot 'post'
-#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_x, color = "Valence", linetype = "post")) + 
-#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=emo_scaled_y, color = "Arousal", linetype = "post")) + 
-#   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=inv_scaled, color = "Investment", linetype = "post")) +
-#   labs(x = "Round", y="Series Z-score") +
-#   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
-#   scale_color_manual(name = " ", values = colors, labels = c("Emotion arousal", "Investment", "Emotion valence")) +
-#   scale_linetype_manual(values = c("pre" = "dotted", "post" = "solid"), labels = c("Pre", "Post")) +
-#   theme_bw() + 
-#   theme(legend.position = "bottom")
-# 
-# # Print the plot
-# print(p)
 
@@
 
-<!-- Figure \ref{fig:emoPlotCoax} shows the average, across participants *in the intervention condition*, of emotion valence, the degree of arousal as well as the HMM's investment z-scores.
-We find a significant positive correlation between the two emotion axis ($r=0.52, p < 0.001$) as well as between valence and Investment ($r=0.47, p < 0.001$), and arousal and Investment ($r=0.50, p < 0.001$).
--->
-
 ```{r, include=FALSE}
@@
 
-<!--
-A key aspect of effective interventions is the emotional change.
-We examined emotion self-reports through fitting a linear mixed effects model to both emotion dimensions (valence and arousal) for the intervention group to explore whether the intervention changed the emotional appraisal of the investment, with fixed effects for Game-number (pre or post intervention) and Investment, as well as interaction between Investment and Game-number, with participant-wide random intercepts and random slopes for Game-number.
-
-Higher investments were associated with more positive emotions ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$), while positive emotions declined between the two games ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
-However, there was no evidence that emotional reaction to the investment was lessened after the intervention.
-This means that participants in the intervention condition returned higher amounts post-intervention despite the emotional reaction to the lower investment being largely unchanged.
--->
-
-<!-- For emotional valence, we find a main effect of Investment ($F(1,4664) = 2902, p < 0.001$), with higher investment leading to more positive emotions.
-We also find a main effect for Game-number, due to the reported emotional valence of investments decreasing significantly after the intervention ($\Delta M = 0.11, 95\% \ CI = [0.05, 0.18], t(\infty) = 3.72, p < .001$).
-For emotional arousal, fitting a similar mixed effects model we find only a main effect of Investment  ($F(1,4668.4) = 1919, p < 0.001$) with higher investment leading to higher arousal.
-These effects are still present if we exclude the defection trial.
-We did not find any interaction between emotional valence or arousal and the investment, which would indicate a moderating effect of the intervention on the reaction to investments.
--->
-
 ## Evaluation of the investor
-
-<!-- One possible reason of the differentiated returns post manipulation between conditions is that participants had a different perception of the investor, post-manipulation, in the control condition compared to the control condition.
-To explore this possibility, we can determine whether participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention) using the players ratings they had to submit at the end of each game.
-To analyse the participants rating of their opponents, we used a linear mixed-effects model for each of the four players ratings (cooperativeness, selfishness, trustworthiness, friendliness) with fixed effects for Game-number (pre or post manipulation) and Condition (intervention or control), as well as interaction between condition and Game-number, and participant-wise random intercepts.
--->
 
@@
 
-<!-- showed a main effect of Game-number on all attributes, with participants rating the second player as less cooperative (∆M = 0.42, 95% CI [0.15, 0.69], t(317.00) = 3.10, p = .002), less trustworthy (∆M = 0.43, 95% CI [0.16, 0.70], t(317.00) = 3.19, p = .002), less friendly (∆M = 0.40, 95% CI [0.17, 0.64], t(317.00) = 3.36, p = .001) and more selfish(∆M = −0.36, 95% CI [−0.61, −0.10], t(317.00) = −2.76, p = .006).
-Importantly, there was a main effect of Condition , with participants in the intervention condition rated players higher than those in the control condition on cooperativeness (∆M = 0.40, 95% CI [0.00, 0.80], t(317.00) = 1.95, p = .052) and lower on selfishness (∆M = −0.41, 95% CI [−0.80, −0.02], t(317.00) = −2.04, p = .042).
-There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
--->
-
 Participants rated the HMM investor in the second game as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result`) and more selfish (`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result`), than the HMM investor in the first game.
@@
 
-<!--
-Participants rated their artificial opponents differently between conditions (intervention vs control) and games (pre- vs post-intervention).
-The players ratings submitted at the end of each game showed a main effect of Game-number on all attributes, with participants rating the second player as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result`) and more selfish(`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result`).
-We also find a main effect of Condition as participants in the intervention condition rated players higher than those in the control condition on cooperativeness (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("condition.f"))))$full_result`) and lower on selfishness (`r apa_print(pairs(emmeans::emmeans(self_mod, c("condition.f"))))$full_result`).
-There was no evidence for an interaction effect between Game-number and Condition on any of the attributes.
--->
-
-<!-- However, breaking down the interaction term by Condition, we find that participants rated the post-intervention player significantly lower on all positive attributes and higher on the negative one (selfish).
-There was no such difference in player ratings the control condition.
--->
+When asked during debrief whether they thought the investors they faced were Human or not, $40$% of participants thought they were either facing a human or were not sure of the nature of the opponent.
+Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behaviour.
 
@@
 We next asked whether the intervention had any discernible effect on participants' behaviour in a different, repeated Prisoner's Dilemma game.
-Predicting the probability of a cooperative action with a logistic mixed-effects regression model, with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, showed a decline in cooperation after defection by the other player, `r papaja::apa_print(ipd_mod)$full_result$phase`, but no evidence for a different cooperation rate in the intervention condition compared to the control condition, `r `r papaja::apa_print(ipd_mod)$full_result$condition_f`, or a different response to defection between the conditions, `r papaja::apa_print(ipd_mod)$full_result$condition_f_phase`.
+Predicting the probability of a cooperative action with a logistic mixed-effects regression model, with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, showed a decline in cooperation after defection by the other player, `r papaja::apa_print(ipd_mod)$full_result$phase`, but no evidence for a different cooperation rate in the intervention condition compared to the control condition, `r papaja::apa_print(ipd_mod)$full_result$condition_f`, or a different response to defection between the conditions, `r papaja::apa_print(ipd_mod)$full_result$condition_f_phase`.
 As such, there is no evidence that the intervention affected behaviour in this game.
 <!-- We also found no difference in cooperation rates post defection trial between conditions.-->
-
-## Self report and debrief questionnaires
-
-<!-- MS: This section doesn't say much.
-It could be reasonable to include questionnaire scores in the main analyses throughout (e.g.
-does BPD trait have an effect or moderate any other effects?
-IF not, a statement somewhere that the scales didn't have an effect, and showing results of accompanying analyses in SI would be fine -->
 
@@
 ```{r, include=FALSE}
-# Install the 'psych' package if you haven't already
+# Install the 'psych' package
 if (!requireNamespace("psych", quietly = TRUE)) {
@@
 
-We find no interaction effect of the questionnaire scores with the Condition variable, nor a main effect of the questionnaire scores on participants returns in the RTG.
-
 ```{r, include=FALSE}
@@
 ```
-
-When asked whether they thought their opponent was Human or not, $40$% of participants thought they were either facing a human or were not sure of the nature of the opponent.
-Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behaviour.
 
@@
 
+load("data/fittedSimple.RData")
+load("data/fittedCtrl.RData")
+load("data/fittedCoax.RData")
+load("data/fittedFullCtrst.RData")
+load("data/fittedPrePost.RData")
+load("data/newFull.RData")
+
+has_converged <- function(object, numeric = TRUE){
+  msg <- object@message
+  if(numeric) as.integer(grepl("converged", msg)) else 0
+}
+
+sapply(fittedSimple[2:7],has_converged)
+sapply(fittedCtrl[2:7],has_converged)
+sapply(fittedCoax[2:7],has_converged)
+sapply(fittedFullCtrst[2:7],has_converged)
+sapply(fittedPrePost[2:7],has_converged)
+sapply(newFull[2:7],has_converged)
+
+```
+
+```{r}
+
 # THE CODE BELOW WAS NOT USED; ALL CONVERGED. PUT IT HERE IN CASE IT IS NEEDED LATER ON.
 # library(depmixS4)
-# 
-# load("data/fittedSimple.RData")
-# load("data/fittedCtrl.RData")
-# load("data/fittedCoax.RData")
-# load("data/fittedFullCtrst.RData")
-# load("data/fittedPrePost.RData")
-# load("data/newFull.RData")
-# 
-# has_converged <- function(object, numeric = TRUE){
-#   msg <- object@message
-#   if(numeric) as.integer(grepl("converged", msg)) else 0
-# }
-# 
-# 
 # fit_until_convergence <- function(fitted_model, max_iterations=2) {
@@
 # 
-# 
-# sapply(fittedSimple[2:7],has_converged)
-# sapply(fittedCtrl[2:7],has_converged)
-# sapply(fittedCoax[2:7],has_converged)
-# sapply(fittedFullCtrst[2:7],has_converged)
-# sapply(fittedPrePost[2:7],has_converged)
-# sapply(newFull[2:7],has_converged)
-
 ```
@@
 Focussing on models with 5 latent states (which is the optimal number for the HMM-full model), likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCtrl[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCoax[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedPrePost[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
-This is consistent with state transitions differing both due to game number and condition.
+This is consistent with state transitions differing both due to game number and condition as can be seen in Figure \ref{fig:plotTransitionsDiscGaus}.
 
@@
 
-```{r postStatesBestMod,  echo=FALSE, fig.cap = "A: Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model.
+```{r postStatesBestModOld,  echo=FALSE, fig.cap = "A: Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model.
 The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social.
@@
 
-ggpubr::ggarrange(trusteeHMMPlot , postHMM , nrow=2, ncol=1,labels = c("A", "B"),common.legend = FALSE)
+# ggpubr::ggarrange(trusteeHMMPlot , postHMM , nrow=2, ncol=1,labels = c("A", "B"),common.legend = FALSE)
+
+```
+
+```{r postStatesBestMod,  echo=FALSE, fig.cap = "Distribution of posterior trustee states post manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.", fig.align="center", fig.height = 4}
+
+postHMM
 
@@
 
-Focusing on the best-fitting 5-state HMM-full model, we used a local decoding procedure to assign observations (participants' returns on trials) to latent states.
+Taking the best-fitting 5-state HMM-full model, we used a local decoding procedure to assign observations (participants' returns on trials) to latent states.
 The states are ordered by expected return, with state 1 having the lowest mean return and state 5 the highest.
-Figure \ref{fig:postStatesBestMod}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
+Figure \ref{fig:postStatesBestMod} shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
 For instance, in round 5, state 1 was the most likely posterior state for only $7$% of participants in the intervention condition compared to $24$% in the control condition ($\chi^2(1) = 8.26, p < 0.01$).
@@
 
-In this experiment, human participants took the role of trustee in a repeated trust game (RTG) where they faced artificial computer agents who's behaviour was partly determined by participants' returns.
+In this experiment, human participants took the role of the trustee in a repeated trust game (RTG) where they faced artificial computer agents who's behaviour was partly determined by participants' returns.
 The behaviour of the artificial investors was determined by a 3-state hidden Markov model (HMM), which was estimated from the behaviour of humans in the RTG in prior research.
@@
 The aim of the cognitive intervention was to articulate the potential unwanted effects of acting on impulse after a transgressive action from the investor in the form of a one-off low investment.
-After the intervention, participants send back higher returns compared to before the intervention, and did not decrease their returns after a transgressive action like participants in the control condition did.
+After the intervention, participants sent back higher returns compared to before the intervention, and did not decrease their returns after a transgressive action like participants in the control condition did.
 The overall higher returns after the intervention occurred despite participants' emotional reactions to the investments remaining largely the same as before the intervention.
@@
 This view was used to justify computational psychiatry's difficulty in establishing differential and reliable predictors of likely treatment response [@hitchcock_computational_2022].
-<!-- MS: how do we know participants are healthy?
--->As we found heterogeneity in reactions to a relatively explicit intervention by relatively healthy participants from the general population.
-is itself heterogeneous as we have shown in this experiment, then the issue of variable treatment responses might the result of the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself.
+Here, we found heterogeneity in reaction to a relatively explicit intervention by a sample of participants from the general population.
+This suggests that the issue of variable treatment responses may result from the interaction of two sources of variability: the phenotyping of the disorder as well as the phenomenological aspects of the intervention itself.
 As such, a rigorous exploration of the determinants of inter-individual differences to an intervention in the general patient population is required.

### 2023-08-14 supplement.Rmd
cleaning up MS edits

@@
 ---
-title: "Supplement"
+title: "Supplementary Information"
 # author: "Ismail Guennouni"
-date: "2023-04-28"
+#date: "2023-04-28"
 output: pdf_document
@@
 Theories of social dysfunction in BPD have focused on dysfunction in the patients' mentalising ability [@allen_handbook_2006-1] as well as difficulties in emotional regulation [@rudge_mechanisms_2020].
-The questionnaires we included in the experiment tried to assess borderline traits (PAI-BOR), emotional regulation capabilities (DERS) and mentalising ability (RFQ8).
+The questionnaires we included in the experiment tried to assess borderline traits (PAI-BOR; @morey_personality_1991), emotional regulation capabilities (DERS; @gratz_multidimensional_2004) and mentalising ability (RFQ8; @fonagy_development_2016).
 As such, we test for any association between scores in these questionnaires and the effect of the intervention.To analyse responses,  we fit a linear mixed effect model to the percentage return of trustees with fixed effects for Condition (intervention or control), Game-number (pre or post manipulation), Investment, and questionnaire score as well as all interactions between the fixed effects.

### 2023-08-14 article.Rmd
modifs article format

@@
 author:
-  - Ismail Guennouni
-  - Quentin Huys
-  - Samuel Dupret
-  - Maarten Speekenbrink
-
-# - name: Ismail Guennouni
-#   address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
-#   email: i.guennouni.17@ucl.ac.uk
-# 
-# - name: Maarten Speekenbrink
-#   address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
-#   email: m.speekenbrink@ucl.ac.uk
-# 
-# - name: Quentin Huys
-#   address: Max Planck Institute of Computational Psychiatry
-#   email: q.huys@ucl.ac.uk
-# 
-# - name: Samuel Dupret
-#   address: HLI
-#   email: sam.dupret@ucl.ac.uk
+  "Ismail Guennouni^1^, Quentin Huys^2^, Samuel Dupret^1^, Maarten Speekenbrink^1^"
+
 keywords:
@@
    toc: false
+---
+\small  
+^1^ *Department of Experimental Psychology, Division of Psychology and Language Sciences, UCL*.  
+^2^ *Division of Psychiatry and Max Planck Centre for Computational Psychiatry and Ageing Research, Queen Square Institute of Neurology, UCL.*
+
 ---
@@
 The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years.
-Participants were paid a fixed fee of £5 plus a bonus payment dependent on their performance.<!--MS: state average bonus--> The experiment had a 2 (Condition: Intervention or Control) by 3 (Game: Trust-Game Pre Intervention, Trust-Game Post Intervention, Prisoner's Dilemma Post Intervention) design, with repeated measures on the second factor.
+Participants were paid a fixed fee of £5 plus a bonus payment dependent on their performance that averaged £0.71.
+The experiment had a 2 (Condition: Intervention or Control) by 3 (Game: Trust-Game Pre Intervention, Trust-Game Post Intervention, Prisoner's Dilemma Post Intervention) design, with repeated measures on the second factor.
 Participants were randomly assigned to one of the two levels of the first factor.
@@
 
-The strategy of the computerised investor was modelled on behaviour of human investors in a 10-round RTG <!-- reference to data -->.
+The strategy of the computerised investor was modelled on behaviour of human investors in a 10-round RTG [@king-casas_rupture_2008].
 Using this data, we estimated a hidden Markov model (HMM) on investors' behaviour with three latent states, reflecting "low-trust", "medium-trust", or "high-trust".
@@
 
-### Repeated Prisoner's Dillema
+### Repeated Prisoner's Dilemma
 
@@
 
-```{r, include=FALSE}
+```{r, include=FALSE, cache=TRUE}
 
@@
 As such, there is no evidence that the intervention affected behaviour in this game.
-<!-- We also found no difference in cooperation rates post defection trial between conditions.-->
 
@@
 But this is driven by the magnitude of their returns, not by a change in the strategy of the investor.
-Finally, as participants rated the first and second HMM agent similarly on attributes such as cooperativeness and trust, the increased returns are unlikely to be the result of a more favourable evaluation of the investor.
+Finally, as there were no differences between conditions in how participants rated the first and second HMM agent on attributes such as cooperativeness and trust, the increased returns are unlikely to be the result of a more favourable evaluation of the investor.
 Rather, we find it most likely that the increased returns are due to participants inferring from the intervention that pro-social and trustworthy behaviour may generally motivate the investor to send high investments, which can provide more beneficial outcomes to them in the long run.

### 2023-08-28 article.Rmd
re-fit HMM models using initial values from simpler models

@@
 ```{r dataLoad, include=FALSE }
-d_finished <- readRDS("data/d_finished.RDS")
+# d_finished <- readRDS("data/d_finished.RDS")
+# d_finished$id <- NULL
+# saveRDS(d_finished, file="data/d_anonym.RDS")
+
+d_finished <- readRDS("data/d_anonym.RDS")
 ```
@@
 avg_ret_df <- d_finished %>%
-  dplyr::select(id, condition.f,roundType,investment,returns,roundNum,gameNum.f,BPD_trait,PBOR_score,DERS_score,RFQ_c,RFQ_u) %>% 
+  dplyr::select(playerId, condition.f,roundType,investment,returns,roundNum,gameNum.f,BPD_trait,PBOR_score,DERS_score,RFQ_c,RFQ_u) %>% 
   mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing"))%>%
@@
   # Creating Quartiles of % returns by participant over BOTH TRUST GAMES
-  group_by(id) %>% 
+  group_by(playerId) %>% 
   mutate(mean_pct_ret = mean(ret_pct), mean_abs_ret = mean(returns), mean_inv = mean(investment)) %>%
@@
 
-mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), avg_ret_df, REML= TRUE, method="KR")
+mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| playerId), avg_ret_df, REML= TRUE, method="KR")
 anova(mod_returns_pct)
@@
 ```
-
-<!-- MS: double check statistics; I get different df when using KR in mixed -->
 
@@
 ```{r, include=FALSE, cache=TRUE}
-mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| id), avg_ret_df, method="KR")
+mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| playerId), avg_ret_df, method="KR")
 summary(mod_invs)
@@
 
-mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| id), pre_int_data, REML= TRUE, method="KR")
+mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| playerId), pre_int_data, REML= TRUE, method="KR")
 anova(mod_returns_pre)
@@
 
-mod_postcoax_trust <- mixed(ret_pct ~ gameNum.f*condition.f*inv_scaled  + ( 1 + gameNum.f|id), post_coax_data)
+mod_postcoax_trust <- mixed(ret_pct ~ gameNum.f*condition.f*inv_scaled  + ( 1 + gameNum.f|playerId), post_coax_data)
 anova(mod_postcoax_trust)
@@
   mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>% 
-  dplyr::select(id,roundType,condition.f,contains("emotionGrid")) %>% 
+  dplyr::select(playerId,roundType,condition.f,contains("emotionGrid")) %>% 
   dplyr::filter(roundType=="trust") %>% dplyr::select (-contains(".y") ) %>% pivot_longer(cols=contains(".x"), names_to = c("gameNumber","roundNum"), names_pattern ="return_trust_emotionGrid_(.*)_(.*)[.]x", values_to = "emo_coord_x") %>%
@@
   mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>%
-  dplyr::select(id,roundType,condition.f,contains("emotionGrid")) %>% 
+  dplyr::select(playerId,roundType,condition.f,contains("emotionGrid")) %>% 
   dplyr::filter(roundType=="trust") %>% dplyr::select(-contains(".x") ) %>% pivot_longer(cols=contains(".y"), names_to = c("gameNumber","roundNum"), names_pattern ="return_trust_emotionGrid_(.*)_(.*)[.]y", values_to = "emo_coord_y") %>%
@@
 # put emotions in one dataframe
-full_emo <- full_join(emo.x,emo.y, by=c("id", "gameNumber","roundNum","roundType", "condition.f"))  %>% 
+full_emo <- full_join(emo.x,emo.y, by=c("playerId", "gameNumber","roundNum","roundType", "condition.f"))  %>% 
   mutate(roundNum=as.numeric(as.character(roundNum))) %>% 
@@
 #merge with returns dataframe
-full_dat <- full_join(avg_ret_df, full_emo, by = c("id","condition.f","gameNum.f","roundNum" )) %>% filter(complete.cases(.))
+full_dat <- full_join(avg_ret_df, full_emo, by = c("playerId","condition.f","gameNum.f","roundNum" )) %>% filter(complete.cases(.))
 #nrow(full_dat)
@@
   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
-  scale_color_manual(name = " ", values = colors, labels = c("Emotion arousal", "Investment", "Emotion valence")) +
+  scale_color_manual(name = "", values = colors, labels = c("Arousal", "Investment", "Emotion valence")) +
   scale_linetype_manual(values = c("a_Pre" = "dotted", "b_Post" = "solid"), labels = c("Pre", "Post")) +
@@
 
-mod_emo_x <- mixed( emo_scaled_x ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), data=datCoax, method="KR")
+mod_emo_x <- mixed( emo_scaled_x ~ gameNum.f*scale(investment) + (1 + gameNum.f| playerId), data=datCoax, method="KR")
 summary(mod_emo_x)
@@
 
-mod_emo_y <- mixed( emo_scaled_y ~ gameNum.f*scale(investment) + (1 + gameNum.f| id), datCoax )
+mod_emo_y <- mixed( emo_scaled_y ~ gameNum.f*scale(investment) + (1 + gameNum.f| playerId), datCoax )
 summary(mod_emo_y)
@@
 # Pivot longer ratings on each attribute 
-df_coop <- d_finished %>% dplyr::select(id,condition.f,contains("cooperative")) %>%  
+df_coop <- d_finished %>% dplyr::select(playerId,condition.f,contains("cooperative")) %>%  
   pivot_longer(cols=contains("cooperative"), names_to = c("gameNumber"), names_pattern ="rating_cooperative_(.*)", values_to = "rating_coop") %>% distinct()
 
-df_selfish <- d_finished %>% dplyr::select(id,condition.f,contains("selfish")) %>% 
+df_selfish <- d_finished %>% dplyr::select(playerId,condition.f,contains("selfish")) %>% 
   pivot_longer(cols=contains("selfish"), names_to = c("gameNumber"), names_pattern ="rating_selfish_(.*)", values_to = "rating_selfish") %>% distinct
 
-df_trustworthy <- d_finished %>% dplyr::select(id,condition.f,contains("trustworthy")) %>% 
+df_trustworthy <- d_finished %>% dplyr::select(playerId,condition.f,contains("trustworthy")) %>% 
   pivot_longer(cols=contains("trustworthy"), names_to = c("gameNumber"), names_pattern ="rating_trustworthy_(.*)", values_to = "rating_trustworthy") %>% distinct()
 
-df_friendly  <-  d_finished %>% dplyr::select(id,condition.f,contains("friendly")) %>% 
+df_friendly  <-  d_finished %>% dplyr::select(playerId,condition.f,contains("friendly")) %>% 
   pivot_longer(cols=contains("friendly"), names_to = c("gameNumber"), names_pattern ="rating_friendly_(.*)", values_to = "rating_friendly") %>%  distinct()
@@
 datRatings <- list(df_coop, df_selfish,df_trustworthy, df_friendly) %>% 
-              reduce(full_join, by=c('id','gameNumber','condition.f') ) %>% 
+              reduce(full_join, by=c('playerId','gameNumber','condition.f') ) %>% 
               mutate(gameNum.f = factor(gameNumber,labels = c("pre","post"),levels=c("1","2")))
@@
 # Cooperative
-coop_mod <- mixed(rating_coop ~ gameNum.f*condition.f + (1 | id), datRatings)
+coop_mod <- mixed(rating_coop ~ gameNum.f*condition.f + (1 | playerId), datRatings)
 summary(coop_mod)
@@
 #Selfish
-self_mod <- mixed(rating_selfish ~ gameNum.f*condition.f + (1 | id), datRatings)
+self_mod <- mixed(rating_selfish ~ gameNum.f*condition.f + (1 | playerId), datRatings)
 summary(self_mod)
@@
 #Trustworthy 
-trust_mod <- mixed(rating_trustworthy ~ gameNum.f*condition.f + (1 | id), datRatings)
+trust_mod <- mixed(rating_trustworthy ~ gameNum.f*condition.f + (1 | playerId), datRatings)
 summary(trust_mod)
@@
 #Friendly
-friend_mod <- mixed(rating_friendly ~ gameNum.f*condition.f + (1 | id), datRatings)
+friend_mod <- mixed(rating_friendly ~ gameNum.f*condition.f + (1 | playerId), datRatings)
 summary(friend_mod)
@@
   mutate( condition.f = fct_recode(condition.f, "intervention" = "coaxing")) %>%
-  dplyr::select(id, condition.f,roundType,roundNum, PDoption,PDchoice, AiChoicePD,gameNum.f, PBOR_score) %>% 
+  dplyr::select(playerId, condition.f,roundType,roundNum, PDoption,PDchoice, AiChoicePD,gameNum.f, PBOR_score) %>% 
                           filter(roundType == "PD",!is.na(roundNum)) %>% 
@@
 
-ipd_mod <- mixed(coop ~ condition.f * phase + (1 |id), data= PD_data, method = "LRT", family= "binomial") 
+ipd_mod <- mixed(coop ~ condition.f * phase + (1 |playerId), data= PD_data, method = "LRT", family= "binomial") 
 summary(ipd_mod)
@@
 # these are repeated measures here, so not independent. need to used mixed effects model.
-mixed_PBOR_pct <- afex::mixed(ret_pct ~ PBOR_scaled*gameNum.f*condition.f + investment + (1 | id ), data= avg_ret_df)
+mixed_PBOR_pct <- afex::mixed(ret_pct ~ PBOR_scaled*gameNum.f*condition.f + investment + (1 | playerId ), data= avg_ret_df)
 summary(mixed_PBOR_pct)
@@
 ## Looking at difference between average returns across rounds
-#scoreDAT <- avg_ret_df %>% dplyr::select(id,diff_pctRet, PBOR_scaled, DERS_scaled, RFQ_c, condition.f) %>% unique()
+#scoreDAT <- avg_ret_df %>% dplyr::select(playerId,diff_pctRet, PBOR_scaled, DERS_scaled, RFQ_c, condition.f) %>% unique()
 
@@
 
-questionnaires <- avg_ret_df %>% group_by(id) %>% dplyr::select(PBOR_score,DERS_score,RFQ_c) %>% unique() %>% ungroup()
+questionnaires <- avg_ret_df %>% group_by(playerId) %>% dplyr::select(PBOR_score,DERS_score,RFQ_c) %>% unique() %>% ungroup()
 # Perform EFA
@@
 # Removing player whose return was not properly recorded by data (NA in one of the rounds) so as to run depmixS4
-id_with_na <-  as.character(avg_ret_df[is.na(avg_ret_df$returns),"id"])
+id_with_na <-  as.character(avg_ret_df[is.na(avg_ret_df$returns),"playerId"])
 
@@
 avg_ret_df <- avg_ret_df %>%
-  filter(id != id_with_na) %>% 
+  filter(playerId != id_with_na) %>% 
   mutate(game_id = rep(1:636, each=15)) %>%
@@
 
+# load("data/fittedSimple.RData")
+# load("data/fittedCtrl.RData")
+# load("data/fittedCoax.RData")
+# load("data/fittedFullCtrst.RData")
+# load("data/fittedPrePost.RData")
+# load("data/newFull.RData")
+# 
+# has_converged <- function(object, numeric = TRUE){
+#   msg <- object@message
+#   if(numeric) as.integer(grepl("converged", msg)) else 0
+# }
+# 
+# 
+# sapply(fittedSimple[2:7],has_converged)
+# sapply(fittedCtrl[2:7],has_converged)
+# sapply(fittedCoax[2:7],has_converged)
+# sapply(fittedFullCtrst[2:7],has_converged)
+# sapply(fittedPrePost[2:7],has_converged)
+# sapply(newFull[2:7],has_converged)
+
+```
+
+```{r, include=F}
+
+# Fitting "Ctrl" models with initial parameters from the fitted "Simple" model.
+
+# newCtrl <- fittedCtrl
+# for (ns in n_state_min : n_state_max){
+# 
+#   fmod <- fittedSimple[[ns]]
+#   origin_pars <- getpars(fmod)
+#   numCovIn <- 2 
+#   numCovTr <- 2
+# 
+#   # create a new vector which has the right number of pars for the initial state probabilities
+#   new_pars <- c(origin_pars[1:(ns*numCovIn)])
+#   # Build a new vector for transition probabilities, leaving space for new contrasts. "from" is state we are transitioning from
+#   for(from in 1:ns) {
+#   mat <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
+#   #print(mat)
+#   new_mat <- mat[,c(1:2,2,2)]
+#   new_pars <- c(new_pars,as.numeric(new_mat))
+#   }
+#   #Concatenate the new vectors with the old vector of  "response parameters" 
+#   new_pars <- c(new_pars,origin_pars[(ns*numCovIn + 1 + (ns - 1)*numCovTr*ns + numCovTr*ns):length(origin_pars)])
+# 
+#   # Set initial parameters of more complex model as the matrix of parameters we created from the simpler model and fit it. 
+#   newCtrl[[ns]] <- setpars(newCtrl[[ns]],new_pars)
+#   newCtrl[[ns]] <- fit(newCtrl[[ns]], emcontrol= em.control(maxit = 1000,random.start = FALSE))
+# }
+# 
+# save(newCtrl, file="data/newCtrl.RData")
+
+```
+
+```{r, include=F}
+
+# Fitting "Coax" models with initial parameters from the fitted "Simple" model.
+
+# newCoax <- fittedCoax
+# for (ns in n_state_min : n_state_max){
+# 
+#   fmod <- fittedSimple[[ns]]
+#   origin_pars <- getpars(fmod)
+#   numCovIn <- 2 
+#   numCovTr <- 2
+# 
+#   # create a new vector which has the right number of pars for the initial state probabilities
+#   new_pars <- c(origin_pars[1:(ns*numCovIn)])
+#   # Build a new vector for transition probabilities, leaving space for new contrasts. "from" is state we are transitioning from
+#   for(from in 1:ns) {
+#   mat <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
+#   #print(mat)
+#   new_mat <- mat[,c(1:2,2,2)]
+#   new_pars <- c(new_pars,as.numeric(new_mat))
+#   }
+#   #Concatenate the new vectors with the old vector of  "response parameters" 
+#   new_pars <- c(new_pars,origin_pars[(ns*numCovIn + 1 + (ns - 1)*numCovTr*ns + numCovTr*ns):length(origin_pars)])
+# 
+#   # Set initial parameters of more complex model as the matrix of parameters we created from the simpler model and fit it. 
+#   newCoax[[ns]] <- setpars(newCoax[[ns]],new_pars)
+#   newCoax[[ns]] <- fit(newCoax[[ns]], emcontrol= em.control(maxit = 1000,random.start = FALSE))
+# }
+# 
+# save(newCoax, file="data/newCoax.RData")
+
+```
+
+```{r, include=F}
+
+# Fitting "Prepost" models with initial parameters from the fitted "Simple" model.
+
+# newPrePost <- fittedPrePost
+# for (ns in n_state_min : n_state_max){
+# 
+#   fmod <- fittedSimple[[ns]]
+#   origin_pars <- getpars(fmod)
+#   numCovIn <- 2 
+#   numCovTr <- 2
+# 
+#   # create a new vector which has the right number of pars for the initial state probabilities
+#   new_pars <- c(origin_pars[1:(ns*numCovIn)])
+#   # Build a new vector for transition probabilities, leaving space for new contrasts. "from" is state we are transitioning from
+#   for(from in 1:ns) {
+#   mat <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
+#   #print(mat)
+#   new_mat <- mat[,c(1:2,2,2)]
+#   new_pars <- c(new_pars,as.numeric(new_mat))
+#   }
+#   #Concatenate the new vectors with the old vector of  "response parameters" 
+#   new_pars <- c(new_pars,origin_pars[(ns*numCovIn + 1 + (ns - 1)*numCovTr*ns + numCovTr*ns):length(origin_pars)])
+# 
+#   # Set initial parameters of more complex model as the matrix of parameters we created from the simpler model and fit it. 
+#   newPrePost[[ns]] <- setpars(newPrePost[[ns]],new_pars)
+#   newPrePost[[ns]] <- fit(newPrePost[[ns]], emcontrol= em.control(maxit = 1000,random.start = FALSE))
+# }
+# 
+# save(newPrePost, file="data/newPrePost.RData")
+
+```
+
+```{r, include=FALSE}
+
+# For initialising newFULL, take the model with the highest likelihood in each num states:
+
+```
+
+```{r, include=FALSE}
+
 load("data/fittedSimple.RData")
@@
 load("data/fittedPrePost.RData")
+
+load("data/newCtrl.RData")
+load("data/newCoax.RData")
+load("data/newPrePost.RData")
 load("data/newFull.RData")
 
-has_converged <- function(object, numeric = TRUE){
-  msg <- object@message
-  if(numeric) as.integer(grepl("converged", msg)) else 0
-}
-
-sapply(fittedSimple[2:7],has_converged)
-sapply(fittedCtrl[2:7],has_converged)
-sapply(fittedCoax[2:7],has_converged)
-sapply(fittedFullCtrst[2:7],has_converged)
-sapply(fittedPrePost[2:7],has_converged)
-sapply(newFull[2:7],has_converged)
-
-```
-
-```{r}
-
-# THE CODE BELOW WAS NOT USED; ALL CONVERGED. PUT IT HERE IN CASE IT IS NEEDED LATER ON.
-# library(depmixS4)
-# fit_until_convergence <- function(fitted_model, max_iterations=2) {
-#   cat(fitted_model@nstates)
-#   iterations <- 0
-#   converged <- has_converged(fitted_model)
-#   
-#   while (!converged && iterations < max_iterations) {
-#     # Use parameters from the fitted model as initial parameters
-#     initial_params <- getpars(fitted_model)
-#     new_model <- setpars(fitted_model, initial_params)
-#     
-#     # Refit the model
-#     fitted_model <- fit(new_model)
-#     converged <- has_converged(fitted_model)
-#     iterations <- iterations + 1
-#   }
-#   
-#   if (converged) {
-#     cat("NS = ", fitted_model@nstates,"Convergence has been reached.\n")
-#     flush.console()
-#     return(fitted_model)
-#   } else {
-#     cat("Maximum iterations reached. Convergence has not been reached.\n")
-#     flush.console()
-#     return(fitted_model)
-#   }
-# }
-# 
-# 
-# run_parallel_fitting <- function(mods_vec,num_cores = 5) {
-#   # Set up the parallel backend
-#   my.cluster <- parallel::makeCluster(num_cores, type = "PSOCK")
-#   doParallel::registerDoParallel(cl = my.cluster)
-#   
-#   # Export the fit_until_convergence function to the workers
-#   parallel::clusterExport(my.cluster, "fit_until_convergence")
-#   parallel::clusterExport(my.cluster, "has_converged")
-# 
-#   # Run the loop in parallel using foreach
-#   converged_mods_vec <- foreach(mod = mods_vec, .packages = c("depmixS4"), .combine = "c") %dopar% {
-#     cat(mod@nstates)
-#     fit_until_convergence(mod)
-#   }
-# 
-#   # Stop the parallel backend
-#   parallel::stopCluster(my.cluster)
-#   return(converged_mods_vec)
-# }
-# 
-```
-
-```{r, include=FALSE}
-# # The full contrast model convergence was not attained. Here we use parameters of fitted PrePost model as initial values of the FullContrast model to speed up fitting and aim for faster convergence.
+```
+
+```{r, include=F}
+
+bestCtrl <- NULL
+# Loop through each index and select the model with the higher log-likelihood
+for(i in n_state_min : n_state_max) {
+  if(logLik(fittedCtrl[[i]]) > logLik(newCtrl[[i]])) {
+    bestCtrl[[i]] <- fittedCtrl[[i]]
+  } else {
+    bestCtrl[[i]] <- newCtrl[[i]]
+  }
+}
+
+bestCoax <- NULL
+# Loop through each index and select the model with the higher log-likelihood
+for(i in n_state_min : n_state_max) {
+  if(logLik(fittedCoax[[i]]) > logLik(newCoax[[i]])) {
+    bestCoax[[i]] <- fittedCoax[[i]]
+  } else {
+    bestCoax[[i]] <- newCoax[[i]]
+  }
+}
+
+bestPrePost <- NULL
+# Loop through each index and select the model with the higher log-likelihood
+for(i in n_state_min : n_state_max) {
+  if(logLik(fittedPrePost[[i]]) > logLik(newPrePost[[i]])) {
+    bestPrePost[[i]] <- fittedPrePost[[i]]
+  } else {
+    bestPrePost[[i]] <- newPrePost[[i]]
+  }
+}
+
+```
+
+```{r, include=FALSE}
+
+# # Here we use parameters of fitted PrePost model as initial values of the FullContrast model to check whether we can approach true maximal likelihood.
 
@@
 # 
-#   fmod <- fittedPrePost[[ns]]
+#   # Use the higher likelihood prepost model parameters as starting values to fit the newFull model.
+#   fmod <- bestPrePost[[ns]]
 #   origin_pars <- getpars(fmod)
@@
 #   mat <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
+#   print(mat)
 #   new_mat <- mat[,c(1:2,3,3,4,4)]
@@
 
-```{r, include=FALSE}
-
-load("data/fittedSimple.RData")
-load("data/fittedCtrl.RData")
-load("data/fittedCoax.RData")
-load("data/fittedFullCtrst.RData")
-load("data/fittedPrePost.RData")
-load("data/newFull.RData")
-
-BICs_simple <- BICs_Ctrl <- BICs_Coax <- BICs_FullCtrst <- BICs_PrePost <-  BICs_newFull <- list()
+```{r}
+
+bestFull <- NULL
+# Loop through each index and select the model with the higher log-likelihood
+for(i in n_state_min : n_state_max) {
+  if(logLik(fittedFullCtrst[[i]]) > logLik(newFull[[i]])) {
+    bestFull[[i]] <- fittedFullCtrst[[i]]
+  } else {
+    bestFull[[i]] <- newFull[[i]]
+  }
+}
+
+```
+
+```{r, include=F}
+
+BICs_simple <- BICs_Ctrl <- BICs_Coax <-  BICs_PrePost <-  BICs_Full <- list()
+
 for(i in n_state_min:n_state_max) {
   BICs_simple[[i]] <- BIC(fittedSimple[[i]])
-  BICs_Ctrl[[i]] <- BIC(fittedCtrl[[i]])
-  BICs_Coax[[i]] <- BIC(fittedCoax[[i]]) 
-  BICs_FullCtrst[[i]] <- BIC(fittedFullCtrst[[i]]) 
-  BICs_PrePost[[i]] <- BIC(fittedPrePost[[i]]) 
-  BICs_newFull[[i]] <- BIC(newFull[[i]])
-
-}
-
-print("SIMPLE HMM models")
-BICs_simple
-
-print("HMM with contrast on post Control vs others")
-BICs_Ctrl
-
-print("HMM with contrast on post Coax vs others")
-BICs_Coax
-
-print("HMM with Pre vs Post Contrast")
-BICs_PrePost
-
-print("HMM with contrast levels Pre, Post Control and Post Coaxing")
-BICs_FullCtrst
-
-print("HMM with contrast levels Pre, Post Control and Post Coaxing, new fitting")
-BICs_newFull
-
-df_bics <- cbind(2:7,as.numeric(BICs_simple[2:7]), as.numeric(BICs_Ctrl[2:7]),as.numeric(BICs_Coax[2:7]), as.numeric(BICs_PrePost[2:7]), as.numeric(BICs_newFull[2:7]))
+  BICs_Ctrl[[i]] <- BIC(bestCtrl[[i]])
+  BICs_Coax[[i]] <- BIC(bestCoax[[i]])
+  BICs_PrePost[[i]] <- BIC(bestPrePost[[i]])
+  BICs_Full[[i]] <- BIC(bestFull[[i]])
+
+}
+
+# print("SIMPLE HMM models")
+# BICs_simple
+# 
+# print("HMM with contrast on post Control vs others")
+# BICs_Ctrl
+# 
+# print("HMM with contrast on post Coax vs others")
+# BICs_Coax
+# 
+# print("HMM with Pre vs Post Contrast")
+# BICs_PrePost
+# 
+# print("HMM with contrast levels Pre, Post Control and Post Coaxing")
+# BICs_FullCtrst
+# 
+# print("HMM with contrast levels Pre, Post Control and Post Coaxing, new fitting")
+# BICs_newFull
+
+df_liks <- cbind(2:7,sapply(fittedSimple[2:7], logLik), sapply(bestCtrl[2:7], logLik), sapply(bestCoax[2:7], logLik), sapply(bestPrePost[2:7], logLik), sapply(bestFull[2:7], logLik))
+df_liks
+
+df_bics <- cbind(2:7,as.numeric(BICs_simple[2:7]), as.numeric(BICs_Ctrl[2:7]),as.numeric(BICs_Coax[2:7]), as.numeric(BICs_PrePost[2:7]), as.numeric(BICs_Full[2:7]))
 df_bics
@@
 library(kableExtra)
+
+# Function to make cell with lowest value bold 
+bold_min <- function(x) {
+  min_val = min(x)
+  sapply(x, function(val) {
+    if (val == min_val) {
+      cell_spec(format(val, digits=4, nsmall=0, big.mark=","), "latex", bold = TRUE)
+    } else {
+      format(val, digits=4, nsmall=0, big.mark=",")
+    }
+  })
+}
+
+# Function to make cell with highest value bold 
+bold_max <- function(x) {
+  max_val = max(x)
+  sapply(x, function(val) {
+    if (val == max_val) {
+      cell_spec(format(val, digits=4, nsmall=0, big.mark=","), "latex", bold = TRUE)
+    } else {
+      format(val, digits=4, nsmall=0, big.mark=",")
+    }
+  })
+}
 
@@
 
-```{r table-BICs-coax, include =FALSE, warning = FALSE, echo=FALSE, ft.align="center", tab.id='table-BICs-coax', label='table-BICs-coax'}
-
-data.frame(df_bics) %>% 
-  `colnames<-` (c("Number of states","HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost","HMM-full")) %>%
-  mutate_if(is.numeric, format, digits=4,nsmall = 0, big.mark = ",") %>% 
-  knitr::kable(.,booktabs = TRUE,
-  caption = 'Table of BICs for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>% kable_styling(latex_options="scale_down")
+```{r table-BICs-coax, include =FALSE, warning = FALSE, echo=FALSE, ft.align="center", tab.playerId='table-BICs-coax', label='table-BICs-coax'}
+
+# data.frame(df_bics) %>% 
+#   `colnames<-` (c("Number of states","HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost","HMM-full")) %>%
+#   mutate_if(is.numeric, format, digits=4,nsmall = 0, big.mark = ",") %>% 
+#   knitr::kable(.,booktabs = TRUE,
+#   caption = 'Table of BICs for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>% kable_styling(latex_options="scale_down")
+
+# Ensure df_bics is a data frame
+df_bics <- as.data.frame(df_bics)
+
+df_bics %>%
+  `colnames<-` (c("Number of states", "HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost", "HMM-full")) %>%
+  mutate_at(vars(-`Number of states`), bold_min) %>%
+  knitr::kable(., escape = FALSE, booktabs = TRUE,
+               caption = 'Table of BICs for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>%
+  kable_styling(latex_options="scale_down")
+
+df_liks <- as.data.frame(df_liks)
+
+df_liks %>%
+  `colnames<-` (c("Number of states", "HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost", "HMM-full")) %>%
+  mutate_at(vars(-`Number of states`), bold_max) %>%
+  knitr::kable(., escape = FALSE, booktabs = TRUE,
+               caption = 'Table of likelihoods for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>%
+  kable_styling(latex_options="scale_down")
+
 ```
@@
 logLik(fittedSimple[[5]])
-logLik(fittedCtrl[[5]])
-logLik(fittedCoax[[5]])
-logLik(fittedPrePost[[5]])
+logLik(bestCtrl[[5]])
+logLik(bestCoax[[5]])
+logLik(bestPrePost[[5]])
 # logLik(fittedFullCtrst[[5]])
-logLik(newFull[[5]])
+logLik(bestFull[[5]])
 
 # Nested model comparison for 5 states, with and without intervention contrast. llratio test shows no effect, meaning interaction term addition does not change goodness of fit of model. 
-llratio(newFull[[5]], fittedSimple[[5]])
-
-llratio(fittedCtrl[[5]],fittedSimple[[5]])
-llratio(fittedCoax[[5]],fittedSimple[[5]])
-llratio(fittedPrePost[[5]],fittedSimple[[5]])
-
-llratio(newFull[[5]],fittedCtrl[[5]])
-llratio(newFull[[5]],fittedCoax[[5]])
-llratio(newFull[[5]],fittedPrePost[[5]])
-
-llratio(newFull[[6]],fittedCtrl[[6]])
-llratio(newFull[[6]],fittedCoax[[6]])
-llratio(newFull[[6]],fittedPrePost[[6]])
+llratio(bestFull[[5]], fittedSimple[[5]])
+
+llratio(bestCtrl[[5]],fittedSimple[[5]])
+llratio(bestCoax[[5]],fittedSimple[[5]])
+llratio(bestPrePost[[5]],fittedSimple[[5]])
+
+llratio(bestFull[[5]],bestCtrl[[5]])
+llratio(bestFull[[5]],bestCoax[[5]])
+llratio(bestFull[[5]],bestPrePost[[5]])
+
+# llratio(bestFull[[6]],bestCtrl[[6]])
+# llratio(bestFull[[6]],bestCoax[[6]])
+# llratio(bestFull[[6]],bestPrePost[[6]])
 ```
@@
 
-Focussing on models with 5 latent states (which is the optimal number for the HMM-full model), likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCtrl[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCoax[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedPrePost[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
+Focusing on models with 5 latent states (which is the optimal number for the HMM-full model), likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCtrl[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCoax[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestPrePost[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$).
 This is consistent with state transitions differing both due to game number and condition as can be seen in Figure \ref{fig:plotTransitionsDiscGaus}.
@@
 <!-- We start by comparing HMM-full with HMM-inv.
-We find that HMM-full fits the data better than HMM-inv ($\chi^2(84) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
-Likewise HMM-ctrl fits better than HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedCtrl[[5]]))) , 2)`$, $p < .001$).
-The same is true for HMM-coax compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedCoax[[5]]))) , 2)`$, $p < .001$) and HMM-prepost compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(fittedPrePost[[5]]))) , 2)`$, $p < .001$).
+We find that HMM-full fits the data better than HMM-inv ($\chi^2(84) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$).
+Likewise HMM-ctrl fits better than HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(bestCtrl[[5]]))) , 2)`$, $p < .001$).
+The same is true for HMM-coax compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(bestCoax[[5]]))) , 2)`$, $p < .001$) and HMM-prepost compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(bestPrePost[[5]]))) , 2)`$, $p < .001$).
 HMM-inv being the worst fitting model compared to the others indicates the existence of differentiated behavior pre vs post manipulation and/or between the control and intervention groups.
@@
 
-<!-- Using likelihood ratio tests, we find that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCtrl[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedCoax[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(fittedPrePost[[5]])) - (-2*as.numeric(logLik(newFull[[5]]))) , 2)`$, $p < .001$).
+<!-- Using likelihood ratio tests, we find that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCtrl[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCoax[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestPrePost[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$).
 This is consistent with a differentiated behavior of the trustees between all three groups: the post-intervention group, the post-control group and the pre-manipulation group.
@@
 ```{r, include=FALSE}
-tr_fdmod_5 <- order_mod_gauss(newFull[[5]])
+tr_fdmod_5 <- order_mod_gauss(bestFull[[5]])
 ```
@@
 
-<!-- Using the best fitting model according to likelihood ratio tests (HMM-full), Figure \ref{fig:trusteeHMMPlot} shows the distribution of the participants' returns conditional on the latent state they are in.
-The states are ordered based on the mean of the Gaussian distribution fitted to the response (percentage return).
-State 1 represents the state in which the returns have have the lowest underlying mean, and state 5 is the state in which the returns have the highest underlying mean.
-The higher the state number the more pro-social the policy adopted.
-More specifically, state 1 can be thought of as a non-cooperative state in which returns are low and close to 0, meaning that the trustee is keeping most of the tripled investment.
-State 2 is a state where the average return is around the investment sent and can be interpreted as a cautious state in which the return on trust is small.
-States 3, 4 and 5 are increasingly cooperative states.
-For instance, in state 5, the average return is close to two thirds of the tripled investment, meaning the trustee is keeping an amount similar to the investment that was sent and returning to the investor double the investment.
--->
-
-<!-- Figure \ref{fig:plotTransitionsDiscGaus} shows the transition between states as a function of the investment received for each group (pre-manipulation, post-control and post-intervention) using results from the best fitting model: HMM-full.
-The best fitting HMM model has multiple states and a high number of parameters.
-We can nonetheless focus on particular states linked to the breakdown and repair of cooperation.
-For instance, focusing on the transition functions to state 1 (the lowest return state with returns close to 0) from higher return states, we can compare the  post-control group to the post-intervention group.
-The red line representing the probability of transitioning to the low-return state 1 when the investment is close to 0 is lower in the intervention group compared to the control group when the trustee is in a relatively pro-social state (states 3 to 5).
-This is pointing towards more "forgiving" behavior where participants in the intervention group were less likely to transition to this anti-social state compared to the control group.
--->
-
-<!-- MS: I think Figure 6 can be moved to the supplement and perhaps Figure 6.A too. -->
-
-<!-- Using the HMM-full model, we can retrieve participants' return distributions based on their latent states (Figures \ref{fig:postStatesBestMod}.A) and transition probabilities between these states (Figure \ref{fig:plotTransitionsDiscGaus}).
-The states are ranked by mean return, with State 1 having the lowest mean return and State 5 the highest.
-A higher state number indicates a more pro-social policy.
-We focused on states related to cooperation's breakdown and repair.
-We compared the transition probabilities between states when the investment is low for post-control and post-intervention groups.
-Figure \ref{fig:plotTransitionsDiscGaus} suggests that the intervention group is more forgiving of low investments, as they are less likely to shift to an anti-social state when faced with defection compared to the control group.
--->
-
 ```{r, include=FALSE}
@@
     to = rep(1:ns, each=100),
-    investment = seq(0,8,length=100),
+    investment = seq(0,20,length=100),
     prob_pre = 0,
@@
   return(trans_prob)
-
-  #  p_pre <- ggplot(trans_prob,aes(x=investment,y=prob_pre, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function pre manipulation") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # p_ctrl <- ggplot(trans_prob,aes(x=investment,y=prob_ctrl, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post control") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # p_coax <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) + ggtitle("Transition function post intervention") + labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + theme_bw()
-  # 
-  # grid.arrange(p_pre, p_ctrl,p_coax, nrow=3, ncol=1)
 
@@
 
-# coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
-#   geom_line() + 
-#   geom_line(aes(y=prob_pre),linetype="dotted") +
-#   facet_wrap(~from) + 
-#   ylim(c(0,1)) + 
-#   ggtitle("Transition function pre- and post-intervention manipulation") + 
-#   labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
-#   theme_bw()
-
 coax_pre_plot <- ggplot(trans_prob,aes(x=investment)) + 
-  geom_line(aes(y=prob_coax, colour = as.factor(to), linetype="Post-intervention")) + 
-  geom_line(aes(y=prob_pre, colour = as.factor(to), linetype="Pre-intervention")) +
+  geom_line(aes(y=prob_coax, colour = as.factor(to), linetype="Post-manipulation")) + 
+  geom_line(aes(y=prob_pre, colour = as.factor(to), linetype="Pre-manipulation")) +
   facet_wrap(~from) + 
@@
   labs(x = "Investment", y = "Transition probability", color='State Transitioned to', linetype = "Line Type") + 
-  scale_linetype_manual(values = c("Post-intervention" = "solid", "Pre-intervention" = "dotted")) +
+  scale_linetype_manual(values = c("Post-manipulation" = "solid", "Pre-manipulation" = "dotted")) +
   theme_bw()
@@
 
-# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
-
-```
-
-<!-- To explore the differences in transition probabilities between the control and coaxing conditions, we can choose an investment and compare the probabilities of transitioning between States.
-For instance, in case the trustee is low in trustworthiness (State 1), and the investor sends an average amount, we can compare the likelihood of the trustee transitioning away from the low trustworthiness state.
-Assuming an investment of 10 (half the endowment), The trustee remains in State 1 with around $85\%$ probability in the control condition, but only $67\%$ probability after the coaxing intervention.
-Likewise, assuming the trustee is in State 4, and receiving a low investment of 2, there is a much lower probability ($0.2\%$) of transitioning to low trustworthiness state in the coaxing condition compared to the control condition ($21\%$).
--->
+```
 
@@
 #   #bootstrap_data <- data[sample(nrow(data), replace=TRUE), ]
-#   bootstrap_data <- avg_ret_df %>% filter(id %in% sample(id,replace=TRUE))
+#   bootstrap_data <- avg_ret_df %>% filter(playerId %in% sample(playerId,replace=TRUE))
 #   
@@
 As such, a rigorous exploration of the determinants of inter-individual differences to an intervention in the general patient population is required.
-<!-- In our case, judging by the inter-individual heterogeneity in responses, some people may not have been convinced that coaxing via high returns was a good way to re-establish cooperation after a transgression.
-Their impulse to “punish” the other player for their transgression may have been too strong to be overridden by the intervention.
-This was also evident from the participants' replies to a question about whether they would change their behaviour, just after seeing the intervention manipulation.
-An important avenue is to explore the role of emotion in decision making in such situations.
-We could aim to measure emotional reactions more accurately and explore whether specific emotions mediate the relationship between the investment received and the decision of what proportion to return.
-Measuring the emotions using the two axes of valence and arousal could be improved: Results indicate that these concepts may not have been well understood by participants since we would not expect to see low arousal after the pre-programmed defection of the investor.-->
+
 Overall, we are encouraged that our brief cognitive intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments, can lead to clearly differentiated behaviour.
@@
 
-<!--
-Second, we selected trustees from the general population, which might not suffer from the inability or unwillingness to repair relationships due to accidental breakdown of trust that characterises some mental health disorders such as BPD.
-As such, it would be interesting to contrast these results with findings from experiments involving trustees that are selected from patient populations known to suffer from difficulties in maintaining or repairing cooperative interactions.
-Third, as we explained above, the choice of the task to measure transfer of intervention learning could be made better by involving less popular paradigms.
-The high popularity of the Prisoner's Dilemma and the strategy of playing tit-for-tat may have resulted in a strong prior on which strategy to adopt in this game irrespective of the intervention.
-We believed that asking people about how they felt in the control condition might have affected how they behaved and might constitute an intervention in itself.
-However, being able to compare the differential impact of the intervention on the emotional interpretation of the opponent action between an intervention and control conditions could lead to insights on the mechanism through which the intervention affects the emotional reaction to the opponent's actions.
--->
-
 # Conclusion
-
-<!-- MS: Don't think we need a conclusion? -->
 

### 2023-08-28 supplement.Rmd
modifs article format
re-fit HMM models using initial values from simpler models

@@
 
+# Distribution of returns for each latent state for HMM model of participant’s returns
+
+Focusing on HMM models with 5 latent states (which is the optimal number for the HMM-full model) we estimated the investors' policy in each of the five latent states assuming a discretised Gaussian response function as highlighted in the previous section.
+Each latent state was associated with a distribution over trustee actions.
+The latent states were ordered by the mean of the estimated Gaussian, such as higher numbered latent states reflect higher "trustworthiness".
+
+```{r trusteeHMMPlot,fig.cap = "Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model.
+The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social", fig.align='center'}
+
+knitr::include_graphics("figures/trusteeHMMPlot.png")
+
+```
+
 # References

### 2023-09-08 supplement.Rmd
effect size calcs

@@
 
-Focusing on HMM models with 5 latent states (which is the optimal number for the HMM-full model) we estimated the investors' policy in each of the five latent states assuming a discretised Gaussian response function as highlighted in the previous section.
+Focusing on the HMM-full models with 5 latent states (please see main manuscript for a definition) we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section.
 Each latent state was associated with a distribution over trustee actions.
-The latent states were ordered by the mean of the estimated Gaussian, such as higher numbered latent states reflect higher "trustworthiness".
+The latent states were ordered by the mean of the estimated Gaussian, such as higher numbered latent states reflect higher mean percentage return.
 

### 2023-09-21 article.Rmd
effect size calcs
sept23 modifs round

@@
 ---
-title: "Repairing cooperation through a cognitive intervention in the repeated Trust Game"
+title: "(Re)building cooperation: Effects of a cognitive intervention on cooperative behavior in games"
 author:
-  "Ismail Guennouni^1^, Quentin Huys^2^, Samuel Dupret^1^, Maarten Speekenbrink^1^"
+  "Ismail Guennouni^1^, Quentin JM Huys^2^, Samuel Dupret^1^, Maarten Speekenbrink^1^"
 
@@
 As such, interventions to foster and strengthen trust-based cooperation are highly desirable.
-Using the repeated Trust Game paradigm, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a pre-programmed, one-off defection by the opponent.
+Using the Repeated Trust Game paradigm, we assess the effectiveness of a cognitive intervention derived from Dialectical Behavior Therapy.
+The intervention's goal was to repair the potential breakdown of cooperation from a pre-programmed, one-off defection by the opponent.
 Over two games, participants are given the role of the trustee and face what they believe are two different players.
 In between games, they either receive a brief cognitive intervention or not.
-The intervention led to more cooperative behavior both pre and post defection by the opponent.
-HMM modelling of participants actions shows participants in the intervention group had a lower probability of transitioning to non cooperative states.
-Posterior latent state analysis also showed a  higher proportion of players best described by more cooperative latent states in the intervention condition compared to the control condition.
+Post-intervention, participants showed more cooperative behavior both before and after defection by the opponent.
+Analysing participants' actions with a hidden Markov model shows that participants in the intervention group had a lower probability of transitioning to non cooperative states, and a higher proportion of cooperative states, than participants in the control group.
+This is consistent with participants inferring from the intervention that pro-social and trustworthy behavior may generally provide more beneficial outcomes to them in the long run.
 
@@
 Determining the other's goals, intentions, and decision-making process is fundamental to successful social interaction.
-This inference is however fraught with uncertainty, as we cannot directly observe these features, and may need extensive prior knowledge of the person.
+This inference is however fraught with uncertainty, as we cannot directly observe these aspects, and may need extensive prior knowledge of the person to infer them.
 Absent a history of interaction, one may decide to trust the other's goals and intentions are aligned with one's own.
@@
 If this trust is misplaced, it can come at a high cost.
-Not trusting others is also risky since opportunities for cooperation may be foregone.
+Not trusting others is also risky since opportunities for beneficial cooperation may be foregone.
 
@@
 
-Evidence from the literature emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016 ; @meng_multilevel_2014].
+Evidence from the literature emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016; @meng_multilevel_2014].
 It affects the health status of individuals by reinforcing social support networks, maintaining community norms and facilitating collective action.
@@
 However, cooperation in this setting is prone to be broken through intentional or simply misinterpreted actions that can convey lack of trust or trustworthiness such as low investments and returns [@bendor_when_1991].
-In order to repair a damaged cooperative equilibrium, players need to infer that their behaviour has violated social norms and offer amends through generous actions at potentially a high cost to them.
+In order to repair a damaged cooperative equilibrium, players need to infer that their behavior has violated social norms and offer amends through generous actions at potentially a high cost to them.
 @king-casas_rupture_2008 links the breakdown of cooperation in trustees with Borderline Personality Disorder to the absence or reduction of activation in brain regions associated with the perception of norm violations.
@@
 Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions to foster and strengthen trust-based cooperation would be highly beneficial to society.
-Such interventions would allow people to more easily repair broken relationships, and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
+Such interventions would allow people to more easily repair broken relationships and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
 
@@
 @axelrod_evolutionary_1986 studied the emergence and stability of behavioral norms to regulate non-cooperative actions in social settings.
-He identifies a behavioral norm as a dominant behavioural strategy which is often punished by others when not adhered to.
+He identifies a behavioral norm as a dominant behavioral strategy which is often punished by others when not adhered to.
 A meta-norm is the propensity to incur a cost in order to enforce a norm.
@@
 
-A well-established paradigm in the study of trust is the repeated trust game [@joyce_trust_1995].
+A well-established paradigm in the study of trust is the Repeated Trust Game (RTG) [@joyce_trust_1995].
 In this game, the "investor" decides how much of an endowment to send to the other player (the "trustee").
@@
 Others chose to intervene directly on the participants.
-For example, @drazkowski_gratitude_2017 found that trust was increased when participants were asked to think about and write down five things that they were grateful for.
+For example, @drazkowski_gratitude_2017 found that trust (as measured by the amount invested) was increased when participants were asked to think about and write down five things that they were grateful for.
 @burnham_friend-or-foe_2000 found that trust was also increased when participants were primed with the concepts of friend and foe.
@@
 Whilst these interventions show that it is possible to improve cooperative outcomes at the start of the game, they do not address how to repair a breakdown of trust that might occur due to intentional or accidental non-cooperative actions by the players.
-Cooperative play in the repeated trust game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor or a return of the trustee below the investment sent [@bendor_when_1991].
-Such ruptures of cooperation appear frequently when the trustee suffers from social disorders such as Borderline Personality Disorder [BPD; @lieb_borderline_2004].
-In theses situations, BPD trustees fail to engage in trust repairing behaviours such as coaxing the investor by signalling trustworthiness via sending high returns.
-This failure may be linked to the misperception that their low returns in the game are not violating social norms [@king-casas_rupture_2008].
+Cooperative play in the Repeated Trust Game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor or a return of the trustee below the investment sent [@bendor_when_1991].
+Such ruptures of cooperation appear frequently when the trustee suffers from social disorders such as Borderline Personality Disorder or BPD [@lieb_borderline_2004].
+In these situations, BPD trustees fail to engage in trust-repairing behaviors such as coaxing the investor by signalling trustworthiness via sending high returns.
+This failure may be linked to BPD patients not realising that low returns in the game violate social norms [@king-casas_rupture_2008].
 
 In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of social dysfunction in BPD patients.
-Whilst there is no proven pharmacological therapy for BPD, psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve various dysfunctional behaviors in BPD patients, including those related to social interaction [@gunderson_borderline_2018].
+Whilst there is no proven pharmacological therapy for BPD, psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve social skills in BPD patients [@gunderson_borderline_2018].
 However, response to these treatments is highly variable, and determining which interventions are effective for particular patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
-One promising approach is the study of how specific components of psychotherapeutic treatment affect quantitative markers of behaviour such as those inferred through computational models [@huys_computational_2016; @reiter_neuro-cognitive_2021].
-Combining the use of specific cognitive probes inspired by therapeutic interventions and computational models of behaviour may allow us to uncover the cognitive mechanisms targeted by common forms of psychotherapy.
+One promising approach is the study of how specific components of psychotherapeutic treatment affect quantitative markers of behavior such as those inferred through computational models [@huys_computational_2016; @reiter_neuro-cognitive_2021; @dercon2022core].
+Combining the use of specific cognitive probes inspired by therapeutic interventions and computational models of behavior may allow us to uncover the cognitive mechanisms targeted by common forms of psychotherapy.
 In turn, this may provide the basis for choosing effective psychotherapeutic interventions for given individuals.
 
-In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a one-off low investment sent by an computerised investor.
+In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a one-off low investment sent by a computerised investor.
 The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation.
 Participants are given the role of the trustee and are randomly assigned to either a control or intervention group.
-They play two instances of the repeated trust game with two different investors.
+They play two instances of the Repeated Trust Game with two different investors.
 After the first instance of the game, they either receive a cognitive intervention (intervention condition) or perform an unrelated task solving anagrams (control condition).
 In reality, participants face the same computerised agent in both instances, which is programmed to play according to a hidden Markov model fitted to real players' data.
-We explore whether the intervention has an effect on the behaviour of the human trustee and whether this effect transfers to a different game (repeated Prisoner's Dilemma) and facing a seemingly new player.
+To foreshadow our results, we find that the intervention led to higher returns by the participants and countered a tendency to send back lower returns after a defection by the investor, but find no evidence of transfer to a different game (Repeated Prisoner’s Dilemma).
 
@@
 d_finished <- readRDS("data/d_anonym.RDS")
+
+sd(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE)
 ```
@@
 
-## Participants and Design
+## Participants
 
 A total of 318 participants were recruited on the Prolific Academic platform (prolific.co).
-The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years.
+The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years, with a `r round(sd(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years standard deviation.
 Participants were paid a fixed fee of £5 plus a bonus payment dependent on their performance that averaged £0.71.
+
+## Design and Procedure
+
 The experiment had a 2 (Condition: Intervention or Control) by 3 (Game: Trust-Game Pre Intervention, Trust-Game Post Intervention, Prisoner's Dilemma Post Intervention) design, with repeated measures on the second factor.
 Participants were randomly assigned to one of the two levels of the first factor.
+The games were designed and implemented online using Empirica [@almaatouq2021empirica].
+
+```{r timeline, fig.cap = "Experiment overview.
+After playing 15 rounds of the RTG as the trustee, participants were randomized to either be part of the control or intervention condition.
+They then played the second set of 15 rounds of RTG (again as the trustee) to examine intervention effects, and 7 rounds of a repeated Prisoner’s Dilemma to examine generalization of intervention effects.
+Finally, participants answered questionnaires and were debriefed.", fig.align='center', out.width="100%", out.height= "120%"}
+
+knitr::include_graphics("figures/timeline.png")
+
+```
 
@@
 
-Participants played a 15-round repeated trust game [@joyce_trust_1995] in the trustee role against a computer-programmed investor.
-On each round the investor was endowed with 20 units and decided how much of that endowment to invest.
-This investment is tripled and the trustee then decides how to split this amount between them and the investor.
+Participants played a 15-round Repeated Trust Game [@joyce_trust_1995] in the trustee role against a computer-programmed investor.
+On each round the investor is endowed with 20 units and decides how much of that endowment to invest.
+This investment is tripled and the trustee then decides how to split this tripled amount between them and the investor.
 If the trustee returns more than one third of the amount, the investor makes a gain.
 The Nash equilibrium for a single-round version is for the investor to send nothing.
-In the repeated version, rewards for both players are maximised if they build trust and share the benefits of the the investment multiplied by three.
-An investor who has been rewarded for taking the risk of sending an investment is more likely to invest more on future rounds.
+In the repeated version, rewards for both players are maximised if they build trust and share the benefits of higher investments.
+An investor who has been rewarded for taking the risk of sending an investment will likely invest more in future rounds.
 An investor obtaining a low return on their investment may choose to reduce future investment and thereby reduce both players’ gains.
@@
            position = "dodge") + 
-  labs(fill='Latent investor state') + 
+  labs(fill='Latent investor state', x = "Investment", y= "Probability") + 
   theme_bw() + 
@@
 
-  ggplot(df,aes(x=ret,y=probs, colour = as.factor(to))) + geom_line() + facet_wrap(~from) + ylim(c(0,1)) +  labs(x = "Investor's Net Return", y = "Transition probability", color='State Transitioned to') +
-    theme_bw() + theme(legend.position = "bottom")
+    # Create a separate data frame with the background colors
+  bg_colors <- data.frame(
+    from = factor(c("low-trust", "medium-trust", "high-trust"), levels=c("low-trust","medium-trust","high-trust"))
+  )
+
+  # plotting code...
+  ggplot() +
+    geom_rect(data = bg_colors, aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, fill = from), alpha = 0.1) +
+    geom_line(data = df, aes(x = ret, y = probs, colour = as.factor(to))) +
+    facet_wrap(~from, labeller = labeller(from = function(x) paste("From", x, "state on trial t"))) +
+    ylim(c(0,1)) +
+    scale_fill_manual(values = c("low-trust" = "red", "medium-trust" = "green", "high-trust" = "blue")) +
+    labs(x = "Investor's net return on trial t", y = "Transition probability to \nState on trial t+1", color = 'State transitioned to') +
+    theme_bw() +
+    theme(legend.position = "bottom", 
+          axis.title.y = element_text(size = 8, angle = 90, vjust = 1.5))
 
@@
 
-```{r HMMPanels, fig.cap="A: Distribution of investments by the artificial investor agent conditional on its latent state as estimated by a three state hidden Markov model fitted to human dyadic play dataset.
-B: Transition function for the HMM investor conditional on its current state and the net return from the previous round of play.", fig.align="center"}
+```{r HMMPanels, fig.cap=" We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
+From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel A.
+The fitted HMM also yields the transition probability of the agent to a state on trial t+1 as a function of the net return (difference between the investment sent and the amount received in return) on trial t as shown in Panel B.
+Each plot in Panel B represents a different starting latent state on trial t, and each line represents the probability of transitioning to a particular state in trial t+1.
+The policy in each state in Panel A and the way the agent transitions between states as defined in Panel B characterises the artificial agent's behavior in the Repeated Trust Game.", fig.align="center"}
 
@@
 
-The strategy of the computerised investor was modelled on behaviour of human investors in a 10-round RTG [@king-casas_rupture_2008].
-Using this data, we estimated a hidden Markov model (HMM) on investors' behaviour with three latent states, reflecting "low-trust", "medium-trust", or "high-trust".
-Each latent state was associated with a distribution over all possible investor actions (from 0 to 20 investment) that reflected the amount of trust (Figure \ref{fig:HMMPanels}.A).
-Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of the net return in the previous round (see Figure \ref{fig:HMMPanels}.B).
-
-In order to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 pre-intervention and 13 post-intervention.
+The strategy of the computerised investor was modelled on behavior of human investors in the Repeated Trust Game (RTG)  over 10-rounds with the same (human) opponent.
+Full detail on the datasets used in the supplement.
+Using this data, we estimated a hidden Markov model (HMM) on investors' behavior with three latent states, reflecting "low-trust", "medium-trust", or "high-trust".
+Each latent state was associated with a distribution over the possible investor actions from 0 to 20 (Figure \ref{fig:HMMPanels}.A).
+Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of the net return ( i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.B).
+In order to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 pre-intervention and round 13 post-intervention.
 On all other rounds, the agent's actions were derived from the HMM (disregarding the participant's response on pre-programmed low investment rounds).
@@
 
-Participants played 7 rounds of a repeated Prisoner's Dilemma.
-In each round, participants could choose between: a cooperative action with a reward of 5 if the player also cooperated and a reward of 1 if not, or a non-cooperative action that would yield a 7 points if the other person chooses the cooperative action and 2 points if not.
+To ascertain whether any effect of the intervention might transfer to a different game, participants played 7 rounds of a Repeated Prisoner’s Dilemma (RPD).
+In each round, participants could choose between: a cooperative action with a reward of 5 if the player also cooperated and a reward of 1 if not, or a non-cooperative action that would yield 7 points if the other person chooses the cooperative action and 2 points if not.
 The Nash equilibrium for a single-round version is to choose the non-cooperative action.
@@
 The computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
-On round 4, the agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
+On round 4, the computerised agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
 
@@
 
-The intervention was built on interventions from DBT skills training, asking patients to reflect on the consequences of actions taken in emotional states [@linehan_dbt_2015].
-Specifically, participants were presented with a low investment and asked to indicate their response.
-They were then invited to consider what their ultimate aim in the game was and whether this response was most likely to achieve their aim.
-The intervention is detailed in the supplementary information.
+The intervention was built on interventions from Dialectical Behavior Therapy (DBT) skills training, asking patients to reflect on the consequences of actions taken in emotional states [@linehan_dbt_2015].
+Specifically, participants were presented with a hypothetical situation in which they receive a low investment and asked to indicate how they would respond.
+They were then presented with an educational slide inviting them to consider that the ultimate aim in the game was to maximise their total reward and reflect on whether punishing the investor for the low investment was most likely to achieve that aim.
+Participants were told that punishment can create a negative feedback loop where the other player might trust them even less.
+An alternative action was suggested, whereby players would respond kindly to such a transgression in the hope of gaining trust from the investor.
+Participants were then asked whether the information just received would change their behavior in such a hypothetical situation and to justify their answer.
+Full details on the intervention are provided in the supplementary information.
 
@@
 ## Procedure
-
-```{r timeline, fig.cap = "Experiment overview.
-After playing 15 rounds of a repeated trust game (RTG) as trustee, participants were randomized to either receive the control or active intervention.
-They then played the second set of 15 rounds of RTG (again as trustee) to examine intervention effects, and 7 rounds of a repeated Prisoner’s Dilemma to examine generalization of intervention effects.
-Finally, participants answered questionnaires and were debriefed.", fig.align='center', out.width="80%"}
-
-knitr::include_graphics("figures/timeline.png")
-
-```
 
@@
 They were not told the number of rounds of each phase.
-Phase one was a 15 round repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
+Phase one was a 15 round Repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
 On each round, after being informed about the amount sent by the investor, participants were asked to provide feedback, with participants in the Intervention condition rating their feeling in terms of valence (from negative to positive) and arousal (from low to high), and participants in the Control condition rating the investment in terms of speed (from slow to fast) and magnitude (from low to high).
@@
 Subsequent phase two was similar to phase one, with participants being told they would face a new player.
-Phase three consisted of 7 rounds of the repeated prisoner's dilemma game (RPD), with participants informed they would face a third player.
+Phase three consisted of 7 rounds of the Repeated Prisoner's Dilemma game (RPD), with participants informed they would face a third player.
 Participants then completed questionnaires related to mentalising abilities, emotion regulation, and BPD traits (see the supplement for details).
@@
 
-To explore whether participants behaved differently after the intervention compared to the control group over all rounds, we estimate a linear-mixed effects model as implemented in the R package "afex" [@singmann_afex_2022], with fixed effects for Condition (intervention or control), Game-number (pre- or post-intervention) and Investment, as well as interactions between Condition and both Investment and Game-number, and participant-wise random intercepts and random slopes for Game-number.
-More complex models with additional random effects provided could not be estimated reliably.
+<!-- To explore whether participants behaved differently in the RTG after the intervention compared to the control group, we estimate a linear-mixed effects model via the "afex" [@singmann_afex_2022] package for R [@R_package], of the percentage return (percentage of tripled investment returned to investor) as the dependent variable and with fixed effects for Condition (intervention vs.
+control), Game (RTG game pre vs.
+post-intervention) and Investment, as well as interactions between Condition and both Investment and Game, and participant-wise random intercepts and random slopes for Game.
+More complex models with additional random effects could not be estimated reliably, and as such the estimated model can be considered to include the optimal random effects structure [@matuschek2017balancing].
+A similar process was used to establish the random effects structures of other linear mixed-effects models used throughout the statistical analyses.
 For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
 We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
-
-To model participants' returns in the RTG across games and conditions, we fit various hidden Markov models to participants' returns using the depmixS4 package [@visser_depmixs4_2021] for R.
+-->
+
+To explore whether participants behaved differently in the RTG after the intervention compared to the control group, we model the percentage return (percentage of tripled investment returned to investor) using a linear mixed-effects model as described below:
+
+\[
+\begin{split}
+R_{ij} = & \beta_0 + \beta_1 \text{ (Condition)}_i + \beta_2 \text{ (Game)}_i + \beta_3 \text{ (Investment)}_i + \\
+& \beta_4 \text{ (Condition × Game)}_i + \beta_5 \text{ (Condition × Investment)}_i + \beta_6 \text{ (Game × Investment)}_i +  \\ 
+& \beta_7 \text{ (Condition × Game × Investment)}_i +b_{0j} + b_{1j} \text{ (Game)}_i + \epsilon_{ij}
+\end{split}
+\]
+
+where:
+
+- \( R_{ij} \): percentage of tripled investment returned to investor for participant \( j \) in observation \( i \)
+- \( \beta_0 \): intercept
+- \( \beta_1 \): effect of Condition (intervention vs. control)
+- \( \beta_2 \): effect of Game (RTG game pre vs. post-intervention)
+- \( \beta_3 \): effect of Investment
+- \( \beta_4 \): interaction effect between Condition and Game
+- \( \beta_5 \): interaction effect between Condition and Investment
+- \( \beta_6 \): interaction effect between Game and Investment
+- \( \beta_7 \): three-way interaction effect between Condition, Game and Investment
+- \( b_{0j} \): participant-wise random intercept for participant \( j \)
+- \( b_{1j} \): participant-wise random slope for Game for participant \( j \)
+- \( \epsilon_{ij} \): error term for participant \( j \) in observation \( i \)
+
+The model was estimated using the `afex` package [@singmann_afex_2022] in R [@R_package].
+More complex models with additional random effects could not be estimated reliably, and as such the estimated model can be considered to include the optimal random effects structure [@matuschek2017balancing].
+A similar process was used to establish the random effects structures of other linear mixed-effects models used throughout the statistical analyses.
+For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
+We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
+
+<!-- To explore whether the HMM investors behaved differently in the RTG after the intervention compared to the control group, we estimate linear mixed effects model of investments sent by the computerised HMM agent with Condition and Game and their interaction as fixed effects -->
+
+To model participants' returns in the RTG across games and conditions, we fit various hidden Markov models [@visser2022hidden] to participants' returns using the depmixS4 package [@visser_depmixs4_2021] for R.
 The transition between latent states is assumed to depend on the investment received and a dummy variable to characterise the group that the participant belongs to.
@@
 
-# Behavioural results
+# Behavioral results
 
@@
 
-```{r gamesPlot, echo=FALSE, fig.cap="Average and standard errors of the trustee's return as a percentage of the multiplied investment received for each round and for both conditions.
-The red line shows the returns pre-manipulation and the blue line post-manipulation.We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel",fig.align="center", fig.width=6, fig.height = 4}
-
-# colors <- c("investment" = "blue", "returns" = "red")
-# 
-# ggplot(avg_ret_df,aes(x=as.factor(roundNum),group = 1)) +
-#   stat_summary(fun = "mean", geom = "line", aes(y=returns, color ="returns")) +
-#   stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=returns) ) +
-#   stat_summary(fun = "mean", geom = "line", alpha =0.4,aes(y=investment, color = "investment")) +
-#   stat_summary(fun.data = "mean_se", geom = "errorbar", alpha =0.3, width = 0.2, aes(y=investment) ) +
-#   facet_wrap(~condition.f*gameNum.f) +
-#   labs(x = "Round",
-#        y = "Investment / Return",
-#        color = "Legend") +
-#   scale_color_manual(values = colors) +
-#   theme_bw() +
-#   theme(legend.position = "bottom")
-
-# Alternative chart with pre vs post percentage returns in one panel as suggested by QH.
+```{r gamesPlot, echo=FALSE, fig.cap="Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+The blue line shows the returns pre-manipulation and the green line post-manipulation.
+We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel",fig.align="center", fig.width=6, fig.height = 4}
 
@@
 
+```{r, include=F}
+
+library(sjstats)
+effectsize::eta_squared(mod_returns_pct)
+
+```
+
 ```{r, include=FALSE}
@@
 Average investments and returns prior to the "defection round" (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
-Mixed-effects analysis on the returns shows a significant main effect of Condition (intervention vs.
+Mixed-effects analysis on the percentage returns shows a significant main effect of Condition (intervention vs.
 control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f`<!--$F(1,315.31) = 9.52$, $p = .002$-->, with higher percentage returns in the intervention compared to the control condition.
@@
 Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:violinPanels}.A).
-This indicates the intervention was effective in increasing cooperative behaviour.
-There was also a significant main effect of Investment, `r papaja::apa_print(mod_returns_pct)$full_result$inv_scaled`<!--$F(1,9208) = 373.6$, $p < 0.001$-->, such that higher investments were associated with higher percentage returns.
-An Investment by Condition interaction, `r papaja::apa_print(mod_returns_pct)$full_result$condition_f_inv_scaled`<!--$F(1,9207) = 45.38$, $p < .001$-->, indicates the positive effect of investment on percentage returns was greater in the control than intervention condition.
-<!-- This suggests that the higher returns we see in the intervention group are not simply due to higher investments.--> There was also an Investment by Game interaction, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_inv_scaled`.
-Finally, we find a three way interaction between Game, Condition and Investment, `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f_inv_scaled`<!--($F(1,8988)= 24.6, p < 0.001$),-->, showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game (pre- vs post intervention).
+This indicates the intervention was effective in increasing cooperative behavior.
+There was also a significant main effect of Investment,
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_returns_pct)$full_result$inv_scaled)`,
+such that higher investments were associated with higher percentage returns. An Investment by Condition interaction, 
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_returns_pct)$full_result$condition_f_inv_scaled)`, indicates the positive effect of investment on percentage returns was greater in the control than intervention condition.
+There was also an Investment by Game interaction,
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_inv_scaled)`. 
+Finally, we find a three way interaction between Game, Condition and Investment, 
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f_inv_scaled)`, showing that the differentiated effect of the investment on the proportion returned by condition is itself moderated by the Game (pre- vs post intervention).
 
@@
 
-We next analysed HMM agent investments with a linear-mixed effects model with fixed effects for Condition (intervention vs control), Game (pre vs post intervention), as well as interaction between Condition and Game, and participant-wise random intercepts and random slopes for Game.
+To explore whether the HMM investors behaved differently in the RTG after the intervention compared to the control group, we estimate a linear mixed-effects model of investments sent by the computerised HMM agent with Condition and Game and their interaction as fixed effects, and a similar random effects structure to the returns model.
 This shows a main effect of Condition, `r papaja::apa_print(mod_invs)$full_result$condition_f`<!--$F(1,317) = 8.7$, $p = .003$-->, and Game, `r papaja::apa_print(mod_invs)$full_result$gameNum_f`<!--$F(1,317) = 8.3$, $p = .004$-->.
@@
 ```
-
-We next analysed returns separately for rounds prior to the pre-programmed transgression (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
-Applying the same mixed effects model as before to returns before the transgression largely replicates the results over all trials.
+```{r, include=F}
+saveRDS(summary(mod_returns_pre), "data/mod_returns_pre")
+```
+
+We next analysed returns separately for rounds prior to the pre-programmed defection (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
+Applying the same mixed-effects model as before to returns before the defection largely replicates the results over all trials.
 Participants in the intervention condition increased their returns in the second game, `r papaja::apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`.
-There was no evidence that participants in the control condition changed their returns in pre-transgression trials between the first and second RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
+There was no evidence that participants in the control condition changed their returns in pre-defection trials between the first and second RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
 Full results are provided in the supplement.
@@
 
+```{r, include=F}
+saveRDS(summary(mod_postcoax_trust), "data/mod_returns_post")
+```
+
 ```{r, include=FALSE}
@@
 
-```{r violinPanels, fig.cap="A: Marginal means and distributions of percentage trustee returns over all rounds, shown across participants by Game number and Condition.
-B: Marginal means and distributions of investments over all rounds for HMM investors, by Game number and Condition.
-C: Marginal means and distributions of percentage trustee returns across all participants for pre-defection trials only, by Game number and Condition.
-D: Marginal means and distributions of percentage trustee returns across all participants for post-defection trials only, by Game number and Condition.", fig.align="center", fig.width=6, fig.height = 6}
+```{r violinPanels, fig.cap="Participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds (Panel A).
+This was also the case both before (Panel C) and after (Panel D) the pre-programmed defection by the HMM investor.
+Those in the control conditions returned similar amounts between games before the defection, and lower amounts in the second game after the defection by the investor.
+Investments by the HMM agent (Panel B) were higher in the second game compared to the first game across conditions.
+All panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition", fig.align="center", fig.width=6, fig.height = 6}
 
@@
 
-Applying the same model to the returns after the transgression (see the supplement for full results), we again find a significant interaction between Condition and Game.
-Participants in the control condition decreased their post-transgression returns from the first to the second RTG, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
+Applying the same model to the returns after the defection (see the supplement for full results), we again find a significant interaction between Condition and Game.
+Participants in the control condition decreased their post-defection returns from the first to the second RTG, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
 There was no significant change for participants in the intervention condition, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`.
-When questionnaire scores for borderline traits, mentalising and emotion regulation abilities were added as explanatory variables, we found no interaction effect of these questionnaire scores with the Condition variable, nor a main effect of the questionnaire scores on participants returns in the RTG.
-
-Taken together, we find that participants in the control condition sent lower percentage returns in the second game, despite the HMM investor sending on average higher investments in the second game.
+<!-- When questionnaire scores for borderline traits, mentalising and emotion regulation abilities were added as explanatory variables, we found no interaction effect of these questionnaire scores with the Condition variable, nor a main effect of the questionnaire scores on participants returns in the RTG.
+-->
+
+Taken together, we find that participants in the control condition sent lower percentage returns in the second game, despite the HMM investor sending on average higher investments in that game.
 Those in the intervention group returned higher percentage returns in the second game, with the investor also sending higher investments.
 These higher returns in the intervention compared to the control condition were not purely driven by reciprocity towards higher investments, since we found a Condition by Game interaction whilst controlling for investment in the model, and a reduced effect of investment in the intervention condition.
-Whilst the intervention increased participants returns overall, it did not appear to increase participants' returns after the transgression by the other player.
-However, it may have countered the tendency to lower returns after the transgression in the second game compared to the first game, which was shown by participants in the control condition.
+The intervention did not increase participants' returns after the defection by the other player.
+Instead, it countered the tendency shown by participants in the control condition to lower returns after the defection in the second game compared to the first game.
 
@@
 
-```{r emoPlotCoax, fig.cap="Self-reported emotion valence and arousal as well as investment z-scores for each round of the repeated Trust Game averaged across participants in the intervention condition only.",fig.align="center", fig.width=6, fig.height = 4}
+```{r emoPlotCoax, fig.cap="Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
+The participants' emotion self-reports for the investor's defection were similar before and after the intervention.",fig.align="center", fig.width=7, fig.height = 4}
 
@@
   stat_summary(data = datCoax[datCoax$gameNum.f == 'post', ], fun = "mean", geom = "line", group =1, aes(x=roundNum, y=inv_scaled, color = "Investment", linetype = "b_Post")) +
-  labs(x = "Round", y="Series Z-score") +
+  labs(x = "Round", y="Z-score") +
   geom_hline(yintercept = 0, linetype="dotted", color = "grey", linewidth=1.5) +
@@
 
-Participants in the intervention condition rated their emotion on valence (negative to positive) and arousal (low to high) after each investment.
-To assess the impact of the intervention on these emotional reactions, we used linear mixed-effects models (one for valence, and one for arousal) with fixed effects for Game (pre vs post intervention) and Investment, as well as interaction between Investment and Game, with participant-wide random intercepts and random slopes for Game.
-This showed that higher investments were associated with more positive emotions, `r papaja::apa_print(mod_emo_x)$full_result$scaleinvestment`, and higher arousal, `r papaja::apa_print(mod_emo_y)$full_result$scaleinvestment`.
-<!-- ($F(1,4664) = 2902, p < 0.001$), and higher arousal ($F(1,4668.4) = 1919, p < 0.001$)--> In addition, the positiveness of emotion declined between the two games, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f`, as did arousal, `r papaja::apa_print(mod_emo_y)$full_result$gameNum_f`.
-There was no indication that the effect of the investment on either aspect of emotion was affected by the intervention, as there was no interaction between Investment and Game on valence, `r papaja::apa_print(mod_emo_x)$full_result$gameNum_f_scaleinvestment`, or arousal, `r papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment`.
+To assess the impact of the intervention on the participant's emotional reactions, we used linear mixed-effects models (one for valence, and one for arousal) with fixed effects for Game (pre vs.
+post intervention) and Investment, as well as interaction between Investment and Game, with participant-wide random intercepts and random slopes for Game.
+This showed that higher investments were associated with more positive emotions,
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_x)$full_result$scaleinvestment)`, 
+and higher arousal, 
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_y)$full_result$scaleinvestment)`. 
+In addition, the positiveness of emotion declined between the two games, 
+`r papaja::apa_print(mod_emo_x)$full_result$gameNum_f`
+, as did arousal, 
+`r papaja::apa_print(mod_emo_y)$full_result$gameNum_f`. 
+There was no indication that the effect of the investment on either aspect of emotion was affected by the intervention, as there was no interaction between Investment and Game on valence, 
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_x)$full_result$gameNum_f_scaleinvestment)`
+, or arousal, 
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment)`. 
 This indicates that participants in the intervention condition returned higher amounts post-intervention, despite their emotional reaction to investments remaining largely the same.
@@
 
+For the Investor evaluation, we estimate a mixed-effects model for participants ratings with Game and Condition as fixed effects and participant-wise random intercepts as random effects.
 Participants rated the HMM investor in the second game as less cooperative (`r apa_print(pairs(emmeans::emmeans(coop_mod, c("gameNum.f"))))$full_result`), less trustworthy (`r apa_print(pairs(emmeans::emmeans(trust_mod, c("gameNum.f"))))$full_result`), less friendly (`r apa_print(pairs(emmeans::emmeans(friend_mod, c("gameNum.f"))))$full_result`) and more selfish (`r apa_print(pairs(emmeans::emmeans(self_mod, c("gameNum.f"))))$full_result`), than the HMM investor in the first game.
@@
 When asked during debrief whether they thought the investors they faced were Human or not, $40$% of participants thought they were either facing a human or were not sure of the nature of the opponent.
-Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behaviour.
-
-## Transfer to the repeated Prisoner's Dilemma game
+Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behavior.
+
+## Transfer to the Repeated Prisoner's Dilemma game
 
@@
 
-```{r PDCoop, include=FALSE, fig.cap="Mean and standard error of the rate at which the cooperative action was chosen by the participants for each round of the repeated Prisoner's Dilemma game.
+```{r PDCoop, include=FALSE, fig.cap="Mean and standard error of the rate at which the cooperative action was chosen by the participants for each round of the Repeated Prisoner's Dilemma game.
 Round 4 is where we programmed the Tit-for-Tat agent to defect, which explains the lower cooperation rate we see in round 5 onwards",fig.align="center", fig.width=6, fig.height =3}
@@
 
-We next asked whether the intervention had any discernible effect on participants' behaviour in a different, repeated Prisoner's Dilemma game.
-Predicting the probability of a cooperative action with a logistic mixed-effects regression model, with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, showed a decline in cooperation after defection by the other player, `r papaja::apa_print(ipd_mod)$full_result$phase`, but no evidence for a different cooperation rate in the intervention condition compared to the control condition, `r papaja::apa_print(ipd_mod)$full_result$condition_f`, or a different response to defection between the conditions, `r papaja::apa_print(ipd_mod)$full_result$condition_f_phase`.
-As such, there is no evidence that the intervention affected behaviour in this game.
+We next asked whether the intervention had any discernible effect on participants' behavior in a different, Repeated Prisoner's Dilemma game.
+Predicting the probability of a cooperative action with a logistic mixed-effects regression model, with Condition and Phase (before or after defection trial) as fixed effects and a random intercept for participants, showed a decline in cooperation after defection by the other player, `r papaja::apa_print(ipd_mod)$full_result$phase`, but no evidence for an overall different cooperation rate in the intervention condition compared to the control condition, `r papaja::apa_print(ipd_mod)$full_result$condition_f`, or a different response to defection between the conditions, `r papaja::apa_print(ipd_mod)$full_result$condition_f_phase`.
+As such, there is no evidence that the intervention affected behavior in this game.
 
@@
 # 
-# set.seed(20221028)
+# fittedCoax <- list()
+# set.seed(20230918)
 # for(i in n_state_min:n_state_max) {
@@
 
-# load("data/fittedSimple.RData")
-# load("data/fittedCtrl.RData")
-# load("data/fittedCoax.RData")
-# load("data/fittedFullCtrst.RData")
-# load("data/fittedPrePost.RData")
-# load("data/newFull.RData")
+load("data/fittedSimple.RData")
+load("data/fittedCtrl.RData")
+load("data/fittedCoax.RData")
+load("data/fittedFullCtrst.RData")
+load("data/fittedPrePost.RData")
+load("data/newFull.RData")
+
 # 
@@
 # Fitting "Coax" models with initial parameters from the fitted "Simple" model.
-
+# 
 # newCoax <- fittedCoax
@@
 #   newCoax[[ns]] <- setpars(newCoax[[ns]],new_pars)
-#   newCoax[[ns]] <- fit(newCoax[[ns]], emcontrol= em.control(maxit = 1000,random.start = FALSE))
+#   newCoax[[ns]] <- fit(newCoax[[ns]], emcontrol= em.control(maxit = 2000,random.start = FALSE))
 # }
@@
 
-# # Here we use parameters of fitted PrePost model as initial values of the FullContrast model to check whether we can approach true maximal likelihood.
+# # Here we use parameters of BEST PrePost model as initial values of the FullContrast model to check whether we can approach true maximal likelihood.
 
@@
 
-```{r table-BICs-coax, include =FALSE, warning = FALSE, echo=FALSE, ft.align="center", tab.playerId='table-BICs-coax', label='table-BICs-coax'}
+```{r table-BICs-coax, include =F, warning = FALSE, echo=FALSE, ft.align="center", tab.playerId='table-BICs-coax', label='table-BICs-coax'}
 
@@
 
-We used hidden Markov models (HMMs) to further assess differences between the intervention and control condition in participants' reactions to the investor.
-As in the models for the investor, these HMMs assume behaviour is governed by latent states, with participants' switches between states now dependent on the investments made.
-We also allowed for differences between games and conditions in how investments govern state transitions.
-More in particular, we fitted five main models which all regressed state transition probabilities onto investments, as well as on additional contrast-coded predictors for condition and/or game number.
-In the most complex model (HMM-full), the transition probabilities were allowed to differ between all four combinations of game number and condition.
-The HMM-coax model allowed differences between post-intervention and the other three conditions (pre-intervention, pre-control, post-control) assuming these latter were the same.
+We used hidden Markov models (HMMs) to further assess differences between the intervention and control condition in participants' reactions to the investor in the Repeated Trust Game.
+As in the models for the investor, these HMMs assume behavior is governed by latent states, with participants' switches between states now dependent on the investments made.
+We also allowed for differences between games and conditions in how investments govern state transitions: We fitted five main models which all regressed state transition probabilities onto investments, as well as on additional contrast-coded predictors for condition and/or Game.
+In the most complex model (HMM-full), the transition probabilities were allowed to differ between all four combinations of Game and condition.
+The HMM-coax model allowed differences between post-intervention and the other three conditions (pre-intervention, pre-control, post-control) treating these latter conditions as the same.
 Similarly, the HMM-ctrl model allowed differences between post-control and the other three conditions.
-The HMM-prepost model allowed differences between the first and second RGT.
-Finally, the HMM-inv model did not allow transition probabilities to differ between conditions or game numbers, modelling them only as a function of investment.
+The HMM-prepost model allowed differences between the first and second RTG.
+Finally, the HMM-inv model did not allow transition probabilities to differ between conditions or games, modelling them only as a function of investment.
 As the number of hidden states was unknown, for each model we estimated versions with 2 to 7 states, and used the BIC to select the best fitting model.
 Generally, best fitting models had between 5 to 7 hidden states.
+Further details on the HMMs and estimation procedure are provided in the Supplementary Information.
 
@@
 
-<!-- MS: There seems to be an issue with the likelihoods of the models.
-For example, for 6 states models, the likelihood of the Ctrl and Coax model are higher than for the Full model, but this is theoretically not possible as additional parameters can only increase the likelihood!
--->
-
 Focusing on models with 5 latent states (which is the optimal number for the HMM-full model), likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCtrl[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCoax[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestPrePost[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$).
-This is consistent with state transitions differing both due to game number and condition as can be seen in Figure \ref{fig:plotTransitionsDiscGaus}.
-
 <!-- We start by comparing HMM-full with HMM-inv.
@@
 
+# plot_state_transitions <- function(fmod, numCovIn, numCovTr) {
+# 
+#   #print(getpars(fmod))
+#   ns <- nstates(fmod)
+#   
+#   trans_prob <- data.frame(
+#     from = rep(1:ns, each=100*ns),
+#     to = rep(1:ns, each=100),
+#     investment = seq(0,20,length=100),
+#     prob_pre = 0,
+#     prob_ctrl = 0,
+#     prob_coax =0
+#   )
+#   
+#   y0 <- matrix(0.0,ncol=ns, nrow=100)
+#   y1 <- matrix(0.0,ncol=ns, nrow=100)
+#   y2 <- matrix(0.0,ncol=ns, nrow=100)
+#   
+#   for(from in 1:ns) {
+#   pars <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
+#   #print(pars)
+#   
+#     for(to in 1:ns) {
+#         x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"investment"]
+#         y0[,to] <- exp(pars[to,1] + pars[to,2]*x)
+#         #ctrst 2 = 1, post intervention vs pre
+#         y2[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,3]*1 + pars[to,5]*x )
+#         #ctrst 1 = 1, post control vs pre
+#         y1[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,4]*1 + pars[to,6]*x )
+#     }
+#     y0 <- y0/rowSums(y0)
+#     y1 <- y1/rowSums(y1)
+#     y2 <- y2/rowSums(y2)
+#     
+#     for(to in 1:ns) {
+#       trans_prob$prob_pre[trans_prob$from == from & trans_prob$to == to] <- y0[,to]
+#       trans_prob$prob_ctrl[trans_prob$from == from & trans_prob$to == to] <- y1[,to]
+#       trans_prob$prob_coax[trans_prob$from == from & trans_prob$to == to] <- y2[,to]
+#     }
+#   }
+#   
+#   
+#   
+#   saveRDS(trans_prob, "data/trans_prob.RDS")
+#   
+#   return(trans_prob)
+# 
+# }
+# 
+# 
+# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6) 
 plot_state_transitions <- function(fmod, numCovIn, numCovTr) {
@@
   trans_prob <- data.frame(
-    from = rep(1:ns, each=100*ns),
-    to = rep(1:ns, each=100),
+    from = rep(paste0("from State ", 1:ns), each=100*ns),
+    to = rep(paste0("State ", 1:ns), times=100),
     investment = seq(0,20,length=100),
@@
 
-  y0 <- matrix(0.0,ncol=ns, nrow=100)
-  y1 <- matrix(0.0,ncol=ns, nrow=100)
-  y2 <- matrix(0.0,ncol=ns, nrow=100)
+  y0 <- matrix(0.0, ncol=ns, nrow=100)
+  y1 <- matrix(0.0, ncol=ns, nrow=100)
+  y2 <- matrix(0.0, ncol=ns, nrow=100)
 
   for(from in 1:ns) {
-  pars <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
+    pars <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)], ncol=numCovTr)
     #print(pars)
@@
     for(to in 1:ns) {
-        x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"investment"]
+        x <- trans_prob[trans_prob$from == paste0("from State ", from) & trans_prob$to == paste0("State ", to), "investment"]
         y0[,to] <- exp(pars[to,1] + pars[to,2]*x)
-        #ctrst 2 = 1, post intervention vs pre
-        y2[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,3]*1 + pars[to,5]*x )
-        #ctrst 1 = 1, post control vs pre
-        y1[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,4]*1 + pars[to,6]*x )
-    }
+        y2[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,3]*1 + pars[to,5]*x)
+        y1[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,4]*1 + pars[to,6]*x)
+    }
+
     y0 <- y0/rowSums(y0)
@@
     for(to in 1:ns) {
-      trans_prob$prob_pre[trans_prob$from == from & trans_prob$to == to] <- y0[,to]
-      trans_prob$prob_ctrl[trans_prob$from == from & trans_prob$to == to] <- y1[,to]
-      trans_prob$prob_coax[trans_prob$from == from & trans_prob$to == to] <- y2[,to]
+      trans_prob$prob_pre[trans_prob$from == paste0("from State ", from) & trans_prob$to == paste0("State ", to)] <- y0[,to]
+      trans_prob$prob_ctrl[trans_prob$from == paste0("from State ", from) & trans_prob$to == paste0("State ", to)] <- y1[,to]
+      trans_prob$prob_coax[trans_prob$from == paste0("from State ", from) & trans_prob$to == paste0("State ", to)] <- y2[,to]
     }
@@
   return(trans_prob)
-
-}
-
-plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)
+}
+
+plot_state_transitions(tr_fdmod_5, numCovIn=2, numCovTr=6)
 
@@
   ggtitle("Transition function pre- and post-control manipulation") + 
-  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
+  labs(x = "Investment", y = "Transition probability", color='Transition to:') + 
   theme_bw()
@@
   ggtitle("Transition function pre- and post-intervention manipulation") + 
-  labs(x = "Investment", y = "Transition probability", color='State Transitioned to', linetype = "Line Type") + 
+  labs(x = "Investment", y = "Transition probability", color='Transition to:', linetype = "Line Type") + 
   scale_linetype_manual(values = c("Post-manipulation" = "solid", "Pre-manipulation" = "dotted")) +
@@
 
-```{r plotTransitionsDiscGaus, fig.cap="Transition function for the HMM-full trustee model.
-Each panel represents the state transitioned from, and each color the state transitioned to.
-Solid lines show estimated transition probabillities post-manipulation.
-Dotted lines show the same probabilities prior to the manipulation",fig.align="center", fig.width=6, fig.height = 7 }
+```{r plotTransitionsDiscGaus, include=F, fig.cap="Transition function for the HMM-full trustee model.
+Each panel represents the state transitioned from.
+For instance the upper left panel represents all transition probabilities from state 1.
+The colors of the lines within each panel indicate the state transitioned to.
+For instance, in the upper left panel, the red line represents the transition probability to state 1 as a function of the received investment.
+In this case this is also the probability of staying in state 1 since we are in the state 1 panel.
+Solid lines show estimated transition probabillities post-manipulation while dotted lines show the same probabilities prior to the manipulation",fig.align="center", fig.width=6, fig.height = 7 }
 
@@
 predTrStates <- posterior(tr_fdmod_5, type="local")
-avg_ret_df$TrState <-  factor(predTrStates, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))
+avg_ret_df$TrState <-  factor(predTrStates, levels= c(1,2,3,4,5),labels=c("State 1","State 2","State 3","State 4","State 5"))
 
@@
 # investor real state distribution (posterior)
+# postHMM <- ggplot(avg_ret_df %>% dplyr::filter(gameNum.f=="post")) +
+#   geom_bar(aes(x = roundNum, group = TrState, fill = TrState),  position = position_stack(reverse = TRUE)) + 
+#   facet_wrap(~condition.f) +  
+#   labs(x = "Round", fill='Posterior trustee state') +
+#   theme_bw() +
+#   theme(legend.position = "bottom")
+
 postHMM <- ggplot(avg_ret_df %>% dplyr::filter(gameNum.f=="post")) +
   geom_bar(aes(x = roundNum, group = TrState, fill = TrState),  position = position_stack(reverse = TRUE)) + 
-  facet_wrap(~condition.f) +  
+  facet_wrap(~factor(condition.f, levels = rev(levels(as.factor(condition.f))))) +  
   labs(x = "Round", fill='Posterior trustee state') +
@@
 For the post-defection trial after the intervention (round 14), state 1 was the most likely state for only $22$% of participants in the intervention condition compared to $43$% in the control condition ($\chi^2(1) = 14.70, p < 0.001$).
-Whilst the posterior states indicate that the intervention was effective, a non-negligible proportion of participants in the intervention condition did not exhibit the coaxing behaviour promoted by the intervention.
+Whilst the posterior states indicate that the intervention was effective, a non-negligible proportion of participants in the intervention condition did not exhibit the coaxing behavior promoted by the intervention.
 Directly following the low investment in round 13, $30.2$% of participants in the intervention condition were assigned to state 1 with the lowest average returns.
@@
 
-The posteriors also suggest that a non-negligible proportion of participants in the intervention condition did not exhibit a behaviour consistent with the goal of the intervention as they were still best fit by low-return states post intervention.
+The posteriors also suggest that a non-negligible proportion of participants in the intervention condition did not exhibit a behavior consistent with the goal of the intervention as they were still best fit by low-return states post intervention.
 For instance, focusing on round 13 post defection $30.2$% of those in the intervention condition were most likely to be in the least pro-social state 1.
@@
 
-In this experiment, human participants took the role of the trustee in a repeated trust game (RTG) where they faced artificial computer agents who's behaviour was partly determined by participants' returns.
-The behaviour of the artificial investors was determined by a 3-state hidden Markov model (HMM), which was estimated from the behaviour of humans in the RTG in prior research.
+In this experiment, human participants took the role of the trustee in a Repeated trust game (RTG) where they faced artificial computer agents who's behavior was partly determined by participants' returns.
+The behavior of the artificial investors was determined by a 3-state hidden Markov model (HMM), which was estimated from the behavior of humans in the RTG in prior research.
 Overall, investments and returns by the artificial and human agents replicated that of human dyads in prior research using the RTG [@charness_investment_2008; @fiedler_social_2011].
-This, together with participants' reported uncertainty about whether they faced a human or artificial investor, shows the potential of using HMM-based artificial agents to mimic human behaviour in economic games, whilst offering a higher degree of experimental control.
+This, together with participants' reported uncertainty about whether they faced a human or artificial investor, shows the potential of using HMM-based artificial agents to mimic human behavior in economic games, whilst offering a higher degree of experimental control than human dyadic interaction.
 
@@
 The overall higher returns after the intervention occurred despite participants' emotional reactions to the investments remaining largely the same as before the intervention.
-This indicates the intervention achieved its goal of encouraging participants to respond in a non-impulsive and considered manner, overriding an emotional urge to retaliate.
+This indicates the intervention achieved its goal of encouraging participants to respond in a non-impulsive and considered manner, possibly overriding the urge to retaliate.
 
 That participants generally send higher returns to the investor after the intervention is unlikely due to a  general learning effect unrelated to the intervention, as participants in the control condition did not increase their returns.
-Also, as participants in the intervention and control condition faced the same HMM investor, the higher post-intervention returns are not solely due to a difference in investor behaviour.
+Also, as participants in the intervention and control condition faced the same HMM investor, the higher post-intervention returns are not solely due to a difference in investor behavior.
 As the investor reacts to participants' returns, those who return more will generally see higher investments.
@@
 Finally, as there were no differences between conditions in how participants rated the first and second HMM agent on attributes such as cooperativeness and trust, the increased returns are unlikely to be the result of a more favourable evaluation of the investor.
-Rather, we find it most likely that the increased returns are due to participants inferring from the intervention that pro-social and trustworthy behaviour may generally motivate the investor to send high investments, which can provide more beneficial outcomes to them in the long run.
+Rather, we find it most likely that the increased returns are due to participants inferring from the intervention that pro-social and trustworthy behavior may generally motivate the investor to send high investments, which can provide more beneficial outcomes to them in the long run.
 
@@
 The RPD also involves much coarser actions (cooperate vs defect) than the finer-grained returns in the RTG.
-This would make it more difficult to observe more subtle effects of the intervention.
-As such, the RPD might not be the best choice for any knowledge transfer.
+This makes it more difficult to observe more subtle effects of the intervention.
+As such, the RPD might not be the best choice of task to measure transfer.
 In any case, we can not rule out that the effects of the brief cognitive intervention, which explicitly focused on the RTG, are confined to the RTG.
@@
 
-Analysing participants' behaviour with hidden Markov models, we found clear individual differences in how returns changed between the pre- and post-intervention RTG, which can be seen as a proxy for the effectiveness of the intervention.
+Analysing participants' behavior with hidden Markov models, we found clear individual differences in how returns changed between the pre- and post-intervention RTG, which can be seen as a proxy for the effectiveness of the intervention.
 Some participants may not have been convinced that coaxing via high returns was a good way to establish cooperation and decided to reduce their returns in the second trust game.
-Their impulse to “punish” the other player for a transgression may have been too strong to be overridden by the intervention.
-This was also evident from the participants' replies to a question about whether they would change their behaviour, just after receiving the intervention.
+Their impulse to “punish” the other player for a defection may have been too strong to be overridden by the intervention.
+This was also evident from participants' replies to a question about whether they would change their behavior, just after receiving the intervention.
 Other participants responded to the intervention and increased their returns.
@@
 
-Overall, we are encouraged that our brief cognitive intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments, can lead to clearly differentiated behaviour.
-In future studies, we aim to explore the effects of improved cognitive interventions to enhance cooperative behaviour.
+Overall, we are encouraged that our brief cognitive intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments, can lead to clearly differentiated behavior.
+In future studies, we aim to explore the effects of improved cognitive interventions to enhance cooperative behavior.
 We may enhance engagement by making the intervention more interactive and visually appealing, rather than the "dry" textual format used in the experiment.
-It would also be of interest to test such interventions with who suffer from an inability or unwillingness to repair relationships after an accidental breakdown of trust, such as people with Borderline Personality Disorder.
-The relative ease by which online interventions can be assigned, and the opportunity for people to test the effect of their behaviour with artificial, but human-like agents, may pave the way for efficient, low-cost, effective treatment programmes which may help a wide-variety of people overcome detrimental actions in social situations.
-
-# Conclusion
-
-We explored the effect of a brief cognitive intervention on the behaviour of human trustees facing adaptive artificial investors designed to replicate the behaviour of human investors in the repeated trust game.
+It would also be of interest to test such interventions with participants that suffer from an inability or unwillingness to repair relationships after an accidental breakdown of trust, such as people with Borderline Personality Disorder.
+The relative ease by which online interventions can be assigned, and the opportunity for people to test the effect of their behavior with artificial but human-like agents, may pave the way for efficient, low-cost, effective treatment programmes which may help a wide-variety of people overcome detrimental actions in social situations.
+
+<!-- # Conclusion -->
+
+<!-- We explored the effect of a brief cognitive intervention on the behavior of human trustees facing adaptive artificial investors designed to replicate the behavior of human investors in the Repeated Trust Game.
 Each state defines different levels of a cooperative response with the agent able to transition between these states based on the behavior of the human opponent.
 Feedback from participants indicated that these agents were sometimes perceived as humans.
-Their strategy led to emergent cooperative behaviour when playing the repeated trust game with human players.
+Their strategy led to emergent cooperative behavior when playing the Repeated Trust Game with human players.
 The intervention, promoting a less impulsive reaction to transgressive actions, led to coaxing behavior and less negative reciprocity when the investor sent a very low investment.
@@
 Whilst this intervention effect varied between participants and generally was not transferred to a new game, an HMM analysis of participant's play post intervention showed differentiated patterns of transitions between latent states, indicating a change in the effect of the opponent action on the probability of transitioning between latent mental states.
+-->
+
+\pagebreak
 

### 2023-09-21 supplement.Rmd
sept23 modifs round

@@
 #date: "2023-04-28"
-output: pdf_document
+#output: pdf_document
+
+output:
+  bookdown::pdf_document2:
+   toc: false
 
@@
 biblio-style: spphys
+
+header-includes:
+  - \renewcommand{\thefigure}{S\arabic{figure}}
 ---
 
-```{r setupCoax, include=FALSE}
+```{r setupCoaxsupp, include=FALSE}
 knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE) 
 knitr::opts_chunk$set(out.width = "\\textwidth")
+library(papaja)
+library(kableExtra)
+library(knitr)
+
+# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
+library(tidyverse)
+library(afex)
+library(PairedData)
+library(multcompView)
+library(lsmeans)
+library(depmixS4)
+library(flextable)
+library(gridExtra)
+library(forcats)
+library(ggsignif)
 ```
@@
 Participants played a 15-round repeated trust game [@joyce_trust_1995] in the trustee role against a computer-programmed investor.
-On each round the investor was endowed with 20 units and decided how much of that endowment to invest.
-This investment is multiplied by a factor of 3 and sent to the trustee, who then decides how to split this between them and the investor.
-If the trustee returns more than a third, then the investor makes a gain.
-The Nash equilibrium for a single-round version is for the investor to send nothing.
-In the repeated version, rewards for both players are maximised if they build trust and share the benefits of the the investment multiplied by three.
-An investor who has been rewarded for taking the risk of sending an investment is more likely to invest more on future rounds.
-An investor obtaining a low return on their investment may choose to reduce future investment and thereby reduce both players’ gains.
+As seen in Figure \ref{fig:trustGameScreenshot} each player was represented with an icon with the participant always on the left of the screen and the opponent on the right.
+The participants were able to choose the icon that represents them at the start of the experiment.
+The icon representing the opponent changed at the start of each new game, to simulate a new interaction partner.
+Participants were not told they were facing computerised opponents.
+We chose to simulate the behavior of a human interaction partner through allowing for a delay whilst pairing with new opponents as the start of each game as well as programming the agents to respond during each round after a random time lapse (randomly chosen between 5 and 10 seconds).
 
-```{r trustGame,fig.cap = "Screenshot of the repeated Trust Game.
+```{r trustGameScreenshot,fig.cap = "Screenshot of the repeated Trust Game.
 The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee.
@@
 
-## Feedback post investment in the repeated Trust Game
-
 ```{r grid,fig.cap = "Screenshot of the two axis grid in the Coaxing condition where participants were asked to report the valence and arousal of their emotional response ", fig.align='center'}
@@
 
-Whilst playing the RTG, participants were asked to provide some feedback, in each round of the game, after seeing the amount sent by the investor.
+On each round of the RTG, before deciding how much to return, participants were asked to provide feedback on the investment sent.
+This feedback consisted of a rating on two dimensions, provided via a two-dimensional field.
+What the axes of the field represented differed between the conditions.
+In the intervention condition, participants were asked to rate their emotional reaction to the other player’s choice of investment in terms of valence (positive or negative) and arousal (low or high).
+In the control condition, participants were asked to rate the choice of investment in terms of speed (slow or fast) and magnitude (low or high).
+Figure \ref{fig:grid} shows a screenshot of the feedback field in the intervention condition, where participants were asked about their emotional response to the investment.
+At the beginning of each game, participants were provided with detailed explanations of the meaning of the two axes as well as the opportunity to provide a baseline emotional state through using the field prior to the start of the game.
+Participants in the control condition were asked to chose any point on the two dimensional grid to show they have understood how to interact with the grid.
+
+<!-- Whilst playing the RTG, participants were asked to provide some feedback, in each round of the game, after seeing the amount sent by the investor.
 This feedback took the form of the answer to a question using a two dimensional field.
@@
 At the beginning of each game, participants were provided with detailed explanations of the meaning of the two axes as well as the opportunity to provide a baseline emotional state through using the field prior to the start of the game.
+-->
 
@@
 
-The other game the participants played is the repeated Prisoner's Dilemma (RPD).
-Over multiple rounds, participants could choose one of two actions: A cooperative action that would yield a high pay-off if the other person also cooperated, and the lowest possible pay-off if they did not cooperate.
-Or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect.
+The other game the participants played is the normal form, double-choice Repeated Prisoner's Dilemma (RPD).
+Over multiple rounds, participants could choose one of two actions: A cooperative action that would yield a high pay-off if the other person also cooperated, and the lowest possible pay-off if they did not cooperate, or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect.
 Figure \ref{fig:payoffsRPD} shows the payoff of each combination of actions as presented to the participants.
-As an opponent in this game, we used an artificial agent that was playing according to Tit-For-Tat [@axelrod_evolution_1981].
+As an opponent in this game, we used an artificial agent that played according to Tit-For-Tat [@axelrod_evolution_1981].
 It started by choosing the cooperative action and then it mirrored whatever the other player played in the previous round.
@@
 Afterwards, participants were asked whether they would send a low or high return in the same hypothetical scenario now that they have read the information on the slide.
-Players were asked to justify their answer.
+Players were then asked to justify their answer.
 For each question during this intervention, participants had to wait for a fixed duration of 20 seconds before being able to write their answers, and they were prevented from proceeding before that time was up.
@@
 The questionnaires we included in the experiment tried to assess borderline traits (PAI-BOR; @morey_personality_1991), emotional regulation capabilities (DERS; @gratz_multidimensional_2004) and mentalising ability (RFQ8; @fonagy_development_2016).
-As such, we test for any association between scores in these questionnaires and the effect of the intervention.To analyse responses,  we fit a linear mixed effect model to the percentage return of trustees with fixed effects for Condition (intervention or control), Game-number (pre or post manipulation), Investment, and questionnaire score as well as all interactions between the fixed effects.
+As such, we test for any association between scores in these questionnaires and the effect of the intervention.
+To analyse responses,  we fit a linear mixed effect model to the percentage return of trustees with fixed effects for Condition (intervention or control), Game-number (pre or post manipulation), Investment, and questionnaire score as well as all interactions between the fixed effects.
 We assume participant-wise random intercepts.
@@
 The HMM assumes that the probability of each investment $I_t=0,…,20$, at each trial t, conditional on the current state of the investor $S_t$, is dependent on an underlying normal distribution with mean $\mu_s$ and standard deviation $\sigma_s$.
-The probability of each discrete investment was determined by the cumulative normal distribution $\Phi$.
+The probability of each discrete investment was determined from the cumulative normal distribution $\Phi$, computing the probability of a Normal variate falling between the midway points of the response options.
+As responses were bounded at 0 and 20, we normalized these probabilities further by taking the endpoints into account.
 For instance, the probability of an investment $I_t=2$ is defined as:
@@
 The advantages of this approach is that it does not require any a priori assumptions about the model features.
-The number of states, the policy conditional on the state, and the transition function between states can all determined in a purely data driven way.
+The number of states, the policy conditional on the state, and the transition function between states can all determined in a purely data-driven way.
 These HMMs can in turn be used to simulate a human-like agent playing the trust game.
 This agent may transition to a new state depending on the other player's actions and adopt a policy reflecting its state, thus simulating changes in emotional dispositions of human players during a repeated game.
-When the investor gains from the interaction, they become more likely to transition to a state where their policy is to be more trusting and invest more.
-However, faced with losses, the investor is more likely to transition to a more cautious policy where its investment belies lower trust in the trustee.
+When the investor gains from the interaction, they become more likely to transition to a state where their policy is more "trusting" with generally higher investments.
+However, faced with losses, the investor is more likely to transition to a more cautious policy with generally lower investments.
 The policies and the transitions between states are sufficient to build an agent that reflects this type of adaptive behavior and reacts to the trustee's action choices in a way that mimics a human player.
+
+We estimated a three-state model for investor's behaviour, using maximum likelihood estimation via the Expectation-Maximisation algorithm as implemented in the depmixS4 (Visser & Speekenbrink) package for R.
+The model was estimated using investments from existing datasets of human dyads playing 10 rounds of the RTG with the same trustee [@king-casas_rupture_2008; **VTC project dataset**].
+The dataset consisted of a total of 381 games.
+
+# Mixed effects models of participants percentage returns
+
+For both pre and post defection trials, we model the percentage return (percentage of tripled investment returned to investor) using the same linear mixed-effects model used for all the rounds as described in the main text:
+
+\[
+\begin{split}
+R_{ij} = & \beta_0 + \beta_1 \text{ (Condition)}_i + \beta_2 \text{ (Game)}_i + \beta_3 \text{ (Investment)}_i + \\
+& \beta_4 \text{ (Condition × Game)}_i + \beta_5 \text{ (Condition × Investment)}_i + \beta_6 \text{ (Game × Investment)}_i +  \\ 
+& \beta_7 \text{ (Condition × Game × Investment)}_i +b_{0j} + b_{1j} \text{ (Game)}_i + \epsilon_{ij}
+\end{split}
+\]
+
+where:
+
+- \( R_{ij} \): percentage of tripled investment returned to investor for participant \( j \) in observation \( i \)
+- \( \beta_0 \): intercept
+- \( \beta_1 \): effect of Condition (intervention vs. control)
+- \( \beta_2 \): effect of Game (RTG game pre vs. post-intervention)
+- \( \beta_3 \): effect of Investment
+- \( \beta_4 \): interaction effect between Condition and Game
+- \( \beta_5 \): interaction effect between Condition and Investment
+- \( \beta_6 \): interaction effect between Game and Investment
+- \( \beta_7 \): three-way interaction effect between Condition, Game and Investment
+- \( b_{0j} \): participant-wise random intercept for participant \( j \)
+- \( b_{1j} \): participant-wise random slope for Game for participant \( j \)
+- \( \epsilon_{ij} \): error term for participant \( j \) in observation \( i \)
+
+## Mixed-effects model results for pre-defection returns
+
+```{r, include=F}
+
+# Create a summary object
+modelPre_summary <- readRDS("data/mod_returns_pre")
+
+# Extract the fixed effects as a data frame
+summary_Pre_df <- as.data.frame(modelPre_summary$coefficients)
+
+summary_Pre_df <- summary_Pre_df %>%
+  rownames_to_column(var = "Term") %>% 
+  mutate(Term = gsub("condition.f1", "Condition", Term),
+         Term = gsub("gameNum.f1", "Game", Term),
+         Term = gsub("inv_scaled", "Investment", Term))
+
+# Create a summary table using apa_table
+summary_Pretable <- papaja::apa_table(
+  summary_Pre_df,
+  caption = "Summary of Mixed-Effects Model",
+  align = c("l", "c", "c", "c", "c", "c")
+)
+
+```
+
+```{r preDefectionModel,fig.cap = "Summary of results of a Mixed-effects model fitted to participants returns restricted to  pre-defection trials", fig.align='center'}
+
+knitr::include_graphics("figures/modelPre.png")
+
+```
+
+<!-- Figure \ref{fig:preDefectionModel} shows the result of fitting a mixed effect model to participants percentage returns in the RTG when we restrict the analysis to pre-defection trials. -->
+
+## Mixed-effects model results for post-defection returns:
+
+```{r, include=F}
+
+# Create a summary object
+modelPost_summary <- readRDS("data/mod_returns_post")
+
+# Extract the fixed effects as a data frame
+summary_Post_df <- as.data.frame(modelPost_summary$coefficients)
+
+summary_Post_df <- summary_Post_df %>%
+  rownames_to_column(var = "Term") %>% 
+  mutate(Term = gsub("condition.f1", "Condition", Term),
+         Term = gsub("gameNum.f1", "Game", Term),
+         Term = gsub("inv_scaled", "Investment", Term))
+
+# Create a summary table using apa_table
+summary_PostTable <- papaja::apa_table(
+  summary_Post_df,
+  caption = "Summary of Mixed-Effects Model",
+  align = c("l", "c", "c", "c", "c", "c"),
+  label = "tab:postDefection-model"
+)
+
+```
+
+```{r postDefectionModel,fig.cap = "Summary of results of a Mixed-effects model fitted to participants returns restricted to  post-defection trials", fig.align='center'}
+
+#summary_PostTable
+knitr::include_graphics("figures/modelPost.png")
+
+```
+
+<!-- Figure \ref{fig:postDefectionModel} shows the result of fitting a mixed effect model to participants percentage returns in the RTG when we restrict the analysis to post-defection trials.  -->
 
@@
 
-To model participants returns in the RTG across games and conditions,  we fit various hidden Markov models to participants returns.
+To model participants' returns in the RTG across games and conditions,  we fit various hidden Markov models to participants returns.
 The response function is modelled as a discretised Gaussian distribution that takes into account what proportion the trustee would ideally like to return, and what returns are possible given the investment.
 For instance, if the investor sends an amount of $2$, the trustee would receive $6$ and they can send back any amount between $0$ and $6$.
-As such, we assume that the response is a distribution over proportions that can be calculated from these possible returns, i.e.
+As such, we assume that the response is a distribution over the possible proportions that can be calculated from these possible returns, i.e.
 $\{0,1/6, 2/6,...,1 \}$.
@@
 
-$$P(S_{t+1} = s' | S_t=s , X_t = x)= \frac{\exp(\beta_{0,s,s'} + \beta_{1,s,s'} \ \text{inv} + \beta_{2,s,s'} \ x)}{\sum_{s''}\exp(\beta_{0,s,s''} + beta_{1,s,s'} \ \text{inv} + \beta_{2,s,s'} \ x)}$$
+$$P(S_{t+1} = s' | S_t=s , X_t = x)= \frac{\exp(\beta_{0,s,s'} + \beta_{1,s,s'} \ \text{x}+ \beta_{2,s,s'} \ d)}{\sum_{s''}\exp(\beta_{0,s,s''} + \beta_{1,s,s'} \ \text{x} + \beta_{2,s,s'} \ d)}$$
 
-where $\text{inv}$ is a variable representing the investment received, $x$ is a dummy variable to characterise the group that the participant belongs to.
+where $\text{x}$ is a variable representing the investment received, $d$ is a dummy variable to characterise the group that the participant belongs to.
 We define four contrast codes for these dummy variables: pre-post (comparing pre and post games), post-coax (compares the post-intervention group to all others), post-control (compares the post-control group to all others) and full-contrast (a three level dummy variable: post-intervention compared to post-control and  all pre games).
 
-# Distribution of returns for each latent state for HMM model of participant’s returns
+```{r table-BICs,fig.cap = "BICs for each of the five estimated HMM models assuming the latent number of states is between 2 and 7. ", fig.align='center'}
 
-Focusing on the HMM-full models with 5 latent states (please see main manuscript for a definition) we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section.
+knitr::include_graphics("figures/table_bics.png")
+
+```
+
+As seen in Figure \ref{fig:table-BICs},  for a simple model without any contrasts (HMM-inv) and a model with post-control only contrast (HMM-ctrl) we find a 6-state model to be best fitting.
+If the contrast is between the post-intervention group and all the other groups (HMM-coax), then a 7 state model is best fitting.
+When the contrast is comparing only pre and post Intervention groups (HMM-prepost), a 5 state model fits best.
+Finally, when we distinguish between pre-manipulation, post-control and post-intervention (HMM-full), we find that a 5 state model fits best.
+Since we only fit models between 2 and 7 states, it is possible that for those where we find the 7 state model to be best fitting, models with a higher number of states could fit the data better.
+We decided to stop at 7 states for computational cost reasons and because the interpretation of models with a higher number of states becomes complex.
+
+## Distribution of returns for each latent state for HMM model of participant’s returns
+
+Focusing on the HMM-full models with 5 latent states (please see main manuscript for a definition) we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section (Figure \ref{fig:trusteeHMMPlot}).
 Each latent state was associated with a distribution over trustee actions.
@@
 
+## Transition function of HMM model describing participant's returns
+
+Using the HMM-full 5 state model, we can plot the transition probabilities of the model for pre and post-intervention as well as pre- and post-control manipulation separately Figure \ref{fig:plotTransitionsSupp}).
+This allows us to see how the transition probabilities between latent states change across Games and Condition.
+
+```{r plotTransitionsSupp, fig.cap="Transition function for the HMM-full trustee model.
+Each panel represents the state transitioned from.
+For instance the upper left panel represents all transition probabilities from state 1.
+The colors of the lines within each panel indicate the state transitioned to.
+For instance, in the upper left panel, the red line represents the transition probability to state 1 as a function of the received investment.
+In this case this is also the probability of staying in state 1 since we are in the state 1 panel.
+Solid lines show estimated transition probabillities post-manipulation while dotted lines show the same probabilities prior to the manipulation",fig.align="center", fig.width=6, fig.height = 7 }
+
+knitr::include_graphics("figures/trusteeHMMTrans.png")
+
+```
+
+\pagebreak
+
 # References

### 2023-09-25 article.Rmd
revision 25sep2023

@@
 Post-intervention, participants showed more cooperative behavior both before and after defection by the opponent.
-Analysing participants' actions with a hidden Markov model shows that participants in the intervention group had a lower probability of transitioning to non cooperative states, and a higher proportion of cooperative states, than participants in the control group.
+Analysing participants' actions with a hidden Markov model shows that participants in the intervention group had a higher proportion of cooperative states than participants in the control group.
 This is consistent with participants inferring from the intervention that pro-social and trustworthy behavior may generally provide more beneficial outcomes to them in the long run.
@@
 biblio-style: spphys
+
 output:
@@
    toc: false
+
 ---
@@
 
-```{r HMMPanels, fig.cap=" We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
+```{r HMMPanels, fig.cap="We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
 From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel A.
@@
 
-```{r, include=FALSE, cache=TRUE}
+```{r modAllReturns, include=FALSE, cache=TRUE}
 
@@
 
+```
+
+```{r, include=F}
+# Function to calculate y_position for geom_signif
+calculate_y_position <- function(plot) {
+  plot_data <- ggplot_build(plot)$data[[1]]
+  max_y <- max(plot_data$ymax, na.rm = TRUE)
+  y_position <- max_y + (max_y * 0.05) # Adding 5% of the maximum y-value as a margin
+  return(y_position)
+}
 ```
@@
   ggtitle("All rounds percentage returns") + 
-  theme(plot.title = element_text(size = 10)) +
-  theme(legend.position = "bottom")
+  theme(plot.title = element_text(size = 16)) +
+  theme(legend.position = "bottom") +
+  geom_signif(xmin = 0.8, xmax = 1.8, annotations = "***", y_position = 0.88, tip_length = 0.03, textsize = 3) +  # Intervention Group
+  geom_signif(xmin = 1.2, xmax = 2.2, annotations = "*", y_position = 0.80, tip_length = 0.03, textsize = 3)  # Control Group
+
+pctRet_all
 
@@
 
-```{r, include=FALSE, cache=TRUE}
+```{r modInvs, include=FALSE, cache=TRUE}
 mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| playerId), avg_ret_df, method="KR")
@@
   labs(y = "HMM Investment", x = "Game") + 
-  theme(plot.title = element_text(size = 10)) +
-  theme(legend.position = "bottom")
+  theme(plot.title = element_text(size = 16)) +
+  theme(legend.position = "bottom") +
+  geom_signif(xmin = 0.8, xmax = 1.8, annotations = "***", y_position = 1, tip_length = -0.03,textsize = 3) +  # Intervention Group
+  geom_signif(xmin = 1.2, xmax = 2.2, annotations = "***", y_position = 18, tip_length = 0.03,textsize = 3)   # Control Group
 
@@
 summary(mod_returns_pre)
+saveRDS(mod_returns_pre, "data/mod_returns_pre")
 
 pairs_pre_int <- pairs(emmeans::emmeans(mod_returns_pre, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400, reverse=TRUE))
-
-```
+saveRDS(pairs_pre_int, "data/pairs_pre_int")
+
+```
+
 ```{r, include=F}
-saveRDS(summary(mod_returns_pre), "data/mod_returns_pre")
+
+# load(mod_returns_pre)
+# load(pairs_pre_int)
 ```
@@
   ggtitle("Pre defection trials percentage returns")+
-  theme(plot.title = element_text(size = 10)) +
-  theme(legend.position = "bottom")
+  theme(plot.title = element_text(size = 16)) +
+  theme(legend.position = "bottom") + 
+  geom_signif(xmin = 0.8, xmax = 1.8, annotations = "***", y_position = 0.95, tip_length = 0.03,textsize = 3) +  # Intervention Group
+  geom_signif(xmin = 1.2, xmax = 2.2, annotations = "n.s", y_position = 0.85, tip_length = 0.03,textsize = 3)   # Control Group
+
 ```
@@
 ```{r, include=FALSE}
+
 pctRet_post <- afex_plot(mod_postcoax_trust, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
@@
   labs(y = "Percentage Return", x = "Game") + 
-  ggtitle("Post defection trials percentage returns")+
-  theme(plot.title = element_text(size = 10)) +
-  theme(legend.position = "bottom")
-```
-
-```{r violinPanels, fig.cap="Participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds (Panel A).
-This was also the case both before (Panel C) and after (Panel D) the pre-programmed defection by the HMM investor.
-Those in the control conditions returned similar amounts between games before the defection, and lower amounts in the second game after the defection by the investor.
+  ggtitle("Post defection trials percentage returns") +
+  theme(plot.title = element_text(size = 16)) +
+  theme(legend.position = "bottom") +
+  geom_signif(xmin = 0.8, xmax = 1.8, annotations = "n.s", y_position = 0.95, tip_length = 0.03,textsize = 3) +  # Intervention Group
+  geom_signif(xmin = 1.2, xmax = 2.2, annotations = "***", y_position = 0.9, tip_length = 0.03,textsize = 3)   # Control Group
+
+```
+
+```{r violinPanels, fig.cap="Participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds (Panel A), whilst those in the Control condition sent back lower returns.
+Focusing on pre-defection trials (Panel C), those in the Control condition returned similar amounts between games, while returns were higher in the Intervention condition in the second game.
+Post-defection (Panel D), returns were similar for those in the Intervention condition while those in the Control condition returned lower amounts in the second game.
 Investments by the HMM agent (Panel B) were higher in the second game compared to the first game across conditions.
-All panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition", fig.align="center", fig.width=6, fig.height = 6}
+All panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition", fig.align="center", fig.height=10, fig.width=10}
 
@@
 ```{r emoPlotCoax, fig.cap="Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
-The participants' emotion self-reports for the investor's defection were similar before and after the intervention.",fig.align="center", fig.width=7, fig.height = 4}
+The participants' emotion reaction measured during the investor's defection round were similar before (round 12) and after (round 13) the intervention.",fig.align="center", fig.width=7, fig.height = 4}
 
@@
 
-```{r, include=FALSE}
+```{r, include=FALSE, echo=FALSE, warning=F}
 
@@
 
+# ordering states for a truncated discretised Gaussian
+order_mod_truncdiscgaus <- function(mod) {
+  ns <- nstates(mod)
+  sum <- rep(0.0,ns)
+  for(i in 1:ns) {
+    # Expected return in each state calculation
+    tpars <- getpars(mod@response[[i]][[1]])
+    dmod <- truncdiscgaus(seq(0, 20), pstart = tpars, min=-0.5, max=20.5)
+    sum[i] <- sum(seq(0,20)*dens(dmod))
+  }
+  cat("Expected values for states: ",sum, "\n")
+  # reordering the states
+  mod <- label_switch(mod, rank(sum, ties.method = "first"))
+  return(mod)
+}
+
+# ordering states for a variable response truncated discretised Gaussian
+order_mod_vtdgaus <- function(mod) {
+  ns <- nstates(mod)
+  sum <- rep(0.0,ns)
+  for(i in 1:ns) {
+    # Expected return in each state calculation
+    tpars <- getpars(mod@response[[i]][[1]])
+    dmod <- vtdgaus(seq(0, 1, length=61), pstart = tpars, yield=rep(60, 61))
+    sum[i] <- sum(seq(0, 1, length=61)*dens(dmod))
+  }
+  # reordering the states
+  mod <- label_switch(mod, rank(sum, ties.method = "first"))
+  return(mod)
+}
+
 ```
@@
 ```{r, include=F}
+# # define a response class which only contains the standard slots, no additional slots
+# setClass("discgaus", contains="response", slots=c(breaks="numeric"))
+# 
+# # define a generic for the method defining the response class
+# 
+# setGeneric("discgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("discgaus"))
+# 
+# # define the method that creates the response class
+# 
+# setMethod("discgaus", 
+#           signature(y="ANY"), 
+#           function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), ...) {
+#             y <- matrix(y,length(y))
+#             x <- matrix(1)
+#             parameters <- list()
+#             npar <- 2
+#             if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
+#             if(!is.null(pstart)) {
+#               if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
+#               parameters$mu <- pstart[1]
+#               parameters$sigma <- pstart[2]
+#             }
+#             mod <- new("discgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, breaks=breaks)
+#             mod
+#           }
+# )
+# 
+# setMethod("show","discgaus",
+#           function(object) {
+#             cat("Gaussian with discrete support\n")
+#             cat("Parameters: \n")
+#             cat("mu: ", object@parameters$mu, "\n")
+#             cat("sigma: ", object@parameters$sigma, "\n")
+#           }
+# )
+# 
+# setMethod("dens","discgaus",
+#           function(object,log=FALSE) {
+#             p <- pnorm(object@breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@breaks[-length(object@breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
+#             if(log) return(log(p[as.numeric(cut(object@y, breaks=object@breaks))])) else return(p[as.numeric(cut(object@y, breaks=object@breaks))])
+#           }
+# )
+# 
+# setMethod("setpars","discgaus",
+#           function(object, values, which="pars", ...) {
+#             npar <- npar(object)
+#             if(length(values)!=npar) stop("length of 'values' must be",npar)
+#             # determine whether parameters or fixed constraints are being set
+#             nms <- names(object@parameters)
+#             switch(which,
+#                    "pars"= {
+#                      object@parameters$mu <- values[1]
+#                      object@parameters$sigma <- values[2]
+#                    },
+#                    "fixed" = {
+#                      object@fixed <- as.logical(values)
+#                    }
+#             )
+#             names(object@parameters) <- nms
+#             return(object)
+#           }
+# )
+# 
+# setMethod("getpars","discgaus",
+#           function(object,which="pars",...) {
+#             switch(which,
+#                    "pars" = {
+#                      parameters <- numeric()
+#                      parameters <- unlist(object@parameters)
+#                      pars <- parameters
+#                    },
+#                    "fixed" = {
+#                      pars <- object@fixed
+#                    }
+#             )
+#             return(pars)
+#           }
+# )
+# 
+# setMethod("fit","discgaus",
+#           function(object,w) {
+#             if(missing(w)) w <- NULL
+#             if(!is.null(w)) {
+#               negLL <- function(pars) {
+#                 object <- setpars(object, c(pars[1], exp(pars[2])))
+#                 -sum(w*log(dens(object)))
+#               }
+#             } else {
+#               negLL <- function(pars) {
+#                 object <- setpars(object, c(pars[1], exp(pars[2])))
+#                 -sum(log(dens(object)))
+#               }
+#             }
+#             pars <- optim(c(object@parameters$mu, log(object@parameters$sigma)), fn=negLL)$par
+#             object <- setpars(object,c(pars[1], exp(pars[2])))
+#             object
+#           }
+# )
+# 
+# setClass("truncdiscgaus", contains="discgaus", slots=c(min="numeric", max="numeric"))
+# 
+# setMethod("dens","truncdiscgaus",
+#           function(object,log=FALSE) {
+#             breaks <- c(object@min, object@breaks[object@breaks > object@min & object@breaks < object@max], object@max)
+#             p <- pnorm(breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(breaks[-length(breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
+#             p <- p/sum(p)
+#             if(log) return(log(p[as.numeric(cut(object@y, breaks=object@breaks))])) else return(p[as.numeric(cut(object@y, breaks=object@breaks))])
+#           }
+# )
+# 
+# setGeneric("truncdiscgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("truncdiscgaus"))
+# 
+# setMethod("truncdiscgaus", 
+#           signature(y="ANY"), 
+#           function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), min=0, max=20, ...) {
+#             y <- matrix(y,length(y))
+#             x <- matrix(1)
+#             parameters <- list()
+#             npar <- 2
+#             if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
+#             if(!is.null(pstart)) {
+#               if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
+#               parameters$mu <- pstart[1]
+#               parameters$sigma <- pstart[2]
+#             }
+#             mod <- new("truncdiscgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, breaks=breaks, min=min, max=max)
+#             mod
+#           }
+# )
+# 
+# 
+# order_mod_gauss <- function(mod) {
+#   ns <- nstates(mod)
+#   sum <- rep(0.0,ns)
+#   for(i in 1:ns) {
+#     # Expected return in each state calculation 
+#     sum[i] = mod@response[[i]][[1]]@parameters$mu
+#   }
+#   # reordering the states
+#   mod <- label_switch(mod, rank(sum))
+#   return(mod)
+# }
+# 
+# # define a response class which only contains the standard slots, no additional slots
+# setClass("vtdgaus", contains="response", slots=c(yield="numeric"))
+# 
+# # define a generic for the method defining the response class
+# 
+# setGeneric("vtdgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("vtdgaus"))
+# 
+# # define the method that creates the response class
+# 
+# setMethod("vtdgaus", 
+#           signature(y="ANY"), 
+#           function(y, yield, pstart=NULL,fixed=NULL, ...) {
+#             y <- matrix(y,length(y))
+#             x <- matrix(1)
+#             parameters <- list()
+#             npar <- 2
+#             if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
+#             if(!is.null(pstart)) {
+#               if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
+#               parameters$mu <- pstart[1]
+#               parameters$sigma <- pstart[2]
+#             } else {
+#               parameters <- list(mu=.5,sigma=1)
+#             }
+#             mod <- new("vtdgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, yield=yield)
+#             mod
+#           }
+# )
+# 
+# setMethod("show","vtdgaus",
+#   function(object) {
+#     cat("Gaussian with variable discrete support for percentage responses\n")
+#     cat("Parameters: \n")
+#     cat("mu: ", object@parameters$mu, "\n")
+#     cat("sigma: ", object@parameters$sigma, "\n")
+#   }
+# )
+# 
+# setMethod("dens","vtdgaus",
+#   function(object,log=FALSE) {
+#       # determine cuts for pnorm based on 
+#       p <- pnorm(sapply(object@y + .5*(1/object@yield),function(x) min(x,1.001)), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(sapply(object@y - .5*(1/object@yield),function(x) max(x,-0.001)), mean = object@parameters$mu, sd = object@parameters$sigma)
+#       norm <- (pnorm(1 + .001, mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(-0.001, mean = object@parameters$mu, sd = object@parameters$sigma))
+#       p <- p/norm
+#       # alternatively, normalize factor based on size of cuts
+#       #p <- pnorm(object@y + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@y - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma)
+#       #p <- p/(pnorm(1 + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(0 - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma))
+#     # probability when yield == 0 is always 1 
+#       p[object@yield == 0] <- 1
+#       if(log) return(log(p)) else return(p)
+#     }
+# )
+# 
+# setMethod("setpars","vtdgaus",
+#           function(object, values, which="pars", ...) {
+#             npar <- npar(object)
+#             if(length(values)!=npar) stop("length of 'values' must be",npar)
+#             # determine whether parameters or fixed constraints are being set
+#             nms <- names(object@parameters)
+#             switch(which,
+#                    "pars"= {
+#                      object@parameters$mu <- values[1]
+#                      object@parameters$sigma <- values[2]
+#                    },
+#                    "fixed" = {
+#                      object@fixed <- as.logical(values)
+#                    }
+#             )
+#             names(object@parameters) <- nms
+#             return(object)
+#           }
+# )
+# 
+# setMethod("getpars","vtdgaus",
+#           function(object,which="pars",...) {
+#             switch(which,
+#                    "pars" = {
+#                      parameters <- numeric()
+#                      parameters <- unlist(object@parameters)
+#                      pars <- parameters
+#                    },
+#                    "fixed" = {
+#                      pars <- object@fixed
+#                    }
+#             )
+#             return(pars)
+#           }
+# )
+# 
+# setMethod("fit","vtdgaus",
+#           function(object,w) {
+#             if(missing(w)) w <- NULL
+#             if(!is.null(w)) {
+#               negLL <- function(pars) {
+#                 object <- setpars(object, c(pars[1], exp(pars[2])))
+#                 -sum(w*log(dens(object)))
+#               }
+#             } else {
+#               negLL <- function(pars) {
+#                 object <- setpars(object, c(pars[1], exp(pars[2])))
+#                 -sum(log(dens(object)))
+#               }
+#             }
+#             pars <- optim(c(object@parameters$mu, log(object@parameters$sigma)), fn=negLL)$par
+#             object <- setpars(object,c(pars[1], exp(pars[2])))
+#             object
+#           }
+# )
+```
+
+```{r,include=F}
 # define a response class which only contains the standard slots, no additional slots
@@
           signature(y="ANY"), 
-          function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), ...) {
+          function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, seq(0, 19) + .5, Inf), ...) {
             y <- matrix(y,length(y))
@@
               parameters$sigma <- pstart[2]
+            } else {
+              parameters <- list(mu = 10, sigma = 3)
             }
@@
             breaks <- c(object@min, object@breaks[object@breaks > object@min & object@breaks < object@max], object@max)
+            prec <- pnorm(object@max, mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@min, mean = object@parameters$mu, sd = object@parameters$sigma)
+            if(prec < 1e-12) {
+              # return uniform probabilities as precision is likely off
+              p <- rep(1/(length(breaks)-1), length(object@y))
+              if(log) return(log(p)) else return(p)
+            } else {
               p <- pnorm(breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(breaks[-length(breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
@@
             }
+          }
 )
@@
           signature(y="ANY"), 
-          function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), min=0, max=20, ...) {
+          function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, seq(0, 19) + .5, Inf), min=-0.5, max=20.5, ...) {
             y <- matrix(y,length(y))
@@
 )
-
-order_mod_gauss <- function(mod) {
-  ns <- nstates(mod)
-  sum <- rep(0.0,ns)
-  for(i in 1:ns) {
-    # Expected return in each state calculation 
-    sum[i] = mod@response[[i]][[1]]@parameters$mu
-  }
-  # reordering the states
-  mod <- label_switch(mod, rank(sum))
-  return(mod)
-}
 
@@
       # determine cuts for pnorm based on 
-      p <- pnorm(sapply(object@y + .5*(1/object@yield),function(x) min(x,1.001)), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(sapply(object@y - .5*(1/object@yield),function(x) max(x,-0.001)), mean = object@parameters$mu, sd = object@parameters$sigma)
-      norm <- (pnorm(1 + .001, mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(-0.001, mean = object@parameters$mu, sd = object@parameters$sigma))
+      #p <- pnorm(sapply(object@y + .5*(1/object@yield), function(x) min(x,1.001)), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(sapply(object@y - .5*(1/object@yield),function(x) max(x,-0.001)), mean = object@parameters$mu, sd = object@parameters$sigma)
+      #norm <- (pnorm(1 + .001, mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(-0.001, mean = object@parameters$mu, sd = object@parameters$sigma))
+      #p <- p/norm
+
+      # alternatively, normalize factor based on size of cuts
+
+      prec <- pnorm(1 + .5*(1/60), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(0 - .5*(1/60), mean = object@parameters$mu, sd = object@parameters$sigma)
+      # check for issues with precision, using highest yield
+      if(prec < 1e-12) {
+        p <- 1/(object@yield + 1)
+      } else {
+        p <- pnorm(object@y + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@y - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma)
+        norm <- pnorm(1 + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(0 - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma)
         p <- p/norm
-      # alternatively, normalize factor based on size of cuts
-      #p <- pnorm(object@y + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@y - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma)
-      #p <- p/(pnorm(1 + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(0 - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma))
+      }
       # probability when yield == 0 is always 1 
@@
 
-  rModels <- rep(list(list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment))),each=i)
+  # rModels <- rep(list(list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment))),each=i)
+
+  ###########################################################
+  mus <- (1:i)*(1/(i+1))
+  sigmas <- rep(1/(i+1), i)
+  rModels <- list()
+  for(s in 1:i) {
+    rModels[[s]] <- list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment, pstart=c(mus[s],sigmas[s])))
+  }
+  #########################################################
 
@@
 }
+
 ```
@@
 # fittedSimple <- fittedCoax  <- fittedCtrl  <- fittedFullCtrst  <- fittedPrePost  <- list()
-# # increase default in multistart from 10 to 20. or set the same seed for every model
-# 
 # set.seed(20221028)
@@
 # 
-#   fittedSimple[[i]] <- multistart(simple_HMMs[[i]],nstart=20)
-# }
-# save(fittedSimple, file="fittedSimple.RData")
+#   #fittedSimple[[i]] <- multistart(simple_HMMs[[i]],nstart=20)
+#   fittedSimple[[i]] <- fit(simple_HMMs[[i]], emcontrol=em.control(random.start = FALSE))
+# }
+# save(fittedSimple, file="data/fittedSimple.RData")
 # ##############################
@@
 # for(i in n_state_min:n_state_max) {
-#   fittedCtrl[[i]] <- multistart(ctrl_HMMs[[i]],nstart=20)
-# }
-# save(fittedCtrl, file="fittedCtrl.RData")
+#   #fittedCtrl[[i]] <- multistart(ctrl_HMMs[[i]],nstart=20)
+#   fittedCtrl[[i]] <- fit(ctrl_HMMs[[i]], emcontrol=em.control(random.start = FALSE))
+# }
+# save(fittedCtrl, file="data/fittedCtrl.RData")
 # ##############################
 # 
-# fittedCoax <- list()
+# 
 # set.seed(20230918)
 # for(i in n_state_min:n_state_max) {
-#   fittedCoax[[i]] <- multistart(coax_HMMs[[i]],nstart=20)
-# }
-# save(fittedCoax, file="fittedCoax.RData")
+#   # fittedCoax[[i]] <- multistart(coax_HMMs[[i]],nstart=20)
+#   fittedCoax[[i]] <- fit(coax_HMMs[[i]], emcontrol=em.control(random.start = FALSE))
+# }
+# save(fittedCoax, file="data/fittedCoax.RData")
 # ##############################
@@
 # for(i in n_state_min:n_state_max) {
-#   fittedPrePost[[i]] <- multistart(prePost_HMMs[[i]],nstart=20)
-# }
-# save(fittedPrePost, file="fittedPrePost.RData")
+#   #fittedPrePost[[i]] <- multistart(prePost_HMMs[[i]],nstart=20)
+#   fittedPrePost[[i]] <- fit(prePost_HMMs[[i]], emcontrol=em.control(random.start = FALSE))
+# }
+# save(fittedPrePost, file="data/fittedPrePost.RData")
 # #############################
 # 
-# 
-# 
+# set.seed(20230922)
 # for(i in n_state_min:n_state_max) {
-#   fittedFullCtrst[[i]] <- multistart(fullCtrst_HMMs[[i]],nstart=20)
-# }
-# save(fittedFullCtrst, file="fittedFullCtrst.RData")
+#   #fittedFullCtrst[[i]] <- multistart(fullCtrst_HMMs[[i]],nstart=20)
+#   fittedFullCtrst[[i]] <- fit(fullCtrst_HMMs[[i]], emcontrol=em.control(random.start = FALSE))
+# }
+# save(fittedFullCtrst, file="data/fittedFullCtrst.RData")
 # ###############################
@@
 load("data/fittedCoax.RData")
+load("data/fittedPrePost.RData")
 load("data/fittedFullCtrst.RData")
-load("data/fittedPrePost.RData")
-load("data/newFull.RData")
-
-# 
-# has_converged <- function(object, numeric = TRUE){
-#   msg <- object@message
-#   if(numeric) as.integer(grepl("converged", msg)) else 0
-# }
-# 
-# 
-# sapply(fittedSimple[2:7],has_converged)
-# sapply(fittedCtrl[2:7],has_converged)
-# sapply(fittedCoax[2:7],has_converged)
-# sapply(fittedFullCtrst[2:7],has_converged)
-# sapply(fittedPrePost[2:7],has_converged)
-# sapply(newFull[2:7],has_converged)
 
@@
 # Fitting "Coax" models with initial parameters from the fitted "Simple" model.
-# 
 # newCoax <- fittedCoax
@@
 
-load("data/fittedSimple.RData")
-load("data/fittedCtrl.RData")
-load("data/fittedCoax.RData")
-load("data/fittedFullCtrst.RData")
-load("data/fittedPrePost.RData")
-
 load("data/newCtrl.RData")
@@
 load("data/newPrePost.RData")
-load("data/newFull.RData")
 
@@
 #   mat <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
-#   print(mat)
+#   #print(mat)
 #   new_mat <- mat[,c(1:2,3,3,4,4)]
@@
 # 
-# save(newFull, file="newFull.RData")
-
-```
-
-```{r}
+# save(newFull, file="data/newFull.RData")
+
+```
+
+```{r, include=F}
+
+load("data/newFull.RData")
 
@@
 ```{r, include=F}
-
 BICs_simple <- BICs_Ctrl <- BICs_Coax <-  BICs_PrePost <-  BICs_Full <- list()
@@
 df_bics
+
+df_bics_full <- data.frame(nstate = 2:7,
+                          logLik = unlist(lapply(bestFull[-1], logLik)),
+                          unlist(lapply(bestFull[-1], function(x) attr(logLik(x), which="df"))),
+                          AIC = unlist(lapply(bestFull[-1], AIC)),
+                          BIC = unlist(lapply(bestFull[-1], BIC)))
+```
+
+```{r, include=F}
+
+df_bics_full %>%
+  `colnames<-` (c("Number of states", "logLikelihood", "df", "AIC", "BIC")) %>%
+  mutate(across(all_of(c("logLikelihood", "df", "AIC", "BIC")), 
+                ~format(., digits=4, nsmall=0, big.mark=","))) %>%
+  knitr::kable(., escape = FALSE, booktabs = TRUE,
+               caption = 'Table comparing HMM-full model fit for assumed number of latent states between 2 and 7') %>%
+  kable_styling(latex_options="scale_down",font_size = 10)
 
@@
 
-# data.frame(df_bics) %>% 
-#   `colnames<-` (c("Number of states","HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost","HMM-full")) %>%
-#   mutate_if(is.numeric, format, digits=4,nsmall = 0, big.mark = ",") %>% 
-#   knitr::kable(.,booktabs = TRUE,
-#   caption = 'Table of BICs for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>% kable_styling(latex_options="scale_down")
-
+df_liks <- as.data.frame(df_liks)
+
+df_liks %>%
+  `colnames<-` (c("Number of states", "HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost", "HMM-full")) %>%
+  mutate_at(vars(-`Number of states`), bold_max) %>%
+  knitr::kable(., escape = FALSE, booktabs = TRUE,
+               caption = 'Table of likelihoods for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>%
+  kable_styling(latex_options="scale_down")
+
+##### BICs ###########
 # Ensure df_bics is a data frame
@@
                caption = 'Table of BICs for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>%
-  kable_styling(latex_options="scale_down")
-
-df_liks <- as.data.frame(df_liks)
-
-df_liks %>%
-  `colnames<-` (c("Number of states", "HMM-inv", "HMM-ctrl", "HMM-coax", "HMM-prepost", "HMM-full")) %>%
-  mutate_at(vars(-`Number of states`), bold_max) %>%
-  knitr::kable(., escape = FALSE, booktabs = TRUE,
-               caption = 'Table of likelihoods for each of the estimated HMM models for assumed number of latent states between 2 and 7') %>%
   kable_styling(latex_options="scale_down")
@@
 Finally, the HMM-inv model did not allow transition probabilities to differ between conditions or games, modelling them only as a function of investment.
-As the number of hidden states was unknown, for each model we estimated versions with 2 to 7 states, and used the BIC to select the best fitting model.
-Generally, best fitting models had between 5 to 7 hidden states.
+
+As the number of hidden states was unknown, we estimated models with 2 to 7 latent states for the most complex HMM-full model, and used the BIC to compare them.
+The best fitting HMM-full model according to the BIC had 6 latent states.
 Further details on the HMMs and estimation procedure are provided in the Supplementary Information.
@@
 ```{r, include=FALSE}
-summary(fittedSimple[[5]])
-
-logLik(fittedSimple[[5]])
-logLik(bestCtrl[[5]])
-logLik(bestCoax[[5]])
-logLik(bestPrePost[[5]])
-# logLik(fittedFullCtrst[[5]])
-logLik(bestFull[[5]])
-
-# Nested model comparison for 5 states, with and without intervention contrast. llratio test shows no effect, meaning interaction term addition does not change goodness of fit of model. 
-llratio(bestFull[[5]], fittedSimple[[5]])
-
-llratio(bestCtrl[[5]],fittedSimple[[5]])
-llratio(bestCoax[[5]],fittedSimple[[5]])
-llratio(bestPrePost[[5]],fittedSimple[[5]])
-
-llratio(bestFull[[5]],bestCtrl[[5]])
-llratio(bestFull[[5]],bestCoax[[5]])
-llratio(bestFull[[5]],bestPrePost[[5]])
+
+llratio(bestFull[[6]], fittedSimple[[6]])
+llratio(bestFull[[6]],bestCtrl[[6]])
+llratio(bestFull[[6]],bestCoax[[6]])
+llratio(bestFull[[6]],bestPrePost[[6]])
 
@@
 
-Focusing on models with 5 latent states (which is the optimal number for the HMM-full model), likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCtrl[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCoax[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestPrePost[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$).
+Focusing on the HMM-full model with 6 latent states, likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCtrl[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCoax[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestPrePost[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$).
 <!-- We start by comparing HMM-full with HMM-inv.
@@
 ```{r, include=FALSE}
-tr_fdmod_5 <- order_mod_gauss(bestFull[[5]])
-```
-
-```{r, include=FALSE}
-
-state1 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[1]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-state2 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[2]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-state3 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[3]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-state4 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[4]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
-
-state5 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_5@response[[5]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
+tr_fdmod_6 <- order_mod_gauss(bestFull[[6]])
+```
+
+```{r, include=FALSE}
+
+state1 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_6@response[[1]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
+
+state2 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_6@response[[2]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
+
+state3 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_6@response[[3]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
+
+state4 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_6@response[[4]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
+
+state5 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_6@response[[5]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
+
+state6 <- dens(truncdiscgaus(seq(0.025,0.975,length=20),pstart=c(unlist(tr_fdmod_6@response[[6]][[1]]@parameters)), breaks = c(0, seq(0.05,0.95,length=19) , 1),  min=0, max=1))
 
@@
 
-response_best_mod <- as.data.frame(cbind(returns,state1,state2,state3,state4,state5)) %>% 
-  pivot_longer(cols=c("state1","state2","state3","state4","state5"),
+response_best_mod <- as.data.frame(cbind(returns,state1,state2,state3,state4,state5, state6)) %>% 
+  pivot_longer(cols=c("state1","state2","state3","state4","state5", "state6"),
                     names_to='Trustee_state',
@@
 
-```{r, include=FALSE}
-
-# plot_state_transitions <- function(fmod, numCovIn, numCovTr) {
-# 
-#   #print(getpars(fmod))
-#   ns <- nstates(fmod)
-#   
-#   trans_prob <- data.frame(
-#     from = rep(1:ns, each=100*ns),
-#     to = rep(1:ns, each=100),
-#     investment = seq(0,20,length=100),
-#     prob_pre = 0,
-#     prob_ctrl = 0,
-#     prob_coax =0
-#   )
-#   
-#   y0 <- matrix(0.0,ncol=ns, nrow=100)
-#   y1 <- matrix(0.0,ncol=ns, nrow=100)
-#   y2 <- matrix(0.0,ncol=ns, nrow=100)
-#   
-#   for(from in 1:ns) {
-#   pars <- matrix(getpars(fmod)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
-#   #print(pars)
-#   
-#     for(to in 1:ns) {
-#         x <- trans_prob[trans_prob$from == from & trans_prob$to == to,"investment"]
-#         y0[,to] <- exp(pars[to,1] + pars[to,2]*x)
-#         #ctrst 2 = 1, post intervention vs pre
-#         y2[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,3]*1 + pars[to,5]*x )
-#         #ctrst 1 = 1, post control vs pre
-#         y1[,to] <- exp(pars[to,1] + pars[to,2]*x + pars[to,4]*1 + pars[to,6]*x )
-#     }
-#     y0 <- y0/rowSums(y0)
-#     y1 <- y1/rowSums(y1)
-#     y2 <- y2/rowSums(y2)
-#     
-#     for(to in 1:ns) {
-#       trans_prob$prob_pre[trans_prob$from == from & trans_prob$to == to] <- y0[,to]
-#       trans_prob$prob_ctrl[trans_prob$from == from & trans_prob$to == to] <- y1[,to]
-#       trans_prob$prob_coax[trans_prob$from == from & trans_prob$to == to] <- y2[,to]
-#     }
-#   }
-#   
-#   
-#   
-#   saveRDS(trans_prob, "data/trans_prob.RDS")
-#   
-#   return(trans_prob)
-# 
-# }
-# 
-# 
-# plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6) 
+```{r, include=F, fig.align="center"}
+
+tr_policy <- list()
+for(i in 1:nstates(tr_fdmod_6)) {
+  tr_policy[[i]] <- dens(vtdgaus(seq(0,1, length=61), yield=3*20, pstart=c(unlist(tr_fdmod_6@response[[i]][[1]]@parameters))))  
+}
+
+perc_return <- seq(0,1, length=61)
+df_tr_policy <- data.frame(trustee_state = rep(1:nstates(tr_fdmod_6), each=length(perc_return)),
+                            perc_return = perc_return,
+                            probability = unlist(tr_policy))
+
+ggplot(df_tr_policy,                            
+       aes(x = perc_return,
+           y = probability,
+           fill = factor(paste0("state ",trustee_state)))) +
+  geom_bar(stat = "identity",
+           position = "dodge") + 
+  labs(fill='Latent trustee state') +
+  xlab("Percentage return") +
+  theme_minimal() + 
+  theme(legend.position = "bottom")
+```
+
+```{r, include=FALSE}
+
 plot_state_transitions <- function(fmod, numCovIn, numCovTr) {
@@
     to = rep(paste0("State ", 1:ns), times=100),
-    investment = seq(0,20,length=100),
+    investment = rep(seq(0,20,length=100),each=ns),
     prob_pre = 0,
@@
 
-plot_state_transitions(tr_fdmod_5, numCovIn=2, numCovTr=6)
+plot_state_transitions(tr_fdmod_6, numCovIn=2, numCovTr=6)
 
@@
 # mention we are using local decoding (refer to the book). 
-predTrStates <- posterior(tr_fdmod_5, type="local")
-avg_ret_df$TrState <-  factor(predTrStates, levels= c(1,2,3,4,5),labels=c("State 1","State 2","State 3","State 4","State 5"))
-
-# avg_ret_df$TrState <-  factor(predTrStates, levels= c(5,4,3,2,1),labels=c("5","4","3","2","1"))
-
-# predTrStates <- posterior(tr_fdmod_5)
-# avg_ret_df$TrState <-  factor(predTrStates$state, levels= c(1,2,3,4,5),labels=c("1","2","3","4","5"))
+predTrStates <- posterior(tr_fdmod_6, type="local")
+avg_ret_df$TrState <-  factor(predTrStates, levels= c(1,2,3,4,5,6),labels=c("State 1","State 2","State 3","State 4","State 5", "State 6"))
 
@@
 ```{r, include=FALSE}
-
-trusteeHMMPlot <- ggplot(response_best_mod,                            
-       aes(x = returns,
-           y = probability,
-           fill = Trustee_state)) +
-  geom_bar(stat = "identity",
-           position = "dodge") + 
-  labs(fill='Latent trustee State') +
-  theme_bw() + 
-  theme(legend.position = "bottom")
-
-# investor real state distribution (posterior)
-# postHMM <- ggplot(avg_ret_df %>% dplyr::filter(gameNum.f=="post")) +
-#   geom_bar(aes(x = roundNum, group = TrState, fill = TrState),  position = position_stack(reverse = TRUE)) + 
-#   facet_wrap(~condition.f) +  
-#   labs(x = "Round", fill='Posterior trustee state') +
-#   theme_bw() +
-#   theme(legend.position = "bottom")
-
 postHMM <- ggplot(avg_ret_df %>% dplyr::filter(gameNum.f=="post")) +
@@
 
-```{r postStatesBestModOld,  echo=FALSE, fig.cap = "A: Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model.
-The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social.
-B: Distribution of posterior trustee states post manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.", fig.align="center", fig.height = 8}
-
-# ggpubr::ggarrange(trusteeHMMPlot , postHMM , nrow=2, ncol=1,labels = c("A", "B"),common.legend = FALSE)
-
-```
-
-```{r postStatesBestMod,  echo=FALSE, fig.cap = "Distribution of posterior trustee states post manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.", fig.align="center", fig.height = 4}
+```{r postStatesBestMod,  echo=FALSE, fig.cap = "Distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.
+States are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.
+This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.", fig.align="center"}
 
@@
 
-prop.test(c(11,29), c(159,159))
+prop.test(c(8,20), c(159,159))
 
@@
 
-Taking the best-fitting 5-state HMM-full model, we used a local decoding procedure to assign observations (participants' returns on trials) to latent states.
+Taking the best-fitting 6-state HMM-full model, we used a local decoding procedure to assign observations (participants' returns on trials) to latent states.
 The states are ordered by expected return, with state 1 having the lowest mean return and state 5 the highest.
 Figure \ref{fig:postStatesBestMod} shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
-For instance, in round 5, state 1 was the most likely posterior state for only $7$% of participants in the intervention condition compared to $24$% in the control condition ($\chi^2(1) = 8.26, p < 0.01$).
-For the post-defection trial after the intervention (round 14), state 1 was the most likely state for only $22$% of participants in the intervention condition compared to $43$% in the control condition ($\chi^2(1) = 14.70, p < 0.001$).
+For instance, in round 5, state 1 was the most likely posterior state for only $5$% of participants in the intervention condition compared to $12$% in the control condition ($\chi^2(1) = 4.73, p = 0.03$).
+For the post-defection trial after the intervention (round 14), state 1 was the most likely state for only $15$% of participants in the intervention condition compared to $31$% in the control condition ($\chi^2(1) = 14.70, p < 0.001$).
 Whilst the posterior states indicate that the intervention was effective, a non-negligible proportion of participants in the intervention condition did not exhibit the coaxing behavior promoted by the intervention.
-Directly following the low investment in round 13, $30.2$% of participants in the intervention condition were assigned to state 1 with the lowest average returns.
-There is thus clear heterogeneity in the effectiveness of the intervention.
+Directly following the low investment in round 13, $17$% of participants in the intervention condition were assigned to state 1 with the lowest average returns highlighting individual differences in the effectiveness of the intervention.
 

### 2023-09-25 supplement.Rmd
revision 25sep2023

@@
 The trustee in turn needs to decide how much of the multiplied investment they want to send back to the investor.
-Shown here is the stage at which the trustee makes a decision of how much to send back the investor", fig.align='center'}
+Shown here is the stage at which the trustee makes a decision of how much to send back the investor", out.width="70%", out.height="70%", fig.align='center'}
 
@@
 
-```{r grid,fig.cap = "Screenshot of the two axis grid in the Coaxing condition where participants were asked to report the valence and arousal of their emotional response ", fig.align='center'}
+```{r grid,fig.cap = "Screenshot of the two axis grid in the Coaxing condition where participants were asked to report the valence and arousal of their emotional response ", out.width="70%", out.height="70%", fig.align='center'}
 
@@
 Or a non-cooperative option that would yield a high pay-off if the other person chooses the cooperative action and a lower pay-off if they also defect.
-Shown here is the table explaining the payoffs of each combination of actions the participant and their opponent choose", fig.align='center'}
+Shown here is the table explaining the payoffs of each combination of actions the participant and their opponent choose", out.width="70%", out.height="70%", fig.align='center'}
 
@@
 
-```{r table-BICs,fig.cap = "BICs for each of the five estimated HMM models assuming the latent number of states is between 2 and 7. ", fig.align='center'}
+```{r table-HMMs,fig.cap = "Table comparing the HMM-full models fit assuming the latent number of states is between 2 and 7.
+Using BIC, the 6 state model fits best", out.width="70%", out.height="70%", fig.align='center'}
 
-knitr::include_graphics("figures/table_bics.png")
+knitr::include_graphics("figures/table_HMMfull_comp.png")
 
@@
 
-As seen in Figure \ref{fig:table-BICs},  for a simple model without any contrasts (HMM-inv) and a model with post-control only contrast (HMM-ctrl) we find a 6-state model to be best fitting.
-If the contrast is between the post-intervention group and all the other groups (HMM-coax), then a 7 state model is best fitting.
-When the contrast is comparing only pre and post Intervention groups (HMM-prepost), a 5 state model fits best.
-Finally, when we distinguish between pre-manipulation, post-control and post-intervention (HMM-full), we find that a 5 state model fits best.
-Since we only fit models between 2 and 7 states, it is possible that for those where we find the 7 state model to be best fitting, models with a higher number of states could fit the data better.
+As seen in Figure \ref{fig:table-HMMs}, using the BIC, the 6 state HMM-full model fits best.
+Since we only fit models between 2 and 7 states, it is possible that models with a higher number of states could fit the data better.
 We decided to stop at 7 states for computational cost reasons and because the interpretation of models with a higher number of states becomes complex.
@@
 
-Focusing on the HMM-full models with 5 latent states (please see main manuscript for a definition) we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section (Figure \ref{fig:trusteeHMMPlot}).
+Focusing on the HMM-full models with 6 latent states (please see main manuscript for a definition) we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section (Figure \ref{fig:trusteeHMMPlot}).
 Each latent state was associated with a distribution over trustee actions.
@@
 
-```{r trusteeHMMPlot,fig.cap = "Distribution of participants' percentage return for each of the latent states in the 5 state HMM-full model.
+```{r trusteeHMMPlot,fig.cap = "Distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model.
 The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social", fig.align='center'}

### 2023-09-25 article.Rmd
cleaned Markdown file

@@
 
-<!-- Figure \ref{fig:timeline} shows the timeline of the experiment.
-After reviewing an information sheet about the experiment, participants were informed that there would be three phases to go through, with them facing a different opponent in each phase.
-They would face the same player throughout the first phase, consisting of the "Investment Game" with several rounds.
-This was the moniker used for the repeated trust game, and a total of 15 rounds were played.
-Participants were then randomly assigned to either a control or intervention condition.
--->
-
-<!-- <!-- After reading instructions on how to play the trust game, players were told that they would be assigned the role of the trustee.
-A comprehension quiz on the trust game followed the instructions.
-The first trust game then ensued:  Each round started with an investment stage where the investor decided how much to send to the trustee and that choice was revealed.
-Immediately afterwards, participants were presented with a two-dimensional field to indicate their emotional state on two dimensions: valence, from unpleasant to pleasant (on the horizontal axis) and arousal, from low arousal to high arousal (on the vertical axis).
-After selecting a point on the field, participants were asked to decide how much to send back to the investor using a slider ranging from sending back nothing to sending back the whole (tripled) investment.
-Following that choice, an outcome page summarised both players decisions and showed the total pay-off for each player and the round then concluded.
-At the end of the game, participants were asked to rate the player they were facing on 4 attributes using a scale from 1 to 10: Trustworthiness, friendliness, cooperativeness and selfishness.
--->
-
-<!-- In the second phase of the experiment, participants were informed they would be paired with a different player.
-This phase was similar to the first phase in terms of the game played (RTG) and the number of rounds.
-In all rounds of the RTG, participants gave feedback after seeing the investment received.
-This feedback was given though a two dimensional grid that was either related to their emotional state (degree of valence of arousal) in the Intervention group, or unrelated to the emotional state in the control group (speed of investor's response and magnitude of investment).
-At the end of each RTG, participants were asked to rate how cooperative, selfish, trustworthy and friendly they thought their interaction partner was.
-Details of the two dimensional grid and player ratings are given in the supplement.
--->
-
-<!-- After both trust games,  players were told they would be paired with a new player in the third phase of the experiment.
-This third phase consisted of 7 rounds of the prisoner's dilemma game, facing the new player.
-Throughout all games, players were explicitly told to aim to maximise the number of points as their bonus would depend on the score they accumulated throughout the experiment.
-The total number of rounds was not communicated to the participants in any of the games played.
--->
-
-<!-- After the three phases were completed, participants were asked to complete a series of questionnaires at the end of the experiment.  -->
-
-<!-- <!-- These included: the PAI-BOR measuring Borderline traits [@morey_personality_1991], the DERS measuring Emotion Regulation ability [@gratz_multidimensional_2004] and the RFQ8 for mentalising abilities [@fonagy_development_2016].
--->
-
-<!-- Finally, participants were asked a series of questions around how they played each phase.
-First, they were asked whether they thought they played differently in the second compared to the first phase of the RTG.
-Second, participants had to select whether they thought the opponents they faced were human or computer agents.
-Finally, we revealed to the participants that they faced the same computer agent throughout the RTG.
-We explained that any change in their perception of the opponent or any change in how the opponent played is due to their own change in behavior as the agent was simply reacting to their actions.
-Finally, we asked participants to reveal whether this experiment has taught them anything about how they should behave in social situations.
--->
-
 At the start of the experiment (Figure \ref{fig:timeline}), participants provided informed consent and were instructed the study would consist of three phases in which they would face a different other player.
@@
 
-<!-- To explore whether participants behaved differently in the RTG after the intervention compared to the control group, we estimate a linear-mixed effects model via the "afex" [@singmann_afex_2022] package for R [@R_package], of the percentage return (percentage of tripled investment returned to investor) as the dependent variable and with fixed effects for Condition (intervention vs.
-control), Game (RTG game pre vs.
-post-intervention) and Investment, as well as interactions between Condition and both Investment and Game, and participant-wise random intercepts and random slopes for Game.
-More complex models with additional random effects could not be estimated reliably, and as such the estimated model can be considered to include the optimal random effects structure [@matuschek2017balancing].
-A similar process was used to establish the random effects structures of other linear mixed-effects models used throughout the statistical analyses.
-For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
-We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
--->
-
 To explore whether participants behaved differently in the RTG after the intervention compared to the control group, we model the percentage return (percentage of tripled investment returned to investor) using a linear mixed-effects model as described below:
@@
 We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
-
-<!-- To explore whether the HMM investors behaved differently in the RTG after the intervention compared to the control group, we estimate linear mixed effects model of investments sent by the computerised HMM agent with Condition and Game and their interaction as fixed effects -->
 
@@
 
-# plot(jitter(ret_post_int$returns), main="Jitter Plot", ylab="Returns", pch=19, col="blue")
-# plot(ecdf(ret_post_int$returns), main="ECDF", xlab="Returns", ylab="Cumulative Probability")
-# 
-# ggplot(ret_post_int , aes(x = "", y = returns)) +
-#   geom_violin(fill="lightblue") +
-#   geom_boxplot(width=0.1, fill="white") +
-#   theme_minimal() +
-#   labs(x = NULL, y = "Returns", title = "Violin plot")
-
 library(ggplot2)
@@
   geom_signif(xmin = 1.2, xmax = 2.2, annotations = "*", y_position = 0.80, tip_length = 0.03, textsize = 3)  # Control Group
-
-pctRet_all
 

### 2023-10-10 article.Rmd
use proper ordering of states

@@
 author:
-  "Ismail Guennouni^1^, Quentin JM Huys^2^, Samuel Dupret^1^, Maarten Speekenbrink^1^"
+  "Ismail Guennouni^1^, Samuel Dupret^1^, Quentin JM Huys^2^, Maarten Speekenbrink^1^"
 
@@
 
-ggplot(avg_ret_df, aes(x=as.factor(roundNum), y=ret_pct, group=gameNum.f, color = gameNum.f)) +
+ggplot(avg_ret_df, aes(x=as.factor(roundNum), y=ret_pct, group=gameNum.f, color = gameNum.f, fill=gameNum.f)) +
   stat_summary(fun = mean, geom = "line") +
   stat_summary(fun.data = mean_se, geom = "ribbon", aes(ymin=..ymin.., ymax=..ymax..), 
-               alpha = 0.3, fill = "grey", linetype = 0) +
+               alpha = 0.3, linetype = 0) +
   labs(x = "Round",
@@
   facet_wrap(~condition.f) +
-  scale_color_manual(values = c("darkblue", "green"))
+  scale_color_manual(values = c("darkblue", "darkgreen")) + scale_fill_manual(values = c("darkblue", "darkgreen"))
 
@@
          intervention_ctrst = factor(ifelse(gameNum.f=="pre", 0,ifelse(condition.f=="control",1,2))),
-         ctrl_only_ctrst = factor(ifelse(gameNum.f=="post" && condition.f=="control", 1,0)),
-         coax_only_ctrst = factor(ifelse(gameNum.f=="post" && condition.f=="intervention", 1,0)),
+         ctrl_only_ctrst = factor(ifelse(gameNum.f=="post" & condition.f=="control", 1,0)),
+         coax_only_ctrst = factor(ifelse(gameNum.f=="post" & condition.f=="intervention", 1,0)),
          pre_post_ctrst = factor(ifelse(gameNum.f=="post", 1,0)))  %>% 
@@
 ```{r, include=FALSE}
-tr_fdmod_6 <- order_mod_gauss(bestFull[[6]])
+tr_fdmod_6 <- order_mod_vtdgaus(bestFull[[6]])
 ```

### 2023-10-17 article.Rmd
deleted cache and article files from repo; started modifcations to text

@@
 keywords:
+- Social Trust
+- Repair of Cooperation
+- Cognitive Intervention 
 - Economic Games 
 - Hidden Markov Models
-- Repair of Cooperation
-- Cognitive Intervention
 
@@
 
-Determining the other's goals, intentions, and decision-making process is fundamental to successful social interaction.
-This inference is however fraught with uncertainty, as we cannot directly observe these aspects, and may need extensive prior knowledge of the person to infer them.
-Absent a history of interaction, one may decide to trust the other's goals and intentions are aligned with one's own.
-The challenge of trust is that it is by construction a risky endeavour.
-If we deem a person trustworthy, we might take the risk of investing in the relationship, hoping for a collaborative outcome.
-If this trust is misplaced, it can come at a high cost.
-Not trusting others is also risky since opportunities for beneficial cooperation may be foregone.
+Determining the other's goals and intentions is fundamental to successful social interaction.
+Inference of these latent motives is fraught with uncertainty [@barnby2023formalising; @feldmanhall2019resolving], as they are not directly observable and we may require extensive prior experience with the person to infer them.
+Absent a history of interaction, we may decide to trust that the other's goals and intentions are aligned with our own.
+Such trust is risky  and if misplaced, it can come at a high cost.
+But not trusting others is also risky as we may forego mutally beneficial cooperation.
 
@@
 
-Evidence from the literature emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016; @meng_multilevel_2014].
-It affects the health status of individuals by reinforcing social support networks, maintaining community norms and facilitating collective action.
+Prior research emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016; @meng_multilevel_2014].
+Social trust affects the health status of individuals by reinforcing social support networks, maintaining community norms and facilitating collective action.
 Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders.
-@fonagy_role_2014 identified epistemic trust, or the belief in the authenticity and personal relevance of interpersonally transmitted knowledge, as an important function of early attachment relationships.
-It allows the individual receiving social information to let go of their natural self-protective vigilance, which can become a pathological hypervigilance frequently observed after traumatic experiences and a key factor for the emergence of multiple mental health disorders [@fonagy_mentalizing_2017].
-
+@fonagy_role_2014 identified epistemic trust -- the belief in the authenticity and personal relevance of interpersonally transmitted knowledge -- as an important function of early attachment relationships.
+It allows the receiver of social information to let go of their natural self-protective vigilance, which can become pathological hypervigilance after adverse or traumatic experiences and a key factor in the emergence of several mental health disorders [@fonagy_mentalizing_2017].
 <!-- A well-established paradigm in the study of the emergence and maintenance of trust is the repeated trust game [@joyce_trust_1995].
@@
 -->
-
-Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions to foster and strengthen trust-based cooperation would be highly beneficial to society.
+Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions that foster and strengthen trust-based cooperation would be highly beneficial to society.
 Such interventions would allow people to more easily repair broken relationships and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
@@
 
-A well-established paradigm in the study of trust is the Repeated Trust Game (RTG) [@joyce_trust_1995].
+A well-established paradigm in the study of trust is the Repeated Trust Game [RTG;  @joyce_trust_1995].
 In this game, the "investor" decides how much of an endowment to send to the other player (the "trustee").
 The amount that is sent is tripled and the trustee decides, in return, how much of the tripled amount to send back to the investor.
-To encourage the emergence and maintenance of trust in this setting, some studies focused on modifying the game mechanism, for example by introducing a third-party who monitors the actions of the other players [@charness_investment_2008; @fiedler_effect_2017].
+The Nash equilibrium for a single-round version of the game is for the investor to send nothing.
+In the repeated version, rewards for both players are maximised if they build trust and share the benefits of higher investments.
+If the investor is rewarded for taking the risk of sending an investment, they are likely invest again in future rounds.
+But if the investor obtains a low return on their investment, they will likely reduce future investments, thereby diminishing the potential gains for both players.
+To encourage the emergence and maintenance of trust in this setting, some studies focused on modification of the game such as introducing a third-party who monitors the actions of the other players [@charness_investment_2008; @fiedler_effect_2017].
 Others chose to intervene directly on the participants.
-For example, @drazkowski_gratitude_2017 found that trust (as measured by the amount invested) was increased when participants were asked to think about and write down five things that they were grateful for.
-@burnham_friend-or-foe_2000 found that trust was also increased when participants were primed with the concepts of friend and foe.
-
-Whilst these interventions show that it is possible to improve cooperative outcomes at the start of the game, they do not address how to repair a breakdown of trust that might occur due to intentional or accidental non-cooperative actions by the players.
-Cooperative play in the Repeated Trust Game can easily break down when there is a transgressive behavior, such as a nil or very low investment by the investor or a return of the trustee below the investment sent [@bendor_when_1991].
-Such ruptures of cooperation appear frequently when the trustee suffers from social disorders such as Borderline Personality Disorder or BPD [@lieb_borderline_2004].
-In these situations, BPD trustees fail to engage in trust-repairing behaviors such as coaxing the investor by signalling trustworthiness via sending high returns.
-This failure may be linked to BPD patients not realising that low returns in the game violate social norms [@king-casas_rupture_2008].
-
-In devising potential interventions to repair trust, we can derive inspiration from the cognitive interventions championed by successful psychological therapies that aim to improve aspects of social dysfunction in BPD patients.
-Whilst there is no proven pharmacological therapy for BPD, psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve social skills in BPD patients [@gunderson_borderline_2018].
-However, response to these treatments is highly variable, and determining which interventions are effective for particular patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
+For example, @drazkowski_gratitude_2017 found that trust (as measured by the amount invested) was increased when participants were asked to think about and write down five things that they were grateful for, and @burnham_friend-or-foe_2000 found that trust increased when participants were primed with the concepts of friend and foe.
+
+Whilst these results show that it is possible to improve cooperative outcomes at the start of the game, they do not address how to repair a breakdown of trust after intentional or accidental non-cooperative actions by the players.
+Cooperation in the RTG can easily break down after a transgressive behavior such as a nil or very low investment by the investor or a return by the trustee below the investment sent [@bendor_when_1991].
+Such breakdown of cooperation are particularly evident when the trustee suffers from social disorders such as Borderline Personality Disorder [BPD; @lieb_borderline_2004].
+Trustees with BPD fail to engage in trust-repairing behaviors such as coaxing the investor by signalling trustworthiness via sending high returns.
+This failure may be due to BPD trustees not realising that low returns in the game violate social norms [@king-casas_rupture_2008].
+
+To devise interventions to repair social trust, we can take inspiration from cognitive interventions championed by successful therapies that aim to improve social dysfunction in BPD.
+Psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve social skills in BPD [@gunderson_borderline_2018].
+However, response to these treatments is highly variable, and determining which interventions are effective for individual patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
 One promising approach is the study of how specific components of psychotherapeutic treatment affect quantitative markers of behavior such as those inferred through computational models [@huys_computational_2016; @reiter_neuro-cognitive_2021; @dercon2022core].
@@
 
-In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a one-off low investment sent by a computerised investor.
+In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a low investment sent by the investor.
 The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation.
 Participants are given the role of the trustee and are randomly assigned to either a control or intervention group.
-They play two instances of the Repeated Trust Game with two different investors.
-After the first instance of the game, they either receive a cognitive intervention (intervention condition) or perform an unrelated task solving anagrams (control condition).
-In reality, participants face the same computerised agent in both instances, which is programmed to play according to a hidden Markov model fitted to real players' data.
-To foreshadow our results, we find that the intervention led to higher returns by the participants and countered a tendency to send back lower returns after a defection by the investor, but find no evidence of transfer to a different game (Repeated Prisoner’s Dilemma).
+They play two instances of the Repeated Trust Game with two different computerized investors.
+Between the first and second instance of the game, they either receive the cognitive intervention (intervention condition) or perform an unrelated task solving anagrams (control condition).
+The computerized investor in both instances of the game was programmed to play according to a hidden Markov model estimated from real players' data in prior research.
+A key aspect of this model is that the actions of the investor depend on a latent "trust state" which reacts to the trustees returns.
+To foreshadow our results, we find that the intervention led to more cooperative actions (higher returns) by the participants and countered a tendency to send back lower returns after a transgression from the investor.
+However, we found no evidence that the effects of the intervention transfer to a different (Repeated Prisoner’s Dilemma) game.
 
@@
 If the trustee returns more than one third of the amount, the investor makes a gain.
-The Nash equilibrium for a single-round version is for the investor to send nothing.
+<!-- The Nash equilibrium for a single-round version is for the investor to send nothing.
 In the repeated version, rewards for both players are maximised if they build trust and share the benefits of higher investments.
 An investor who has been rewarded for taking the risk of sending an investment will likely invest more in future rounds.
-An investor obtaining a low return on their investment may choose to reduce future investment and thereby reduce both players’ gains.
-
+An investor obtaining a low return on their investment may choose to reduce future investment and thereby reduce both players’ gains.-->
 ```{r, include=FALSE}
@@
 The strategy of the computerised investor was modelled on behavior of human investors in the Repeated Trust Game (RTG)  over 10-rounds with the same (human) opponent.
-Full detail on the datasets used in the supplement.
-Using this data, we estimated a hidden Markov model (HMM) on investors' behavior with three latent states, reflecting "low-trust", "medium-trust", or "high-trust".
-Each latent state was associated with a distribution over the possible investor actions from 0 to 20 (Figure \ref{fig:HMMPanels}.A).
-Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of the net return ( i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.B).
-In order to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 pre-intervention and round 13 post-intervention.
-On all other rounds, the agent's actions were derived from the HMM (disregarding the participant's response on pre-programmed low investment rounds).
+Full detail on the datasets used in the Supplementary Information.
+Using this data, we estimated a hidden Markov model (HMM) on investors' behavior with three latent states.
+Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.A).
+These distributions reflect "low-trust", "medium-trust", or "high-trust".
+Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of their net return (i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.B).
+In order to instigate a potential breakdown of trust, thereby allowing us to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 (pre-intervention) or round 13 (post-intervention).
+On all other rounds, the investor's actions were determined by randomly drawing an investment from the state-conditional distribution, with the state over rounds determined by randomly drawing the next state from the state-transition distribution as determined from the net return on the previous round (disregarding the net return immediately after the pre-programmed low investment rounds).
+The starting state in each instance of the game was the XXX.<!-- MS: what was the starting state?
+-->
+
+On each round, immediately after being informed of the investment sent, participants in the intervention condition were asked to provide an evaluation of their emotion in terms of valence (from negative to positive) and arousal (from low to high).
+Participants in the control condition were asked to evaluate the investment in terms of speed (from slow to fast) and magnitude (from low to high).
+These evaluations were made by clicking on a two-dimensional field with labelled axes.
 
@@
 
-To ascertain whether any effect of the intervention might transfer to a different game, participants played 7 rounds of a Repeated Prisoner’s Dilemma (RPD).
-In each round, participants could choose between: a cooperative action with a reward of 5 if the player also cooperated and a reward of 1 if not, or a non-cooperative action that would yield 7 points if the other person chooses the cooperative action and 2 points if not.
+To ascertain whether any effect of the intervention would transfer to a different game, participants played 7 rounds of a Repeated Prisoner’s Dilemma (RPD).
+In each round, participants could choose between a cooperative action with a reward of 5 (the other player also cooperates) or 1 (the other player defects), or a defect action with a reward of 7 (the other player cooperates) or 2 (the other player defects).
 The Nash equilibrium for a single-round version is to choose the non-cooperative action.
-
-The computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
+In the repeated version, both players can maximise their reward by choosing to cooperate.
+In this game, the computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
 On round 4, the computerised agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
+<!-- MS: did participants have to do the emotion/action evaluations here as well?
+-->
 
@@
 
-The intervention was built on interventions from Dialectical Behavior Therapy (DBT) skills training, asking patients to reflect on the consequences of actions taken in emotional states [@linehan_dbt_2015].
+The intervention was built on Dialectical Behavior Therapy (DBT) skills training, asking patients to reflect on the consequences of actions taken in emotional states [@linehan_dbt_2015].
 Specifically, participants were presented with a hypothetical situation in which they receive a low investment and asked to indicate how they would respond.
-They were then presented with an educational slide inviting them to consider that the ultimate aim in the game was to maximise their total reward and reflect on whether punishing the investor for the low investment was most likely to achieve that aim.
+They were then presented with an educational slide inviting them to consider that the ultimate aim in the game is to maximise their total reward and to reflect on whether punishing the investor for the low investment is beneficial to achieving that aim.
 Participants were told that punishment can create a negative feedback loop where the other player might trust them even less.
@@
 Phase one was a 15 round Repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
-On each round, after being informed about the amount sent by the investor, participants were asked to provide feedback, with participants in the Intervention condition rating their feeling in terms of valence (from negative to positive) and arousal (from low to high), and participants in the Control condition rating the investment in terms of speed (from slow to fast) and magnitude (from low to high).
-These ratings were made by indicating a point on a two-dimensional grid.
-Participants then decided on how much of the tripled investment to return to the investor, before continuing to the next round.
-After completing 15 rounds of the RTG, participants rated how cooperative, selfish, trustworthy and friendly they perceived their interaction partner (all on a scale from 1 to 10).
+On each round, after being informed about the amount sent by the investor, participants were asked to evaluate their emotion (invervention condition) or the investment (control condition).
+<!-- provide feedback, with participants in the Intervention condition rating their feeling in terms of valence (from negative to positive) and arousal (from low to high), and participants in the Control condition rating the investment in terms of speed (from slow to fast) and magnitude (from low to high).
+These ratings were made by indicating a point on a two-dimensional grid.--> Participants then decided on how much of the tripled investment to return to the investor, before continuing to the next round.
+After completing 15 rounds of the RTG, participants rated how cooperative, selfish, trustworthy and friendly they perceived the investor to be (all on a scale from 1 to 10).
 After phase one, participants in the intervention condition completed the intervention, and participants in the control condition solved anagrams.

### 2023-11-19 article.Rmd
ismail modifs psych science

@@
 abstract: |
-  Social trust is an important building block of strong social bonds, and its absence is a risk factor for social dysfunction.
+  Social trust is an important building block of strong social bonds, and its absence is a risk factor for social dysfunction and psychopathology.
 As such, interventions to foster and strengthen trust-based cooperation are highly desirable.
 Using the Repeated Trust Game paradigm, we assess the effectiveness of a cognitive intervention derived from Dialectical Behavior Therapy.
-The intervention's goal was to repair the potential breakdown of cooperation from a pre-programmed, one-off defection by the opponent.
+The intervention's goal was to repair the potential breakdown of cooperation from a pre-programmed, one-off defection by the co-player.
 Over two games, participants are given the role of the trustee and face what they believe are two different players.
 In between games, they either receive a brief cognitive intervention or not.
-Post-intervention, participants showed more cooperative behavior both before and after defection by the opponent.
+Post-intervention, participants showed more cooperative behavior both before and after defection by the co-player.
 Analysing participants' actions with a hidden Markov model shows that participants in the intervention group had a higher proportion of cooperative states than participants in the control group.
@@
     toc: false
-
+header-includes:
+  - \usepackage{lscape}
 ---
@@
 library(flextable)
+library(grid)
 library(gridExtra)
@@
 library(ggsignif)
+library(magick)
 
@@
 Such trust is risky  and if misplaced, it can come at a high cost.
-But not trusting others is also risky as we may forego mutally beneficial cooperation.
-
-<!-- and any substitution for trust, such as excessive suspicion, over-reliance on self and other maladaptive strategies are likely to add burden and costs to a person. -->
+But not trusting others is also risky as we may forego mutually beneficial cooperation.
 
@@
 @fonagy_role_2014 identified epistemic trust -- the belief in the authenticity and personal relevance of interpersonally transmitted knowledge -- as an important function of early attachment relationships.
-It allows the receiver of social information to let go of their natural self-protective vigilance, which can become pathological hypervigilance after adverse or traumatic experiences and a key factor in the emergence of several mental health disorders [@fonagy_mentalizing_2017].
-<!-- A well-established paradigm in the study of the emergence and maintenance of trust is the repeated trust game [@joyce_trust_1995].
-In this game, one player takes the role of the "investor" and is provided with a fixed endowment at the start of each trial.
-They get to decide how much of their endowment to invest with the other player taking the role of the "trustee".
-The amount that is sent is tripled and the trustee gets to decide, in return, how much of the tripled amount to send back to the investor.
-If the investor sends a non-zero amount, they express trust in the other player for that round, as the amount they will receive back is uncertain.
-Assuming the trustee sends back more than the initial investment, they signal trustworthiness to the investor and both players make gains.
-This scenario would constitute a cooperative exchange and would be mutually beneficial.
-However, cooperation in this setting is prone to be broken through intentional or simply misinterpreted actions that can convey lack of trust or trustworthiness such as low investments and returns [@bendor_when_1991].
-In order to repair a damaged cooperative equilibrium, players need to infer that their behavior has violated social norms and offer amends through generous actions at potentially a high cost to them.
-@king-casas_rupture_2008 links the breakdown of cooperation in trustees with Borderline Personality Disorder to the absence or reduction of activation in brain regions associated with the perception of norm violations.
--->
+It allows the receiver of social information to let go of their natural self-protective vigilance, which can become pathological hyper-vigilance after adverse or traumatic experiences and a key factor in the emergence of several mental health disorders [@fonagy_mentalizing_2017; @nolte2023role].
+
 Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions that foster and strengthen trust-based cooperation would be highly beneficial to society.
@@
 Trustees with BPD fail to engage in trust-repairing behaviors such as coaxing the investor by signalling trustworthiness via sending high returns.
-This failure may be due to BPD trustees not realising that low returns in the game violate social norms [@king-casas_rupture_2008].
+This failure may be due to BPD trustees not realising that low returns in the game violate social norms and the mentalizing difficulties that are associated with appraising others’ intentions [@king-casas_rupture_2008; @hula2018model].
 
@@
 Psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve social skills in BPD [@gunderson_borderline_2018].
-However, response to these treatments is highly variable, and determining which interventions are effective for individual patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
+However, response to these treatments is highly variable, and determining which interventions are effective for particular sub-groups of patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
 One promising approach is the study of how specific components of psychotherapeutic treatment affect quantitative markers of behavior such as those inferred through computational models [@huys_computational_2016; @reiter_neuro-cognitive_2021; @dercon2022core].
@@
 ```{r dataLoad, include=FALSE }
-# d_finished <- readRDS("data/d_finished.RDS")
-# d_finished$id <- NULL
-# saveRDS(d_finished, file="data/d_anonym.RDS")
 
@@
 
-```{r timeline, fig.cap = "Experiment overview.
+```{r timeline, include=F, fig.cap = "Experiment overview.
 After playing 15 rounds of the RTG as the trustee, participants were randomized to either be part of the control or intervention condition.
@@
 If the trustee returns more than one third of the amount, the investor makes a gain.
-<!-- The Nash equilibrium for a single-round version is for the investor to send nothing.
-In the repeated version, rewards for both players are maximised if they build trust and share the benefits of higher investments.
-An investor who has been rewarded for taking the risk of sending an investment will likely invest more in future rounds.
-An investor obtaining a low return on their investment may choose to reduce future investment and thereby reduce both players’ gains.-->
+Each player was represented with an icon with the participant always on the left of the screen and the co-player on the right (Figure \ref{fig:HMMPanels}.A).
+The participants were able to choose the icon that represents them at the start of the experiment.
+The icon representing the co-player changed at the start of each new game, to simulate a new interaction partner.
+Participants were not told they were facing computerised co-players.
+
+The strategy of the computerised investor was modelled on behavior of human investors in the Repeated Trust Game (RTG)  over 10-rounds with the same (human) co-player.
+Full detail on the datasets used in the Supplementary Information.
+Using this data, we estimated a hidden Markov model (HMM) on investors' behavior with three latent states.
+Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.C).
+These distributions reflect "low-trust", "medium-trust", or "high-trust".
+Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of their net return (i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.D).
+In order to instigate a potential breakdown of trust, thereby allowing us to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 (pre-intervention) or round 13 (post-intervention).
+On all other rounds, the investor's actions were determined by randomly drawing an investment from the state-conditional distribution, with the state over rounds determined by randomly drawing the next state from the state-transition distribution as determined from the net return on the previous round (disregarding the net return immediately after the pre-programmed low investment rounds).
+The initial state for the HMM investor in each instance of the game was the "mid-trust" state.
+
+On each round, immediately after being informed of the investment sent, participants in the intervention condition were asked to provide an evaluation of their emotion in terms of valence (from negative to positive) and arousal (from low to high).
+Participants in the control condition were asked to evaluate the investment in terms of speed (from slow to fast) and magnitude (from low to high).
+These evaluations were made by clicking on a two-dimensional field with labelled axes as shown in Figure \ref{fig:HMMPanels}.C for the intervention condition.
+
+### Repeated Prisoner's Dilemma
+
+To ascertain whether any effect of the intervention would transfer to a different game, participants played 7 rounds of a Repeated Prisoner’s Dilemma (RPD).
+In each round, participants could choose between a cooperative action with a reward of 5 (the other player also cooperates) or 1 (the other player defects), or a defect action with a reward of 7 (the other player cooperates) or 2 (the other player defects).
+The Nash equilibrium for a single-round version is to choose the non-cooperative action.
+In the repeated version, both players can maximise their reward by choosing to cooperate.
+In this game, the computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
+On round 4, the computerised agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
+<!-- MS: did participants have to do the emotion/action evaluations here as well?
+-->
+
 ```{r, include=FALSE}
@@
   theme_bw() + 
-  theme(legend.position = "bottom")
-
+  theme(legend.position = "bottom",  legend.text = element_text(size = 12),  legend.title = element_text(size = 14))
+
+plotinvHMM
 ```
@@
     ylim(c(0,1)) +
-    scale_fill_manual(values = c("low-trust" = "red", "medium-trust" = "green", "high-trust" = "blue")) +
+    scale_fill_manual(values = c("low-trust" = "red", "medium-trust" = "green", "high-trust" = "blue"),
+                    name = "From state") +  # Changed legend title for 'fill' here
+    scale_color_manual(values = c("low-trust" = "red", "medium-trust" = "green", "high-trust" = "blue"),
+                       labels = c("low-trust", "medium-trust", "high-trust"),
+                       name = "State transitioned to") +
     labs(x = "Investor's net return on trial t", y = "Transition probability to \nState on trial t+1", color = 'State transitioned to') +
@@
     theme(legend.position = "bottom",
-          axis.title.y = element_text(size = 8, angle = 90, vjust = 1.5))
-
-}
-
-```
-
-```{r, include=FALSE}
+          legend.text = element_text(size = 12),
+          legend.key.size = unit(1, 'lines'),
+          legend.spacing.x = unit(0.1, 'in'),
+          legend.title = element_text(size = 14),
+          legend.margin = margin(t = 0.2, b = 0, unit = 'cm'),
+          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"),
+          strip.text = element_text(size = 10),
+          legend.box = "vertical" # Arrange legends vertically
+    ) +
+    guides(fill = guide_legend(order = 1, title.position = "left", title.hjust = 0.3),
+           color = guide_legend(order = 2, title.position = "left", title.hjust = 0.3))
+}
+
+```
+
+```{r, include=F}
 
 plotInvTran <- plot_HMM_transitions(3, pars_inv) 
-
-```
-
-```{r HMMPanels, fig.cap="We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
-From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel A.
-The fitted HMM also yields the transition probability of the agent to a state on trial t+1 as a function of the net return (difference between the investment sent and the amount received in return) on trial t as shown in Panel B.
-Each plot in Panel B represents a different starting latent state on trial t, and each line represents the probability of transitioning to a particular state in trial t+1.
-The policy in each state in Panel A and the way the agent transitions between states as defined in Panel B characterises the artificial agent's behavior in the Repeated Trust Game.", fig.align="center"}
-
-ggpubr::ggarrange(plotinvHMM , plotInvTran, nrow=2, ncol=1, labels = c("A", "B"), common.legend = TRUE, legend = "bottom")
-
-```
-
-The strategy of the computerised investor was modelled on behavior of human investors in the Repeated Trust Game (RTG)  over 10-rounds with the same (human) opponent.
-Full detail on the datasets used in the Supplementary Information.
-Using this data, we estimated a hidden Markov model (HMM) on investors' behavior with three latent states.
-Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.A).
-These distributions reflect "low-trust", "medium-trust", or "high-trust".
-Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of their net return (i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.B).
-In order to instigate a potential breakdown of trust, thereby allowing us to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 (pre-intervention) or round 13 (post-intervention).
-On all other rounds, the investor's actions were determined by randomly drawing an investment from the state-conditional distribution, with the state over rounds determined by randomly drawing the next state from the state-transition distribution as determined from the net return on the previous round (disregarding the net return immediately after the pre-programmed low investment rounds).
-The starting state in each instance of the game was the XXX.<!-- MS: what was the starting state?
--->
-
-On each round, immediately after being informed of the investment sent, participants in the intervention condition were asked to provide an evaluation of their emotion in terms of valence (from negative to positive) and arousal (from low to high).
-Participants in the control condition were asked to evaluate the investment in terms of speed (from slow to fast) and magnitude (from low to high).
-These evaluations were made by clicking on a two-dimensional field with labelled axes.
-
-### Repeated Prisoner's Dilemma
-
-To ascertain whether any effect of the intervention would transfer to a different game, participants played 7 rounds of a Repeated Prisoner’s Dilemma (RPD).
-In each round, participants could choose between a cooperative action with a reward of 5 (the other player also cooperates) or 1 (the other player defects), or a defect action with a reward of 7 (the other player cooperates) or 2 (the other player defects).
-The Nash equilibrium for a single-round version is to choose the non-cooperative action.
-In the repeated version, both players can maximise their reward by choosing to cooperate.
-In this game, the computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
-On round 4, the computerised agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
-<!-- MS: did participants have to do the emotion/action evaluations here as well?
--->
+print(plotInvTran)
+
+```
+
+\begin{landscape}
+```{r HMMPanels, fig.cap= "\\small{A: Screenshot of the repeated Trust Game.
+The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee.
+The investor is endowed with 20 units at the start of each round.
+They need to decide how much of that endowment they want to invest with the trustee.
+The investment is then multiplied by a factor of 3 and sent to the trustee who needs to decide how much of the multiplied investment they want to send back to the investor.
+Shown here is the stage at which the trustee makes a decision of how much to send back the investor.
+Immediately before making this decision, participant are shown a two dimensional grid (Panel C) where they need to report their reaction to the investment.
+Those in the intervention condition were asked questions about their emotional state and those in the control condition were asked to report features of the investment unrelated to their emotion.
+Panels B - D: We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
+From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel C.
+The fitted HMM also yields the transition probability of the agent to a state on trial t+1 as a function of the net return (difference between the investment sent and the amount received in return) on trial t as shown in Panel D.
+Each plot in Panel D represents a different starting latent state on trial t, and each line represents the probability of transitioning to a particular state in trial t+1.}",echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+
+library(magick)
+
+# Read in the images
+image1 <- image_read("figures/trust_game.png")
+image2 <- image_read("figures/HMMinvPolicy2.png")
+image3 <- image_read("figures/emotion_grid.png")
+image4 <- image_read("figures/HMMinvTrans2.png")
+
+# Determine the target width for all images, for example, the width of the widest image
+target_width <- max(image_info(image1)$width, image_info(image2)$width, 
+                    image_info(image3)$width, image_info(image4)$width)
+
+target_height <- max(image_info(image1)$height, image_info(image2)$height, 
+                    image_info(image3)$height, image_info(image4)$height)
+
+# Scale images to have the same width
+image1 <- image_scale(image1, paste0(target_width, "x", target_height))
+image2 <- image_scale(image2, paste0(target_width, "x", target_height))
+image3 <- image_scale(image3, paste0(target_width, "x", target_height))
+image4 <- image_scale(image4, paste0(target_width, "x", target_height))
+
+# Annotate each image with a label
+image1 <- image_annotate(image1, text = "A", location = "+200+10", size = 90, color = "black", gravity = "northwest")
+image2 <- image_annotate(image2, text = "B", location = "+0+10", size = 90, color = "black", gravity = "northwest")
+image3 <- image_annotate(image3, text = "C", location = "-0+10", size = 90, color = "black", gravity = "northwest")
+image4 <- image_annotate(image4, text = "D", location = "+0+10", size = 90, color = "black", gravity = "northwest")
+
+# Assuming a 300 DPI resolution for good print quality
+dpi <- 300
+
+# Spacing of 0.1 inches converted to pixels
+spacing <- 0.05 * dpi
+
+# Calculating the width and height for each image
+width_per_image <- ((12 - 0.1) / 2) * dpi
+height_per_image <- ((7.4 - 0.1) / 2) * dpi
+# The geometry string for each image, including spacing (assuming no borders)
+geometry_string <- paste0(width_per_image, 'x', height_per_image, '+', spacing, '+', spacing)
+
+# Now create the montage with the specified geometry
+combined_image <- image_montage(
+  c(image1, image2, image3, image4), 
+  tile = "2x2",
+  geometry = geometry_string
+)
+
+# Display the combined image
+plot(combined_image)
+```
+\end{landscape}
 
@@
 
-In the control condition, participants were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
+In order to separate any general practice effects from the effect of the intervention, we added a control condition in which participants  were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
 They provided their answers in a free-form text box.
@@
 
-At the start of the experiment (Figure \ref{fig:timeline}), participants provided informed consent and were instructed the study would consist of three phases in which they would face a different other player.
+At the start of the experiment, participants provided informed consent and were instructed the study would consist of three phases in which they would face a different other player.
 Participants were told their goal was to maximise the number of points in all phases.
@@
 Phase one was a 15 round Repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
-On each round, after being informed about the amount sent by the investor, participants were asked to evaluate their emotion (invervention condition) or the investment (control condition).
+On each round, after being informed about the amount sent by the investor, participants were asked to evaluate their emotion (intervention condition) or the investment (control condition).
 <!-- provide feedback, with participants in the Intervention condition rating their feeling in terms of valence (from negative to positive) and arousal (from low to high), and participants in the Control condition rating the investment in terms of speed (from slow to fast) and magnitude (from low to high).
@@
 
-```{r gamesPlot, echo=FALSE, fig.cap="Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+```{r gamesPlot, include=FALSE, echo=FALSE, fig.cap="Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
 The blue line shows the returns pre-manipulation and the green line post-manipulation.
 We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel",fig.align="center", fig.width=6, fig.height = 4}
+
+# ggplot(avg_ret_df, aes(x=as.factor(roundNum), y=ret_pct, group=gameNum.f, color = gameNum.f, fill=gameNum.f)) +
+#   stat_summary(fun = mean, geom = "line") +
+#   stat_summary(fun.data = mean_se, geom = "ribbon", aes(ymin=..ymin.., ymax=..ymax..), 
+#                alpha = 0.3, linetype = 0) +
+#   labs(x = "Round",
+#        y = "Percentage Return",
+#        color = "Game") +
+#   theme_bw() +
+#   theme(legend.position = "bottom") +
+#   facet_wrap(~condition.f) +
+#   scale_color_manual(values = c("darkblue", "darkgreen")) + scale_fill_manual(values = c("darkblue", "darkgreen"))
 
@@
        y = "Percentage Return",
-       color = "Game") +
+       color = "Trust Game Phase") +
   theme_bw() +
-  theme(legend.position = "bottom") +
+  theme(legend.position = "bottom",
+        legend.key = element_blank(),
+        #legend.key = element_rect(fill = NA), # Make legend key background transparent
+        legend.margin = margin(t = 0, b = 0, unit = "pt"), # Adjust top and bottom margin of each legend
+        legend.box.margin = margin(t = 0, b = 0, unit = "pt")) + # Adjust top and bottom margin of the legend box
   facet_wrap(~condition.f) +
-  scale_color_manual(values = c("darkblue", "darkgreen")) + scale_fill_manual(values = c("darkblue", "darkgreen"))
+  scale_color_manual(values = c("darkblue", "darkgreen"),
+                     labels = c("Pre-manipulation", "Post-manipulation")) +
+  scale_fill_manual(values = c("darkblue", "darkgreen"),
+                    guide = "none") + # Hide the fill legend
+  guides(color = guide_legend(override.aes = list(fill = NA))) # Remove fill for color legend keys
 
@@
             data_arg = list(width = 0.5),
-            factor_levels = list(gameNum.f = c("Pre", "Post")), legend_title = "Condition") + 
+            factor_levels = list(gameNum.f = c("Pre-manipulation", "Post-manipulation")), legend_title = "Condition") + 
   theme_bw() + 
-  labs(y = "Percentage Return", x = "Game") + 
+  labs(y = "Percentage Return", x = "Trust Game Phase") + 
   ggtitle("All rounds percentage returns") + 
@@
 
-Average investments and returns prior to the "defection round" (Figure \ref{fig:gamesPlot}) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
+Average investments and returns prior to the "defection round" (Figure \ref{fig:TrustGameResults}.A) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
 Mixed-effects analysis on the percentage returns shows a significant main effect of Condition (intervention vs.
@@
 post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f`<!--$F(1,314.2) = 26.9$, $p < .001$-->.
-Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:violinPanels}.A).
+Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:TrustGameResults}.C).
 This indicates the intervention was effective in increasing cooperative behavior.
@@
             data_arg = list(width = 0.5),
-            factor_levels = list(gameNum.f = c("Pre", "Post")), 
+            factor_levels = list(gameNum.f = c("Pre-manipulation", "Post-manipulation")), 
             legend_title = "Condition") + 
@@
   ggtitle("All rounds investments") +
-  labs(y = "HMM Investment", x = "Game") + 
+  labs(y = "HMM Investment", x = "Trust Game Phase") + 
   theme(plot.title = element_text(size = 16)) +
@@
 
-To explore whether the HMM investors behaved differently in the RTG after the intervention compared to the control group, we estimate a linear mixed-effects model of investments sent by the computerised HMM agent with Condition and Game and their interaction as fixed effects, and a similar random effects structure to the returns model.
+To explore the HMM investors' behavior across games and conditions, we estimate a linear mixed-effects model of investments sent by the computerised HMM agent with Condition and Game and their interaction as fixed effects, and a similar random effects structure to the returns model.
 This shows a main effect of Condition, `r papaja::apa_print(mod_invs)$full_result$condition_f`<!--$F(1,317) = 8.7$, $p = .003$-->, and Game, `r papaja::apa_print(mod_invs)$full_result$gameNum_f`<!--$F(1,317) = 8.3$, $p = .004$-->.
-As can be seen in Figure \ref{fig:violinPanels}.B, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
+As can be seen in Figure \ref{fig:TrustGameResults}.D, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
 
@@
 
-We next analysed returns separately for rounds prior to the pre-programmed defection (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
+We next analysed returns separately for rounds prior to the pre-programmed low investment by the HMM (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
 Applying the same mixed-effects model as before to returns before the defection largely replicates the results over all trials.
@@
 Full results are provided in the supplement.
+
+\newpage
+\begin{landscape}
+```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
+B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
+The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round were similar before (round 12) and after (round 13) the intervention.
+The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
+Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
+Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+library(magick)
+
+# Read in the images
+image5 <- image_read("figures/resultsTrust.png")
+image6 <- image_read("figures/emotionReaction2.png")
+violin_ret <- image_read("figures/violin_ret.png")
+violin_inv <- image_read("figures/violin_inv.png")
+
+image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
+violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
+violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
+
+# Assuming a 300 DPI resolution for good print quality
+dpi <- 300
+
+# Spacing of 0.1 inches converted to pixels
+spacing <- 0.05 * dpi
+
+# Calculating the width and height for each image
+width_per_image <- ((12 - 0.1) / 2) * dpi
+height_per_image <- ((7.4 - 0.1) / 2) * dpi
+# The geometry string for each image, including spacing (assuming no borders)
+geometry_string <- paste0(width_per_image, 'x', height_per_image, '+', spacing, '+', spacing)
+
+# Now create the montage with the specified geometry
+combined_image2 <- image_montage(
+  c(image5, image6, violin_ret, violin_inv), 
+  tile = "2x2",
+  geometry = geometry_string
+)
+
+# Display the combined image
+plot(combined_image2)
+```
+\end{landscape}
+\newpage
 
@@
             data_arg = list(width = 0.5),
-            factor_levels = list(gameNum.f = c("Pre", "Post")), 
+            factor_levels = list(gameNum.f = c("Pre-manipulation", "Post-manipulation")), 
             legend_title = "Condition") + 
   theme_bw() + 
-  labs(y = "Percentage Return", x = "Game") + 
+  labs(y = "Percentage Return", x = "Trust Game Phase") + 
   ggtitle("Pre defection trials percentage returns")+
@@
             data_arg = list(width = 0.5),
-            factor_levels = list(gameNum.f = c("Pre", "Post")), 
+            factor_levels = list(gameNum.f = c("Pre-manipulation", "Post-manipulation")), 
             legend_title = "Condition") + 
   theme_bw() + 
-  labs(y = "Percentage Return", x = "Game") + 
+  labs(y = "Percentage Return", x = "Trust Game Phase") + 
   ggtitle("Post defection trials percentage returns") +
@@
 
-```{r violinPanels, fig.cap="Participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds (Panel A), whilst those in the Control condition sent back lower returns.
+```{r violinPanels, include=F, fig.cap="Participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds (Panel A), whilst those in the Control condition sent back lower returns.
 Focusing on pre-defection trials (Panel C), those in the Control condition returned similar amounts between games, while returns were higher in the Intervention condition in the second game.
@@
 
-ggpubr::ggarrange(pctRet_all, inv_all, pctRet_pre, pctRet_post, nrow=2, ncol=2, labels = c("A", "B", "C", "D"), common.legend = TRUE, legend = "bottom")
+ggpubr::ggarrange(pctRet_all, inv_all, pctRet_pre, pctRet_post, nrow=2, ncol=2, common.legend = TRUE, legend = "bottom")
 ```
@@
 
-```{r emoPlotCoax, fig.cap="Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
+```{r emoPlotCoax, include=F, fig.cap="Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
 The participants' emotion reaction measured during the investor's defection round were similar before (round 12) and after (round 13) the intervention.",fig.align="center", fig.width=7, fig.height = 4}
@@
 # Define the colors in alphabetical order
-colors <- c("Arousal" = "green", "Investment" = "blue", "Valence" = "red")
+colors <- c("Arousal" = "forestgreen", "Investment" = "blue", "Valence" = "red")
 
@@
   scale_color_manual(name = "", values = colors, labels = c("Arousal", "Investment", "Emotion valence")) +
-  scale_linetype_manual(values = c("a_Pre" = "dotted", "b_Post" = "solid"), labels = c("Pre", "Post")) +
+  scale_linetype_manual(values = c("a_Pre" = "dotted", "b_Post" = "solid"), labels = c("Pre-intervention", "Post-intervention")) +
   scale_x_continuous(breaks = 1:max(datCoax$roundNum)) +
@@
 `r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment)`. 
-This indicates that participants in the intervention condition returned higher amounts post-intervention, despite their emotional reaction to investments remaining largely the same.
+This indicates that participants in the intervention condition returned higher amounts post-intervention, despite their emotional reaction to investments remaining largely the same (Figure \ref{fig:TrustGameResults}.B).
 
@@
 
-When asked during debrief whether they thought the investors they faced were Human or not, $40$% of participants thought they were either facing a human or were not sure of the nature of the opponent.
-Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial opponent's behavior.
+When asked during debrief whether they thought the investors they faced were Human or not, $40$% of participants thought they were either facing a human or were not sure of the nature of the co-player.
+Many answers reflected participants projecting human traits such as "spitefulness" or "greed" onto the artificial co-player's behavior.
 
@@
 
-```{r, include=F}
-# # define a response class which only contains the standard slots, no additional slots
-# setClass("discgaus", contains="response", slots=c(breaks="numeric"))
-# 
-# # define a generic for the method defining the response class
-# 
-# setGeneric("discgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("discgaus"))
-# 
-# # define the method that creates the response class
-# 
-# setMethod("discgaus", 
-#           signature(y="ANY"), 
-#           function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), ...) {
-#             y <- matrix(y,length(y))
-#             x <- matrix(1)
-#             parameters <- list()
-#             npar <- 2
-#             if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
-#             if(!is.null(pstart)) {
-#               if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
-#               parameters$mu <- pstart[1]
-#               parameters$sigma <- pstart[2]
-#             }
-#             mod <- new("discgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, breaks=breaks)
-#             mod
-#           }
-# )
-# 
-# setMethod("show","discgaus",
-#           function(object) {
-#             cat("Gaussian with discrete support\n")
-#             cat("Parameters: \n")
-#             cat("mu: ", object@parameters$mu, "\n")
-#             cat("sigma: ", object@parameters$sigma, "\n")
-#           }
-# )
-# 
-# setMethod("dens","discgaus",
-#           function(object,log=FALSE) {
-#             p <- pnorm(object@breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@breaks[-length(object@breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
-#             if(log) return(log(p[as.numeric(cut(object@y, breaks=object@breaks))])) else return(p[as.numeric(cut(object@y, breaks=object@breaks))])
-#           }
-# )
-# 
-# setMethod("setpars","discgaus",
-#           function(object, values, which="pars", ...) {
-#             npar <- npar(object)
-#             if(length(values)!=npar) stop("length of 'values' must be",npar)
-#             # determine whether parameters or fixed constraints are being set
-#             nms <- names(object@parameters)
-#             switch(which,
-#                    "pars"= {
-#                      object@parameters$mu <- values[1]
-#                      object@parameters$sigma <- values[2]
-#                    },
-#                    "fixed" = {
-#                      object@fixed <- as.logical(values)
-#                    }
-#             )
-#             names(object@parameters) <- nms
-#             return(object)
-#           }
-# )
-# 
-# setMethod("getpars","discgaus",
-#           function(object,which="pars",...) {
-#             switch(which,
-#                    "pars" = {
-#                      parameters <- numeric()
-#                      parameters <- unlist(object@parameters)
-#                      pars <- parameters
-#                    },
-#                    "fixed" = {
-#                      pars <- object@fixed
-#                    }
-#             )
-#             return(pars)
-#           }
-# )
-# 
-# setMethod("fit","discgaus",
-#           function(object,w) {
-#             if(missing(w)) w <- NULL
-#             if(!is.null(w)) {
-#               negLL <- function(pars) {
-#                 object <- setpars(object, c(pars[1], exp(pars[2])))
-#                 -sum(w*log(dens(object)))
-#               }
-#             } else {
-#               negLL <- function(pars) {
-#                 object <- setpars(object, c(pars[1], exp(pars[2])))
-#                 -sum(log(dens(object)))
-#               }
-#             }
-#             pars <- optim(c(object@parameters$mu, log(object@parameters$sigma)), fn=negLL)$par
-#             object <- setpars(object,c(pars[1], exp(pars[2])))
-#             object
-#           }
-# )
-# 
-# setClass("truncdiscgaus", contains="discgaus", slots=c(min="numeric", max="numeric"))
-# 
-# setMethod("dens","truncdiscgaus",
-#           function(object,log=FALSE) {
-#             breaks <- c(object@min, object@breaks[object@breaks > object@min & object@breaks < object@max], object@max)
-#             p <- pnorm(breaks[-1], mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(breaks[-length(breaks)], mean = object@parameters$mu, sd = object@parameters$sigma)
-#             p <- p/sum(p)
-#             if(log) return(log(p[as.numeric(cut(object@y, breaks=object@breaks))])) else return(p[as.numeric(cut(object@y, breaks=object@breaks))])
-#           }
-# )
-# 
-# setGeneric("truncdiscgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("truncdiscgaus"))
-# 
-# setMethod("truncdiscgaus", 
-#           signature(y="ANY"), 
-#           function(y,pstart=NULL,fixed=NULL, breaks = c(-Inf, 0:19 + .5, Inf), min=0, max=20, ...) {
-#             y <- matrix(y,length(y))
-#             x <- matrix(1)
-#             parameters <- list()
-#             npar <- 2
-#             if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
-#             if(!is.null(pstart)) {
-#               if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
-#               parameters$mu <- pstart[1]
-#               parameters$sigma <- pstart[2]
-#             }
-#             mod <- new("truncdiscgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, breaks=breaks, min=min, max=max)
-#             mod
-#           }
-# )
-# 
-# 
-# order_mod_gauss <- function(mod) {
-#   ns <- nstates(mod)
-#   sum <- rep(0.0,ns)
-#   for(i in 1:ns) {
-#     # Expected return in each state calculation 
-#     sum[i] = mod@response[[i]][[1]]@parameters$mu
-#   }
-#   # reordering the states
-#   mod <- label_switch(mod, rank(sum))
-#   return(mod)
-# }
-# 
-# # define a response class which only contains the standard slots, no additional slots
-# setClass("vtdgaus", contains="response", slots=c(yield="numeric"))
-# 
-# # define a generic for the method defining the response class
-# 
-# setGeneric("vtdgaus", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("vtdgaus"))
-# 
-# # define the method that creates the response class
-# 
-# setMethod("vtdgaus", 
-#           signature(y="ANY"), 
-#           function(y, yield, pstart=NULL,fixed=NULL, ...) {
-#             y <- matrix(y,length(y))
-#             x <- matrix(1)
-#             parameters <- list()
-#             npar <- 2
-#             if(is.null(fixed)) fixed <- as.logical(rep(0,npar))
-#             if(!is.null(pstart)) {
-#               if(length(pstart)!=npar) stop("length of 'pstart' must be ",npar)
-#               parameters$mu <- pstart[1]
-#               parameters$sigma <- pstart[2]
-#             } else {
-#               parameters <- list(mu=.5,sigma=1)
-#             }
-#             mod <- new("vtdgaus",parameters=parameters,fixed=fixed,x=x,y=y,npar=npar, yield=yield)
-#             mod
-#           }
-# )
-# 
-# setMethod("show","vtdgaus",
-#   function(object) {
-#     cat("Gaussian with variable discrete support for percentage responses\n")
-#     cat("Parameters: \n")
-#     cat("mu: ", object@parameters$mu, "\n")
-#     cat("sigma: ", object@parameters$sigma, "\n")
-#   }
-# )
-# 
-# setMethod("dens","vtdgaus",
-#   function(object,log=FALSE) {
-#       # determine cuts for pnorm based on 
-#       p <- pnorm(sapply(object@y + .5*(1/object@yield),function(x) min(x,1.001)), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(sapply(object@y - .5*(1/object@yield),function(x) max(x,-0.001)), mean = object@parameters$mu, sd = object@parameters$sigma)
-#       norm <- (pnorm(1 + .001, mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(-0.001, mean = object@parameters$mu, sd = object@parameters$sigma))
-#       p <- p/norm
-#       # alternatively, normalize factor based on size of cuts
-#       #p <- pnorm(object@y + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(object@y - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma)
-#       #p <- p/(pnorm(1 + .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma) - pnorm(0 - .5*(1/object@yield), mean = object@parameters$mu, sd = object@parameters$sigma))
-#     # probability when yield == 0 is always 1 
-#       p[object@yield == 0] <- 1
-#       if(log) return(log(p)) else return(p)
-#     }
-# )
-# 
-# setMethod("setpars","vtdgaus",
-#           function(object, values, which="pars", ...) {
-#             npar <- npar(object)
-#             if(length(values)!=npar) stop("length of 'values' must be",npar)
-#             # determine whether parameters or fixed constraints are being set
-#             nms <- names(object@parameters)
-#             switch(which,
-#                    "pars"= {
-#                      object@parameters$mu <- values[1]
-#                      object@parameters$sigma <- values[2]
-#                    },
-#                    "fixed" = {
-#                      object@fixed <- as.logical(values)
-#                    }
-#             )
-#             names(object@parameters) <- nms
-#             return(object)
-#           }
-# )
-# 
-# setMethod("getpars","vtdgaus",
-#           function(object,which="pars",...) {
-#             switch(which,
-#                    "pars" = {
-#                      parameters <- numeric()
-#                      parameters <- unlist(object@parameters)
-#                      pars <- parameters
-#                    },
-#                    "fixed" = {
-#                      pars <- object@fixed
-#                    }
-#             )
-#             return(pars)
-#           }
-# )
-# 
-# setMethod("fit","vtdgaus",
-#           function(object,w) {
-#             if(missing(w)) w <- NULL
-#             if(!is.null(w)) {
-#               negLL <- function(pars) {
-#                 object <- setpars(object, c(pars[1], exp(pars[2])))
-#                 -sum(w*log(dens(object)))
-#               }
-#             } else {
-#               negLL <- function(pars) {
-#                 object <- setpars(object, c(pars[1], exp(pars[2])))
-#                 -sum(log(dens(object)))
-#               }
-#             }
-#             pars <- optim(c(object@parameters$mu, log(object@parameters$sigma)), fn=negLL)$par
-#             object <- setpars(object,c(pars[1], exp(pars[2])))
-#             object
-#           }
-# )
-```
-
 ```{r,include=F}
@@
 Finally, the HMM-inv model did not allow transition probabilities to differ between conditions or games, modelling them only as a function of investment.
-
 As the number of hidden states was unknown, we estimated models with 2 to 7 latent states for the most complex HMM-full model, and used the BIC to compare them.
@@
 Focusing on the HMM-full model with 6 latent states, likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCtrl[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCoax[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestPrePost[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$).
+Using this HMM, we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section (Figure \ref{fig:trusteeHMM}.A).
+Each latent state was associated with a distribution over trustee actions.
+The latent states were ordered by the mean of the estimated Gaussian, such as higher numbered latent states reflect higher mean percentage return.
+
 <!-- We start by comparing HMM-full with HMM-inv.
@@
 
-```{r postStatesBestMod,  echo=FALSE, fig.cap = "Distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.
+```{r postStatesBestMod,  include=F, echo=FALSE, fig.cap = "Distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure.
 States are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.
@@
 The states are ordered by expected return, with state 1 having the lowest mean return and state 5 the highest.
-Figure \ref{fig:postStatesBestMod} shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
+Figure \ref{fig:trusteeHMM}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
 For instance, in round 5, state 1 was the most likely posterior state for only $5$% of participants in the intervention condition compared to $12$% in the control condition ($\chi^2(1) = 4.73, p = 0.03$).
@@
 The overall higher returns after the intervention occurred despite participants' emotional reactions to the investments remaining largely the same as before the intervention.
-This indicates the intervention achieved its goal of encouraging participants to respond in a non-impulsive and considered manner, possibly overriding the urge to retaliate.
+This indicates the intervention achieved its goal of encouraging participants to respond in a non-impulsive and considered manner, possibly overriding the emotional reaction to the investment which might prompt an urge to retaliate.
+
+\newpage
+\begin{landscape}
+```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
+The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social.
+B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
+The distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure is visibly more weighted towards higher return states.
+As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+library(magick)
+
+# Read in the images
+image7 <- image_read("figures/trusteeHMMPlot.png")
+image8 <- image_read("figures/postHMM.png")
+
+image7 <- image_annotate(image7, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image8 <- image_annotate(image8, text = "B", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+
+# Combine image2 and image3 side-by-side
+final_image <- c(image7, image8) %>% magick::image_append(stack = FALSE)
+
+# Display the combined image
+plot(final_image)
+```
+\end{landscape}
+\newpage
 
@@
 
+\pagebreak
+
+# Disclosures
+
+**Author Contribution:**
+I.
+Guennouni, Q.
+Huys, and M.
+Speekenbrink designed and developed the study concept.
+Experiment design was done by S.
+Dupret and I.
+Guennouni.
+Testing and data collection were performed by I.
+Guennouni.
+I.
+Guennouni analysed and interpreted the data under the supervision of Q.
+Huys and M.
+Speekenbrink.
+M.
+Speekenbrink and I.
+Guennouni jointly performed the HMM modelling.
+All authors jointly wrote and approved the final version of the manuscript for submission.
+
+**Declaration of Conflicting Interests:**
+The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
+
+**Funding:**
+Funding was provided by XXXXX
+
+**Open Practices:**
+All data from this study have been made publicly available via XXXX and can be accessed at XXXX .
+The design and analysis plans were not preregistered.
+The complete Open Practices Disclosure for this article can be found at XXXX
+
 <!-- # Conclusion -->
@@
 <!-- We explored the effect of a brief cognitive intervention on the behavior of human trustees facing adaptive artificial investors designed to replicate the behavior of human investors in the Repeated Trust Game.
-Each state defines different levels of a cooperative response with the agent able to transition between these states based on the behavior of the human opponent.
+Each state defines different levels of a cooperative response with the agent able to transition between these states based on the behavior of the human co-player.
 Feedback from participants indicated that these agents were sometimes perceived as humans.
@@
 It also led to more trustworthy behavior prior to the pre-programmed defection trial and to coaxing behavior after defection.
-Whilst this intervention effect varied between participants and generally was not transferred to a new game, an HMM analysis of participant's play post intervention showed differentiated patterns of transitions between latent states, indicating a change in the effect of the opponent action on the probability of transitioning between latent mental states.
+Whilst this intervention effect varied between participants and generally was not transferred to a new game, an HMM analysis of participant's play post intervention showed differentiated patterns of transitions between latent states, indicating a change in the effect of the co-player action on the probability of transitioning between latent mental states.
 -->

### 2023-11-19 supplement.Rmd
ismail modifs psych science

@@
 Participants played a 15-round repeated trust game [@joyce_trust_1995] in the trustee role against a computer-programmed investor.
-As seen in Figure \ref{fig:trustGameScreenshot} each player was represented with an icon with the participant always on the left of the screen and the opponent on the right.
+Each player was represented with an icon with the participant always on the left of the screen and the opponent on the right.
 The participants were able to choose the icon that represents them at the start of the experiment.
@@
 
-```{r trustGameScreenshot,fig.cap = "Screenshot of the repeated Trust Game.
+```{r trustGameScreenshot, include=F, fig.cap = "Screenshot of the repeated Trust Game.
 The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee.
@@
 
-```{r grid,fig.cap = "Screenshot of the two axis grid in the Coaxing condition where participants were asked to report the valence and arousal of their emotional response ", out.width="70%", out.height="70%", fig.align='center'}
+```{r grid, include=F, fig.cap = "Screenshot of the two axis grid in the Coaxing condition where participants were asked to report the valence and arousal of their emotional response ", out.width="70%", out.height="70%", fig.align='center'}
 
@@
 In the control condition, participants were asked to rate the choice of investment in terms of speed (slow or fast) and magnitude (low or high).
-Figure \ref{fig:grid} shows a screenshot of the feedback field in the intervention condition, where participants were asked about their emotional response to the investment.
 At the beginning of each game, participants were provided with detailed explanations of the meaning of the two axes as well as the opportunity to provide a baseline emotional state through using the field prior to the start of the game.
@@
 
-# Self report questionnaires
+# Self-report questionnaires
 
@@
 
-```{r postDefectionModel,fig.cap = "Summary of results of a Mixed-effects model fitted to participants returns restricted to  post-defection trials", fig.align='center'}
+```{r postDefectionModel,fig.cap = "Summary of results of a Mixed-effects model fitted to participants returns restricted to  post-defection trials", fig.align='center',fig.pos="H"}
 
@@
 ```{r table-HMMs,fig.cap = "Table comparing the HMM-full models fit assuming the latent number of states is between 2 and 7.
-Using BIC, the 6 state model fits best", out.width="70%", out.height="70%", fig.align='center'}
+Using BIC, the 6 state model fits best", out.width="70%", out.height="70%", fig.align='center',fig.pos="H"}
 
@@
 
-## Distribution of returns for each latent state for HMM model of participant’s returns
-
-Focusing on the HMM-full models with 6 latent states (please see main manuscript for a definition) we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section (Figure \ref{fig:trusteeHMMPlot}).
-Each latent state was associated with a distribution over trustee actions.
-The latent states were ordered by the mean of the estimated Gaussian, such as higher numbered latent states reflect higher mean percentage return.
-
-```{r trusteeHMMPlot,fig.cap = "Distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model.
+```{r trusteeHMMPlot, include=F, fig.cap = "Distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model.
 The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social", fig.align='center'}

### 2023-12-18 article.Rmd
QH comments included

@@
 
-Determining the other's goals and intentions is fundamental to successful social interaction.
+Cooperation refers to the collaborative efforts of individuals or entities working towards a shared goal or advantage [@tomasello2012two].
+This coordinated approach often leads to outcomes that exceed the sum of individual contributions.
+Trust is a key driver of cooperation, enabling individuals to engage in mutually beneficial interactions without fear of exploitation [@balliet2013trust].
+This aligns with some definitions of Trust as “a psychological state comprising the intention to accept vulnerability based on positive expectations of the intentions or behavior of another” [@rousseau1998not].
+When we trust others, we are more likely to cooperate with them, even when there is a risk of being cheated.
+Prior research also emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016; @meng_multilevel_2014].
+Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders [@fonagy_role_2014].
+
+<!-- Determining the other's goals and intentions is fundamental to successful social interaction.
 Inference of these latent motives is fraught with uncertainty [@barnby2023formalising; @feldmanhall2019resolving], as they are not directly observable and we may require extensive prior experience with the person to infer them.
@@
 But not trusting others is also risky as we may forego mutually beneficial cooperation.
-
-Prior research emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016; @meng_multilevel_2014].
+-->
+
+<!-- Prior research emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016; @meng_multilevel_2014].
 Social trust affects the health status of individuals by reinforcing social support networks, maintaining community norms and facilitating collective action.
@@
 It allows the receiver of social information to let go of their natural self-protective vigilance, which can become pathological hyper-vigilance after adverse or traumatic experiences and a key factor in the emergence of several mental health disorders [@fonagy_mentalizing_2017; @nolte2023role].
-
-Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions that foster and strengthen trust-based cooperation would be highly beneficial to society.
+-->
+
+<!-- Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions that foster and strengthen trust-based cooperation would be highly beneficial to society.
 Such interventions would allow people to more easily repair broken relationships and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
+-->
 
@@
 But if the investor obtains a low return on their investment, they will likely reduce future investments, thereby diminishing the potential gains for both players.
-To encourage the emergence and maintenance of trust in this setting, some studies focused on modification of the game such as introducing a third-party who monitors the actions of the other players [@charness_investment_2008; @fiedler_effect_2017].
-Others chose to intervene directly on the participants.
-For example, @drazkowski_gratitude_2017 found that trust (as measured by the amount invested) was increased when participants were asked to think about and write down five things that they were grateful for, and @burnham_friend-or-foe_2000 found that trust increased when participants were primed with the concepts of friend and foe.
-
+
+Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions that foster and strengthen trust-based cooperation would be highly beneficial to society.
+Such interventions would allow people to more easily repair broken relationships and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
+
+To encourage the emergence and maintenance of trust in the RTG setting, some studies have focused on modification of the game, e.g.
+through introducing a third-party who monitors the actions of the other players [@charness_investment_2008; @fiedler_effect_2017].
+Others chose to prime participants towards feeling gratitude @drazkowski_gratitude_2017 or with the concepts of friend and foe @burnham_friend-or-foe_2000.
 Whilst these results show that it is possible to improve cooperative outcomes at the start of the game, they do not address how to repair a breakdown of trust after intentional or accidental non-cooperative actions by the players.
 Cooperation in the RTG can easily break down after a transgressive behavior such as a nil or very low investment by the investor or a return by the trustee below the investment sent [@bendor_when_1991].
-Such breakdown of cooperation are particularly evident when the trustee suffers from social disorders such as Borderline Personality Disorder [BPD; @lieb_borderline_2004].
-Trustees with BPD fail to engage in trust-repairing behaviors such as coaxing the investor by signalling trustworthiness via sending high returns.
-This failure may be due to BPD trustees not realising that low returns in the game violate social norms and the mentalizing difficulties that are associated with appraising others’ intentions [@king-casas_rupture_2008; @hula2018model].
-
-To devise interventions to repair social trust, we can take inspiration from cognitive interventions championed by successful therapies that aim to improve social dysfunction in BPD.
+Such breakdowns of cooperation are particularly evident when the trustee suffers from social disorders such as Borderline Personality Disorder [BPD; @lieb_borderline_2004].
+Trustees with BPD fail to engage in trust-repairing behaviors such as coaxing the investor by signalling trustworthiness via sending high returns [@king-casas_rupture_2008].
+Neuroimaging analysis from this study is consistent with the idea that individuals with BPD may not recognize how offering low returns in such interactions conflicts with societal expectations.
+Further, computational analysis by @hula2018model, links this issue to some BPD individuals' mentalizing difficulties, such as their inability to foresee the impact of their low returns on the investor's future actions.
+
+In devising interventions to repair trust in the RTG, we can take inspiration from cognitive interventions championed by successful therapies that aim to improve social dysfunction in BPD.
 Psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve social skills in BPD [@gunderson_borderline_2018].
@@
 
-In this study, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation from a low investment sent by the investor.
+In this study, using a randomised control trial design, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation in the RTG from a low investment sent by a computerized investor.
 The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation.
-Participants are given the role of the trustee and are randomly assigned to either a control or intervention group.
+The computerized investor was programmed to play according to a hidden Markov model estimated from real players' data in prior research.
+A key aspect of this model is that the actions of the investor depend on a latent "trust state" which reacts dynamically to the trustees returns simulating real-life trust-building scenarios.
+Such a model, informed by empirical data and integrating a responsive trust mechanism, represents a novel approach to study interactive behavior in multi-player games whilst keeping a high degree of experimental control.
+To foreshadow our results, we find that the intervention led to more cooperative actions (higher returns) by the participants and countered a tendency to send back lower returns after a transgression from the investor.
+However, we found no evidence that the effects of the intervention transfer to a different (Repeated Prisoner’s Dilemma) game.
+
+<!-- Participants are given the role of the trustee and are randomly assigned to either a control or intervention group.
 They play two instances of the Repeated Trust Game with two different computerized investors.
 Between the first and second instance of the game, they either receive the cognitive intervention (intervention condition) or perform an unrelated task solving anagrams (control condition).
-The computerized investor in both instances of the game was programmed to play according to a hidden Markov model estimated from real players' data in prior research.
-A key aspect of this model is that the actions of the investor depend on a latent "trust state" which reacts to the trustees returns.
-To foreshadow our results, we find that the intervention led to more cooperative actions (higher returns) by the participants and countered a tendency to send back lower returns after a transgression from the investor.
-However, we found no evidence that the effects of the intervention transfer to a different (Repeated Prisoner’s Dilemma) game.
+-->
 
@@
 
-```{r gamesPlot, include=FALSE, echo=FALSE, fig.cap="Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+```{r gamesPlot, include=F, echo=FALSE, fig.cap="Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
 The blue line shows the returns pre-manipulation and the green line post-manipulation.
@@
 
-# ggplot(avg_ret_df, aes(x=as.factor(roundNum), y=ret_pct, group=gameNum.f, color = gameNum.f, fill=gameNum.f)) +
-#   stat_summary(fun = mean, geom = "line") +
-#   stat_summary(fun.data = mean_se, geom = "ribbon", aes(ymin=..ymin.., ymax=..ymax..), 
-#                alpha = 0.3, linetype = 0) +
-#   labs(x = "Round",
-#        y = "Percentage Return",
-#        color = "Game") +
-#   theme_bw() +
-#   theme(legend.position = "bottom") +
-#   facet_wrap(~condition.f) +
-#   scale_color_manual(values = c("darkblue", "darkgreen")) + scale_fill_manual(values = c("darkblue", "darkgreen"))
-
+# Create a data frame for the vertical linesr
+vline_data <- data.frame(
+  xintercept = c(12, 13),
+  Defection_round = factor(c("Pre-manipulation", "Post-manipulation"), levels = c("Pre-manipulation", "Post-manipulation"))
+)
+# Plot
 ggplot(avg_ret_df, aes(x=as.factor(roundNum), y=ret_pct, group=gameNum.f, color = gameNum.f, fill=gameNum.f)) +
@@
                alpha = 0.3, linetype = 0) +
+  geom_vline(data = vline_data, aes(xintercept = xintercept, linetype = Defection_round), color = "black", size = 0.6) +
+  scale_linetype_manual(values = c("Pre-manipulation" = "dotted", "Post-manipulation" = "dashed"),
+                        name = "Defection round") +
   labs(x = "Round",
@@
   theme(legend.position = "bottom",
+        legend.box = "vertical", # This will stack the legends vertically
         legend.key = element_blank(),
-        #legend.key = element_rect(fill = NA), # Make legend key background transparent
-        legend.margin = margin(t = 0, b = 0, unit = "pt"), # Adjust top and bottom margin of each legend
-        legend.box.margin = margin(t = 0, b = 0, unit = "pt")) + # Adjust top and bottom margin of the legend box
+        legend.margin = margin(t = 0.2, b = 0.2, unit = "pt"),
+        legend.box.margin = margin(t = 0, b = 0, unit = "pt"),
+        legend.title = element_text(size = 12),
+        legend.text = element_text(size = 10)) +
   facet_wrap(~condition.f) +
@@
   scale_fill_manual(values = c("darkblue", "darkgreen"),
-                    guide = "none") + # Hide the fill legend
-  guides(color = guide_legend(override.aes = list(fill = NA))) # Remove fill for color legend keys
+                    guide = "none") +
+  guides(color = guide_legend(title = "Trust Game Phase", override.aes = list(fill = NA)),
+         linetype = guide_legend(title = "Defection round"))
 
@@
 such that higher investments were associated with higher percentage returns. An Investment by Condition interaction, 
-`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_returns_pct)$full_result$condition_f_inv_scaled)`, indicates the positive effect of investment on percentage returns was greater in the control than intervention condition.
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_returns_pct)$full_result$condition_f_inv_scaled)`, indicates that returns were more affected by investments in the control condition.
 There was also an Investment by Game interaction,
@@
 ```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
-We note a different reaction to the pre-programmed one-off low investment between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
+We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
 B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
-The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round were similar before (round 12) and after (round 13) the intervention.
+The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
 The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
@@
 
-# p <- datCoax %>%
-#   ggplot(aes(x=roundNum)) + stat_summary(fun = "mean", geom = "line", aes(y=emo_scaled_x, color = "Valence")) + stat_summary(fun = "mean", geom = "line", aes(y=emo_scaled_y, color = "Arousal")) + stat_summary(fun = "mean", geom = "line", aes(y=inv_scaled, color = "Investment")) + facet_wrap(~gameNum_f, scales = "free_x")
-
-# Plot 'pre'
+# # Define the vertical line data
+# vline_data <- data.frame(
+#   xintercept = c(12, 13),
+#   linetype = c("Pre-manipulation", "Post-manipulation"),  # Names corresponding to the existing scale
+#   roundGroup = c("Rounds 11-15", "Rounds 11-15")
+# )
+
 p <- ggplot(datCoax[datCoax$gameNum.f == 'pre', ], aes(x=roundNum)) + 
@@
   scale_color_manual(name = "", values = colors, labels = c("Arousal", "Investment", "Emotion valence")) +
-  scale_linetype_manual(values = c("a_Pre" = "dotted", "b_Post" = "solid"), labels = c("Pre-intervention", "Post-intervention")) +
+  scale_linetype_manual(values = c("a_Pre" = "dotted", "b_Post" = "solid"),
+                        labels = c("Pre-manipulation", "Post-manipulation")) +
+geom_vline(data = subset(datCoax, roundGroup == "Rounds 11-15" & roundNum == 12), aes(xintercept = roundNum), linetype = "dotted", color = "darkgrey", size = 0.6, show.legend = FALSE) +
+  geom_vline(data = subset(datCoax, roundGroup == "Rounds 11-15" & roundNum == 13), aes(xintercept = roundNum), linetype = "solid", color = "darkgrey", size = 0.6, show.legend = FALSE) +
   scale_x_continuous(breaks = 1:max(datCoax$roundNum)) +
@@
   theme_bw() + 
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom",
+        legend.box = "vertical", # This will stack the legends vertically
+        legend.key = element_blank(),
+        legend.margin = margin(t = 0.2, b = 0.2, unit = "pt"),
+        legend.box.margin = margin(t = 0, b = 0, unit = "pt"),
+        legend.title = element_text(size = 12),
+        legend.text = element_text(size = 10)) +
+  guides(color = guide_legend(title = "", override.aes = list(fill = NA)),
+         linetype = guide_legend(title = "Trust Game Phase"))
 
@@
 Focusing on the HMM-full model with 6 latent states, likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCtrl[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCoax[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestPrePost[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$).
-Using this HMM, we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section (Figure \ref{fig:trusteeHMM}.A).
+Using HMM, we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section (Figure \ref{fig:trusteeHMM}.A).
 Each latent state was associated with a distribution over trustee actions.
@@
 
-In this experiment, human participants took the role of the trustee in a Repeated trust game (RTG) where they faced artificial computer agents who's behavior was partly determined by participants' returns.
+<!-- In this experiment, human participants took the role of the trustee in a Repeated trust game (RTG) where they faced artificial computer agents whose behavior was partly determined by participants' returns.
 The behavior of the artificial investors was determined by a 3-state hidden Markov model (HMM), which was estimated from the behavior of humans in the RTG in prior research.
@@
 This, together with participants' reported uncertainty about whether they faced a human or artificial investor, shows the potential of using HMM-based artificial agents to mimic human behavior in economic games, whilst offering a higher degree of experimental control than human dyadic interaction.
-
-The aim of the cognitive intervention was to articulate the potential unwanted effects of acting on impulse after a transgressive action from the investor in the form of a one-off low investment.
+-->
+
+<!-- The aim of the cognitive intervention was to articulate the potential unwanted effects of acting on impulse after a transgressive action from the investor in the form of a one-off low investment.
 After the intervention, participants sent back higher returns compared to before the intervention, and did not decrease their returns after a transgressive action like participants in the control condition did.
-The overall higher returns after the intervention occurred despite participants' emotional reactions to the investments remaining largely the same as before the intervention.
-This indicates the intervention achieved its goal of encouraging participants to respond in a non-impulsive and considered manner, possibly overriding the emotional reaction to the investment which might prompt an urge to retaliate.
+The overall higher returns after the intervention occurred despite participants' emotional reactions to the investments remaining largely the same as before the intervention,suggesting that the intervention mitigated the typical reduction in trustee returns after a breakdown of cooperation by the investor.
+-->
+
+This experiment validates the use of HMM-based artificial agents in economic games, effectively replicating investment and returns from human dyadic interactions.
+Participants were often uncertain whether they interacted with human or artificial investors, highlighting the agents' realism.
+Following a cognitive intervention, participants increased their returns without a corresponding change in emotional response, indicating the intervention's effectiveness in preserving trust despite a breach of cooperation.
+Those in the control condition returned similar proportions pre-defection and reduced their returns post-defection.
+An HMM analysis showed that those in the intervention condition were less prone to low-return states after defection.
+The findings suggest that cognitive interventions can promote resilience in cooperative behaviors following trust violations.
 
 \newpage
-\begin{landscape}
 ```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
-The latent states are ordered by the mean of the Gaussian that best fits the policy in that state, so higher numbered states are more pro-social.
+The latent states are ordered by the mean of the discretized Gaussian that best fits the policy in that state, so higher numbered states are more pro-social.
 B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
 The distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure is visibly more weighted towards higher return states.
-As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
 library(magick)
@@
 # Combine image2 and image3 side-by-side
-final_image <- c(image7, image8) %>% magick::image_append(stack = FALSE)
+final_image <- c(image7, image8) %>% magick::image_append(stack = TRUE)
 
@@
 ```
-\end{landscape}
 \newpage
 
-That participants generally send higher returns to the investor after the intervention is unlikely due to a  general learning effect unrelated to the intervention, as participants in the control condition did not increase their returns.
+That participants in the intervention condition generally send higher returns to the investor after the intervention is unlikely due to a  general learning effect unrelated to the intervention, as participants in the control condition did not increase their returns.
 Also, as participants in the intervention and control condition faced the same HMM investor, the higher post-intervention returns are not solely due to a difference in investor behavior.

### 2023-12-18 supplement.Rmd
QH comments included

@@
 
-Using the HMM-full 5 state model, we can plot the transition probabilities of the model for pre and post-intervention as well as pre- and post-control manipulation separately Figure \ref{fig:plotTransitionsSupp}).
+Using the HMM-full 6 state model, we can plot the transition probabilities of the model for pre and post-intervention as well as pre- and post-control manipulation separately Figure \ref{fig:plotTransitionsSupp}).
 This allows us to see how the transition probabilities between latent states change across Games and Condition.

### 2024-01-22 article.Rmd
latest revisions PsychScience

@@
 abstract: |
-  Social trust is an important building block of strong social bonds, and its absence is a risk factor for social dysfunction and psychopathology.
+  Social trust is a key component of strong social bonds.
+Its absence is a risk factor for social dysfunction and psychopathology.
 As such, interventions to foster and strengthen trust-based cooperation are highly desirable.
-Using the Repeated Trust Game paradigm, we assess the effectiveness of a cognitive intervention derived from Dialectical Behavior Therapy.
-The intervention's goal was to repair the potential breakdown of cooperation from a pre-programmed, one-off defection by the co-player.
-Over two games, participants are given the role of the trustee and face what they believe are two different players.
-In between games, they either receive a brief cognitive intervention or not.
+We used the Repeated Trust Game to evaluate a cognitive intervention aiming to repair cooperation breakdowns caused by a one-time defection by the co-player.
+In this study, 318 participants played the role of trustee across two online games, believing they were facing two different players.
+Between games, some received a brief cognitive intervention.
 Post-intervention, participants showed more cooperative behavior both before and after defection by the co-player.
-Analysing participants' actions with a hidden Markov model shows that participants in the intervention group had a higher proportion of cooperative states than participants in the control group.
-This is consistent with participants inferring from the intervention that pro-social and trustworthy behavior may generally provide more beneficial outcomes to them in the long run.
+Analysis using a hidden Markov model revealed that those in the intervention group had a higher proportion of cooperative states than participants in the control group.
+This is consistent with participants inferring from the intervention that pro-social behavior may generally provide more beneficial outcomes to them in the long run.
 
@@
 
+## Disclosures {.unnumbered}
+
+Conflicts of interest: The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
+Funding: I.
+Guennouni was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1.
+QJM.
+Huys acknowledges support by the UCLH NIHR BRC.
+He has received fees and options for consultancies for Aya Technologies and Alto Neuroscience.
+Ethics: This research received approval from a local ethics board (ID:21029/001).
+Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
+Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available at: https://github.com/ismailg/XXXXXXX.
+The design and analysis plans were not preregistered.
+
+<!-- Author Contribution: I.
+Guennouni, QJM.
+Huys and M.
+Speekenbrink designed and developed the study concept.
+Experiment design was done by S.
+Dupret and I.
+Guennouni.
+Testing and data collection were performed by I.
+Guennouni.
+I.
+Guennouni analysed and interpreted the data under the supervision of QJM.
+Huys and M.
+Speekenbrink.
+M.
+Speekenbrink and I.
+Guennouni jointly performed the HMM modelling.
+All authors jointly wrote and approved the final version of the manuscript for submission.
+-->
+
 # Introduction
@@
 Trust is a key driver of cooperation, enabling individuals to engage in mutually beneficial interactions without fear of exploitation [@balliet2013trust].
-This aligns with some definitions of Trust as “a psychological state comprising the intention to accept vulnerability based on positive expectations of the intentions or behavior of another” [@rousseau1998not].
+This aligns with some definitions of trust as “a psychological state comprising the intention to accept vulnerability based on positive expectations of the intentions or behavior of another” [@rousseau1998not].
 When we trust others, we are more likely to cooperate with them, even when there is a risk of being cheated.
@@
 
-<!-- Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions that foster and strengthen trust-based cooperation would be highly beneficial to society.
-Such interventions would allow people to more easily repair broken relationships and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
--->
-
-<!-- Mechanism design, pioneered by @vickrey_counterspeculation_1961, is a field that studies incentive alignment and looks for ways to promote social welfare or revenue maximization, despite self-interest of the individual actors.
-In the context of social dilemmas, key mechanisms were explored with good effect to foster and maintain the cooperative outcome.
-@axelrod_evolutionary_1986 studied the emergence and stability of behavioral norms to regulate non-cooperative actions in social settings.
-He identifies a behavioral norm as a dominant behavioral strategy which is often punished by others when not adhered to.
-A meta-norm is the propensity to incur a cost in order to enforce a norm.
-@axelrod_evolutionary_1986 showed that when playing a social dilemma game, individuals have a strong incentive to enforce punishment of defectors lest they are in turn punished by others.
-This led to a decline of defection.
-Thus, meta-norms can be seen as a mechanism to promote and sustain cooperation in a population.
-In the context of the trust game, @charness_investment_2008 explored the effect a third party monitor can have on the amounts sent and received.
-This third-party's payoff is unaffected by the decisions made by the investor and trustee.
-However, the study allowed the third party to punish overly selfish trustees or reward Investors making a loss on the interaction.
-They found that the actions of both players were materially more cooperative in the presence of this third party.
-@fiedler_effect_2017 found that the introduction of a third party that monitors the investments and returns of the players led to more cooperative behavior, even when the third party had no ability to reward or punish the players.
--->
-
-A well-established paradigm in the study of trust is the Repeated Trust Game [RTG;  @joyce_trust_1995].
+A well-established paradigm in the study of trust is the Repeated Trust Game (RTG; @joyce_trust_1995).
 In this game, the "investor" decides how much of an endowment to send to the other player (the "trustee").
@@
 through introducing a third-party who monitors the actions of the other players [@charness_investment_2008; @fiedler_effect_2017].
-Others chose to prime participants towards feeling gratitude @drazkowski_gratitude_2017 or with the concepts of friend and foe @burnham_friend-or-foe_2000.
+Others chose to prime participants towards feeling gratitude [@drazkowski_gratitude_2017] or with the concepts of friend and foe [@burnham_friend-or-foe_2000].
 Whilst these results show that it is possible to improve cooperative outcomes at the start of the game, they do not address how to repair a breakdown of trust after intentional or accidental non-cooperative actions by the players.
 Cooperation in the RTG can easily break down after a transgressive behavior such as a nil or very low investment by the investor or a return by the trustee below the investment sent [@bendor_when_1991].
-Such breakdowns of cooperation are particularly evident when the trustee suffers from social disorders such as Borderline Personality Disorder [BPD; @lieb_borderline_2004].
+Such breakdowns of cooperation are particularly evident when the trustee suffers from social disorders such as Borderline Personality Disorder (BPD; @lieb_borderline_2004).
 Trustees with BPD fail to engage in trust-repairing behaviors such as coaxing the investor by signalling trustworthiness via sending high returns [@king-casas_rupture_2008].
-Neuroimaging analysis from this study is consistent with the idea that individuals with BPD may not recognize how offering low returns in such interactions conflicts with societal expectations.
-Further, computational analysis by @hula2018model, links this issue to some BPD individuals' mentalizing difficulties, such as their inability to foresee the impact of their low returns on the investor's future actions.
+Neuroimaging analysis from the study of @king-casas_rupture_2008 is consistent with the idea that individuals with BPD may not recognize how offering low returns in such interactions conflicts with societal expectations.
+Further, computational analysis by @hula2018model links this issue to some BPD individuals' mentalizing difficulties, such as their inability to foresee the impact of their low returns on the investor's future actions.
 
@@
 The computerized investor was programmed to play according to a hidden Markov model estimated from real players' data in prior research.
-A key aspect of this model is that the actions of the investor depend on a latent "trust state" which reacts dynamically to the trustees returns simulating real-life trust-building scenarios.
+A key aspect of this model is that the actions of the investor depend on a latent "trust state" which reacts dynamically to the trustees' returns simulating real-life trust-building scenarios.
 Such a model, informed by empirical data and integrating a responsive trust mechanism, represents a novel approach to study interactive behavior in multi-player games whilst keeping a high degree of experimental control.
@@
 The investment is then multiplied by a factor of 3 and sent to the trustee who needs to decide how much of the multiplied investment they want to send back to the investor.
-Shown here is the stage at which the trustee makes a decision of how much to send back the investor.
+Shown here is the stage at which the trustee decides how much to send back to the investor.
 Immediately before making this decision, participant are shown a two dimensional grid (Panel C) where they need to report their reaction to the investment.
@@
 Participants were then asked whether the information just received would change their behavior in such a hypothetical situation and to justify their answer.
-Full details on the intervention are provided in the supplementary information.
+Full details on the intervention are provided in the Supplementary Information.
 
@@
 Applying the same model to the returns after the defection (see the supplement for full results), we again find a significant interaction between Condition and Game.
-Participants in the control condition decreased their post-defection returns from the first to the second RTG, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
+Participants in the control condition decreased their post-defection returns from the first to the second RTG, pre-post, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Control_Pre_post`.
 There was no significant change for participants in the intervention condition, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`.
@@
 There was no indication that the effect of the investment on either aspect of emotion was affected by the intervention, as there was no interaction between Investment and Game on valence, 
-`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_x)$full_result$gameNum_f_scaleinvestment)`
-, or arousal, 
+`r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_x)$full_result$gameNum_f_scaleinvestment)`, or arousal, 
 `r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment)`. 
@@
 As in the models for the investor, these HMMs assume behavior is governed by latent states, with participants' switches between states now dependent on the investments made.
-We also allowed for differences between games and conditions in how investments govern state transitions: We fitted five main models which all regressed state transition probabilities onto investments, as well as on additional contrast-coded predictors for condition and/or Game.
-In the most complex model (HMM-full), the transition probabilities were allowed to differ between all four combinations of Game and condition.
+We also allowed for differences between games and conditions in how investments govern state transitions: We fitted five main models which all regressed state transition probabilities onto investments, as well as on additional contrast-coded predictors for Condition and/or Game.
+In the most complex model (HMM-full), the transition probabilities were allowed to differ between all four combinations of Game and Condition.
 The HMM-coax model allowed differences between post-intervention and the other three conditions (pre-intervention, pre-control, post-control) treating these latter conditions as the same.
@@
 
-Focusing on the HMM-full model with 6 latent states, likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCtrl[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCoax[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestPrePost[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$).
-Using HMM, we estimated the investors' policy in each state assuming a discretised Gaussian response function as highlighted in the previous section (Figure \ref{fig:trusteeHMM}.A).
-Each latent state was associated with a distribution over trustee actions.
-The latent states were ordered by the mean of the estimated Gaussian, such as higher numbered latent states reflect higher mean percentage return.
+Focusing on models with 6 latent states, likelihood ratio tests showed that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCtrl[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestCoax[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(60) = `r round(-2*as.numeric(logLik(bestPrePost[[6]])) - (-2*as.numeric(logLik(bestFull[[6]]))) , 2)`$, $p < .001$).
+As such, there is evidence that participants reacted differently to the investments in the four combinations of Condition and Game.
+The estimated state-dependent policy of trustee actions, according to the HMM-full model, is depicted in Figure \ref{fig:trusteeHMM}.A.
 
@@
 Taking the best-fitting 6-state HMM-full model, we used a local decoding procedure to assign observations (participants' returns on trials) to latent states.
-The states are ordered by expected return, with state 1 having the lowest mean return and state 5 the highest.
-Figure \ref{fig:trusteeHMM}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
+The states are ordered by expected return, with state 1 having the lowest mean return and state 6 the highest.
+Figure \ref{fig:trusteeHMM}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition, both pre and post defection.
 For instance, in round 5, state 1 was the most likely posterior state for only $5$% of participants in the intervention condition compared to $12$% in the control condition ($\chi^2(1) = 4.73, p = 0.03$).
@@
 
-This experiment validates the use of HMM-based artificial agents in economic games, effectively replicating investment and returns from human dyadic interactions.
-Participants were often uncertain whether they interacted with human or artificial investors, highlighting the agents' realism.
 Following a cognitive intervention, participants increased their returns without a corresponding change in emotional response, indicating the intervention's effectiveness in preserving trust despite a breach of cooperation.
@@
 The findings suggest that cognitive interventions can promote resilience in cooperative behaviors following trust violations.
+This also validates the use of HMM-based artificial agents in economic games, effectively replicating investment and returns from human dyadic interactions.
+Participants were often uncertain whether they interacted with human or artificial investors, highlighting the agents’ realism.
 
@@
 ```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
-The latent states are ordered by the mean of the discretized Gaussian that best fits the policy in that state, so higher numbered states are more pro-social.
+The latent states are ordered by the mean of the discretized Gaussian representing the policy in that state, so higher numbered states can be considered more pro-social.
 B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
@@
 
-\pagebreak
-
-# Disclosures
-
-**Author Contribution:**
-I.
-Guennouni, Q.
-Huys, and M.
-Speekenbrink designed and developed the study concept.
-Experiment design was done by S.
-Dupret and I.
-Guennouni.
-Testing and data collection were performed by I.
-Guennouni.
-I.
-Guennouni analysed and interpreted the data under the supervision of Q.
-Huys and M.
-Speekenbrink.
-M.
-Speekenbrink and I.
-Guennouni jointly performed the HMM modelling.
-All authors jointly wrote and approved the final version of the manuscript for submission.
-
-**Declaration of Conflicting Interests:**
-The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
-
-**Funding:**
-Funding was provided by XXXXX
-
-**Open Practices:**
-All data from this study have been made publicly available via XXXX and can be accessed at XXXX .
-The design and analysis plans were not preregistered.
-The complete Open Practices Disclosure for this article can be found at XXXX
-
 <!-- # Conclusion -->

### 2024-01-22 supplement.Rmd
latest revisions PsychScience

@@
 ---
-title: "Supplementary Information"
+title: "(Re)building cooperation: Effects of a cognitive intervention on
+cooperative behavior in games"
+subtitle: "Supplementary Information"
 # author: "Ismail Guennouni"
@@
 We estimated a three-state model for investor's behaviour, using maximum likelihood estimation via the Expectation-Maximisation algorithm as implemented in the depmixS4 (Visser & Speekenbrink) package for R.
-The model was estimated using investments from existing datasets of human dyads playing 10 rounds of the RTG with the same trustee [@king-casas_rupture_2008; **VTC project dataset**].
-The dataset consisted of a total of 381 games.
+The model was estimated using investments from existing datasets of human dyads playing 10 rounds of the RTG with the same trustee.
+The dataset consisted of a total of 381 games from two data sources: First, a total of 93 repeated trust games with healthy investors and a mix of healthy trustees and trustees diagnosed with Borderline Personality Disorder (BPD) [@king-casas_rupture_2008].
+The second source was from data collected as part of a project investigating social exchanges at the Montague lab at Virginia Tech and consists of 288 games.
 

### 2024-01-25 article.Rmd
anonymisation

@@
 title: "(Re)building cooperation: Effects of a cognitive intervention on cooperative behavior in games"
-author:
-  "Ismail Guennouni^1^, Samuel Dupret^1^, Quentin JM Huys^2^, Maarten Speekenbrink^1^"
+# author:
+#   "Ismail Guennouni^1^, Samuel Dupret^1^, Quentin JM Huys^2^, Maarten Speekenbrink^1^"
 
@@
 ---
-\small  
-^1^ *Department of Experimental Psychology, Division of Psychology and Language Sciences, UCL*.  
-^2^ *Division of Psychiatry and Max Planck Centre for Computational Psychiatry and Ageing Research, Queen Square Institute of Neurology, UCL.*
+<!-- \small   -->
+<!-- ^1^ *Department of Experimental Psychology, Division of Psychology and Language Sciences, UCL*.   -->
+<!-- ^2^ *Division of Psychiatry and Max Planck Centre for Computational Psychiatry and Ageing Research, Queen Square Institute of Neurology, UCL.* -->
 
@@
 Conflicts of interest: The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
-Funding: I.
-Guennouni was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1.
-QJM.
-Huys acknowledges support by the UCLH NIHR BRC.
+Funding: Author 1 was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1.
+Author 3 acknowledges support by the UCLH NIHR BRC.
 He has received fees and options for consultancies for Aya Technologies and Alto Neuroscience.
@@
 Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
-Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available at: https://github.com/ismailg/XXXXXXX.
+Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available.
 The design and analysis plans were not preregistered.
@@
 
-<!-- Determining the other's goals and intentions is fundamental to successful social interaction.
-Inference of these latent motives is fraught with uncertainty [@barnby2023formalising; @feldmanhall2019resolving], as they are not directly observable and we may require extensive prior experience with the person to infer them.
-Absent a history of interaction, we may decide to trust that the other's goals and intentions are aligned with our own.
-Such trust is risky  and if misplaced, it can come at a high cost.
-But not trusting others is also risky as we may forego mutually beneficial cooperation.
--->
-
-<!-- Prior research emphasises the importance of social trust in determining why some people fare better than others physically and mentally [@giordano_trust_2016; @meng_multilevel_2014].
-Social trust affects the health status of individuals by reinforcing social support networks, maintaining community norms and facilitating collective action.
-Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders.
-@fonagy_role_2014 identified epistemic trust -- the belief in the authenticity and personal relevance of interpersonally transmitted knowledge -- as an important function of early attachment relationships.
-It allows the receiver of social information to let go of their natural self-protective vigilance, which can become pathological hyper-vigilance after adverse or traumatic experiences and a key factor in the emergence of several mental health disorders [@fonagy_mentalizing_2017; @nolte2023role].
--->
-
 A well-established paradigm in the study of trust is the Repeated Trust Game (RTG; @joyce_trust_1995).
@@
 
-<!-- Participants are given the role of the trustee and are randomly assigned to either a control or intervention group.
-They play two instances of the Repeated Trust Game with two different computerized investors.
-Between the first and second instance of the game, they either receive the cognitive intervention (intervention condition) or perform an unrelated task solving anagrams (control condition).
--->
-
 ```{r dataLoad, include=FALSE }
@@
 In the repeated version, both players can maximise their reward by choosing to cooperate.
-In this game, the computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
-On round 4, the computerised agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
-<!-- MS: did participants have to do the emotion/action evaluations here as well?
--->
 
@@
 
+In this game, the computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
+On round 4, the computerised agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
+
 ## Intervention
@@
 On each round, after being informed about the amount sent by the investor, participants were asked to evaluate their emotion (intervention condition) or the investment (control condition).
-<!-- provide feedback, with participants in the Intervention condition rating their feeling in terms of valence (from negative to positive) and arousal (from low to high), and participants in the Control condition rating the investment in terms of speed (from slow to fast) and magnitude (from low to high).
-These ratings were made by indicating a point on a two-dimensional grid.--> Participants then decided on how much of the tripled investment to return to the investor, before continuing to the next round.
+Participants then decided on how much of the tripled investment to return to the investor, before continuing to the next round.
 After completing 15 rounds of the RTG, participants rated how cooperative, selfish, trustworthy and friendly they perceived the investor to be (all on a scale from 1 to 10).
@@
 Mixed-effects analysis on the percentage returns shows a significant main effect of Condition (intervention vs.
-control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f`<!--$F(1,315.31) = 9.52$, $p = .002$-->, with higher percentage returns in the intervention compared to the control condition.
+control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f`, with higher percentage returns in the intervention compared to the control condition.
 Importantly, we also find an interaction between Condition and Game (RTG pre- vs.
-post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f`<!--$F(1,314.2) = 26.9$, $p < .001$-->.
+post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f`.
 Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:TrustGameResults}.C).
@@
 ```
-
-```{r, include=F}
-
-# load(mod_returns_pre)
-# load(pairs_pre_int)
-```
-
-We next analysed returns separately for rounds prior to the pre-programmed low investment by the HMM (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
-Applying the same mixed-effects model as before to returns before the defection largely replicates the results over all trials.
-Participants in the intervention condition increased their returns in the second game, `r papaja::apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`.
-There was no evidence that participants in the control condition changed their returns in pre-defection trials between the first and second RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
-Full results are provided in the supplement.
-
-\newpage
-\begin{landscape}
-```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
-We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
-B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
-The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
-The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
-Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
-Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
-library(magick)
-
-# Read in the images
-image5 <- image_read("figures/resultsTrust.png")
-image6 <- image_read("figures/emotionReaction2.png")
-violin_ret <- image_read("figures/violin_ret.png")
-violin_inv <- image_read("figures/violin_inv.png")
-
-image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
-violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
-violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
-
-# Assuming a 300 DPI resolution for good print quality
-dpi <- 300
-
-# Spacing of 0.1 inches converted to pixels
-spacing <- 0.05 * dpi
-
-# Calculating the width and height for each image
-width_per_image <- ((12 - 0.1) / 2) * dpi
-height_per_image <- ((7.4 - 0.1) / 2) * dpi
-# The geometry string for each image, including spacing (assuming no borders)
-geometry_string <- paste0(width_per_image, 'x', height_per_image, '+', spacing, '+', spacing)
-
-# Now create the montage with the specified geometry
-combined_image2 <- image_montage(
-  c(image5, image6, violin_ret, violin_inv), 
-  tile = "2x2",
-  geometry = geometry_string
-)
-
-# Display the combined image
-plot(combined_image2)
-```
-\end{landscape}
-\newpage
 
@@
 
-```{r violinPanels, include=F, fig.cap="Participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds (Panel A), whilst those in the Control condition sent back lower returns.
-Focusing on pre-defection trials (Panel C), those in the Control condition returned similar amounts between games, while returns were higher in the Intervention condition in the second game.
-Post-defection (Panel D), returns were similar for those in the Intervention condition while those in the Control condition returned lower amounts in the second game.
-Investments by the HMM agent (Panel B) were higher in the second game compared to the first game across conditions.
-All panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition", fig.align="center", fig.height=10, fig.width=10}
-
-ggpubr::ggarrange(pctRet_all, inv_all, pctRet_pre, pctRet_post, nrow=2, ncol=2, common.legend = TRUE, legend = "bottom")
-```
+We next analysed returns separately for rounds prior to the pre-programmed low investment by the HMM (rounds 1 to 11 pre-intervention and 1 to 12 post-intervention) and rounds after (rounds 12 to 15 pre-intervention and rounds 13 to 15 post-intervention).
+Applying the same mixed-effects model as before to returns before the defection largely replicates the results over all trials.
+Participants in the intervention condition increased their returns in the second game, `r papaja::apa_print(pairs_pre_int)$full_result$Intervention_Pre_post`.
+There was no evidence that participants in the control condition changed their returns in pre-defection trials between the first and second RTG, `r papaja::apa_print(pairs_pre_int)$full_result$Control_Pre_post`.
+Full results are provided in the supplement.
 
@@
 There was no significant change for participants in the intervention condition, `r papaja::apa_print(pairs(postcoax_interaction, by = "condition.f", reverse=FALSE))$full_result$Intervention_Pre_post`.
-<!-- When questionnaire scores for borderline traits, mentalising and emotion regulation abilities were added as explanatory variables, we found no interaction effect of these questionnaire scores with the Condition variable, nor a main effect of the questionnaire scores on participants returns in the RTG.
--->
 
@@
 Instead, it countered the tendency shown by participants in the control condition to lower returns after the defection in the second game compared to the first game.
+
+\newpage
+\begin{landscape}
+```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
+B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
+The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
+The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
+Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
+Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+library(magick)
+
+# Read in the images
+image5 <- image_read("figures/resultsTrust.png")
+image6 <- image_read("figures/emotionReaction2.png")
+violin_ret <- image_read("figures/violin_ret.png")
+violin_inv <- image_read("figures/violin_inv.png")
+
+image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
+violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
+violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
+
+# Assuming a 300 DPI resolution for good print quality
+dpi <- 300
+
+# Spacing of 0.1 inches converted to pixels
+spacing <- 0.05 * dpi
+
+# Calculating the width and height for each image
+width_per_image <- ((12 - 0.1) / 2) * dpi
+height_per_image <- ((7.4 - 0.1) / 2) * dpi
+# The geometry string for each image, including spacing (assuming no borders)
+geometry_string <- paste0(width_per_image, 'x', height_per_image, '+', spacing, '+', spacing)
+
+# Now create the montage with the specified geometry
+combined_image2 <- image_montage(
+  c(image5, image6, violin_ret, violin_inv), 
+  tile = "2x2",
+  geometry = geometry_string
+)
+
+# Display the combined image
+plot(combined_image2)
+```
+\end{landscape}
+\newpage
 
@@
 
-# Conduction t-tests 
-# t.test(rating_coop ~ gameNumber, data = datRatingsCoax, paired = TRUE)
-# t.test(rating_selfish ~ gameNumber, data = datRatingsCoax, paired = TRUE)
-# t.test(rating_trustworthy ~ gameNumber, data = datRatingsCoax, paired = TRUE)
-# t.test(rating_friendly ~ gameNumber, data = datRatingsCoax, paired = TRUE)
-
 ```
@@
 
-# Average cooperation rates per round
-#PD_data %>% group_by(roundNum, condition.f) %>% summarise(coopRate = mean(coop))
 ```
@@
 
-<!-- Table \ref{tab:table-BICs-coax} shows the BICs of the various fitted models for an assumed number of states between 2 and 7.
-For a simple model without any contrasts (HMM-inv) and a model with post-control only contrast (HMM-ctrl) we find a 6-state model to be best fitting.
-If the contrast is between the post-intervention group and all the other groups (HMM-coax), then a 7 state model is best fitting.
-When the contrast is comparing only pre and post Intervention groups (HMM-prepost), a 5 state model fits best.
-Finally, when we distinguish between pre-manipulation, post-control and post-intervention (HMM-full), we find that a 5 state model fits best.
-Since we only fit models between 2 and 7 states, it is possible that for those where we find the 7 state model to be best fitting, models with a higher number of states could fit the data better.
-We decided to stop at 7 states for computational cost reasons and because the interpretation of models with a higher number of states becomes complex.
--->
-
 ```{r, include=FALSE}
@@
 The estimated state-dependent policy of trustee actions, according to the HMM-full model, is depicted in Figure \ref{fig:trusteeHMM}.A.
-
-<!-- We start by comparing HMM-full with HMM-inv.
-We find that HMM-full fits the data better than HMM-inv ($\chi^2(84) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$).
-Likewise HMM-ctrl fits better than HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(bestCtrl[[5]]))) , 2)`$, $p < .001$).
-The same is true for HMM-coax compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(bestCoax[[5]]))) , 2)`$, $p < .001$) and HMM-prepost compared to HMM-inv ($\chi^2(44) = `r round(-2*as.numeric(logLik(fittedSimple[[5]])) - (-2*as.numeric(logLik(bestPrePost[[5]]))) , 2)`$, $p < .001$).
-HMM-inv being the worst fitting model compared to the others indicates the existence of differentiated behavior pre vs post manipulation and/or between the control and intervention groups.
--->
-
-<!-- Using likelihood ratio tests, we find that the HMM-full model fits significantly better than HMM-ctrl ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCtrl[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$), HMM-coax ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestCoax[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$) and HMM-prepost ($\chi^2(40) = `r round(-2*as.numeric(logLik(bestPrePost[[5]])) - (-2*as.numeric(logLik(bestFull[[5]]))) , 2)`$, $p < .001$).
-This is consistent with a differentiated behavior of the trustees between all three groups: the post-intervention group, the post-control group and the pre-manipulation group.
--->
 
@@
 
-<!-- To quantitatively explore the differences in transition probabilities between the control and intervention conditions, we can estimate from the model, using local decoding methods from the depmixS4 package [@visser_depmixs4_2021], the most likely posterior state of the trustee participants by round given the actions they have taken.
-Figure \ref{fig:postStatesBestMod}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition both pre and post defection.
-For instance, in round 5, state 1 was the most likely posterior state for only $7$% of participants in the intervention condition compared to $24$% in the control condition ($\chi^2(1) = 8.26, p < 0.01$).
-For the post-defection trial after the intervention (round 14), state 1 was the most likely state for only $22$% of participants in the intervention condition compared to $43$% in the control condition ($\chi^2(1) = 14.70, p < 0.001$).
-
-The posteriors also suggest that a non-negligible proportion of participants in the intervention condition did not exhibit a behavior consistent with the goal of the intervention as they were still best fit by low-return states post intervention.
-For instance, focusing on round 13 post defection $30.2$% of those in the intervention condition were most likely to be in the least pro-social state 1.
-These differences can be seen as an indication of important heterogeneity in the effectiveness of the intervention.
--->
-
-```{r, include=FALSE}
-# library(depmixS4)
-# 
-# n_bootstraps <- 1  # number of bootstrap resamples
-# bootstrap_estimates <- matrix(NA, nrow=n_bootstraps, ncol=1)  # to store bootstrap estimates
-# 
-# ns <- 3
-# numCovIn <- 2
-# numCovTr <- 6
-# from <- 3
-# to <- 1
-# 
-# for (i in 1:n_bootstraps) {
-#   # create a bootstrap resample of the data
-#   #bootstrap_data <- data[sample(nrow(data), replace=TRUE), ]
-#   bootstrap_data <- avg_ret_df %>% filter(playerId %in% sample(playerId,replace=TRUE))
-#   
-#   rModels <- rep(list(list(vtdgaus(y=bootstrap_data$ret_pct_0,yield=3*bootstrap_data$investment))),each=ns)
-#   
-#   simple_mod <- depmix(ret_pct ~ 1, data = bootstrap_data, nstates = ns, transition = ~ next_investment*intervention_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-#   
-#   
-#   # fit the model to the bootstrap resample
-# 
-#   model <- makeDepmix(response=rModels, transition = simple_mod@transition , prior = simple_mod@prior, initdata=priordat, ntimes = rep(15,636), homogeneous=FALSE)
-#   
-#   cat("two")
-#   # trust_fullCtrst[[i]] <- depmix(return_pct_bin ~ 1, data = avg_ret_df, nstates = i, transition = ~ next_investment*intervention_ctrst, prior = ~ investment, initdata=priordat, family=multinomial("mlogit"), ntimes = rep(15,636))
-#   
-#   
-# 
-#   fit <- fit(model)
-#   cat("post-fit")
-# 
-#   # store the estimates
-#   #bootstrap_estimates[i, ] <- getpars(fit)
-#   
-#   pars <- matrix(getpars(fit)[seq(ns*numCovIn + 1 + (from - 1)*numCovTr*ns, ns*numCovIn + 1 + (from - 1)*numCovTr*ns + numCovTr*ns - 1)],ncol=numCovTr)
-#   
-#    bootstrap_estimates[i, ] <- pars[to,3]
-#   
-# }
-# 
-# # calculate 95% confidence intervals
-# ci_lower <- apply(bootstrap_estimates, 2, function(x) quantile(x, 0.025))
-# ci_upper <- apply(bootstrap_estimates, 2, function(x) quantile(x, 0.975))
-# 
-# # print the confidence intervals
-# print(ci_lower)
-# print(ci_upper)
-
-```
-
 # Discussion
-
-<!-- In this experiment, human participants took the role of the trustee in a Repeated trust game (RTG) where they faced artificial computer agents whose behavior was partly determined by participants' returns.
-The behavior of the artificial investors was determined by a 3-state hidden Markov model (HMM), which was estimated from the behavior of humans in the RTG in prior research.
-Overall, investments and returns by the artificial and human agents replicated that of human dyads in prior research using the RTG [@charness_investment_2008; @fiedler_social_2011].
-This, together with participants' reported uncertainty about whether they faced a human or artificial investor, shows the potential of using HMM-based artificial agents to mimic human behavior in economic games, whilst offering a higher degree of experimental control than human dyadic interaction.
--->
-
-<!-- The aim of the cognitive intervention was to articulate the potential unwanted effects of acting on impulse after a transgressive action from the investor in the form of a one-off low investment.
-After the intervention, participants sent back higher returns compared to before the intervention, and did not decrease their returns after a transgressive action like participants in the control condition did.
-The overall higher returns after the intervention occurred despite participants' emotional reactions to the investments remaining largely the same as before the intervention,suggesting that the intervention mitigated the typical reduction in trustee returns after a breakdown of cooperation by the investor.
--->
 
@@
 Future research will need to assess whether transfer to other games is possible.
-<!-- For those that took on the intervention message and showed coaxing behavior in the second trust game, the fact that the investor still defected in the final rounds might have reinforced the idea that not reciprocating negative behavior is a losing strategy after all.-->
 
@@
 Other participants responded to the intervention and increased their returns.
-<!-- This raises important questions for the measurement of intervention effectiveness.--> Heterogeneity in response to treatment is common in psychiatry and related fields.
+Heterogeneity in response to treatment is common in psychiatry and related fields.
 Such heterogeneity may reflect the complex nature of mental health problems, which may be best viewed as complex systems involving interactions between neuro-computational processes and socio-environmental contexts evolving over time [@fried_moving_2017].
@@
 
-<!-- # Conclusion -->
-
-<!-- We explored the effect of a brief cognitive intervention on the behavior of human trustees facing adaptive artificial investors designed to replicate the behavior of human investors in the Repeated Trust Game.
-Each state defines different levels of a cooperative response with the agent able to transition between these states based on the behavior of the human co-player.
-Feedback from participants indicated that these agents were sometimes perceived as humans.
-Their strategy led to emergent cooperative behavior when playing the Repeated Trust Game with human players.
-The intervention, promoting a less impulsive reaction to transgressive actions, led to coaxing behavior and less negative reciprocity when the investor sent a very low investment.
-It also led to more trustworthy behavior prior to the pre-programmed defection trial and to coaxing behavior after defection.
-Whilst this intervention effect varied between participants and generally was not transferred to a new game, an HMM analysis of participant's play post intervention showed differentiated patterns of transitions between latent states, indicating a change in the effect of the co-player action on the probability of transitioning between latent mental states.
--->
-
 \pagebreak

### 2024-01-25 supplement.Rmd
anonymisation

@@
 subtitle: "Supplementary Information"
-# author: "Ismail Guennouni"
-#date: "2023-04-28"
-#output: pdf_document
 
@@
 # Repeated Trust Game
-<!-- Participants played two iterations of the standard version of the repeated trust game [@joyce_trust_1995].
-The game is played in dyads, with one player assigned the role of the "investor" and the other player that of the "trustee".
-In the variant of the game we chose, the investor is endowed with 20 units at the start of each round.
-They need to decide how much of that endowment they want to invest with the trustee.
-The investment is then multiplied by a factor of 3 and sent to the trustee.
-As shown in Figure \ref{fig:trustGame}, the trustee in turn needs to decide how much of the (multiplied) investment they want to send back to the investor.
-If they send back more than a third of what they received, then both the investor and the trustee make a gain.
-Otherwise, the trustee would benefit but the investor would lose on their investment.
-If the interaction lasts for only one round, the Nash equilibrium of this game is for the investor to send nothing, as there is no incentive for the trustee to send back any return.
-In the repeated version, to maximise their rewards over time, both players need to build trust so that they can share the benefits of the bigger pie (the investment multiplied by three).
-If during the course of the interaction, the investor has been rewarded for taking the risk of sending an investment, then they would be more likely to invest more, and the multiplied investment would give both a bigger pie to share.
-If however the investor felt that they were not getting a return on their investment, then they would refrain from investing and neither would gain from the interaction.
--->
 
@@
 Participants in the control condition were asked to chose any point on the two dimensional grid to show they have understood how to interact with the grid.
-
-<!-- Whilst playing the RTG, participants were asked to provide some feedback, in each round of the game, after seeing the amount sent by the investor.
-This feedback took the form of the answer to a question using a two dimensional field.
-What the axes of the field represented differed by condition.
-In the intervention condition, participants were asked to rate their emotional state with regard to the other player's choice of investment, with the x-axis representing the valence of the emotion they felt (positive or negative) and the Y-axis representing the emotional "arousal" they experienced (low or high).
-In the control condition, players were asked to rate attributes of the investment that were not related to their emotion, with the X-axis rating of how fast the investor is (slow or fast) and the Y-axis the magnitude of the investment (low or high).
-Figure \ref{fig:grid} shows a screenshot of the field in the intervention condition where participants were asked about their own emotional response to the investment.
-At the beginning of each game, participants were provided with detailed explanations of the meaning of the two axes as well as the opportunity to provide a baseline emotional state through using the field prior to the start of the game.
--->
 
@@
 We Z-transform the questionnaire scores and Investment as centering would be beneficial to interpreting the main effects more easily.
-<!-- ## Statistical analysis of Behavior -->
 
@@
 
-<!-- Figure \ref{fig:preDefectionModel} shows the result of fitting a mixed effect model to participants percentage returns in the RTG when we restrict the analysis to pre-defection trials. -->
-
 ## Mixed-effects model results for post-defection returns:
@@
 ```
-
-<!-- Figure \ref{fig:postDefectionModel} shows the result of fitting a mixed effect model to participants percentage returns in the RTG when we restrict the analysis to post-defection trials.  -->
 

### 2024-01-25 example.R

@@ -1,50 +1,0 @@
-# Create a synthetic dataset
-set.seed(42)
-n <- 300
-states <- c(rep(1, n/3), rep(2, n/3), rep(3, n/3))
-y <- numeric(n)
-x <- numeric(n)
-
-y[states == 1] <- rnorm(sum(states == 1), mean = 0, sd = 1)
-y[states == 2] <- rnorm(sum(states == 2), mean = 5, sd = 1)
-y[states == 3] <- rnorm(sum(states == 3), mean = 10, sd = 1)
-
-x[states == 1] <- sample(0:1, size = sum(states == 1), prob = c(0.7, 0.3), replace = TRUE)
-x[states == 2] <- sample(0:1, size = sum(states == 2), prob = c(0.3, 0.7), replace = TRUE)
-x[states == 3] <- sample(0:1, size = sum(states == 3), prob = c(0.5, 0.5), replace = TRUE)
-
-data <- data.frame(y = y, x = x)
-
-# Fit an HMM model with a binary covariate in the transition function
-hmm <- depmix(y ~ 1, data = data, nstates = 3, family = gaussian(),
-              transition = ~ x)
-fitted_model <- fit(hmm)
-
-# Get the estimates of the transition function
-transition_pars <- getpars(fitted_model, which = "transition")
-
-# Get the covariance matrix of the transition function parameters
-cov_matrix <- vcov(fitted_model, which = "transition")
-
-
-# Find the indices of the binary covariate coefficients in the transition function
-binary_covariate_indices <- c(4, 8)
-
-# Wald tests
-for (i in binary_covariate_indices) {
-  estimate <- transition_pars[i]
-  standard_error <- sqrt(cov_matrix$vcov[i, i])
-  wald_statistic <- (estimate / standard_error)^2
-  p_value <- pchisq(wald_statistic, df = 1, lower.tail = FALSE)
-  
-  cat("Wald statistic (", i, "):", wald_statistic, "\n")
-  cat("p-value (", i, "):", p_value, "\n")
-  
-  # Interpret the result
-  alpha <- 0.05
-  if (p_value < alpha) {
-    cat("The binary covariate coefficient (", i, ") is significantly different from 0.\n")
-  } else {
-    cat("The binary covariate coefficient (", i, ") is not significantly different from 0.\n")
-  }
-}

### 2024-01-26 article.Rmd
statement anonymisation

@@
 Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
-Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available.
+Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available on: https://github.com/ismailg/coax_psych_science.
 The design and analysis plans were not preregistered.
@@
 
+In this game, the computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
+On round 4, the computerised agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
+
+## Intervention
+
+The intervention was built on Dialectical Behavior Therapy (DBT) skills training, asking patients to reflect on the consequences of actions taken in emotional states [@linehan_dbt_2015].
+Specifically, participants were presented with a hypothetical situation in which they receive a low investment and asked to indicate how they would respond.
+They were then presented with an educational slide inviting them to consider that the ultimate aim in the game is to maximise their total reward and to reflect on whether punishing the investor for the low investment is beneficial to achieving that aim.
+Participants were told that punishment can create a negative feedback loop where the other player might trust them even less.
+An alternative action was suggested, whereby players would respond kindly to such a transgression in the hope of gaining trust from the investor.
+Participants were then asked whether the information just received would change their behavior in such a hypothetical situation and to justify their answer.
+Full details on the intervention are provided in the Supplementary Information.
+
+In order to separate any general practice effects from the effect of the intervention, we added a control condition in which participants  were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
+They provided their answers in a free-form text box.
+The time given to solve the anagrams was the same as that given to respond to questions in the intervention manipulation.
+
+## Procedure
+
+At the start of the experiment, participants provided informed consent and were instructed the study would consist of three phases in which they would face a different other player.
+Participants were told their goal was to maximise the number of points in all phases.
+They were not told the number of rounds of each phase.
+Phase one was a 15 round Repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
+On each round, after being informed about the amount sent by the investor, participants were asked to evaluate their emotion (intervention condition) or the investment (control condition).
+Participants then decided on how much of the tripled investment to return to the investor, before continuing to the next round.
+After completing 15 rounds of the RTG, participants rated how cooperative, selfish, trustworthy and friendly they perceived the investor to be (all on a scale from 1 to 10).
+After phase one, participants in the intervention condition completed the intervention, and participants in the control condition solved anagrams.
+Subsequent phase two was similar to phase one, with participants being told they would face a new player.
+Phase three consisted of 7 rounds of the Repeated Prisoner's Dilemma game (RPD), with participants informed they would face a third player.
+Participants then completed questionnaires related to mentalising abilities, emotion regulation, and BPD traits (see the supplement for details).
+They were then asked about the strategy in the games, as well as whether they thought the other players were human or computer agents.
+They were then debriefed and thanked for their participation.
+
 \begin{landscape}
@@
 \end{landscape}
-
-In this game, the computerised agent was programmed to act according to a tit-for-tat strategy [@axelrod_evolution_1981], starting with a cooperative action and then mirroring what the other player chose in the preceding round.
-On round 4, the computerised agent was pre-programmed to choose the defect action, regardless of the participant's preceding action.
-
-## Intervention
-
-The intervention was built on Dialectical Behavior Therapy (DBT) skills training, asking patients to reflect on the consequences of actions taken in emotional states [@linehan_dbt_2015].
-Specifically, participants were presented with a hypothetical situation in which they receive a low investment and asked to indicate how they would respond.
-They were then presented with an educational slide inviting them to consider that the ultimate aim in the game is to maximise their total reward and to reflect on whether punishing the investor for the low investment is beneficial to achieving that aim.
-Participants were told that punishment can create a negative feedback loop where the other player might trust them even less.
-An alternative action was suggested, whereby players would respond kindly to such a transgression in the hope of gaining trust from the investor.
-Participants were then asked whether the information just received would change their behavior in such a hypothetical situation and to justify their answer.
-Full details on the intervention are provided in the Supplementary Information.
-
-In order to separate any general practice effects from the effect of the intervention, we added a control condition in which participants  were asked to solve five anagrams ("listen", "triangle", "deductions", "players", "care").
-They provided their answers in a free-form text box.
-The time given to solve the anagrams was the same as that given to respond to questions in the intervention manipulation.
-
-## Procedure
-
-At the start of the experiment, participants provided informed consent and were instructed the study would consist of three phases in which they would face a different other player.
-Participants were told their goal was to maximise the number of points in all phases.
-They were not told the number of rounds of each phase.
-Phase one was a 15 round Repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
-On each round, after being informed about the amount sent by the investor, participants were asked to evaluate their emotion (intervention condition) or the investment (control condition).
-Participants then decided on how much of the tripled investment to return to the investor, before continuing to the next round.
-After completing 15 rounds of the RTG, participants rated how cooperative, selfish, trustworthy and friendly they perceived the investor to be (all on a scale from 1 to 10).
-After phase one, participants in the intervention condition completed the intervention, and participants in the control condition solved anagrams.
-Subsequent phase two was similar to phase one, with participants being told they would face a new player.
-Phase three consisted of 7 rounds of the Repeated Prisoner's Dilemma game (RPD), with participants informed they would face a third player.
-Participants then completed questionnaires related to mentalising abilities, emotion regulation, and BPD traits (see the supplement for details).
-They were then asked about the strategy in the games, as well as whether they thought the other players were human or computer agents.
-They were then debriefed and thanked for their participation.
 
@@
 
-prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
-
-cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
+#prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
+#cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
 ```
@@
 effectsize::eta_squared(mod_returns_pct)
+
+# Subset the data for pre and post measurements
+pre_data <- avg_ret_df$ret_pct[avg_ret_df$gameNum.f == 'pre']
+post_data <- avg_ret_df$ret_pct[avg_ret_df$gameNum.f == 'post']
+
+# Calculate the correlation
+correlation <- cor(pre_data, post_data, use = "complete.obs")
+
+# Print the result
+print(correlation)
 
@@
 Instead, it countered the tendency shown by participants in the control condition to lower returns after the defection in the second game compared to the first game.
-
-\newpage
-\begin{landscape}
-```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
-We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
-B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
-The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
-The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
-Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
-Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
-library(magick)
-
-# Read in the images
-image5 <- image_read("figures/resultsTrust.png")
-image6 <- image_read("figures/emotionReaction2.png")
-violin_ret <- image_read("figures/violin_ret.png")
-violin_inv <- image_read("figures/violin_inv.png")
-
-image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
-violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
-violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
-
-# Assuming a 300 DPI resolution for good print quality
-dpi <- 300
-
-# Spacing of 0.1 inches converted to pixels
-spacing <- 0.05 * dpi
-
-# Calculating the width and height for each image
-width_per_image <- ((12 - 0.1) / 2) * dpi
-height_per_image <- ((7.4 - 0.1) / 2) * dpi
-# The geometry string for each image, including spacing (assuming no borders)
-geometry_string <- paste0(width_per_image, 'x', height_per_image, '+', spacing, '+', spacing)
-
-# Now create the montage with the specified geometry
-combined_image2 <- image_montage(
-  c(image5, image6, violin_ret, violin_inv), 
-  tile = "2x2",
-  geometry = geometry_string
-)
-
-# Display the combined image
-plot(combined_image2)
-```
-\end{landscape}
-\newpage
 
@@
 
+\newpage
+\begin{landscape}
+```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
+B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
+The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
+The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
+Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
+Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+library(magick)
+
+# Read in the images
+image5 <- image_read("figures/resultsTrust.png")
+image6 <- image_read("figures/emotionReaction2.png")
+violin_ret <- image_read("figures/violin_ret.png")
+violin_inv <- image_read("figures/violin_inv.png")
+
+image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
+violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
+violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
+
+# Assuming a 300 DPI resolution for good print quality
+dpi <- 300
+
+# Spacing of 0.1 inches converted to pixels
+spacing <- 0.05 * dpi
+
+# Calculating the width and height for each image
+width_per_image <- ((12 - 0.1) / 2) * dpi
+height_per_image <- ((7.4 - 0.1) / 2) * dpi
+# The geometry string for each image, including spacing (assuming no borders)
+geometry_string <- paste0(width_per_image, 'x', height_per_image, '+', spacing, '+', spacing)
+
+# Now create the montage with the specified geometry
+combined_image2 <- image_montage(
+  c(image5, image6, violin_ret, violin_inv), 
+  tile = "2x2",
+  geometry = geometry_string
+)
+
+# Display the combined image
+plot(combined_image2)
+```
+\end{landscape}
+\newpage
+
 ## Evaluation of the investor
@@
 
+```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
+The latent states are ordered by the mean of the discretized Gaussian representing the policy in that state, so higher numbered states can be considered more pro-social.
+B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
+The distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure is visibly more weighted towards higher return states.
+As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
+library(magick)
+
+# Read in the images
+image7 <- image_read("figures/trusteeHMMPlot.png")
+image8 <- image_read("figures/postHMM.png")
+
+image7 <- image_annotate(image7, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image8 <- image_annotate(image8, text = "B", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+
+# Combine image2 and image3 side-by-side
+final_image <- c(image7, image8) %>% magick::image_append(stack = TRUE)
+
+# Display the combined image
+plot(final_image)
+```
+
 <!--    ORDER THE STATES    -->
@@
 Participants were often uncertain whether they interacted with human or artificial investors, highlighting the agents’ realism.
-
-\newpage
-```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
-The latent states are ordered by the mean of the discretized Gaussian representing the policy in that state, so higher numbered states can be considered more pro-social.
-B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
-The distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure is visibly more weighted towards higher return states.
-As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
-library(magick)
-
-# Read in the images
-image7 <- image_read("figures/trusteeHMMPlot.png")
-image8 <- image_read("figures/postHMM.png")
-
-image7 <- image_annotate(image7, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-image8 <- image_annotate(image8, text = "B", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-
-# Combine image2 and image3 side-by-side
-final_image <- c(image7, image8) %>% magick::image_append(stack = TRUE)
-
-# Display the combined image
-plot(final_image)
-```
-\newpage
 

### 2024-01-29 article.Rmd
changed transparency statement

@@
 
-## Disclosures {.unnumbered}
+## Research Transparency Statement {.unnumbered}
+
+### General Disclosures {.unnumbered}
 
@@
 Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
-Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available on: https://github.com/ismailg/coax_psych_science.
-The design and analysis plans were not preregistered.
+Reproducibility: [The authors are applying for a Computational Reproducibility Badge which will be awarded pending checks by the STAR Team.]
+
+### Study Disclosures {.unnumbered}
+
+Preregistration: The hypotheses and methods were not preregistered.The analysis plan was not preregistered.
+Materials: All study materials are publicly available (https://github.com/ismailg/coax_psych_science).
+Data: All primary data are publicly available (https://github.com/ismailg/coax_psych_science).
+Analysis scripts: All analysis scripts are publicly available (https://github.com/ismailg/coax_psych_science).
 
@@
 
+## Statistical analysis
+
+To explore whether participants behaved differently in the RTG after the intervention compared to the control group, we model the percentage return (percentage of tripled investment returned to investor) using a linear mixed-effects model as described below:
+
+\[
+\begin{split}
+R_{ij} = & \beta_0 + \beta_1 \text{ (Condition)}_i + \beta_2 \text{ (Game)}_i + \beta_3 \text{ (Investment)}_i + \\
+& \beta_4 \text{ (Condition × Game)}_i + \beta_5 \text{ (Condition × Investment)}_i + \beta_6 \text{ (Game × Investment)}_i +  \\ 
+& \beta_7 \text{ (Condition × Game × Investment)}_i +b_{0j} + b_{1j} \text{ (Game)}_i + \epsilon_{ij}
+\end{split}
+\]
+
+where:
+
+- \( R_{ij} \): percentage of tripled investment returned to investor for participant \( j \) in observation \( i \)
+- \( \beta_0 \): intercept
+- \( \beta_1 \): effect of Condition (intervention vs. control)
+- \( \beta_2 \): effect of Game (RTG game pre vs. post-intervention)
+- \( \beta_3 \): effect of Investment
+- \( \beta_4 \): interaction effect between Condition and Game
+- \( \beta_5 \): interaction effect between Condition and Investment
+- \( \beta_6 \): interaction effect between Game and Investment
+- \( \beta_7 \): three-way interaction effect between Condition, Game and Investment
+- \( b_{0j} \): participant-wise random intercept for participant \( j \)
+- \( b_{1j} \): participant-wise random slope for Game for participant \( j \)
+- \( \epsilon_{ij} \): error term for participant \( j \) in observation \( i \)
+
+The model was estimated using the `afex` package [@singmann_afex_2022] in R [@R_package].
+More complex models with additional random effects could not be estimated reliably, and as such the estimated model can be considered to include the optimal random effects structure [@matuschek2017balancing].
+A similar process was used to establish the random effects structures of other linear mixed-effects models used throughout the statistical analyses.
+For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
+We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
+
+To model participants' returns in the RTG across games and conditions, we fit various hidden Markov models [@visser2022hidden] to participants' returns using the depmixS4 package [@visser_depmixs4_2021] for R.
+The transition between latent states is assumed to depend on the investment received and a dummy variable to characterise the group that the participant belongs to.
+Details on how the models are constructed can be found in the supplement.
+We fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978-1] to select the best model.
+
 \begin{landscape}
@@
 \end{landscape}
-
-## Statistical analysis
-
-To explore whether participants behaved differently in the RTG after the intervention compared to the control group, we model the percentage return (percentage of tripled investment returned to investor) using a linear mixed-effects model as described below:
-
-\[
-\begin{split}
-R_{ij} = & \beta_0 + \beta_1 \text{ (Condition)}_i + \beta_2 \text{ (Game)}_i + \beta_3 \text{ (Investment)}_i + \\
-& \beta_4 \text{ (Condition × Game)}_i + \beta_5 \text{ (Condition × Investment)}_i + \beta_6 \text{ (Game × Investment)}_i +  \\ 
-& \beta_7 \text{ (Condition × Game × Investment)}_i +b_{0j} + b_{1j} \text{ (Game)}_i + \epsilon_{ij}
-\end{split}
-\]
-
-where:
-
-- \( R_{ij} \): percentage of tripled investment returned to investor for participant \( j \) in observation \( i \)
-- \( \beta_0 \): intercept
-- \( \beta_1 \): effect of Condition (intervention vs. control)
-- \( \beta_2 \): effect of Game (RTG game pre vs. post-intervention)
-- \( \beta_3 \): effect of Investment
-- \( \beta_4 \): interaction effect between Condition and Game
-- \( \beta_5 \): interaction effect between Condition and Investment
-- \( \beta_6 \): interaction effect between Game and Investment
-- \( \beta_7 \): three-way interaction effect between Condition, Game and Investment
-- \( b_{0j} \): participant-wise random intercept for participant \( j \)
-- \( b_{1j} \): participant-wise random slope for Game for participant \( j \)
-- \( \epsilon_{ij} \): error term for participant \( j \) in observation \( i \)
-
-The model was estimated using the `afex` package [@singmann_afex_2022] in R [@R_package].
-More complex models with additional random effects could not be estimated reliably, and as such the estimated model can be considered to include the optimal random effects structure [@matuschek2017balancing].
-A similar process was used to establish the random effects structures of other linear mixed-effects models used throughout the statistical analyses.
-For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
-We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
-
-To model participants' returns in the RTG across games and conditions, we fit various hidden Markov models [@visser2022hidden] to participants' returns using the depmixS4 package [@visser_depmixs4_2021] for R.
-The transition between latent states is assumed to depend on the investment received and a dummy variable to characterise the group that the participant belongs to.
-Details on how the models are constructed can be found in the supplement.
-We fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978-1] to select the best model.
 
@@
 
+<!-- Linear mixed effects model for all returns  -->
 ```{r modAllReturns, include=FALSE, cache=TRUE}
@@
 
-#prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
-#cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
-```
-
+```
+
+```{r modemmeans, include=F, cache=TRUE }
+prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
+cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
+```
+
+<!-- Secondary analyses for effect size and correlation between repeated measures.  -->
 ```{r, include=F}
@@
 
+<!-- Linear mixed effects model for Investments -->
 ```{r modInvs, include=FALSE, cache=TRUE}
@@
 
+<!-- Linear fixed effects model for returns: ALL ROUNDS BEFORE DEFECTION TRIAL -->
 ```{r, include=FALSE, cache=TRUE}
-# ALL ROUNDS BEFORE DEFECTION TRIAL
+
 pre_int_data <- avg_ret_df %>% filter(roundType=="trust",!is.na(gameNum.f),(roundNum < 12 & gameNum.f =="pre")| (roundNum < 13 & gameNum.f =="post"))
@@
 
+<!-- Linear fixed effects model for returns: ALL ROUNDS AFTER DEFECTION TRIAL -->
 ```{r, include=FALSE, cache=TRUE}
@@
 datCoax$roundGroup <- ifelse(datCoax$roundNum <= 10, "Rounds 1-10", "Rounds 11-15")
-
-# # Define the vertical line data
-# vline_data <- data.frame(
-#   xintercept = c(12, 13),
-#   linetype = c("Pre-manipulation", "Post-manipulation"),  # Names corresponding to the existing scale
-#   roundGroup = c("Rounds 11-15", "Rounds 11-15")
-# )
 
@@
 
-# afex_plot(mod_emo_x, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
-#             data_geom = geom_violin, 
-#             data_arg = list(width = 0.5))
-#
-
-# library(GGally)
-# ggpairs(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,inv_scaled))
-
 cor(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,investment))
@@
 
-\newpage
-\begin{landscape}
-```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
-We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
-B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
-The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
-The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
-Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
-Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
-library(magick)
-
-# Read in the images
-image5 <- image_read("figures/resultsTrust.png")
-image6 <- image_read("figures/emotionReaction2.png")
-violin_ret <- image_read("figures/violin_ret.png")
-violin_inv <- image_read("figures/violin_inv.png")
-
-image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
-violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
-violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
-
-# Assuming a 300 DPI resolution for good print quality
-dpi <- 300
-
-# Spacing of 0.1 inches converted to pixels
-spacing <- 0.05 * dpi
-
-# Calculating the width and height for each image
-width_per_image <- ((12 - 0.1) / 2) * dpi
-height_per_image <- ((7.4 - 0.1) / 2) * dpi
-# The geometry string for each image, including spacing (assuming no borders)
-geometry_string <- paste0(width_per_image, 'x', height_per_image, '+', spacing, '+', spacing)
-
-# Now create the montage with the specified geometry
-combined_image2 <- image_montage(
-  c(image5, image6, violin_ret, violin_inv), 
-  tile = "2x2",
-  geometry = geometry_string
-)
-
-# Display the combined image
-plot(combined_image2)
-```
-\end{landscape}
-\newpage
-
 ## Evaluation of the investor
@@
 
+\newpage
+\begin{landscape}
+```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
+B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
+The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
+The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
+Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
+Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+library(magick)
+
+# Read in the images
+image5 <- image_read("figures/resultsTrust.png")
+image6 <- image_read("figures/emotionReaction2.png")
+violin_ret <- image_read("figures/violin_ret.png")
+violin_inv <- image_read("figures/violin_inv.png")
+
+image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
+violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
+violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
+
+# Assuming a 300 DPI resolution for good print quality
+dpi <- 300
+
+# Spacing of 0.1 inches converted to pixels
+spacing <- 0.05 * dpi
+
+# Calculating the width and height for each image
+width_per_image <- ((12 - 0.1) / 2) * dpi
+height_per_image <- ((7.4 - 0.1) / 2) * dpi
+# The geometry string for each image, including spacing (assuming no borders)
+geometry_string <- paste0(width_per_image, 'x', height_per_image, '+', spacing, '+', spacing)
+
+# Now create the montage with the specified geometry
+combined_image2 <- image_montage(
+  c(image5, image6, violin_ret, violin_inv), 
+  tile = "2x2",
+  geometry = geometry_string
+)
+
+# Display the combined image
+plot(combined_image2)
+```
+\end{landscape}
+\newpage
+
 ```{r, include=FALSE}
@@
 
-```{r, include=FALSE}
-# Install the 'psych' package
-if (!requireNamespace("psych", quietly = TRUE)) {
-  install.packages("psych")
-}
-
-# Load the 'psych' package
-library(psych)
-
-questionnaires <- avg_ret_df %>% group_by(playerId) %>% dplyr::select(PBOR_score,DERS_score,RFQ_c) %>% unique() %>% ungroup()
-# Perform EFA
-efa_result <- fa(questionnaires %>% dplyr::select(PBOR_score,DERS_score,RFQ_c), nfactors = 2, fm = "minres", rotate = "varimax")
-# Print the EFA result
-print(efa_result)
-
-```
-
+<!-- Analyse participants response to Turing test -->
 ```{r, include=FALSE}
@@
 
+<!-- Here we extend the depmixS4 package functionality for analyzing data using hidden Markov models (HMMs). It involves defining new response classes and their associated methods. -->
+
 ```{r,include=F}
@@
 for(i in n_state_min:n_state_max) {
-
-  # rModels <- rep(list(list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment))),each=i)
-
   ###########################################################

### 2024-04-19 article.Rmd
ready for submission

@@
 title: "(Re)building cooperation: Effects of a cognitive intervention on cooperative behavior in games"
-# author:
-#   "Ismail Guennouni^1^, Samuel Dupret^1^, Quentin JM Huys^2^, Maarten Speekenbrink^1^"
+author:
+  "Ismail Guennouni^1^*, Samuel Dupret^1^, Quentin JM Huys^2^, Maarten Speekenbrink^1^"
 
@@
 
-bibliography: "bib/cogIntervention.bib"
-biblio-style: spphys
-
 output:
@@
   - \usepackage{lscape}
+  # - \usepackage{natbib}
+
+bibliography: "bib/cogIntervention.bib"
+csl: nature-no-superscript.csl
+
 ---
-<!-- \small   -->
-<!-- ^1^ *Department of Experimental Psychology, Division of Psychology and Language Sciences, UCL*.   -->
-<!-- ^2^ *Division of Psychiatry and Max Planck Centre for Computational Psychiatry and Ageing Research, Queen Square Institute of Neurology, UCL.* -->
+\small
+^1^ *Department of Experimental Psychology, Division of Psychology and Language Sciences, UCL*
+
+^2^ *Division of Psychiatry and Max Planck Centre for Computational Psychiatry and Ageing Research, Queen Square Institute of Neurology, UCL.*
+
+^\*^ *Email: ismail.guennouni@zi-mannheim.de*
 
@@
 
-## Research Transparency Statement {.unnumbered}
-
-### General Disclosures {.unnumbered}
-
-Conflicts of interest: The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
-Funding: Author 1 was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1.
-Author 3 acknowledges support by the UCLH NIHR BRC.
-He has received fees and options for consultancies for Aya Technologies and Alto Neuroscience.
-Ethics: This research received approval from a local ethics board (ID:21029/001).
-Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
-Reproducibility: [The authors are applying for a Computational Reproducibility Badge which will be awarded pending checks by the STAR Team.]
-
-### Study Disclosures {.unnumbered}
-
-Preregistration: The hypotheses and methods were not preregistered.The analysis plan was not preregistered.
-Materials: All study materials are publicly available (https://github.com/ismailg/coax_psych_science).
-Data: All primary data are publicly available (https://github.com/ismailg/coax_psych_science).
-Analysis scripts: All analysis scripts are publicly available (https://github.com/ismailg/coax_psych_science).
-
-<!-- Author Contribution: I.
-Guennouni, QJM.
-Huys and M.
-Speekenbrink designed and developed the study concept.
-Experiment design was done by S.
-Dupret and I.
-Guennouni.
-Testing and data collection were performed by I.
-Guennouni.
-I.
-Guennouni analysed and interpreted the data under the supervision of QJM.
-Huys and M.
-Speekenbrink.
-M.
-Speekenbrink and I.
-Guennouni jointly performed the HMM modelling.
-All authors jointly wrote and approved the final version of the manuscript for submission.
--->
-
-# Introduction
+# Introduction {.unnumbered}
 
@@
 
-# Method
-
-## Participants
+# Methods {.unnumbered}
+
+## Participants  {.unnumbered}
 
@@
 
-## Design and Procedure
+## Design and Procedure {.unnumbered}
 
@@
 The games were designed and implemented online using Empirica [@almaatouq2021empirica].
+This research received approval from a UCL ethics board (ID:21029/001) and the experiment was performed in accordance with the ethics board guidelines and regulations.
 
@@
 
-## Tasks and Measures
-
-### Repeated Trust Game
+## Tasks and Measures {.unnumbered}
+
+### Repeated Trust Game {.unnumbered}
 
@@
 If the trustee returns more than one third of the amount, the investor makes a gain.
-Each player was represented with an icon with the participant always on the left of the screen and the co-player on the right (Figure \ref{fig:HMMPanels}.A).
+Each player was represented with an icon with the participant always on the left of the screen and the co-player on the right (Figure \ref{fig:HMMPanels}.a).
 The participants were able to choose the icon that represents them at the start of the experiment.
@@
 Using this data, we estimated a hidden Markov model (HMM) on investors' behavior with three latent states.
-Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.C).
+Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.c).
 These distributions reflect "low-trust", "medium-trust", or "high-trust".
-Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of their net return (i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.D).
+Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of their net return (i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.d).
 In order to instigate a potential breakdown of trust, thereby allowing us to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 (pre-intervention) or round 13 (post-intervention).
@@
 Participants in the control condition were asked to evaluate the investment in terms of speed (from slow to fast) and magnitude (from low to high).
-These evaluations were made by clicking on a two-dimensional field with labelled axes as shown in Figure \ref{fig:HMMPanels}.C for the intervention condition.
-
-### Repeated Prisoner's Dilemma
+These evaluations were made by clicking on a two-dimensional field with labelled axes as shown in Figure \ref{fig:HMMPanels}.c for the intervention condition.
+
+### Repeated Prisoner's Dilemma {.unnumbered}
 
@@
 
-## Intervention
+## Intervention {.unnumbered}
 
@@
 
-## Procedure
+## Procedure {.unnumbered}
 
@@
 
-## Statistical analysis
+## Statistical analysis {.unnumbered}
 
@@
 A similar process was used to establish the random effects structures of other linear mixed-effects models used throughout the statistical analyses.
+There is no agreed upon way to calculate effect sizes for mixed effects models, as such we will report instead on testing differences in marginal means.
 For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
+Unless otherwise stated, the default adjustment method for multiple comparison is Tukey's HSD.
 We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
@@
 \begin{landscape}
-```{r HMMPanels, fig.cap= "\\small{A: Screenshot of the repeated Trust Game.
+```{r HMMPanels, fig.cap= "\\small{a: Screenshot of the repeated Trust Game.
 The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee.
@@
 Shown here is the stage at which the trustee decides how much to send back to the investor.
-Immediately before making this decision, participant are shown a two dimensional grid (Panel C) where they need to report their reaction to the investment.
+Immediately before making this decision, participant are shown a two dimensional grid (Panel c) where they need to report their reaction to the investment.
 Those in the intervention condition were asked questions about their emotional state and those in the control condition were asked to report features of the investment unrelated to their emotion.
-Panels B - D: We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
-From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel C.
-The fitted HMM also yields the transition probability of the agent to a state on trial t+1 as a function of the net return (difference between the investment sent and the amount received in return) on trial t as shown in Panel D.
-Each plot in Panel D represents a different starting latent state on trial t, and each line represents the probability of transitioning to a particular state in trial t+1.}",echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+Panels b - d: We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
+From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel c.
+The fitted HMM also yields the transition probability of the agent to a state on trial t+1 as a function of the net return (difference between the investment sent and the amount received in return) on trial t as shown in Panel d.
+Each plot in Panel d represents a different starting latent state on trial t, and each line represents the probability of transitioning to a particular state in trial t+1.}",echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
 
@@
 # Annotate each image with a label
-image1 <- image_annotate(image1, text = "A", location = "+200+10", size = 90, color = "black", gravity = "northwest")
-image2 <- image_annotate(image2, text = "B", location = "+0+10", size = 90, color = "black", gravity = "northwest")
-image3 <- image_annotate(image3, text = "C", location = "-0+10", size = 90, color = "black", gravity = "northwest")
-image4 <- image_annotate(image4, text = "D", location = "+0+10", size = 90, color = "black", gravity = "northwest")
+image1 <- image_annotate(image1, text = "a", location = "+200+10", size = 90, color = "black", gravity = "northwest")
+image2 <- image_annotate(image2, text = "b", location = "+0+10", size = 90, color = "black", gravity = "northwest")
+image3 <- image_annotate(image3, text = "c", location = "-0+10", size = 90, color = "black", gravity = "northwest")
+image4 <- image_annotate(image4, text = "d", location = "+0+10", size = 90, color = "black", gravity = "northwest")
 
@@
 
-# Behavioral results
+# Behavioral results {.unnumbered}
 
@@
 
-mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| playerId), avg_ret_df, REML= TRUE, method="KR")
+# mod_returns_pct <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| playerId), avg_ret_df, REML= TRUE, method="KR")
+# save(mod_returns_pct, file = "data/mod_returns_pct.RData")
+
+```
+
+```{r, include=FALSE}
+
+load("data/mod_returns_pct.RData")
 anova(mod_returns_pct)
 summary(mod_returns_pct)
-
-```
-
-```{r modemmeans, include=F, cache=TRUE }
-prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
-cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
-```
-
-<!-- Secondary analyses for effect size and correlation between repeated measures.  -->
-```{r, include=F}
-
 library(sjstats)
@@
 
-# Subset the data for pre and post measurements
-pre_data <- avg_ret_df$ret_pct[avg_ret_df$gameNum.f == 'pre']
-post_data <- avg_ret_df$ret_pct[avg_ret_df$gameNum.f == 'post']
-
-# Calculate the correlation
-correlation <- cor(pre_data, post_data, use = "complete.obs")
-
-# Print the result
-print(correlation)
-
-```
-
+```
+
+```{r modemmeans, include=F, cache=TRUE }
+# prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
+# save(prepost_bycond, file="data/prepost_bycond.RData")
+#cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
+```
+
+```{r}
+load("data/prepost_bycond.RData")
+```
+
+<!-- VIOLIN PLOTS OF ALL RETURNS MODEL -->
 ```{r, include=F}
@@
 
-Average investments and returns prior to the "defection round" (Figure \ref{fig:TrustGameResults}.A) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
-Mixed-effects analysis on the percentage returns shows a significant main effect of Condition (intervention vs.
-control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f`, with higher percentage returns in the intervention compared to the control condition.
-Importantly, we also find an interaction between Condition and Game (RTG pre- vs.
-post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f`.
-Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:TrustGameResults}.C).
+Average investments and returns prior to the "defection round" (Figure \ref{fig:TrustGameResults}.a) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
+Mixed-effects analysis on the percentage returns shows a significant main effect of Condition (intervention vs. control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f`, 
+<!-- with an effect size (partial eta-squared) of $\eta_p^2$ = `r round(effectsize::eta_squared(mod_returns_pct)$Eta2_partial[2],2)`, -->
+due to overall higher percentage returns in the intervention compared to the control condition.
+Importantly, we also find an interaction between Condition and Game (RTG pre- vs. post-intervention), `r papaja::apa_print(mod_returns_pct)$full_result$gameNum_f_condition_f`. 
+<!-- with an effect size of $\eta_p^2$ = `r round(effectsize::eta_squared(mod_returns_pct)$Eta2_partial[4],2)` -->
+Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:TrustGameResults}.c).
 This indicates the intervention was effective in increasing cooperative behavior.
+
 There was also a significant main effect of Investment, 
 `r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_returns_pct)$full_result$inv_scaled)`, 
+<!-- $\eta_p^2$ = `r round(effectsize::eta_squared(mod_returns_pct)$Eta2_partial[3],2)`, -->
 such that higher investments were associated with higher percentage returns. An Investment by Condition interaction, 
@@
 This shows a main effect of Condition, `r papaja::apa_print(mod_invs)$full_result$condition_f`<!--$F(1,317) = 8.7$, $p = .003$-->, and Game, `r papaja::apa_print(mod_invs)$full_result$gameNum_f`<!--$F(1,317) = 8.3$, $p = .004$-->.
-As can be seen in Figure \ref{fig:TrustGameResults}.D, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
-
-<!-- Linear fixed effects model for returns: ALL ROUNDS BEFORE DEFECTION TRIAL -->
-```{r, include=FALSE, cache=TRUE}
+As can be seen in Figure \ref{fig:TrustGameResults}.d, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
+
+<!-- Linear fixed effects model for returns: ROUNDS BEFORE DEFECTION TRIAL -->
+```{r preDefMod, include=FALSE, cache=TRUE}
 
@@
 
-mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| playerId), pre_int_data, REML= TRUE, method="KR")
-anova(mod_returns_pre)
-summary(mod_returns_pre)
-saveRDS(mod_returns_pre, "data/mod_returns_pre")
-
-pairs_pre_int <- pairs(emmeans::emmeans(mod_returns_pre, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400, reverse=TRUE))
-saveRDS(pairs_pre_int, "data/pairs_pre_int")
-
+# mod_returns_pre <- mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| playerId), pre_int_data, REML= TRUE, method="KR")
+# anova(mod_returns_pre)
+# summary(mod_returns_pre)
+# save(mod_returns_pre, file="data/mod_returns_pre.RData")
+# 
+# pairs_pre_int <- pairs(emmeans::emmeans(mod_returns_pre, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400, reverse=TRUE))
+# save(pairs_pre_int, file="data/pairs_pre_int.RData")
+
+```
+
+```{r loadPreDefMod, include=F}
+load("data/mod_returns_pre.RData")
+load("data/pairs_pre_int.RData")
 ```
@@
 
-mod_postcoax_trust <- mixed(ret_pct ~ gameNum.f*condition.f*inv_scaled  + ( 1 + gameNum.f|playerId), post_coax_data)
-anova(mod_postcoax_trust)
-
-postcoax_bygame <- emmeans::emmeans(mod_postcoax_trust, ~gameNum.f, pbkrtest.limit = 9400)
-postcoax_bycond <- emmeans::emmeans(mod_postcoax_trust, ~condition.f, pbkrtest.limit = 9400)
-
-postcoax_interaction <- emmeans::emmeans(mod_postcoax_trust, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400)
-postcoax_interaction
-
-pairs(emmeans::emmeans(mod_postcoax_trust, c("gameNum.f"), by = "condition.f"))
+# mod_postcoax_trust <- mixed(ret_pct ~ gameNum.f*condition.f*inv_scaled  + ( 1 + gameNum.f|playerId), post_coax_data)
+# anova(mod_postcoax_trust)
+# save(mod_postcoax_trust, file="data/mod_postcoax_trust.RData")
+# 
+# 
+# postcoax_interaction <- emmeans::emmeans(mod_postcoax_trust, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400)
+# save(postcoax_interaction, file="data/postcoax_interaction.RData")
+
 ```
@@
 ```{r, include=F}
-saveRDS(summary(mod_postcoax_trust), "data/mod_returns_post")
+load("data/mod_postcoax_trust.RData")
+load("data/postcoax_interaction.RData")
 ```
@@
 
-## Emotion self-reports
+## Emotion self-reports {.unnumbered}
 
@@
 `r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment)`. 
-This indicates that participants in the intervention condition returned higher amounts post-intervention, despite their emotional reaction to investments remaining largely the same (Figure \ref{fig:TrustGameResults}.B).
-
-## Evaluation of the investor
+This indicates that participants in the intervention condition returned higher amounts post-intervention, despite their emotional reaction to investments remaining largely the same (Figure \ref{fig:TrustGameResults}.b).
+
+## Evaluation of the investor {.unnumbered}
 
@@
 
-## Transfer to the Repeated Prisoner's Dilemma game
+## Transfer to the Repeated Prisoner's Dilemma game {.unnumbered}
 
@@
 \begin{landscape}
-```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+```{r TrustGameResults, fig.cap="\\small{Panel a: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
 We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
-B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
+b:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
 The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
 The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
-Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
-Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+Panel c shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
+Investments by the HMM agent (Panel d) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
 library(magick)
@@
 
-image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
-violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
-violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
+image5 <- image_annotate(image5, text = "a", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image6 <- image_annotate(image6, text = "b", location = "+20+0", size = 90, color = "black", gravity = "northwest")
+violin_ret<- image_annotate(violin_ret, text = "c", location = "+0+20", size = 70, color = "black", gravity = "northwest")
+violin_inv  <- image_annotate(violin_inv , text = "d", location = "+0+0", size = 70, color = "black", gravity = "northwest")
 
@@
 
-# HMM analysis of participant returns
+# HMM analysis of participant returns {.unnumbered}
 
@@
 As such, there is evidence that participants reacted differently to the investments in the four combinations of Condition and Game.
-The estimated state-dependent policy of trustee actions, according to the HMM-full model, is depicted in Figure \ref{fig:trusteeHMM}.A.
-
-```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
+The estimated state-dependent policy of trustee actions, according to the HMM-full model, is depicted in Figure \ref{fig:trusteeHMM}.a.
+
+```{r trusteeHMM, fig.cap="\\small{Panel a: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
 The latent states are ordered by the mean of the discretized Gaussian representing the policy in that state, so higher numbered states can be considered more pro-social.
-B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
+b: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
 The distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure is visibly more weighted towards higher return states.
-As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
+As in Panel a, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
 library(magick)
@@
 
-image7 <- image_annotate(image7, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-image8 <- image_annotate(image8, text = "B", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image7 <- image_annotate(image7, text = "a", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image8 <- image_annotate(image8, text = "b", location = "+20+20", size = 70, color = "black", gravity = "northwest")
 
@@
 The states are ordered by expected return, with state 1 having the lowest mean return and state 6 the highest.
-Figure \ref{fig:trusteeHMM}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition, both pre and post defection.
+Figure \ref{fig:trusteeHMM}.b shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition, both pre and post defection.
 For instance, in round 5, state 1 was the most likely posterior state for only $5$% of participants in the intervention condition compared to $12$% in the control condition ($\chi^2(1) = 4.73, p = 0.03$).
@@
 
-# Discussion
+# Discussion {.unnumbered}
 
@@
 
-# References
+# Author contributions statement {.unnumbered}
+I.
+Guennouni, QJM.
+Huys and M.
+Speekenbrink designed and developed the study concept.
+Experiment design was done by S.
+Dupret and I.
+Guennouni.
+Testing and data collection were performed by I.
+Guennouni.
+I.
+Guennouni analysed and interpreted the data under the supervision of QJM.
+Huys and M.
+Speekenbrink.
+M.
+Speekenbrink and I.
+Guennouni jointly performed the HMM modelling.
+All authors jointly wrote and approved the final version of the manuscript for submission.
+
+# Funding {.unnumbered}
+I.
+Guennouni was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1.
+QJM.
+Huys acknowledges support by the UCLH NIHR BRC.
+He has received fees and options for consultancies for Aya Technologies and Alto Neuroscience.
+
+# Competing interests statement {.unnumbered}
+The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
+
+# Additional information  {.unnumbered}
+
+## Correspondence {.unnumbered}
+
+All correspondence and requests for materials should be addressed to I. Guennouni.
+
+## Transparency and data availability {.unnumbered}
+
+Preregistration: The hypotheses and methods were not preregistered.The analysis plan was not preregistered.
+Materials: All study materials are publicly available (https://github.com/ismailg/CoaxIntervention).
+Data: All primary data are publicly available (https://github.com/ismailg/CoaxIntervention).
+Analysis scripts: All analysis scripts are publicly available (https://github.com/ismailg/CoaxIntervention).
+
+<!-- Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article. -->
+
+# References {.unnumbered}

### 2024-04-19 supplement.Rmd
ready for submission

@@
 bibliography: "bib/cogIntervention.bib"
-biblio-style: spphys
+# biblio-style: spphys
+csl: nature-no-superscript.csl
 
@@
 
+We fit the above linear mixed effects model to all trials prior to the pre-programmed defection by the HMM investor (occurring on round 12 pre-manipulation, and round 13 post).
+A summary of results can be seen in Figure \ref{fig:preDefectionModel}.
+
 ```{r, include=F}
@@
 
-```{r preDefectionModel,fig.cap = "Summary of results of a Mixed-effects model fitted to participants returns restricted to  pre-defection trials", fig.align='center'}
+```{r preDefectionModel, fig.cap = "Summary of results of a Mixed-effects model fitted to participants returns restricted to  pre-defection trials", fig.align='center'}
 
@@
 ```
+
+In the same way, we fit the linear mixed effects model to all post-defection trials by the HMM investor, including the round on which the defection occurs.
+A summary of results is presented in Figure \ref{fig:postDefectionModel}
 

### 2024-09-05 article.Rmd
version May24

@@
 Using this data, we estimated a hidden Markov model (HMM) on investors' behavior with three latent states.
-Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.c).
+Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.b).
 These distributions reflect "low-trust", "medium-trust", or "high-trust".
@@
 Panels b - d: We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
-From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel c.
+From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel b.
 The fitted HMM also yields the transition probability of the agent to a state on trial t+1 as a function of the net return (difference between the investment sent and the amount received in return) on trial t as shown in Panel d.

### 2024-09-07 article.Rmd
new draft version1

@@
 abstract: |
-  Social trust is a key component of strong social bonds.
-Its absence is a risk factor for social dysfunction and psychopathology.
-As such, interventions to foster and strengthen trust-based cooperation are highly desirable.
-We used the Repeated Trust Game to evaluate a cognitive intervention aiming to repair cooperation breakdowns caused by a one-time defection by the co-player.
-In this study, 318 participants played the role of trustee across two online games, believing they were facing two different players.
-Between games, some received a brief cognitive intervention.
-Post-intervention, participants showed more cooperative behavior both before and after defection by the co-player.
-Analysis using a hidden Markov model revealed that those in the intervention group had a higher proportion of cooperative states than participants in the control group.
-This is consistent with participants inferring from the intervention that pro-social behavior may generally provide more beneficial outcomes to them in the long run.
+  Cooperation, underpinned by trust, is crucial for social interactions yet fragile once broken.
+This study investigates the effectiveness of a brief cognitive intervention in promoting resilient cooperative behavior in economic games.
+Using a randomized controlled online experiment, we examined how 318 participants, acting as trustees in the Repeated Trust Game (RTG), responded to an intervention inspired by Dialectical Behavior Therapy.
+Participants played two 15-round RTGs against a novel computer-simulated investor using a hidden Markov model (HMM) trained on human data, enabling adaptive, human-like behavior while maintaining experimental control.
+The intervention significantly increased cooperative behavior, with participants showing more resilient cooperation even after experiencing low investments.
+HMM analysis revealed that the intervention increased the probability of participants occupying high-cooperation states.
+However, these effects did not transfer to a subsequent Repeated Prisoner's Dilemma game.
+Our findings demonstrate the potential of targeted cognitive interventions to enhance cooperative behavior, while showcasing the value of HMM-based agents in studying dynamic social interactions.
 
@@
 
-Cooperation refers to the collaborative efforts of individuals or entities working towards a shared goal or advantage [@tomasello2012two].
+<!-- Cooperation refers to the collaborative efforts of individuals or entities working towards a shared goal or advantage [@tomasello2012two].
 This coordinated approach often leads to outcomes that exceed the sum of individual contributions.
@@
 Research into the determinants of psychopathology has linked trust-based constructs to the emergence of mental health disorders [@fonagy_role_2014].
-
-A well-established paradigm in the study of trust is the Repeated Trust Game (RTG; @joyce_trust_1995).
+-->
+
+Cooperation, defined as individuals or entities working together towards a shared goal, plays a fundamental role in promoting collective success and social harmony [@tomasello_two_2012].
+At the heart of cooperation is trust—the belief that others will act in ways that are mutually beneficial, even when they have the opportunity to exploit the situation [@rousseau_introduction_1998].
+Trust enables individuals to engage in risky interactions where immediate self-interest could easily override long-term benefits [@balliet_trust_2013].
+Without trust, cooperation tends to break down, leading to suboptimal outcomes for all parties involved.
+Understanding how to maintain and repair cooperation following such breakdowns is therefore of significant interest to researchers and practitioners alike.
+
+<!-- A well-established paradigm in the study of trust is the Repeated Trust Game (RTG; @joyce_trust_1995).
 In this game, the "investor" decides how much of an endowment to send to the other player (the "trustee").
@@
 But if the investor obtains a low return on their investment, they will likely reduce future investments, thereby diminishing the potential gains for both players.
-
-Since a lack of epistemic trust is a risk factor for social dysfunction [@fonagy_mentalizing_2017], and given the importance of trust for building and maintaining strong social bonds, interventions that foster and strengthen trust-based cooperation would be highly beneficial to society.
+-->
+
+The Repeated Trust Game (RTG) has emerged as a well-established paradigm for studying trust and cooperation in controlled settings [@joyce_trust_1995].
+In this game, an "investor" decides how much of an endowment to send to a "trustee." The amount sent is typically multiplied by 3, and the trustee then decides how much of this multiplied amount to return to the investor.
+Cooperation emerges when both parties act in ways that promote mutual gains over multiple rounds.
+However, trust is fragile, and a single instance of defection—where one player fails to reciprocate appropriately—can lead to the breakdown of cooperation [@bendor_when_1991].
+Once trust is violated, it is often difficult to re-establish, even if doing so would be mutually beneficial [@harth_spiral_2017].
+
+Previous research has explored ways to encourage initial cooperation in trust games, such as using third-party enforcement [@charness_investment_2008; @fiedler_effect_2017], gratitude priming [@drazkowski_gratitude_2017], or with the concepts of friend and foe [@burnham_friend-or-foe_2000].
+While these approaches improve early cooperative behavior, they often fail to address the more challenging task of repairing cooperation after trust has been broken.
+Once defection occurs, individuals may react impulsively by reducing their own cooperative efforts, even if re-establishing trust would be mutually beneficial.
+Thus, interventions aimed at restoring cooperation in these contexts are crucial but understudied.
+
+<!-- Given the importance of trust for building and maintaining strong social bonds, interventions that foster and strengthen cooperation would be highly beneficial to society.
 Such interventions would allow people to more easily repair broken relationships and continue harvesting the benefits of cooperation even in the presence of accidental or intentional social norm violations.
-
-To encourage the emergence and maintenance of trust in the RTG setting, some studies have focused on modification of the game, e.g.
+Previous studies have attempted to restore cooperation in trust games through mechanisms such as third-party enforcement [@charness_investment_2008; @fiedler_effect_2017] or gratitude priming [@drazkowski_gratitude_2017].
+Whilst these results show that it is possible to improve cooperative outcomes at the start of the game, they do not address how to repair a breakdown of trust after intentional or accidental non-cooperative actions by the players.
+-->
+
+<!-- To encourage the emergence and maintenance of trust in the RTG setting, some studies have focused on modification of the game, e.g.
 through introducing a third-party who monitors the actions of the other players [@charness_investment_2008; @fiedler_effect_2017].
@@
 Further, computational analysis by @hula2018model links this issue to some BPD individuals' mentalizing difficulties, such as their inability to foresee the impact of their low returns on the investor's future actions.
-
-In devising interventions to repair trust in the RTG, we can take inspiration from cognitive interventions championed by successful therapies that aim to improve social dysfunction in BPD.
+-->
+
+In this study, we focus on the role of the trustee in the RTG, as a driver of cooperation dynamics.
+While the trustee does not exercise trust in the same way as the investor, their decisions to reciprocate (or not) play a critical role in maintaining or disrupting the cooperative relationship.
+A lack of reciprocation from trustees erodes trust over time [@servatka_words_2011] and is particularly evident when the trustee suffers from some personality disorders [@lieb_borderline_2004].
+These trustees fail to engage in trust-repairing behaviors such as coaxing the investor by signalling trustworthiness via sending high returns [@king-casas_rupture_2008].
+Additionally, unpredictable behavior from trustees fosters mistrust and impedes future cooperation [@rigdon_sustaining_2007].
+In contrast, consistent cooperation from trustees promotes trust and encourages further collaboration, as evidenced by neural data [@king-casas_getting_2005].
+Therefore, emphasizing the role of trustees in rebuilding cooperation is essential; when trustees demonstrate reliability and reciprocity, even after breaches of trust, cooperation can be restored and sustained.
+
+Given the pivotal role of trustees' behavior in shaping cooperative dynamics, it is worth exploring whether interventions aimed at improving interpersonal skills could positively influence their decision-making in the RTG.
+In the broader field of psychological therapies, cognitive interventions inspired by  Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] and Mentalisation Based Therapy [@allen_handbook_2006-1] have shown promise in enhancing social skills among individuals with interpersonal difficulties.
+These approaches often focus on helping individuals recognize the impact of their actions on others and consider alternative behavioral strategies.
+However, response to these treatments is highly variable, and determining which interventions are effective for particular sub-groups of patients is challenging [@rudge_mechanisms_2020; @arch_longitudinal_2012].
+One promising approach is the study of how specific components of psychotherapeutic treatment affect quantitative markers of behavior such as those inferred through computational models [@huys_computational_2016; @reiter_neuro-cognitive_2021; @dercon_core_2024].
+Combining the use of specific cognitive probes inspired by therapeutic interventions and computational models of behavior may allow us to uncover the cognitive mechanisms targeted by common forms of psychotherapy.
+In turn, this may provide the basis for choosing effective psychotherapeutic interventions for given individuals, potentially extending to improving trustee behavior and fostering cooperation in the RTG.
+
+<!-- In devising interventions to repair trust in the RTG, we can take inspiration from cognitive interventions championed by successful therapies that aim to improve social dysfunction in BPD.
 Psychotherapies such as Mentalisation Based Therapy [@allen_handbook_2006-1] and Dialectical Behavior Therapy [@linehan_cognitive-behavioral_1993] have been shown to improve social skills in BPD [@gunderson_borderline_2018].
@@
 In turn, this may provide the basis for choosing effective psychotherapeutic interventions for given individuals.
-
-In this study, using a randomised control trial design, we assess the effectiveness of a cognitive intervention aimed at repairing the potential breakdown of cooperation in the RTG from a low investment sent by a computerized investor.
-The intervention focuses on explaining the potential harm from reciprocating non-cooperative actions and suggesting a non-impulsive course of action to coax the investor back into cooperation.
-The computerized investor was programmed to play according to a hidden Markov model estimated from real players' data in prior research.
-A key aspect of this model is that the actions of the investor depend on a latent "trust state" which reacts dynamically to the trustees' returns simulating real-life trust-building scenarios.
-Such a model, informed by empirical data and integrating a responsive trust mechanism, represents a novel approach to study interactive behavior in multi-player games whilst keeping a high degree of experimental control.
+-->
+
+Drawing inspiration from such therapeutic approaches, we employ a randomized control trial to evaluate a cognitive intervention aimed at repairing cooperation after low investments from a computerized investor.
+The intervention in this study is a brief, multi-component cognitive intervention inspired by Dialectical Behavior Therapy (DBT) principles.
+It combines elements aimed at understanding long-term consequences of actions and promoting prosocial behavior.
+This approach mirrors real-world cognitive interventions that often employ multiple strategies to effect behavioral change [@linehan_dbt_2015].
+Specifically, we hypothesize that encouraging participants to reflect on the consequences of their actions and consider a non-impulsive course of action might lead to more resilient cooperative behavior, even in the face of perceived non-cooperation from their partner.
+
+We conducted an online experiment with 318 participants acting as trustees in two RTG rounds, with the intervention administered between rounds to a subset of participants.
+While previous studies have often relied on predetermined or simplistic computer strategies in economic games, our study introduces a novel approach using Hidden Markov Models (HMMs) to create more realistic, adaptive computer agents.
+A key aspect of these agents is that their actions depend on a latent “trust state” which reacts dynamically to the trustees’ returns, simulating real-life trust-building scenarios.
 To foreshadow our results, we find that the intervention led to more cooperative actions (higher returns) by the participants and countered a tendency to send back lower returns after a transgression from the investor.
@@
 
-A total of 318 participants were recruited on the Prolific Academic platform (prolific.co).
+A total of 320 participants were recruited on the Prolific Academic platform (prolific.co).
+Two players had incomplete trust game entries and their data was disregarded, leaving data for 318 participants for analysis, equally split between the two conditions.
+The required sample size was determined using an *a priori* power analysis to have an 80% probability to detect a small effect size (Cohen's f = 0.10) for a within-between interaction with a 5% type I error rate in a repeated measures ANOVA.
+The sample size calculation assumed 2 groups, 2 measurement per group and was performed using the G*Power software [@faul_statistical_2009].
 The mean age of participants was `r round(mean(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years, with a `r round(sd(as.numeric(d_finished$exitSurvey.age), na.rm=TRUE),1)` years standard deviation.
@@
 
-The experiment had a 2 (Condition: Intervention or Control) by 3 (Game: Trust-Game Pre Intervention, Trust-Game Post Intervention, Prisoner's Dilemma Post Intervention) design, with repeated measures on the second factor.
-Participants were randomly assigned to one of the two levels of the first factor.
-The games were designed and implemented online using Empirica [@almaatouq2021empirica].
+The experiment employed a 2 (Condition: Intervention or Control) by 2 (Game: Trust-Game Pre-Intervention, Trust-Game Post-Intervention) design, with repeated measures on the second factor.
+Participants were randomly assigned to either the intervention or control condition.
+Following the post-intervention Trust Game, all participants completed a Repeated Prisoner's Dilemma (RPD) game to assess potential transfer effects (See Figure \ref{fig:HMMPanels}.A for experiment overview).
+The games were designed and implemented online using Empirica [@almaatouq_empirica_2021-1].
 This research received approval from a UCL ethics board (ID:21029/001) and the experiment was performed in accordance with the ethics board guidelines and regulations.
@@
 
-Participants played a 15-round Repeated Trust Game [@joyce_trust_1995] in the trustee role against a computer-programmed investor.
+Participants played two separate 15-round Repeated Trust Games [@joyce_trust_1995] in the role of trustee.
+They were told (correctly) that each 15-round game was played against the same co-player, and that they will face a new player when they started a new 15-round game.
+Participants were led to believe they were interacting with human co-players when in fact they faced the same computerised investor in all trust games.
+This design allows us to examine the effects of our intervention while controlling for individual differences in play style, as well as minimizing the influence of reputational concerns or carry-over effects that might occur if participants believed they were facing the same partner twice.
+In each round of the RTG, the investor (computer-simulated) was endowed with 20 units and decided how much of that endowment to invest.
+This investment was tripled, and the participant, as the trustee, then decided how to split this tripled amount between themselves and the investor.
+If the trustee returns more than one third of the amount, the investor makes a gain.
+On each round, immediately after being informed of the investment sent, participants in the intervention condition were asked to provide an evaluation of their emotion in terms of valence (from negative to positive) and arousal (from low to high).
+Participants in the control condition were asked to evaluate the investment in terms of speed (from slow to fast) and magnitude (from low to high).
+These evaluations were made by clicking on a two-dimensional field with labelled axes as shown in Figure \ref{fig:HMMPanels}.C for the intervention condition.
+
+<!-- Participants played a 15-round Repeated Trust Game [@joyce_trust_1995] in the trustee role against a computer-programmed investor.
 On each round the investor is endowed with 20 units and decides how much of that endowment to invest.
@@
 If the trustee returns more than one third of the amount, the investor makes a gain.
-Each player was represented with an icon with the participant always on the left of the screen and the co-player on the right (Figure \ref{fig:HMMPanels}.a).
+Each player was represented with an icon with the participant always on the left of the screen and the co-player on the right (Figure \ref{fig:HMMPanels}.A).
 The participants were able to choose the icon that represents them at the start of the experiment.
@@
 Participants were not told they were facing computerised co-players.
-
-The strategy of the computerised investor was modelled on behavior of human investors in the Repeated Trust Game (RTG)  over 10-rounds with the same (human) co-player.
-Full detail on the datasets used in the Supplementary Information.
+-->
+
+### Adaptive Computerised Investor {.unnumbered}
+
+The strategy of the computerised investor was modelled on behavior of human investors in the Repeated Trust Game (RTG) over 10-rounds with the same (human) co-player from existing datasets.
+Full detail on the data sources used are in the Supplementary Information.
 Using this data, we estimated a hidden Markov model (HMM) on investors' behavior with three latent states.
-Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.b).
+Each latent state was associated with a state-conditional distribution over the possible investments from 0 to 20 (Figure \ref{fig:HMMPanels}.B).
 These distributions reflect "low-trust", "medium-trust", or "high-trust".
-Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of their net return (i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.d).
+Over rounds, the investor can move between states, and the probability of these transitions was modelled as a function of their net return (i.e return - investment) in the previous round (see Figure \ref{fig:HMMPanels}.D).
 In order to instigate a potential breakdown of trust, thereby allowing us to probe efforts to repair trust, the computerised agent was programmed to provide a low investment on round 12 (pre-intervention) or round 13 (post-intervention).
@@
 
-On each round, immediately after being informed of the investment sent, participants in the intervention condition were asked to provide an evaluation of their emotion in terms of valence (from negative to positive) and arousal (from low to high).
-Participants in the control condition were asked to evaluate the investment in terms of speed (from slow to fast) and magnitude (from low to high).
-These evaluations were made by clicking on a two-dimensional field with labelled axes as shown in Figure \ref{fig:HMMPanels}.c for the intervention condition.
+Our use of HMMs to model investor behavior represents a significant advancement in experimental design for economic games.
+Unlike traditional fixed-strategy computer opponents, our HMM-based agents adapt their behavior based on the participant's actions, mirroring the complex decision-making processes observed in human players.
+This approach allows us to maintain experimental control while significantly enhancing the ecological validity of our study.
 
@@
 
-At the start of the experiment, participants provided informed consent and were instructed the study would consist of three phases in which they would face a different other player.
-Participants were told their goal was to maximise the number of points in all phases.
+At the start of the experiment, participants provided informed consent and were instructed the study would consist of three phases.
+Participants across conditions were told their goal was to maximise the number of points in all phases.
+Participants had to pass comprehension checks about the number of phases, the fact the co-player was the same within each phase, and that they would face a new player at the start of each new phase.
 They were not told the number of rounds of each phase.
-Phase one was a 15 round Repeated Trust Game (RTG) in which participants took the role of trustee, facing the same investor over all 15 rounds.
+
+Phase one was a 15 round RTG in which participants took the role of trustee, facing the same investor over all 15 rounds.
+Participants were given details instructions about the game and had to pass comprehension checks to test their understanding of their and their co-player's payoff in a hypothetical situation.
 On each round, after being informed about the amount sent by the investor, participants were asked to evaluate their emotion (intervention condition) or the investment (control condition).
@@
 Subsequent phase two was similar to phase one, with participants being told they would face a new player.
+
 Phase three consisted of 7 rounds of the Repeated Prisoner's Dilemma game (RPD), with participants informed they would face a third player.
@@
 They were then asked about the strategy in the games, as well as whether they thought the other players were human or computer agents.
-They were then debriefed and thanked for their participation.
+Finally, participants were debriefed and thanked for their participation.
 
@@
 
-The model was estimated using the `afex` package [@singmann_afex_2022] in R [@R_package].
-More complex models with additional random effects could not be estimated reliably, and as such the estimated model can be considered to include the optimal random effects structure [@matuschek2017balancing].
+Our choice of linear mixed-effects models (LMMs) over mixed ANOVA was based on their greater flexibility in handling our complex data structure, including continuous predictors and nested repeated measures.
+LMMs offer increased statistical power and more flexible assumptions, particularly regarding sphericity, which is often violated in repeated measures designs.
+The model was estimated using the `afex` package [@singmann_afex_2022] in R.
+More complex models with additional random effects could not be estimated reliably, and as such the estimated model can be considered to include the optimal random effects structure [@matuschek_balancing_2017].
 A similar process was used to establish the random effects structures of other linear mixed-effects models used throughout the statistical analyses.
-There is no agreed upon way to calculate effect sizes for mixed effects models, as such we will report instead on testing differences in marginal means.
+As there is no agreed upon way to calculate effect sizes for mixed effects models, we will report instead on testing differences in marginal means.
 For the $F$-tests, we used the Kenward-Roger approximation to the degrees of freedom, as implemented in the R package "afex".
-Unless otherwise stated, the default adjustment method for multiple comparison is Tukey's HSD.
+For all post-hoc pairwise comparisons following significant effects in the mixed-effects models, we used Tukey's Honestly Significant Difference (HSD) test to adjust for multiple comparisons, unless otherwise stated.
 We Z-transform the Investment variable as centering is beneficial to interpreting the main effects more easily in the presence of interactions.
 
-To model participants' returns in the RTG across games and conditions, we fit various hidden Markov models [@visser2022hidden] to participants' returns using the depmixS4 package [@visser_depmixs4_2021] for R.
+To model participants' returns in the RTG across games and conditions, we fit various hidden Markov models [@visser_hidden_2022] to participants' returns using the depmixS4 package [@visser_depmixs4_2021] for R.
 The transition between latent states is assumed to depend on the investment received and a dummy variable to characterise the group that the participant belongs to.
 Details on how the models are constructed can be found in the supplement.
-We fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978-1] to select the best model.
+We fit models with different numbers of hidden states, and use the Bayesian Information Criterion [@schwarz_estimating_1978-1] to select the best fitting model.
 
 \begin{landscape}
-```{r HMMPanels, fig.cap= "\\small{a: Screenshot of the repeated Trust Game.
-The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee.
-The investor is endowed with 20 units at the start of each round.
-They need to decide how much of that endowment they want to invest with the trustee.
-The investment is then multiplied by a factor of 3 and sent to the trustee who needs to decide how much of the multiplied investment they want to send back to the investor.
-Shown here is the stage at which the trustee decides how much to send back to the investor.
-Immediately before making this decision, participant are shown a two dimensional grid (Panel c) where they need to report their reaction to the investment.
+```{r HMMPanels, fig.cap= "\\small{Panel A: Experimental design overview.
+Participants in both conditions played two 15-round Repeated Trust Games (RTGs) with human-like Hidden Markov Model (HMM) investors, separated by a manipulation phase.
+The intervention condition received a cognitive intervention, while the control condition solved anagrams.
+Both groups then completed a 7-round Repeated Prisoner's Dilemma (RPD) with a tit-for-tat (TFT) co-player to assess transfer effects.
+This design allows for comparison of cooperative behavior before and after the intervention, as well as between conditions.
+Immediately before making return decisions in the RTG, participants are shown a two dimensional grid (Panel C) where they need to report their reaction to the investment.
 Those in the intervention condition were asked questions about their emotional state and those in the control condition were asked to report features of the investment unrelated to their emotion.
-Panels b - d: We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
-From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel b.
-The fitted HMM also yields the transition probability of the agent to a state on trial t+1 as a function of the net return (difference between the investment sent and the amount received in return) on trial t as shown in Panel d.
-Each plot in Panel d represents a different starting latent state on trial t, and each line represents the probability of transitioning to a particular state in trial t+1.}",echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+Panels B - D: We construct the artificial investor agent by fitting a three-state hidden Markov model to data of human investors engaged in the 10 round Repeated Trust Game against human trustees.
+From the fitted HMM, we get the distribution of investments by the artificial investor agent conditional on its latent state as shown in Panel B.
+The fitted HMM also yields the transition probability of the agent to a state on trial t+1 as a function of the net return (difference between the investment sent and the amount received in return) on trial t as shown in Panel D.
+Each plot in Panel D represents a different starting latent state on trial t, and each line represents the probability of transitioning to a particular state in trial t+1.}",echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
 
@@
 # Read in the images
-image1 <- image_read("figures/trust_game.png")
+image1 <- image_read("figures/timeline.png")
 image2 <- image_read("figures/HMMinvPolicy2.png")
@@
 # Annotate each image with a label
-image1 <- image_annotate(image1, text = "a", location = "+200+10", size = 90, color = "black", gravity = "northwest")
-image2 <- image_annotate(image2, text = "b", location = "+0+10", size = 90, color = "black", gravity = "northwest")
-image3 <- image_annotate(image3, text = "c", location = "-0+10", size = 90, color = "black", gravity = "northwest")
-image4 <- image_annotate(image4, text = "d", location = "+0+10", size = 90, color = "black", gravity = "northwest")
+image1 <- image_annotate(image1, text = "A", location = "+0+10", size = 90, color = "black", gravity = "northwest")
+image2 <- image_annotate(image2, text = "B", location = "+0+10", size = 90, color = "black", gravity = "northwest")
+image3 <- image_annotate(image3, text = "C", location = "-0+10", size = 90, color = "black", gravity = "northwest")
+image4 <- image_annotate(image4, text = "D", location = "+0+10", size = 90, color = "black", gravity = "northwest")
 
@@
 
-# %>%
-#   filter(complete.cases(.))   # <- one player had NA in one round as a return, so we exclude him from analysis.
+# average investment for first 10 rounds pre intervention
+avg_pct <- avg_ret_df %>% filter(roundNum < 11 , gameNum.f == "pre") %>% summarise(avg_inv = mean(inv_pct), avg_ret = mean(ret_pct, na.rm=TRUE))
+
+# Find rows with NAs, excluding the 'ret_pct' column
+df_temp <- avg_ret_df%>%dplyr::select(playerId,condition.f,investment,returns,roundNum)
+
+# Identify the playerId(s) with NA values
+na_player <- df_temp[!complete.cases(df_temp), "playerId"]
+
+# Remove rows corresponding to the playerId with NA values
+avg_ret_df <- avg_ret_df[!avg_ret_df$playerId %in% na_player, ]
+
+# Display the cleaned dataframe
+avg_ret_df
 
@@
 
-# average investment for first 10 rounds pre intervention
-avg_pct <- avg_ret_df %>% filter(roundNum < 11 , gameNum.f == "pre") %>% summarise(avg_inv = mean(inv_pct), avg_ret = mean(ret_pct, na.rm=TRUE))
 ```
@@
 
-Average investments and returns prior to the "defection round" (Figure \ref{fig:TrustGameResults}.a) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
+Average investments and returns prior to the "defection round" (Figure \ref{fig:TrustGameResults}.A) were within the range of reported investments (40-60% of endowment) and returns (35-50% of total yield) in the literature [@charness_investment_2008; @fiedler_social_2011].
 Mixed-effects analysis on the percentage returns shows a significant main effect of Condition (intervention vs. control), `r papaja::apa_print(mod_returns_pct)$full_result$condition_f`, 
@@
 <!-- with an effect size of $\eta_p^2$ = `r round(effectsize::eta_squared(mod_returns_pct)$Eta2_partial[4],2)` -->
-Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:TrustGameResults}.c).
+Post-hoc tests show an increase in the percentage returned in the intervention condition, pre - post, `r papaja::apa_print(prepost_bycond)$full_result$Intervention_Pre_post`, but a decrease in the control condition, `r papaja::apa_print(prepost_bycond)$full_result$Control_Pre_post` (see Figure \ref{fig:TrustGameResults}.C).
 This indicates the intervention was effective in increasing cooperative behavior.
@@
 This shows a main effect of Condition, `r papaja::apa_print(mod_invs)$full_result$condition_f`<!--$F(1,317) = 8.7$, $p = .003$-->, and Game, `r papaja::apa_print(mod_invs)$full_result$gameNum_f`<!--$F(1,317) = 8.3$, $p = .004$-->.
-As can be seen in Figure \ref{fig:TrustGameResults}.d, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
+As can be seen in Figure \ref{fig:TrustGameResults}.D, investment was higher in the intervention compared to the control condition across games, and higher in the second game compared to first across conditions.
 
@@
 Instead, it countered the tendency shown by participants in the control condition to lower returns after the defection in the second game compared to the first game.
+
+We also examined whether participants' questionnaire scores were associated with their behavior or interacted with the experimental conditions.
+Linear mixed-effects models including these scores as covariates revealed no significant associations or interactions with other variables such as condition and game, suggesting that the observed effects were not moderated by the individual differences measured in our questionnaires.
 
@@
 `r gsub("(\\d{1,3}),(\\d{3})", "\\1\\2", papaja::apa_print(mod_emo_y)$full_result$gameNum_f_scaleinvestment)`. 
-This indicates that participants in the intervention condition returned higher amounts post-intervention, despite their emotional reaction to investments remaining largely the same (Figure \ref{fig:TrustGameResults}.b).
+This indicates that participants in the intervention condition returned higher amounts post-intervention, despite their emotional reaction to investments remaining largely the same (Figure \ref{fig:TrustGameResults}.B).
 
@@
 \begin{landscape}
-```{r TrustGameResults, fig.cap="\\small{Panel a: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
-We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition in the right panel.
-b:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
+```{r TrustGameResults, fig.cap="\\small{Panel A: Averages and standard errors of the trustee's return as a percentage of the multiplied investment received by Condition, Phase, and game round.
+We note a different reaction to the pre-programmed one-off low investment (vertical black lines) between the two conditions: Whilst there is a dip in returns pre-manipulation for both conditions,  post manipulation we see higher returns in the intervention condition compared to the dip in returns seen in the control condition.
+Panel B:  Self-reported emotion valence and arousal as well as investment z-scores for each round of the Repeated Trust Game averaged across participants in the intervention condition only.
 The participants' emotion reaction measured during the investor's pre-programmed one-off low investment round (vertical grey lines) were similar before (round 12) and after (round 13) the intervention.
 The bottom panels show marginal means and distributions of either investments or percentage returns across participants by Game and Condition.
-Panel c shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
-Investments by the HMM agent (Panel d) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
+Panel C shows that participants in the Intervention condition returned higher proportions of the multiplied investment received in the second game compared to the first game over all ronds, whilst those in the Control condition sent back lower returns.
+Investments by the HMM agent (Panel D) were higher in the second game compared to the first game across conditions.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='1\\linewidth', out.height='1\\textheight', fig.align='center'}
 library(magick)
@@
 
-image5 <- image_annotate(image5, text = "a", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-image6 <- image_annotate(image6, text = "b", location = "+20+0", size = 90, color = "black", gravity = "northwest")
-violin_ret<- image_annotate(violin_ret, text = "c", location = "+0+20", size = 70, color = "black", gravity = "northwest")
-violin_inv  <- image_annotate(violin_inv , text = "d", location = "+0+0", size = 70, color = "black", gravity = "northwest")
+image5 <- image_annotate(image5, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image6 <- image_annotate(image6, text = "B", location = "+20+0", size = 90, color = "black", gravity = "northwest")
+violin_ret<- image_annotate(violin_ret, text = "C", location = "+0+20", size = 70, color = "black", gravity = "northwest")
+violin_inv  <- image_annotate(violin_inv , text = "D", location = "+0+0", size = 70, color = "black", gravity = "northwest")
 
@@
 ```{r, include=FALSE}
+
+# Filter the dataframe for PBOR scores higher than 40 and group by condition
+result <- avg_ret_df %>%
+  filter(PBOR_score >= 40) %>%
+  group_by(condition.f) %>%
+  summarise(count = n())
+
+# Print the result
+print(result)
+
+```
+
+```{r, include=FALSE}
 ########### HOW DO PBOR SCORES affect returns and intervention effect ?########
@@
 # these are repeated measures here, so not independent. need to used mixed effects model.
-mixed_PBOR_pct <- afex::mixed(ret_pct ~ PBOR_scaled*gameNum.f*condition.f + investment + (1 | playerId ), data= avg_ret_df)
+#afex::mixed( ret_pct ~ gameNum.f*condition.f*inv_scaled+ (1 + gameNum.f| playerId), avg_ret_df, REML= TRUE, method="KR")
+mixed_PBOR_pct <- afex::mixed(ret_pct ~ PBOR_scaled*gameNum.f*condition.f*inv_scaled + (1 | playerId ), data= avg_ret_df,REML= TRUE, method="KR")
 summary(mixed_PBOR_pct)
@@
 emmeans(mixed_PBOR_pct, pairwise ~ PBOR_scaled * condition.f )
+
+mixed_PBOR_inv <- afex::mixed(investment ~ PBOR_scaled*gameNum.f*condition.f + (1 | playerId ), data= avg_ret_df,REML= TRUE, method="KR")
+summary(mixed_PBOR_inv)
 
@@
 As such, there is evidence that participants reacted differently to the investments in the four combinations of Condition and Game.
-The estimated state-dependent policy of trustee actions, according to the HMM-full model, is depicted in Figure \ref{fig:trusteeHMM}.a.
-
-```{r trusteeHMM, fig.cap="\\small{Panel a: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
+The estimated state-dependent policy of trustee actions, according to the HMM-full model, is depicted in Figure \ref{fig:trusteeHMM}.A.
+
+```{r trusteeHMM, fig.cap="\\small{Panel A: the distribution of participants' percentage return for each of the latent states in the 6 state HMM-full model shows distinct policies centered around different return levels.
 The latent states are ordered by the mean of the discretized Gaussian representing the policy in that state, so higher numbered states can be considered more pro-social.
-b: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
+Panel B: This figure characterises behavioral differences between conditions as the result of participants being in more pro-social (higher return) states in the intervention condition compared to the control condition both pre- and post-defection.
 The distribution of posterior trustee states post-manipulation by condition for all rounds, as estimated by the most likely posterior state in the best fitting HMM model (HMM-full) using a local decoding procedure is visibly more weighted towards higher return states.
-As in Panel a, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
+As in Panel A, states here are represented in increasing degrees of average percentage returns from the lowest (state 1) to the highest (state 6) return state.}", echo=FALSE, message=FALSE, warning=FALSE, out.width='0.95\\linewidth', out.height='0.80\\textheight', fig.align='center'}
 library(magick)
@@
 
-image7 <- image_annotate(image7, text = "a", location = "+20+20", size = 70, color = "black", gravity = "northwest")
-image8 <- image_annotate(image8, text = "b", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image7 <- image_annotate(image7, text = "A", location = "+20+20", size = 70, color = "black", gravity = "northwest")
+image8 <- image_annotate(image8, text = "B", location = "+20+20", size = 70, color = "black", gravity = "northwest")
 
@@
 The states are ordered by expected return, with state 1 having the lowest mean return and state 6 the highest.
-Figure \ref{fig:trusteeHMM}.b shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition, both pre and post defection.
+Figure \ref{fig:trusteeHMM}.B shows that participants were more likely to be in a lower return state in the control condition compared to the intervention condition, both pre and post defection.
 For instance, in round 5, state 1 was the most likely posterior state for only $5$% of participants in the intervention condition compared to $12$% in the control condition ($\chi^2(1) = 4.73, p = 0.03$).
@@
 
-Following a cognitive intervention, participants increased their returns without a corresponding change in emotional response, indicating the intervention's effectiveness in preserving trust despite a breach of cooperation.
+<!-- Following a cognitive intervention, participants increased their returns without a corresponding change in emotional response, indicating the intervention's effectiveness in preserving trust despite a breach of cooperation.
 Those in the control condition returned similar proportions pre-defection and reduced their returns post-defection.
@@
 Participants were often uncertain whether they interacted with human or artificial investors, highlighting the agents’ realism.
-
-That participants in the intervention condition generally send higher returns to the investor after the intervention is unlikely due to a  general learning effect unrelated to the intervention, as participants in the control condition did not increase their returns.
+-->
+Following a cognitive intervention, participants increased their returns without a corresponding change in emotional response, indicating the intervention's effectiveness in preserving cooperation and reducing retaliation to a breach of cooperation.
+Those in the control condition returned similar proportions pre-defection and reduced their returns post-defection.
+An HMM analysis showed that those in the intervention condition were less prone to low-return states after defection.
+These findings suggest that cognitive interventions can promote resilience in cooperative behaviors following trust violations.
+
+<!-- That participants in the intervention condition generally send higher returns to the investor after the intervention is unlikely due to a  general learning effect unrelated to the intervention, as participants in the control condition did not increase their returns.
 Also, as participants in the intervention and control condition faced the same HMM investor, the higher post-intervention returns are not solely due to a difference in investor behavior.
@@
 Rather, we find it most likely that the increased returns are due to participants inferring from the intervention that pro-social and trustworthy behavior may generally motivate the investor to send high investments, which can provide more beneficial outcomes to them in the long run.
-
-The effect of the intervention was not transferred to the Repeated Prisoner's Dilemma (RPD) game.
+-->
+The increased returns in the intervention condition are unlikely due to a general learning effect, as participants in the control condition did not increase their returns.
+Additionally, since both conditions faced the same HMM investor, the higher post-intervention returns are not solely due to differences in investor behavior.
+While the investor reacts to participants' returns, with higher returns generally leading to higher investments, this is driven by the magnitude of participants' returns, not by a change in the investor's strategy.
+Furthermore, the absence of differences between conditions in participants' ratings of the first and second HMM agent suggests that the increased returns are not due to a more favorable evaluation of the investor.
+
+The increased cooperation observed post-intervention could potentially be attributed to demand expectancy effects [@orne_social_1962; @nichols_good-subject_2008], given that the educational slide explicitly suggests a preferred reaction to co-player defection.
+However, several factors challenge this interpretation.
+First, participants in the intervention group exhibited higher returns on average even before encountering the pre-programmed defection that the intervention specifically addressed.
+This behavior diverges from what would be expected if participants were merely responding to perceived experimental demands.
+It is still possible that participants inferred from the intervention a "demand" to behave in cooperative ways in general.
+However, the effect of the intervention did not transfer to the Repeated Prisoner's Dilemma (RPD) game, with no difference between conditions in cooperation rates.
+This specificity argues against the intervention merely prompting participants to align with perceived experimenter expectations.
+If participants were simply trying to please the experimenter by acting cooperatively post-intervention, we would expect to see elevated cooperation rates in the RPD game for the intervention group.
+The absence of such an effect suggests that the intervention's impact was specific to the Trust Game context.
+Rather, we posit that the increased returns stem from participants inferring that pro-social and trustworthy behavior may motivate the investor to send high investments, potentially leading to more beneficial long-term outcomes.
+
+While we cannot entirely rule out the influence of demand characteristics on the observed behavior, it's important to consider whether this effect, if present, diminishes the intervention's value, particularly in clinical contexts.
+For individuals with high interpersonal dysfunction, such as those with Borderline Personality Disorder, the ability to recognize and respond to social cues - even if initially driven by perceived expectations - can be a crucial step towards more adaptive behavior [@linehan_cognitive-behavioral_1993].
+Research has shown that explicitly teaching social skills and appropriate responses can lead to improved outcomes in various clinical populations [@bornovalova_how_2007].
+Moreover, the concept of "therapeutic demand characteristics" has been proposed, suggesting that aligning with perceived therapeutic expectations can be an active ingredient in treatment effectiveness [@trachsel_how_2019].
+In the context of our study, even if participants' initial cooperation was partly motivated by perceived experimenter expectations, this could potentially translate into more adaptive real-world behaviors over time.
+This perspective aligns with the principles of cognitive-behavioral therapies, which often explicitly teach and reinforce desired behaviors [@beck_cognitive_2011].
+Therefore, rather than viewing potential demand characteristics as a limitation, we might consider them as a possible mechanism for initiating behavioral change, particularly in populations that may not inherently be motivated to please therapists or adhere strictly to treatment protocols.
+
+Interestingly, we observed a decrease in both emotional positivity and arousal in the second RTG compared to the first, across both conditions.
+This general decline in emotional intensity is likely attributable to factors such as decreased engagement or increased fatigue as the experiment progressed, rather than being a specific effect of the intervention.
+Importantly, despite this reduction in emotional intensity, participants in the intervention condition maintained higher levels of cooperative behavior, suggesting that the intervention may have promoted more deliberate, strategic decision-making rather than emotionally-driven responses.
+
+<!-- The effect of the intervention was not transferred to the Repeated Prisoner's Dilemma (RPD) game.
 There was no difference between the intervention and control condition in the rate of cooperation, whether before or after a preprogrammed defection by the artificial agent.
@@
 Future research will need to assess whether transfer to other games is possible.
+-->
+<!-- The lack of transfer of the intervention effect to the Repeated Prisoner's Dilemma (RPD) game may initially suggest limited, game-specific effects of our cognitive intervention.
+However, this very specificity argues against the intervention merely prompting participants to align with perceived experimenter expectations.
+If participants were simply trying to please the experimenter by acting cooperatively post-intervention, we would expect to see elevated cooperation rates in the RPD game for the intervention group.
+Instead, cooperation rates in the RPD were similar across conditions.
+This suggests that the intervention's effects were specific to the context in which it was delivered (the Trust Game), rather than a general increase in cooperative behavior due to demand characteristics.
+Future research could explore whether more generalized interventions might produce effects that transfer across different economic games or social scenarios.
+-->
+<!-- The effect of the intervention did not transfer to the Repeated Prisoner's Dilemma (RPD) game, with no difference between conditions in cooperation rates.
+This lack of transfer may initially suggest limited, game-specific effects of our cognitive intervention.
+However, this specificity argues against the intervention merely prompting participants to align with perceived experimenter expectations.
+If participants were simply trying to please the experimenter by acting cooperatively post-intervention, we would expect to see elevated cooperation rates in the RPD game for the intervention group.
+The absence of such an effect suggests that the intervention's impact was specific to the Trust Game context.
+-->
+
+<!-- The RPD's coarser actions (cooperate vs.
+defect) compared to the RTG's finer-grained returns may have made it more difficult to observe subtle effects of the intervention.
+Additionally, participants' potential prior strategies for the well-known Prisoner's Dilemma may have been resistant to change.
+Future research should explore whether more generalized interventions could produce effects that transfer across different economic games or social scenarios.
+-->
 
@@
 This was also evident from participants' replies to a question about whether they would change their behavior, just after receiving the intervention.
-Other participants responded to the intervention and increased their returns.
 Heterogeneity in response to treatment is common in psychiatry and related fields.
@@
 
-Overall, we are encouraged that our brief cognitive intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments, can lead to clearly differentiated behavior.
+<!-- A limitation of this study is that the multi-component nature of our intervention makes it challenging to disentangle the specific effects of each element.
+The intervention was designed as a cohesive unit, reflecting real-world therapeutic approaches that often combine multiple strategies.
+Future research could employ more complex experimental designs, such as factorial designs, to investigate the relative contributions of each component.
+However, our primary aim was to assess the overall effectiveness of a brief, DBT-inspired cognitive intervention in promoting cooperative behavior, which this design accomplishes.
+The significant behavioral changes observed suggest that even a brief, multi-component intervention can be effective in this context.
+-->
+Several limitations of this study warrant consideration.
+First, the multi-component nature of our intervention makes it challenging to disentangle the specific effects of each element.
+While this design reflects real-world therapeutic approaches, future research could employ factorial designs to investigate the relative contributions of individual components.
+Second, our focus on the trustee role in the RTG and the use of HMMs as co-players, while allowing us to examine responses to potential trust violations, limits our ability to directly assess changes in trust as traditionally conceptualized in the first-mover role.
+Finally, the brief nature of our intervention and the use of a general population sample may limit generalizability to clinical settings or longer-term behavioral changes.
+
+<!-- Overall, we are encouraged that our brief cognitive intervention, consisting of reading a short text detailing a non-impulsive reaction to low investments, can lead to clearly differentiated behavior.
 In future studies, we aim to explore the effects of improved cognitive interventions to enhance cooperative behavior.
@@
 The relative ease by which online interventions can be assigned, and the opportunity for people to test the effect of their behavior with artificial but human-like agents, may pave the way for efficient, low-cost, effective treatment programmes which may help a wide-variety of people overcome detrimental actions in social situations.
+-->
+Despite these limitations, we are encouraged that our brief cognitive intervention led to differentiated behavior.
+Future studies could explore improved cognitive interventions to enhance cooperative behavior, possibly making them more interactive and visually appealing.
+Testing such interventions with participants who struggle to repair relationships after trust breakdowns, such as those with Borderline Personality Disorder, could be particularly valuable.
+The ease of assigning online interventions and the use of artificial but human-like agents open up possibilities for efficient, low-cost treatment programs to help a wide variety of people overcome detrimental actions in social situations.
 
